\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,array}
\usepackage[hidelinks]{hyperref}

\newcommand{\IUT}{IUT}
\newcommand{\Lean}{Lean}
\newcommand{\R}{\mathbb{R}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\ThetaPilot}{\Theta\text{-pilot}}
\newcommand{\qPilot}{q\text{-pilot}}

\title{A First Lean Formalization Audit of the IUT III Corollary 3.12 Corridor}
\author{IUT Lean formalization project}
\date{May 28, 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
This note records the present state of a Lean formalization of a narrow part of
Mochizuki's inter-universal Teichmuller theory: the passage from IUT III,
Theorem 3.11 to Corollary 3.12, with attention to the Scholze--Stix objection.
The current Lean code proves conditional route theorems and obstruction lemmas.
It does not prove Corollary 3.12 and does not refute it.  The main formal result
so far is that a nonarchimedean \((\mathrm{Ind3})\) entry, together with explicit
Hodge/SHE square-weight transport data, feeds a hull/log-volume
\(q\)-to-\(\Theta\) comparison, while several simplified collapse mechanisms are
rejected by Lean.
\end{abstract}

\section{Scope}

The review used the local Markdown conversions of IUT I--IV, Mochizuki's 2026
formalization note, and the Scholze--Stix note.  The relevant source passages are:
\begin{itemize}
\item IUT I: initial \(\Theta\)-data, prime strips, Hodge theaters, and
  non-scheme-theoretic \(\Theta\)-links.
\item IUT II: Hodge--Arakelov evaluation, theta values of shape \(q^{j^2}\),
  multiradiality, and Gaussian monoids.
\item IUT III: Theorem 3.11; Corollary 3.12, especially Steps (x) and (xi);
  Remarks 3.12.2 and 3.12.3.
\item IUT IV: later explicit log-volume estimates and Diophantine consequences.
\item Scholze--Stix: the ordered real-line identification problem in their
  Section 2.2.
\item Mochizuki 2026: the ``3.11.5 \(\Rightarrow\) 3.12'' fourth-triangle
  decomposition.
\end{itemize}

\section{Mathematical Target}

IUT III Step (x) treats procession-normalized log-volumes as invariants for
\((\mathrm{Ind1})\) and \((\mathrm{Ind2})\), and turns \((\mathrm{Ind3})\) into
an upper inequality.  Step (xi) then uses the multiradial construction, IPL, SHE,
holomorphic hulls, determinants, and log-volume to place the \(q\)-pilot
log-volume in an upper ray controlled by the \(\Theta\)-pilot log-volume:
\[
  -|\log(q)| \in \R_{\le -|\log(\Theta)|}
  \quad\Rightarrow\quad
  -|\log(q)| \le -|\log(\Theta)|.
\]
Mochizuki's 2026 note isolates the final comparison as:
\[
\begin{array}{ccccc}
\text{Theorem 3.11}
& \xrightarrow{\mathrm{APT}+\mathrm{IPL}}
& \text{``3.11.5''}
& \xrightarrow{\mathrm{SHE}+\mathrm{IPL}}
& \text{Corollary 3.12}.
\end{array}
\]
The present formalization targets only this corridor, not the full construction
of Theorem 3.11.

\section{Dispute Interface}

Scholze--Stix require explicit bookkeeping for all ordered one-dimensional real
vector spaces.  Their pressure point is that the \(\Theta\)-side concrete
objects carry \(j^2\)-scaled degrees, while a consistent identification of the
real lines appears to leave no room for inserting all these scalars.

The formalization therefore separates:
\[
\begin{array}{c}
\text{representative } j^2 \text{ data}\\
\text{balanced sign-compatible data}\\
\text{aggregate averaged data}\\
\text{final hull/log-volume data}
\end{array}
\qquad
\text{and}
\qquad
\begin{array}{c}
\text{raw real equality}\\
\text{transported equality}\\
\text{matched transport scales}\\
\text{cancellable ordered-line comparison.}
\end{array}
\]
This separation is the main correctness guard in the current code.

\section{Lean Coverage}

The relevant implementation is in
\[
\texttt{Iut/Stage1/IUTStage1Source.lean}
\quad\text{and}\quad
\texttt{Iut/Stage1/IUTStage1Experiments.lean}.
\]
The code currently covers:
\begin{itemize}
\item labeled real-line copies and positive-scale transports;
\item a finite \(\F_\ell\)-label model with representative square weights
  \(j \mapsto j^2\);
\item a representative pilot-degree profile
  \(\deg(\Theta_j)=j^2\deg(q)\);
\item proof that one label-independent scale cannot absorb all representative
  \(j^2\) scales in this model;
\item proof that, for nonzero \(\deg(q)\), one label-independent scale cannot
  account for all representative \(\Theta_j\)-degrees;
\item proof that the raw representative \(j^2\) theta-degree rule does not
  descend to the sign quotient \(|F_\ell|=F_\ell/\{\pm1\}\) when \(\deg(q)\ne0\);
\item an absolute-label exponent on \(|F_\ell|=\{0\}\cup F_\ell^\times/\{\pm1\}\)
  which agrees with \(j^2\) for the canonical representatives
  \(0\le j\le(\ell-1)/2\), and the corresponding theta-degree profile;
\item the degree-level Gaussian evaluation
  \(q\mapsto(q^{j^2})_{j\in |F_\ell|}\), including identity at \(j=1\);
\item a log-volume shadow of the IUT III splitting-monoid action: the generator
  attached to a procession label contributes \(j^2\deg(q)\), contributes \(0\) at
  the core label, and adds its finite generator sum to the tensor-packet
  log-volume;
\item the finite procession containers
  \(S^\pm_{j+1}=\{0,\ldots,j\}\), their nested inclusions, core-label stability,
  stage cardinality \(j+1\), and total procession ambiguity \((\ell^\pm)!\)
  rather than \((\ell^\pm)^{\ell^\pm}\);
\item the map from the final procession container to \(|F_\ell|\), sending the
  core label to \(0\) and recovering the exponent \(j^2\);
\item the log-volume shadow of the tensor packet over \(S^\pm_{j+1}\), with
  each factor a finite-fiber direct sum over places above \(v_\mathbb{Q}\), total
  log-volume given by the finite sum over the container, normalized denominator
  \(j+1\), and invariance under container permutations;
\item base-valuation products of tensor packets, the finite
  \((F_{\mathrm{mod}}^\times)_j\)-action shadow, and a coric transfer shadow
  \(F\to D\to D^\vdash\) preserving product log-volume without identifying
  Hodge-theater histories;
\item the Step (xi-d)--(xi-g) shadow: determinant normalization, upper-ray
  membership, and equality of the two \(q\)-pilot log-volume computations;
\item the Step (xi-h) warning: for \(N\ge2\) and \(\Theta<0\), the tensor-power
  boundary satisfies \(N\Theta<\Theta\);
\item the Step (xii) shadow: local Frobenioid \(p_v^N\)-ambiguity changes
  log-volume by an integer shift, while global calibration fixes exponent \(0\);
\item the Remark 3.12.1(iii) arithmetic fact
  \(\mathbb{Q}_{>0}\cap\mathbb{Z}^{\times}=\{1\}\);
\item the Remark 3.12.1(ii) generalized-link numerical bound
  \(C_\Theta\ge-\lambda\) for \(\lambda\in\mathbb{Q}_{>0}\), with strict
  strengthening over the \(\lambda=1\) bound when \(\lambda<1\);
\item the Remark 3.12.2 distinct-label implication
  \(q\text{-itw}\Rightarrow q\text{-itw}\wedge\Theta\text{-itw}/\mathrm{indets}\),
  with q-native and \(\Theta\)-native labels proved distinct;
\item the Remark 3.12.2 toy calculation: forgotten concrete assignments
  \(-h\) and \(-2h\) are incompatible for \(h>0\), while
  \(-h\in\R_{\le-2h+\epsilon}\) implies \(h\le\epsilon\);
\item the Fig. 3.9 column table: both \(\bullet_0\) and \(\circ\) roles are
  required in both columns, while q-pilot multiradiality is absent;
\item the Remark 3.12.2(v) absorption distinction: zero-column unit
  indeterminacy is absorbed by a hull upper ray, while one-column logarithmic
  conjugacy is absorbed as log-volume equality;
\item the Remark 3.12.3(i) metric analogy:
  \(\operatorname{vol}(S)>0\) and \(\chi_S=-\operatorname{vol}(S)\) imply
  \(\chi_S<0\);
\item the Remark 3.12.4(iii) factor-\(p\) analogy: theta-label normalization
  divides a gap log-volume by \(\ell\), and multiplication by \(\ell\) recovers it;
\item the Remark 3.12.4(v) p-adic analogue:
  an inclusion, not isomorphism, gives \((1-p)(2g-2)\le0\);
\item the IUT IV, Theorem 1.10 algebraic handoff: an explicit expression for
  \(C_\Theta\), together with \(C_\Theta\ge-1\) and the remaining elementary
  estimates, implies the displayed \(\frac16\log(q)\) bound;
\item the final elementary coefficient estimates in IUT IV, Theorem 1.10:
  \((1-12/\ell^2)^{-1}\le2\) and
  \((1-12/\ell^2)^{-1}\frac14(1+36d_{\mathrm{mod}}/\ell)
   \le 1+80d_{\mathrm{mod}}/\ell\);
\item the IUT IV, Theorem 1.10 base-change monotonicity:
  \(\log(d_{F_{\mathrm{tpd}}})+\log(f_{F_{\mathrm{tpd}}})
   \le \log(d_F)+\log(f_F)\) propagates through the final right-hand side;
\item comparison levels:
  pointwise representative, aggregate representative, balanced sign-compatible,
  and hull/log-volume;
\item endpoint audits for the \(3.11.5 \Rightarrow 3.12\) comparison chart;
\item nonarchimedean and archimedean \((\mathrm{Ind3})\) local orientations;
\item ordered real-line alignment with cancellation only after scale equality;
\item a canonical unit-scale ordered alignment from a nonarchimedean
  \((\mathrm{Ind3})\) entry;
\item a bridge from factored square/full-label SHE obligations to the
  Hodge-descent \((\mathrm{Ind3})\) route.
\end{itemize}

\section{Current Lean Results}

The current first-pass experiment report evaluates to:
\[
\begin{array}{ll}
\text{route theorem flags} & = \texttt{true},\\
\text{collapse-obstruction flags} & = \texttt{true},\\
\text{Gaussian/procession finite-model flags} & = \texttt{true},\\
\texttt{balancedLevelRejectedAtFinalRouteTheoremAvailable} & = \texttt{true},\\
\texttt{disputeSettledByCurrentStage} & = \texttt{false}.
\end{array}
\]
Here the route flags are ordered real-line, nonarchimedean entry, and factored
SHE availability.  The obstruction flags are raw-cancellation failure,
label-independent \(j^2\) failure, and sign-quotient representative descent
failure.  The Gaussian/procession flags include finite tensor-packet, monoid
action, base-valuation product, coric-transfer, determinant-normalization,
upper-ray, \(q\)-pilot two-computation, tensor-power warning, and global
Frobenioid-calibration shadows, plus positive-rational unit rigidity.
The generalized-link flag records the rational parameter inequality
\(C_\Theta\ge-\lambda\).
The distinct-label flag records the logical intertwining display in
Remark 3.12.2 and rejects collapse of the q-native and \(\Theta\)-native labels.
The toy-model flag records the resulting upper-ray arithmetic \(h\le\epsilon\).
The column-table flag records the Fig. 3.9 theta/q similarity-difference split.
The absorption flag records the zero-column upper-bound versus one-column
equality distinction.
The metric flag records the Gauss--Bonnet sign calculation used as analogy for
the upper semi-compatibility inequality.
The factor-\(p\) flag records the \(F_\ell\)-label averaging denominator.
The Frobenius-derivative flag records the degree inequality from inclusion.
The IUT IV flag records the downstream Theorem 1.10 use of the Corollary 3.12
lower bound on \(C_\Theta\), including the final coefficient estimates and the
tripodal-to-\(F\) log-degree monotonicity.
The theorem-level route is:
\[
\begin{array}{ccccc}
\text{nonarch. }(\mathrm{Ind3})\text{ entry}
& \to &
\text{canonical ordered } \R\text{-alignment}
& \to &
\text{source/target alignment}
\\[3pt]
& & \downarrow & & \downarrow
\\[-2pt]
\text{factored SHE transport}
& \to &
\text{Hodge-descent audit}
& \to &
q_{\mathrm{signed}}\le \Theta_{\mathrm{signed}}.
\end{array}
\]
The route remains conditional on the displayed hypotheses.

\section{Audit Findings}

No formal statement currently proves IUT III, Corollary 3.12 from Mochizuki's
published hypotheses.  The strongest positive result is conditional: if the
nonarchimedean \((\mathrm{Ind3})\) entry, ordered real-line alignment, and
Hodge/SHE square-weight transport audit are supplied, then Lean checks the final
signed \(q\)-to-\(\Theta\) inequality.

The strongest negative result is also limited: in the current \(\F_\ell\)-label
model, Lean rejects a single label-independent scale accounting for all
representative \(j^2\) factors, and it rejects balanced sign-compatible evidence
as the final hull/log-volume comparison level.  Lean also rejects direct descent
of arbitrary raw representative \(j^2\) theta-degree data to \(|F_\ell|\), while
accepting the half-range exponent convention stated in IUT II.
Lean also checks that an \(N\)-th tensor-power boundary is a strict strengthening
for \(N\ge2\) and negative pilot log-volume.  It also checks the Step (xii)
numerical warning: nonzero local Frobenioid shifts change log-volume, whereas
global calibration restores the unshifted value.  The positive rational unit
rigidity fact in Remark 3.12.1(iii) is formalized directly over \(\mathbb{Q}\).
For generalized links, Lean records that \(\lambda<1\) makes \(-\lambda>-1\).
Lean also checks that the Remark 3.12.2 simultaneous-intertwining step depends
on distinct labels rather than an unlabeled identification.
In the accompanying toy model, Lean proves the final upper bound exactly from
the upper-ray membership hypothesis.
Lean also records that the q-pilot column lacks the theta-side multiradiality
used in Theorem 3.11(iii)(c).
For Remark 3.12.2(v), Lean separates hull absorption of unit shifts from
log-volume equality after logarithmic-conjugate compatibility.
For Remark 3.12.3(i), Lean proves the stated negative Euler-characteristic sign
from positivity of metric volume.
For Remark 3.12.4(iii), Lean checks the \(\ell\)-denominator normalization
identity for the theta-label averaging analogy.
For Remark 3.12.4(v), Lean proves the displayed nonpositive degree defect from
\(p\ge2\) and \(g\ge2\).
For IUT IV, Theorem 1.10, Lean proves the algebraic implication from the
computed \(C_\Theta\) expression and \(C_\Theta\ge-1\) to the final
\(\frac16\log(q)\) estimate, conditional on the separate elementary estimates.
Lean now also proves the two displayed final elementary coefficient estimates
from \(\ell\ge5\).
It also proves the final monotonic replacement of the tripodal log-degree sum by
the larger \(F\)-level log-degree sum, conditional on the two component
monotonicity inequalities cited from Proposition 1.3(i).

\section{Missing Mathematics}

The present code does not yet formalize:
\begin{itemize}
\item initial \(\Theta\)-data as in IUT I;
\item actual Hodge theaters, Frobenioids, prime strips, log-shells, or
  \(\Theta\)-links;
\item the Hodge--Arakelov theta evaluation and Gaussian monoids of IUT II;
\item the construction of the actual theta values, Gaussian/splitting monoids,
  \(F_{\mathrm{mod}}^\times\)-actions, Kummer isomorphisms,
  mono-analyticization, and Frobenioids behind the present shadows;
\item the actual construction of log-shells and tensor packets attached to
  mono-analytic prime-strips in IUT III, Theorem 3.11;
\item the genuine holomorphic hull and determinant operations of Step (xi),
  beyond the present finite determinant/upper-ray/two-computation/tensor-power
  shadows;
\item the global realified Frobenioids of Step (xii), beyond the present integer
  log-volume shift model;
\item the arithmetic-divisor and local log-volume construction behind the IUT IV
  Theorem 1.10 numerical estimates, and the Diophantine applications;
\item a proof that the current Hodge/SHE transport obligations follow from
  Mochizuki's full hypotheses.
\end{itemize}

\section{Next Work}

The next significant formal step is not another wrapper.  It is to replace
current explicit Hodge/SHE transport assumptions by constructions closer to the
papers:
\[
\begin{array}{c}
\text{theta values }q^{j^2}\\
\leadsto\ \text{Gaussian and splitting monoids}\\
\leadsto\ \text{square/full-label preservation}\\
\leadsto\ \text{hull/log-volume route}.
\end{array}
\]
Only after this bridge is formalized can the first-pass experiment begin to test
the actual mathematical load-bearing part of Mochizuki's response to
Scholze--Stix.

\begingroup
\small
\begin{thebibliography}{9}
\bibitem{IUT1}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory I:
Construction of Hodge Theaters}.

\bibitem{IUT2}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory II:
Hodge-Arakelov-theoretic Evaluation}.

\bibitem{IUT3}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory III:
Canonical Splittings of the Log-theta-lattice}.

\bibitem{IUT4}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory IV:
Log-volume Computations and Set-theoretic Foundations}.

\bibitem{MochizukiLean}
S. Mochizuki, \emph{On the Formalization of IUT: Preliminary Progress Report},
2026.

\bibitem{ScholzeStix}
P. Scholze and J. Stix, \emph{Why abc is still a conjecture}.
\end{thebibliography}
\endgroup

\end{document}
