\chapter{The Source Stage 1 Route}
\label{ch:stage1-source}

\section{The source objects}

\begin{definition}[Initial theta and theater data]
  \label{def:initial-theta-data}
  \lean{Iut.InitialThetaData}
  \notready
  The source construction begins with the initial \(\Theta\)-data of \IUT{} I:
  a number field, an elliptic curve, bad places, label data, and the
  arithmetic hypotheses from which Hodge theaters are built.  The repository
  contains typed shadows of initial theta data, but the full arithmetic
  construction is not yet the active Stage 1 input.
\end{definition}

\begin{definition}[Hodge theater histories]
  \label{def:hodge-theater-histories}
  \notready
  A Hodge theater carries an arithmetic holomorphic structure.  The Stage 1
  argument must keep the domain history of the \ThetaPilot{} and the codomain
  history of the \qPilot{} distinct, even when their weakened data are compared
  in a common container.
\end{definition}

\begin{definition}[Prime strips and links]
  \label{def:prime-strip-links}
  \notready
  The \(\Theta^{\times\mu}_{\mathrm{LGP}}\)-link between the \(0\)- and
  \(1\)-columns has a value-group portion and a unit portion.  The value-group
  portion relates \ThetaPilot{} data at \((0,0)\) to \qPilot{} data at
  \((1,0)\).  The input prime-strip link property \(\IPL\) records that the
  output possibilities of the multiradial algorithm remain linked to the input
  prime-strip data at the comparison boundary.
\end{definition}

\section{Theorem 3.11 and Step (x)}

\begin{definition}[Indeterminacy generator interface]
  \label{def:indeterminacy-generator-interface}
  \lean{Iut.Stage1.IUTStage1Theorem311IndeterminacySourceData}
  \leanok
  The Stage 1 interface names the three source-facing indeterminacy
  generators separately: procession automorphism, local tensor symmetry, and
  upper-semi compatibility.  This is a Lean-checked naming interface, not yet
  a construction of the source Step (x) estimates.
\end{definition}

\begin{definition}[Step (x) averaged corridor record]
  \label{def:step-x-averaged-corridor-record}
  \lean{Iut.Stage1.IUTStage1ProcessionNormalizedIndeterminacyCorridor,Iut.Stage1.IUTStage1ProcessionNormalizedIndeterminacyCorridor.before_average_le_ind3UpperBound}
  \leanok
  The averaged corridor record is the conditional Lean shape of Step (x):
  \(\Ind{1}\) and \(\Ind{2}\) preserve the procession-normalized average, and
  \(\Ind{3}\) supplies the upper-semi bound.  Its Lean theorem proves the
  resulting averaged inequality from those record fields.
\end{definition}

\begin{proposition}[Step (x) corridor]
  \label{prop:step-x-corridor}
  \uses{def:indeterminacy-generator-interface,def:step-x-averaged-corridor-record}
  \notready
  The source Step (x) data should produce a corridor
  \[
    A_0 = A_1 = A_2 \le U_{\Ind{3}},
  \]
  where \(A_0,A_1,A_2\) are the averaged log-volumes before
  indeterminacy, after \(\Ind{1}\), and after \(\Ind{2}\), and
  \(U_{\Ind{3}}\) is the upper-semi target coming from \(\Ind{3}\).
\end{proposition}

\begin{proof}
  In the current code this is an interface-level object.  The proof from the
  source papers must still account for the log-volume invariance under
  \(\Ind{1}\) and \(\Ind{2}\), the upper-semi orientation of \(\Ind{3}\), and
  the normalization conventions for averaging over labels.
\end{proof}

\begin{theorem}[Theorem 3.11 source output]
  \label{thm:theorem-311-source-output}
  \uses{def:initial-theta-data,def:hodge-theater-histories,def:prime-strip-links,prop:step-x-corridor}
  \notready
  From the initial \(\Theta\)-data and the machinery of \IUT{} I--III,
  Theorem 3.11 should construct multiradial output possibilities, equipped
  with the \(\Ind{1}\), \(\Ind{2}\), and \(\Ind{3}\) behavior needed for
  the Stage 1 comparison.
\end{theorem}

\section{Step (xi)}

\begin{definition}[Simultaneous holomorphic expressibility]
  \label{def:she}
  \notready
  The \(\SHE\) property says that the relevant output possibilities may be
  expressed relative to the arithmetic holomorphic structure in the \(1\)-column
  while keeping the \qPilot{} log-volume fixed as input data.
\end{definition}

\begin{definition}[Algorithmic parallel transport]
  \label{def:apt}
  \notready
  The \(\APT\) property records how the multiradial algorithm transports data
  through gluings up to indeterminacy.  It belongs primarily to the implication
  from Theorem 3.11 to the reorganized hull-plus-determinant checkpoint.
\end{definition}

\begin{definition}[Hull plus determinant checkpoint]
  \label{def:hdd}
  \notready
  The \(\HDD\) checkpoint is the composite of descent with holomorphic hull
  and determinant formation.  It is the source-side operation that turns
  multiradial output regions into objects comparable with the \qPilot{} at
  the level of signed real log-volume.
\end{definition}

\begin{proposition}[Step (xi) upper-ray input]
  \label{prop:step-xi-upper-ray-input}
  \uses{thm:theorem-311-source-output,def:she,def:hdd}
  \notready
  The multiradial construction, followed by holomorphic hull, determinant, and
  log-volume, should produce a signed upper ray
  \[
    \R_{\le -|\log(\Theta)|}
  \]
  of possible output log-volumes, and the \qPilot{} reading
  \(-|\log(q)|\) should lie in this ray.
\end{proposition}

\begin{proof}
  This is the central source obligation.  It is exactly where the comparison
  must avoid identifying the arithmetic holomorphic histories too early while
  still obtaining a common log-volume container in which the final inequality
  is meaningful.
\end{proof}
