\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm,array}
\usepackage[hidelinks]{hyperref}

\newcommand{\IUT}{IUT}
\newcommand{\Lean}{Lean}
\newcommand{\R}{\mathbb{R}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\ThetaPilot}{\Theta\text{-pilot}}
\newcommand{\qPilot}{q\text{-pilot}}
\newcommand{\Ind}{\ensuremath{\mathrm{Ind}}}
\newcommand{\SHE}{\ensuremath{\mathrm{SHE}}}
\newcommand{\HDD}{\ensuremath{\mathrm{HDD}}}
\newcommand{\IPL}{\ensuremath{\mathrm{IPL}}}
\newcommand{\APT}{\ensuremath{\mathrm{APT}}}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{A Lean Audit of the IUT III Corollary 3.12 Corridor}
\author{IUT Lean formalization project}
\date{June 25, 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
We report on a first \Lean{} formalization of the logical corridor from
\IUT{} III, Theorem 3.11 to Corollary 3.12.  The formalization is deliberately
neutral with respect to the correctness of \IUT{} as a proof of the abc
conjecture.  It isolates the ordered-real comparison required at the end of
Corollary 3.12, tracks the finite \(q^{j^2}\) and label-quotient phenomena
that enter the public dispute, and records exactly which source-facing
construction hypotheses are still external.

The code still has conditional layers, but the preferred finite-divisor
surfaces are no longer merely the ordered-real implication.  The oldest
boundary proves \(C_\Theta\ge -1\) from the supplied signed comparison
\(-|\log(\Theta)|\le C_\Theta|\log(q)|\).  The newer source-facing boundaries
derive that comparison from Remark~3.9.5 hull/determinant data together with
local-to-global \(\IUT{}\,\mathrm{IV}\) \(C_\Theta\) source objects.  The
latest closed \(C_\Theta\) wrappers now thread the constructed qualitative
Hodge/\(\SHE\)/\(\IPL\) source through the one-sided finite-place route and the
strongest additive-Haar arithmetic-degree/\(p\)-adic formula route, rather than
using a free-standing \(\IPL\) record.  This does not prove Corollary 3.12 from
Mochizuki's published hypotheses; it identifies the remaining mathematical
construction problem at a lower, source-facing boundary.

After a source audit against \IUT{} I--IV, Mochizuki's 2026 LeanForm report,
and Scholze--Stix, the status is unchanged in kind but sharper in formulation:
the final ordered-real implication is formalized, several collapse-prone
comparison levels are separated, and the current local-to-global \(C_\Theta\)
route is proof-carrying.  The code still assumes substantial source
constructions: the full Hodge-theater/Frobenioid/log-Kummer apparatus,
genuine holomorphic hulls and determinants, and the deepest \(\IUT{}\,\mathrm{IV}\)
local analytic estimates.
\end{abstract}

\section{Aim and Sources}

The project formalizes a narrow and contested part of Mochizuki's
inter-universal Teichmuller theory.  The source base is the local copy of
\IUT{} I--IV, Mochizuki's 2026 report on formalization, and the Scholze--Stix
note.  The current target is the portion that Mochizuki's report calls Stage 1:
\[
\begin{array}{ccccc}
\text{\IUT{} III, Theorem 3.11}
& \xrightarrow{\APT+\IPL} &
\text{``3.11.5''}
& \xrightarrow{\SHE+\IPL} &
\text{\IUT{} III, Corollary 3.12}.
\end{array}
\]
The notation ``3.11.5'' is not a statement in \IUT{} III.  It is Mochizuki's
2026 name for the reorganized boundary where the hull-plus-determinant
operation is moved before the final simultaneous comparison of the
\(\Theta\)-pilot and the \(q\)-pilot.

The formalization is source-facing but not source-complete.  It does not
construct Hodge theaters, Frobenioids, log-shells, prime strips, or theta links
from first principles.  Instead, these are represented by typed records with
named hypotheses.  The point of the current work is to test whether the
claimed formal corridor is coherent once every comparison level, label
quotient, ordered real line, hull boundary, and quotient collapse is made
explicit.

\section{Framework and Tooling}

The repository is organized as a Lean verification project, not as a prose
annotation project.  The source papers in \texttt{docs/} are treated as the
mathematical source of truth.  The formalization then moves through three
layers:
\[
\begin{array}{c}
\text{source papers}\\
\Downarrow\\
\text{\Lean{} definitions, records, and theorems}\\
\Downarrow\\
\text{this paper draft}.
\end{array}
\]
The paper draft records only the current mathematical state of the
formalization.  It is not a research log.

The Lean code uses typed interfaces to prevent comparison-level drift.  A datum
that is merely a representative \(j^2\)-coordinate computation has a different
type from a balanced full-label datum, and both differ from the final
hull/log-volume comparison datum.  Likewise, ordered real-line transports,
Hodge/SHE preservation records, upper-ray membership, and quotient-collapse
audits are separate structures.  This is the main anti-collapse mechanism in
the framework: a proof cannot silently use a raw coordinate equality where the
Corollary 3.12 corridor asks for a hull/log-volume comparison.

The module roles are:
\begin{itemize}
\item \texttt{IUTStage1SourceCore}: core real-line, pilot, hull, quotient, and
  \(C_\Theta\) algebra.
\item \texttt{IUTStage1Remark312Absorption}: Remark 3.12.2(v) absorption
  interfaces.
\item \texttt{IUTStage1IUTIVAlgebra}: Remark 3.12 sign shadows and the
  conditional \IUT{} IV real-algebra handoff estimates.
\item \texttt{IUTStage1FiniteLabels}: finite local log-volume endpoints,
  \(F_\ell\)-label/torsor/sign/cusp-label models, \(ZMod\) full labels,
  theta-root cusp-label source packages, and label-averaged log-volume
  compatibility.
\item \texttt{IUTStage1StepX}: procession tensor-packet log-volume, the
  Step (x) indeterminacy corridor, the theta-hull upper-ray handoff, and
  local Frobenioid shift diagnostics attached to that boundary.
\item \texttt{IUTStage1Gaussian}: weighted label averages, \(ZMod\)
  square-weight profiles, Gaussian monoid degree evaluations, and
  Hodge--Arakelov theta-evaluation source objects.
\item \texttt{IUTStage1HodgeSHE}: square-weighted full-label transport
  audits, Hodge/SHE local object data, packet-normalization support,
  direct-summand local tensor actions, and upper-semi compatibility states.
\item \texttt{IUTStage1Theorem311}: Theorem 3.11 choice/indeterminacy records,
  multiradial possible-image records, algorithm-output records, and
  SHE-alignment source records.
\item \texttt{IUTStage1StepXI}: Step (xi) hull/determinant and IPL source
  objects, source obligations, package-audit constructors, and holomorphic
  hull/determinant source routes.
\item \texttt{IUTStage1FrobenioidShift}: endpoint-audit surfaces together with
  the nonarchimedean realified-Frobenioid/log-Kummer, vertical-\(IQ\), and
  root-of-unity support routes.
\item \texttt{IUTStage1EndpointAudit}: nested LogVolumeChartAudit refinements
  around the place-audited multiradial theta-hull endpoint.
\item \texttt{IUTStage1Source}: remaining public source-package audit surface
  around the Corollary 3.12 corridor.
\item \texttt{IUTStage1Experiments}: compiled endpoint checks and diagnostic
  theorems.
\end{itemize}
The experiment file is not a substitute for proof.  It is a curated surface
that forces the important route theorems to elaborate together and exposes
Boolean/report endpoints such as whether the present stage settles the dispute.
At present that endpoint is deliberately false.

The build discipline is simple.  Each mathematical increment is checked by
\Lean{} via \texttt{lake build Iut.Stage1.IUTStage1Experiments}; the paper is
rebuilt from this LaTeX source; and the code is scanned for explicit proof
placeholder and trust-boundary tokens.  The
long-term collaboration plan is compatible with Apodixis: the current typed
route endpoints and missing-obligation records give a natural surface for a
collaboration tool to show which mathematical interfaces are proved and which
remain open.

\section{Dispute Interface}

In \IUT{} III, Step (x) treats the procession-normalized log-volume as
unchanged under \((\Ind1)\) and \((\Ind2)\), while \((\Ind3)\) supplies a
one-sided upper-semi comparison.  Step (xi) then passes through multiradiality,
\(\IPL\), \(\SHE\), holomorphic hulls, determinants, and log-volume to place
the \(q\)-pilot reading in the signed-log upper ray determined by the
\(\Theta\)-pilot:
\[
  -|\log(q)|\in\R_{\le -|\log(\Theta)|}.
\]
The active source-facing Corollary 3.12 route does not use equality of
possible-image regions across an \((\Ind3)\) generator.  Such an equality exists
only in separate quotient bookkeeping interfaces as an explicit stronger
hypothesis; the route uses the one-sided upper-semi corridor as its Step (x)
input.
The current Theorem 3.11 source record now bundles structured
\(\IPL/\SHE/\APT\) input, coric multiradial output, possible theta-pilot images,
the 0-column/1-column pilot distinction, distinct log-shell treatments, and the
Hodge-theater history guard.  This is still not a full construction of
Theorem~3.11, but the indeterminacy/log-volume boundary is no longer a single
raw record: the finite \(F_l\)-averaged procession source now constructs the
typed \((\Ind1),(\Ind2),(\Ind3)\) core, deriving \((\Ind1)\) and \((\Ind2)\)
log-volume invariance from theta-pilot-class invariance.  A stronger
upper-semi comparison source now derives the \((\Ind3)\) average inequality
from two alignments with the source and target log-volume coordinates of the
upper-semi compatibility state, together with the existing one-sided
upper-semi bound.  This has now been lowered once more: a vertical
log-Kummer packet-alignment source inserts a typed nonarchimedean local tensor
packet for each concrete choice, proves that the theta-pilot average is the
packet-normalized log-volume, and then aligns the source and target packets
with the upper-semi source and target coordinates.  This packet-aligned source
now feeds the public one-sided Theorem~3.11 multiradial constructor: the typed
core, quotient possible images, canonical \(F_l\)-procession action, selected
q-region, and exclusion of \((\Ind3)\) from the equality quotient are all
exported through the same endpoint used by the Remark~3.9.5 and \(C_\Theta\)
corridor.  The remaining mathematical payload is to construct the packet
calibrations themselves from the full vertical log-Kummer/log-link data, rather
than taking them as boundary fields.
The \(\IPL\) layer has been separated into a typed log-volume transport datum:
it carries the source and target Hodge-theater sides, identifies the prime-strip
link endpoints with the input and output prime strips, records equality of the
transported real log-volume, and retains the no-history-identification guard.
It is not yet a construction of the full log-link.
The current \(\SHE\) layer now has a synchronization constructor: equality of
the canonical one-label Hodge--Arakelov theta-value degree constructs the
factored square/full-label preservation package used by the route.  This is a
Stage 1 source constructor for the available finite-label shadow of \(\SHE\),
not yet the full simultaneous-holomorphic-expressibility theorem.
The hull/determinant layer now has a source constructor attached to the
Theorem 3.11 record.  It reads the algorithmic certificate and \(\SHE\)
alignment from that record, keeps the record's theta possible-image union tied
to the hull endpoint, and derives the determinant-bound comparison
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).  The bridge used by this
source data can now be constructed from a displayed common hull containing the
target union and a determinant/log-volume bound for that hull; the analytic
construction of the hull and determinant remains external source data.
The strongest Hodge--Arakelov packet-target route no longer takes the
target-side log-volume equality or \(q\)-pilot positivity as independent
inputs: target equality is derived from the \(\SHE\) synchronization constructor,
and positivity is read from the hull/determinant constructor.  The source-side
chart calibration is no longer a raw equality input: it is a full-label
theta/Hodge calibration certificate, from which equality of the cusp
log-volume compatibility records is derived extensionally.
The strongest current labelled Step (x) route now consumes a theta-root
realified-Frobenioid log-Kummer entry source.  The Kummer and mono-analytic
forgetting transfers, realization tags, holomorphic-forgetting assertion, and
packet-local source alignment are projected from this source object instead of
being passed separately to the Corollary 3.12 route.
Its labelled \(ZMod(\ell)\) capsule family is now constructed as the constant
packet-local family over the audited packet local object; the route no longer
accepts an arbitrary labelled family or a separate local-object equality for
that family.
The exact vertical-\(IQ\) target has also been retained inside a refined
realified Step (x) source, so the route consumes one source object carrying both
the realified log-Kummer entry data and the \(FMOD\)-exact target guard.
The refined source now also requires the realified packet target calibration to
be exactly the calibration induced by this retained vertical-\(IQ\) target.
The strongest public experiment route now constructs this refined source from
theta-root data, realified Frobenioid transfer data, source alignment, and the
vertical-\(IQ\) target before entering the Corollary 3.12 corridor.
A finite-divisor form of the same route derives the packet-local source
alignment from the finite divisor/Frobenioid packet product before constructing
the refined exact source.
Its public experiment audit endpoint exposes the packet-local/source equality,
mono-analytic product equality, divisor-degree normalization,
\((\Ind3)\)-source equality, and upper-semi inequality used by this
construction.
For the canonical packet-local labelled family, this exact route no longer
requires direct packet-normalization: Hodge labelwise averaging identifies the
canonical labelled average with the theta-source average, and the retained
vertical-\(IQ\) target identifies that average with the packet-normalized
capsule value.
The final numerical step is elementary:
\[
  -|\log(q)|\le -|\log(\Theta)|
  \le C_\Theta|\log(q)|,\qquad |\log(q)|>0
  \quad\Longrightarrow\quad C_\Theta\ge -1 .
\]

Scholze--Stix object to the comparison because the \(\Theta\)-side data carries
\(j^2\)-scaled degrees, while a naive identification of ordered real lines
appears to remove the room needed for these scalars.  The formalization
therefore separates four comparison levels:
\[
\begin{array}{c}
\text{representative }j^2\text{ data}\\
\text{balanced sign-compatible data}\\
\text{averaged cusp-label data}\\
\text{hull/log-volume data}.
\end{array}
\]
The final route consumes only the hull/log-volume comparison level.  \Lean{}
rejects the balanced sign-compatible level as sufficient for the final
comparison.

\section{Source Audit}

The local sources impose the following constraints on the formalization.
\IUT{} I constructs the initial \(\Theta\)-data and the
\(\Theta^{\pm\mathrm{ell}}\mathrm{NF}\)-Hodge theaters.  It is not merely a
notation layer: the paper's central point is that the Hodge theaters separate
the additive and multiplicative combinatorial dimensions of a number field.
\IUT{} II supplies the Hodge--Arakelov theta evaluation, theta values at
\(\ell\)-torsion points, Gaussian Frobenioids, conjugate synchronization, and
the multiradial/coric phenomena needed later.  The current code models only
finite label and Gaussian degree shadows of this material.

\IUT{} III is the direct source for the formal corridor.  Step (x) says that
procession-normalized log-volumes are invariant under \((\Ind1)\) and
\((\Ind2)\), while \((\Ind3)\) becomes an upper-semi inequality after applying
log-volume.  Step (xi) uses the multiradial construction, \(\IPL\), \(\SHE\),
holomorphic hulls, determinants, and the 1-column log-Kummer correspondence to
put the \(q\)-pilot log-volume in the signed-log upper ray
\(\R_{\le -|\log(\Theta)|}\).  Step (xii) warns that replacing global
realified Frobenioids by local Frobenioids loses calibration because local
objects carry \(p_v^N\)-type endomorphisms.  Remark 3.12.2 further stresses
that the argument depends on weakened data, distinct \(q/\Theta\) labels,
upper-semi indeterminacy, and the asymmetry between the 0-column
\(\Theta\)-pilot and the 1-column \(q\)-pilot.
The current Step (x) packet source reflects this asymmetry by packaging the
1-column \(q\)-pilot non-interference, Kummer/forgetting product preservation,
source packet calibration, and packet-normalized target calibration in a single
realified-Frobenioid log-Kummer source object.
The latest route theorem uses this object directly: it still assumes the finite
source object, but it no longer permits the downstream proof to mix unrelated
Kummer, forgetting, realization, and packet-local calibration witnesses.
The labelled procession average used by this route is also no longer arbitrary:
Lean constructs the constant \(ZMod(\ell)\)-indexed capsule family from the
packet local object and proves its normalized value by averaging a constant
finite family.
The exact target face is now represented by a refined source object rather than
by a discarded calibration projection: the object keeps the vertical-\(IQ\)
target itself and exposes the \(FMOD\)-exactness predicate together with the
packet-normalized target equalities.
It also ties the realified packet target calibration to the retained
vertical-\(IQ\) target, so the exact face cannot be displayed while an
unrelated packet calibration is used downstream.
This removes direct packet-normalization only for the canonical exact source
route; arbitrary labelled families still require their own
packet-normalization evidence.

\IUT{} IV uses the resulting log-volume estimate as input to elementary
log-volume and Diophantine inequalities.  Our \IUT{} IV code is therefore only
conditional algebra at present: it records how later estimates consume a
Corollary 3.12-shaped bound, but it does not prove that bound from the full
arithmetic constructions.

Mochizuki's 2026 report explicitly recommends Stage 1 as the implication
\(\IUT{}\,\mathrm{III}\), Theorem 3.11 \(\Rightarrow\) Corollary 3.12, with a
reorganized intermediate ``3.11.5'' obtained by moving the hull-plus-determinant
operation before the final simultaneous comparison.  The same report states
that the current official code is skeletal.  Our formalization is best read as a
more diagnostic Stage 1 interface: it does not replace Stage 2, because it has
not constructed Theorem 3.11.

Scholze--Stix argue that, after simplification, the comparison loses the
\(j^2\)-scaled theta contribution and becomes essentially contentless.  The
Lean code therefore treats the \(j^2\)-representative level, sign quotient,
averages, square/full-label preservation, ordered real-line transports, and
hull/log-volume endpoint as different types.  This confirms that the final
Corollary 3.12 endpoint cannot be obtained from the balanced sign-compatible
level alone.  It does not prove that Mochizuki's source constructions supply the
missing higher-level data.

\section{Formalized Corridor}

The relevant implementation lives in the following Lean modules:
\begin{itemize}
\item \texttt{Iut/Stage1/IUTStage1SourceCore.lean}
\item \texttt{Iut/Stage1/IUTStage1Remark312Absorption.lean}
\item \texttt{Iut/Stage1/IUTStage1IUTIVAlgebra.lean}
\item \texttt{Iut/Stage1/IUTStage1FiniteLabels.lean}
\item \texttt{Iut/Stage1/IUTStage1StepX.lean}
\item \texttt{Iut/Stage1/IUTStage1Gaussian.lean}
\item \texttt{Iut/Stage1/IUTStage1HodgeSHE.lean}
\item \texttt{Iut/Stage1/IUTStage1Theorem311.lean}
\item \texttt{Iut/Stage1/IUTStage1StepXI.lean}
\item \texttt{Iut/Stage1/IUTStage1FrobenioidShift.lean}
\item \texttt{Iut/Stage1/IUTStage1EndpointAudit.lean}
\item \texttt{Iut/Stage1/IUTStage1Source.lean}
\item \texttt{Iut/Stage1/IUTStage1Experiments.lean}
\end{itemize}

\subsection{Finite label model}

The code defines a finite \(\F_\ell\)-label model, the quotient
\(|F_\ell|\) consisting of the zero class together with
\(\F_\ell^\times/\{\pm 1\}\), and the canonical half-range representatives
\[
  j=0,\ldots,(\ell-1)/2 .
\]
The Stage 1 label model is now connected to the bad-local theta-root data of
\IUT{} I, Definition 3.1(e),(f).  A new source package consumes the
quotient-\(\mathbb{Z}\) data of a bad local theta-root model and derives the
Stage 1 full label from its canonical coordinate.  It also carries the
canonical-generator-up-to-sign witness.  In the concrete \(Z/\ell Z\) quotient
case this derived full label is exactly the nonzero canonical full label
corresponding to coordinate \(1\).
It proves, for the descended full-label degree model:
\[
  \deg(\Theta_j)=j^2\deg(q)
\]
for the degree-level Gaussian endpoint, with sign invariance on the full-label
quotient.  It also proves that \(j=1\) and \(j=2\) give distinct degrees exactly
when \(\deg(q)\ne0\).  Thus the \(q^{j^2}\) phenomenon is present in the model;
it is not hidden inside a scalar identification.

The raw coordinate square-weight profile on \(\mathbb{Z}/\ell\mathbb{Z}\) is kept as a
diagnostic object and is not identified with the descended \(|F_\ell|\)
theta exponent.  The coordinate average, the nonzero-coordinate average, and
the absolute-label average are all formalized separately.  \Lean{} proves the exact denominator
relations and shows that these averages differ strictly for nonzero
environment degree.  This prevents silently replacing the paper's
\(\ell\)-denominator convention by an auxiliary nonzero-only average.

\subsection{Indeterminacy and upper-semi route}

The Step (x) corridor is represented as:
\[
\begin{array}{cccccc}
A_0 & = & A_1 & = & A_2 & \le U_{\Ind3},
\end{array}
\]
where \(A_0,A_1,A_2\) are the before-, after-\((\Ind1)\)-, and
after-\((\Ind2)\)-averaged log-volumes, and \(U_{\Ind3}\) is the
\((\Ind3)\) upper-semi target.  From this data and the hull/determinant
identifications, the code constructs the Step (xi) upper-ray datum:
\[
  q_{\mathrm{avg}}\le \Theta_{\mathrm{hull}} .
\]
The same route constructs the two \(q\)-pilot readings in Step (xi-g) and
proves that they are equal to the same fixed real value.
The typed \((\Ind3)\) law is now represented by
\texttt{Ind3UpperSemiStepAudit} and
\texttt{Ind3UpperSemiRelationAudit}.  These certificates record the source and
target log-volume coordinates of each \((\Ind3)\) step, the one-sided
upper-semi inequality, and the explicit exclusion of \((\Ind3)\) from the
\((\Ind1)/(\Ind2)\) equality quotient used for possible-image identifications.

\subsection{SHE and Hodge-descent boundary}

The current \SHE{} layer is conditional.  It has typed records for:
\[
\begin{array}{c}
\text{structured \SHE{} square-weight transport}\\
\text{factored square/full-label preservation}\\
\text{Hodge-descent packet transport}\\
\text{nonarchimedean \((\Ind3)\) source-target alignment}.
\end{array}
\]
Given these inputs, \Lean{} constructs the weighted theta comparison consumed
by the final route:
\[
  q_{\mathrm{signed}}\le \Theta_{\mathrm{signed}}.
\]
The nonarchimedean \((\Ind3)\) entry, factored square/full-label preservation,
and Hodge-descent packet transport now compose directly to this comparison.
With the \(q\)-pilot positivity condition and the displayed
\(C_\Theta\)-bound, the same composed route instantiates the signed
\(C_\Theta\) endpoint and proves \(C_\Theta\ge -1\).
The instantiated endpoint also exposes the strict and boundary alternatives:
strict source comparison gives \(C_\Theta>-1\), while \(C_\Theta=-1\) forces
equality of the signed \(q\)- and \(\Theta\)-readings and makes the
\(\Theta\)-reading negative.
These facts are now also packaged as a single route-level alternative:
boundary equality with negative \(\Theta\)-reading, or strict
\(C_\Theta>-1\).
The code also proves a Gaussian-to-factored-\SHE{} bridge at the present finite
degree level.  In particular, equality of the source and target environment
degrees gives full-label value preservation; nonzero-label target bounds are
enough because the zero label has square weight zero.
The newest route uses this bridge before applying the nonarchimedean endpoint:
Gaussian degree evaluations with preserved environment degree now construct the
factored square/full-label preservation package consumed by the
nonarchimedean \(C_\Theta\) dichotomy.  This removes one primitive preservation
input from that route, but it still assumes the nonarchimedean \((\Ind3)\)
alignment and the Hodge-descent/SHE source audit.
There is also an identity-coordinate specialization.  In that case equality of
Gaussian degree at the canonical full label \(1\) implies preservation of the
environment degree, so the nonarchimedean \(C_\Theta\) dichotomy no longer
takes environment-degree preservation as an independent hypothesis.
The Hodge--Arakelov/Gaussian bridge is now source-facing at the current
degree level.  A theta-value evaluation source carries the bad-local theta-root
label data and a theta-monoid degree \(d\), and constructs the Gaussian degree
evaluation
\[
  \deg_{\mathrm{gau}}(\lambda)
  = e(\lambda)\,d,
\]
where \(e(\lambda)\) is the absolute-label theta exponent.  The zero label has
degree \(0\), and the canonical label \(1\) has degree \(d\).  Thus equality at
the canonical label derives equality of the environment degree and feeds the
factored \SHE{} square/full-label obligations.
The raw nonarchimedean entry alignment has also been refactored through a
source-facing nonarchimedean upper-semi object equipped with 1-column q-pilot
log-Kummer data.  The upper-semi inequality remains the Step (x) input; the
1-column datum records the q-pilot column and log-Kummer non-interference
before converting to the raw real equalities consumed by the current route.
For the source side of this compatibility, the code can now use the existing
finite tensor-packet chain: Kummer transfer
\(\mathrm{holomorphicF}\to\mathrm{holomorphicD}\) and mono-analytic forgetting
\(\mathrm{holomorphicD}\to D^\vdash\) preserve product log-volume.  Thus the
source-side upper-semi equality may be derived from this chain rather than
postulated as a bare equality.
The newest source package attaches this finite Kummer/forgetting chain to the
bad-local theta-root cusp-label source.  It carries the canonical nonzero
\(|F_\ell|\)-label and derives the nonarchimedean \((\Ind3)\) source equality
from product-log-volume preservation along
\[
  \mathrm{holomorphicF}\to\mathrm{holomorphicD}\to D^\vdash .
\]
The packet local object, local entry source, mono-analytic product, and
holomorphic source product are now packaged as one source-side log-Kummer
packet calibration object.  The object itself is still supplied source data,
but the equality from entry source to \((\Ind3)\) source is derived from it
together with the Kummer and forgetting maps.
The source calibration can now also be constructed from the explicit
packet-local/source alignment, the packet-local \((\Ind3)\)-source alignment,
and the two product-preservation maps.  Thus the route no longer has to accept
the holomorphic source-product equality as a primitive field when these
Step (x) alignments are available.
The source and target packet calibrations are now joined by a finite
log-Kummer packet-correspondence source carrying the q-pilot column and
non-interference guard.  Its target face carries the common packet-normalized
capsule value, and \Lean{} derives the direct theta-to-entry, theta-to-packet,
and entry-to-\((\Ind3)\)-target equalities consumed by the upper-semi route.
The target calibration no longer contains an independent real representative
for this common value: all target equalities are stated directly against the
packet-normalized capsule log-volume.  This removes one artificial
identification layer from the Step (x) interface.
The target face has also been refined by a vertical-\(IQ\) source object,
following \IUT{} III, Proposition 3.10(ii).  The theta average, the
\((\Ind3)\)-target value, and the local entry target are represented as points
of one log-Kummer \(IQ\)-target whose values agree with the packet-normalized
point.  The packet-target calibration is then constructed from this
vertical-\(IQ\) source, so the corresponding theta-to-entry and
entry-to-\((\Ind3)\)-target equalities are derived from common-target
compatibility rather than passed as separate target-calibration inputs.
This object is guarded by the exact \(FMOD\) side of Proposition 3.10(iii) and
Remark 3.10.1: the one-sided \(Fmod\) upper-semi mode is classified separately
and is not accepted as an exact vertical-\(IQ\) target calibration.
The local entry target can now also be constructed from the packet-normalized
capsule value itself.  A packet-normalized entry-target source builds a
nonarchimedean upper-semi entry whose target finite log-volume is definitionally
the packet-normalized capsule value.  The corresponding target calibration
therefore no longer needs an independent proof for the entry-target equality;
only the theta-average and \((\Ind3)\)-target identifications with the same
packet-normalized value remain as inputs at this level.
The latter can now be reduced further: if the Step (x) target-side
\((\Ind3)\) alignment gives equality of the theta average with the \((\Ind3)\)
target, then \Lean{} derives the \((\Ind3)\)-target-to-packet-normalized
equality from this alignment and the theta-average-to-packet-normalized
equality.
The packet-correspondence source itself can now be built from this reduced
target data together with the source packet/product calibration.  Thus the
correspondence constructor no longer needs a completed target-calibration
record when the target entry and theta-target alignment are available.
It can also be built directly from the packet-local source alignments and the
same target theta alignment.  In this form both the source packet calibration
and the target packet calibration are generated before the q-pilot
non-interference endpoint is projected.
The same reduction has been lifted through the realified-Frobenioid packet
source: realified Kummer compatibility still supplies the
\(\mathrm{holomorphicF}\to\mathrm{holomorphicD}\to D^\vdash\) transfer, while
the target face is now generated from the packet-normalized entry target and
theta-target alignment.
The realified entry source and the theta-root attached realified entry source
can also consume the vertical-\(IQ\) target source directly; their upper-semi
endpoint then derives the theta-to-entry and entry-to-\((\Ind3)\)-target
equalities through the common log-Kummer target rather than through separate
target alignment inputs.
This vertical-\(IQ\) source now reaches the integrated Hodge/SHE/IPL/hull
route: the first-pass \(C_\Theta\) dichotomy can be stated without the
ordered-real-line target alignment and without the auxiliary packet-normalized
\(ZMod(\ell)\) route whenever the exact common \(IQ\)-target is supplied.
The same route has a source-reduced form: packet-local/source alignment,
entry-source/mono-analytic-product alignment, packet-local/\((\Ind3)\)-source
alignment, and the realified Kummer/forgetting compatibilities construct the
source calibration internally before the vertical-\(IQ\) target enters the
final inequality route.
This reduction now also exists at the Step (x) source-object level: an
upper-semi packet-normalized entry, packet-local source alignments, realified
Kummer/forgetting compatibility, and an exact vertical-\(IQ\) target construct
one realified log-Kummer entry source before the Hodge/SHE/IPL/hull route is
applied.
The realified source can now also generate the source packet calibration from
packet-local/source alignments before forming the correspondence; consequently
the strongest realified Step (x) constructor no longer needs a completed source
calibration as input.
The first-pass Gaussian route also has a one-correspondence form: it consumes
a finite log-Kummer packet-correspondence source and projects the source
packet/product calibration and target packet-normalized calibration from that
single object before entering the upper-semi corridor.
The same correspondence now has a transfer-chain endpoint exposing the
\(\mathrm{holomorphicF}\to\mathrm{holomorphicD}\to D^\vdash\) product
log-volume equalities, the source equality with the \((\Ind3)\) real source,
the target packet-normalized equalities, and q-pilot non-interference from the
same object.
The current strongest Step (x) entry source places this correspondence below
the realified Frobenioid layer: the selected nonarchimedean upper-semi entry
and the realified-Frobenioid packet source are bundled together, and \Lean{}
projects the Kummer transfer, mono-analytic forgetting transfer, source
calibration, target packet calibration, and q-pilot non-interference guard from
that single source object.
There is now a reduced constructor for this entry source: entry membership,
packet-local/source alignment, packet-local \((\Ind3)\)-source alignment,
packet-normalized target data, and theta-target alignment construct the
realified packet source internally and then derive the upper-semi inequality.
The bad-local theta-root label source is now attached to this realified entry
source.  The corresponding Hodge--Arakelov route consumes one object carrying
the canonical nonzero theta-root label, the selected upper-semi entry, and the
realified-Frobenioid log-Kummer packet source before entering the
\(C_\Theta\)-dichotomy.
This theta-root attached source now has the same source-reduced
vertical-\(IQ\) constructor: the theta-root label package is combined with the
upper-semi packet-normalized entry, packet-local source alignments, realified
Kummer/forgetting compatibility, and the exact vertical-\(IQ\) target.  \Lean{}
then projects the canonical-label facts, transfer-chain product equalities,
target packet calibrations, q-pilot non-interference, and the Step (x)
upper-semi inequality from this single source object.
The packet-local source side is now bundled as a named alignment object:
packet-local/source equality, entry-source/mono-analytic-product equality, and
packet-local/\((\Ind3)\)-source equality travel together before constructing
the packet source calibration.
Conversely, a source packet/product calibration together with the Kummer and
mono-analytic forgetting transfers reconstructs this packet-local alignment
object; the packet-local/\((\Ind3)\)-source equality is derived through the
transfer chain rather than supplied as a parallel datum.
When the mono-analytic packet product is supplied by the finite
divisor/Frobenioid product source, \Lean{} now derives the
entry-source/mono-analytic-product equality from the packet-local object
identification and the finite divisor realified log-volume computation.
This recovery has now been lifted to the realified-Frobenioid packet source:
\Lean{} uses the source object's own Kummer and mono-analytic forgetting
compatibilities to reconstruct the packet-local source alignment.
At the realified Step (x) entry level, the same projection also carries the
upper-semi membership of the selected nonarchimedean entry.
At the theta-root attached level, the projection also carries the canonical
bad-local theta-root generator and nonzero full-label facts.
The final Hodge/\(\SHE/\IPL\)/hull route now has an audit form that returns
this recovered packet-local source alignment together with the \(C_\Theta\)
dichotomy.
The target-only \((\Ind3)\) alignment is also derived at route level from the
Step (x) packet-normalized theta source and the exact vertical-\(IQ\) target,
with the \(FMOD\)-exactness guard retained.
An audit form of this route exposes the derived equality between the
Hodge-descent theta average and the \((\Ind3)\) target value.
At the packet-correspondence layer, this source-alignment object and the exact
vertical-\(IQ\) target now construct one log-Kummer correspondence source.  The
realified-Frobenioid packet source uses this correspondence-level constructor,
so source and target Step (x) calibrations enter through a single packet source
before the theta-root entry source is formed.
The same correspondence-level reduction is now available for the
packet-normalized ordered target: the named source-alignment object constructs
the source face before the theta-average and target \((\Ind3)\) alignments
construct the target face.
The theta-root attached entry source now also projects this packet
correspondence, so the canonical bad-local label facts and the full Step (x)
transfer/target calibration endpoint are exposed from one source object.
The Hodge/\(\SHE/\IPL\)/hull route has the same realified endpoint: its
alignment record supplies the Hodge--Arakelov Gaussian comparison,
canonical-one preservation, q-pilot positivity, and theta/Hodge log-volume
calibration, while the Step (x) data enters through the single theta-root
attached realified source.
The route now also has a source-reduced endpoint: the theta-root label package,
entry membership, packet-local source alignments, packet-normalized target
alignment, and realified Frobenioid compatibility construct the Step (x) source
inside the theorem before proving the same \(C_\Theta=-1\) boundary alternative
or strict \(C_\Theta>-1\) conclusion.
For the vertical-\(IQ\) form, the theorem now constructs the theta-root
attached realified Step (x) source object directly from this source-alignment
object and the exact \(IQ\)-target before applying the
Hodge/\(\SHE/\IPL\)/hull endpoint.
At the non-theta-root realified entry level, the corresponding source-aligned
vertical-\(IQ\) endpoint now exposes the \(FMOD\)-exactness guard itself,
together with Kummer/forgetting product preservation, target packet
normalization, q-pilot non-interference, and the upper-semi inequality.
The same exactness exposure has been lifted through the bad-local theta-root
source: the canonical theta-root label data, exact vertical-\(IQ\) condition,
packet-normalized target equalities, and Step (x) upper-semi inequality now
appear in one theta-root attached endpoint.
The packet-normalized theta-source calibration is now also consumed through a
single Step (x) alignment object: the constant \(ZMod(\ell)\)
packet-normalized route and the proof that it has the same theta source as the
Hodge-descent route are bundled before \Lean{} derives the
theta-average-to-packet-normalized equality used by the final corridor.
The ordered-real-line form now has the same source-aligned boundary: the
packet-local source-alignment object and realified Kummer/forgetting
compatibility construct the source calibration internally before the matched
theta-target alignment is used.
This has been narrowed further to a target-only \((\Ind3)\) alignment:
source-side packet-to-\((\Ind3)\) information is taken from the packet-local
source-alignment object, while only the theta-average-to-target equality
remains as ordered-real input.
That target-only alignment is now constructible from Step (x)
packet-normalized theta-source alignment together with an exact vertical-\(IQ\)
target: \Lean{} derives both sides through the common packet-normalized value
and keeps the \(FMOD\)-exactness guard visible.
The corresponding realified-source audit removes the independent
packet-local source-alignment parameter: the alignment is recovered from the
theta-root attached realified log-Kummer entry source, while the exact
vertical-\(IQ\) target supplies the target-side equality and \(FMOD\) guard.
The stronger realified-source audit also removes the separate
packet-normalized theta-source route at this boundary: theta packet
normalization is projected from the same realified log-Kummer entry source,
and the vertical-\(IQ\) target supplies only the \((\Ind3)\)-target
packet-normalized equality.
The procession-normalized log-volume layer now has a direct finite
\(\mathbb{F}_\ell\)-labelled source: capsule log-volumes are indexed by
\(ZMod(\ell)\), the total is the finite sum over all labels, the normalized
value is this sum divided by \(\ell\), and \Lean{} proves invariance of the
average under label translation.
At this finite-label boundary, the \((\Ind1)\)/\((\Ind2)\) preservation step no
longer has to be represented as pointwise equality of labelled summands:
\Lean{} proves preservation of the normalized average by reindexing the
\(ZMod(\ell)\)-sum.  The next lowering replaces the old direct \((\Ind3)\)
average inequality by an upper-semi comparison source: the source average is
identified with the upper-semi source log-volume, the target average with the
upper-semi target log-volume, and the inequality is then the
\(\mathrm{source}\le\mathrm{target}\) law of the upper-semi compatibility
datum.  The preferred source for this boundary is now one step lower: it
identifies both averages with packet-normalized log-volumes of typed
nonarchimedean local tensor packets before passing to the upper-semi
coordinates.  This is no longer an isolated typed-core source: the record
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaVerticalLogKummer}\\
\quad\texttt{PacketAlignedSource}
\end{array}
\]
combines the theta-pilot class image source, its pullback equality with the
Theorem~3.11 record images, the packet-normalized vertical log-Kummer source,
the \(F_l\)-gluing torsor, and the selected q-choice.  Its constructor enters
the public one-sided multiradial source directly, so the selected q-region is
already a quotient possible image at this packet-aligned boundary.
The target-side packet calibration can now consume this labelled Step (x)
average directly: the equality
\(\theta_{\mathrm{avg}}=\mathrm{packetNormalized}\) is derived by composing
\(\theta_{\mathrm{avg}}\) with the labelled normalized average and then with the
audited packet-normalized capsule value.  This dependency is tagged separately
from a bare direct real-line identification.
The same labelled-average dependency has been lifted into the realified
Frobenioid packet source constructor, so the realified Step (x) packet source no
longer needs a raw packet-normalized theta-average equality at this boundary.
It is now also lifted through the theta-root attached Step (x) entry source and
through the Hodge/\(\SHE/\IPL\)/hull route: the route may consume the labelled
average and its equality with the Hodge-descent theta average directly, rather
than a constant packet-normalized \(ZMod(\ell)\) route object.
The same route now has a source-aligned form: the source packet/product
calibration is constructed from packet-local source alignment and the
Kummer/forgetting transfers, while the target packet calibration is constructed
from the labelled procession average.
A further route removes the raw theta-source-to-labelled-average real equality:
the labelled capsule source is aligned labelwise with the theta-source
\(ZMod(\ell)\)-average, and \Lean{} derives equality of the two averages from
the finite averaging formula.
The labelled-average-to-packet-normalized equality is now also derived in the
source layer: if each labelled capsule has the displayed local object, \Lean{}
proves that the labelled average is that local object's finite log-volume, and
direct packet-normalization then identifies it with the packet-normalized
capsule value.
The labelled route can now replace its remaining target-side ordered-real
alignment by an exact vertical-\(IQ\) target: \Lean{} derives the
\((\Ind3)\)-target equality from the same packet-normalized value used by the
labelled theta-source alignment.
In the finite-divisor variant, the source packet-local alignment is now
constructed from the finite divisor/Frobenioid tensor packet product before
the direct-labelled vertical-\(IQ\) route is applied.
The labelwise equality between the labelled capsule source and the
Hodge-descent theta-source \(ZMod(\ell)\)-average is now derived from local
Hodge-descent transport: each theta-source label is identified with the
packet local object's finite log-volume, as is each labelled capsule value.
The vertical-\(IQ\) route can now also be instantiated with a finite
divisor/Frobenioid packet product on the mono-analytic side.  In this form the
route constructs the theta-root attached realified log-Kummer entry source
from the finite divisor packet product and the exact vertical-\(IQ\) target
before applying the Hodge/\(\SHE/\IPL\)/hull endpoint.  The packet-local source
alignment is now recovered inside that source object, not passed as a separate
route input.
The finite-divisor packet-local source itself can now be recovered from the
realified Frobenioid log-Kummer packet source when its mono-analytic side is
the finite divisor realization.  Thus the divisor-realified equality and the
packet-local \((\Ind3)\)-source equality are obtained from the packet
correspondence and its Kummer/forgetting calibration, rather than being
parallel fields at the finite packet boundary.
This recovery has now been threaded through the current preferred constructed
input-prime-strip record-hull boundary, both with and without the constructed
qualitative checkpoint audit.  Those public endpoints consume the realified
packet source and expose the recovered finite-divisor and \((\Ind3)\) source
equalities next to the \(C_\Theta\) dichotomy.
On the Theorem~3.11 side, the vertical log-Kummer packet-aligned multiradial
constructor has been lowered one step.  It can now be built from a classified
packet-local-object source: the finite procession average is identified with the
packet local object's finite log-volume, classified packet-normalization
identifies that local object with the normalized capsule log-volume, and the
\((\Ind3)\) source/target alignments are stated at the local-object level.  A
direct finite-capsule variant promotes
\texttt{IUTStage1DirectPacketNormalizationData} to this classified source before
entering the public one-sided constructor.  This has now been lowered again by
\texttt{LogThetaLabelProcessionVerticalLogKummerClassifiedPacketLocalObjectSource}.
That source supplies the log-theta procession values label by label, identifies
their finite \(F_\ell\)-average with the classified packet local object's finite
log-volume, and derives both the label-wise upper-semi source and the older
classified packet-local source.  Thus neither the packet-normalized equality nor
the averaged procession object is primitive at this boundary.  It has also
been lowered to
\texttt{LogThetaLabelProcessionVerticalLogKummerDirectPacketLocalObjectSource}:
direct finite-capsule packet-normalization data now induces the classified
packet compatibility, the local-object equals capsule-average equation, the
label-wise classified source, and the one-sided endpoint.  The next lowering is
\texttt{LogThetaLabelProcessionVerticalLogKummerCapsulePacketLocalObjectSource}:
it no longer takes direct packet-normalization as primitive.  Instead it assumes
the typed capsule family already attached to the packet, the total-as-sum
formula for its capsule log-volumes, and the paper-side equality saying that
the packet local object's finite log-volume is the uniform capsule average.
\Lean{} reconstructs the direct packet-normalization record from these data.
The preferred boundary is now lower again: the transported \(ZMod(\ell)\)
log-shell packet source, whose Lean suffix is
\texttt{TransportedZModLogShellPacketLocalObjectSource}.
Here the full \(F_\ell\)-procession is not supplied as a normalized family.
Instead, the source gives a base local log-shell object, labelled
representatives, and transport of every representative back to the base object.
\Lean{} constructs the labelled log-shell family, its total log-volume, its
normalized log-volume, the capsule family, and the packet-local capsule state.
This boundary has now been lowered once more by
\texttt{ColumnLogLinkZModLogShellPacketLocalObjectSource}.  For each
theta-pilot class the source gives a realified-Frobenioid column
log-Kummer compatibility and label-wise vertical log-link operations.  Lean
uses Proposition~3.10-style preservation of the realified log-volume, together
with the local-object identification of the log-link, to construct the
transport of every labelled log-shell representative back to the base object.
The preferred boundary is now one step lower.  A
\texttt{ColumnRealifiedLogShellZModLogShellPacketLocalObjectSource} supplies, at
each column, an IUT~I, Example~3.5(iii), realified Frobenioid log-shell divisor
source.  Lean constructs the finite local log-shell object from the
log-shell divisor log-volume and identifies it with the corresponding
realified Frobenioid degree object under the normalized-Frobenius condition.
The boundary has now been lowered again to a raw divisor-column source.  At this
level the source gives only the column-indexed log-shell divisor data, one
normalization, normalized-Frobenius witnesses, realified log-volume preservation
under column translation, and the labelled local-object identity.  Lean derives
the labelled log-shell divisor log-volume equality, constructs the local
log-volume objects, and promotes the result to the column realified-log-shell
source.  The \((\Ind3)\) base comparison has now also been lowered through this
construction: a base-volume source states the source and target comparisons for
the raw base divisor's realified Frobenioid log-volume, and Lean derives the
finite local log-shell object equalities required by the older raw-column
source.  The raw column boundary has now been lowered below its translation
fields by
\texttt{ColumnLogKummerRealifiedLogShellDivisorFamilySource}.  This source
starts from a column Frobenioid/log-Kummer compatibility, a divisor realization
of each vertical column, and the labelled log-link local-object identity.  Lean
derives realified log-volume preservation under vertical column translation,
derives the labelled base-object equality, promotes the data to the raw
divisor-column source, and exposes the same one-sided Step~(xi) endpoint.  The
boundary has now been lowered again to compatible ordinary/theta/log-shell
copies of the finite realified Frobenioid divisor data.  At this level
\Lean{} derives the log-shell divisor realization from the ordinary divisor
realization and the compatible-copy base equality, obtains the normalized
Frobenius witnesses from the Example~3.5 compatibility package, and upgrades an
object-level labelled log-link identity to the full local-object identity by
using the column log-Kummer preservation of realified log-volume.  The
boundary has now been lowered one step further by
\texttt{DegreeRealizedCompatibleCopiesColumnLogKummerDivisorFamilySource}.  The
ordinary copy no longer realizes the column log-Kummer object by a supplied
record equality; the source gives the component data--local object, divisor
degree, and unit log-volume--and \Lean{} reconstructs the realified
Frobenioid degree-object equality.  At the base-volume level, the \((\Ind3)\)
comparison is stated at the column compatibility degree object, and \Lean{}
derives the older ordinary-copy comparison.  This has now been sharpened by
\texttt{LocalObjectDegreeRealizedCompatibleCopiesColumnLogKummerDivisorFamilySource}.
The labelled log-link input is no longer merely the equality of the underlying
base objects; it is the equality of the finite local log-volume objects after
the common log-shell normalization.  \Lean{} projects the older object equality
from this local-object equality and threads the result through the same
Theorem~3.11 and Step~(xi) constructors.  The compatible-copy package has now
also been split by
\texttt{SplitCopiesLocalObjectDegreeRealizedColumnLogKummerDivisorFamilySource}.
Instead of receiving one opaque ordinary/theta/log-shell copy column, the source
receives the ordinary divisor column, theta divisor column, and log-shell
divisor column separately, plus the Example~3.5 base-identification and
normalization laws.  \Lean{} constructs the compatible-copy package at each
column and derives the theta/log-shell log-volume equalities with the ordinary
realified divisor volume.  This has now been lowered again by
\texttt{NormalizedExample35LocalObjectDegreeRealizedColumnLogKummerDivisorFamilySource}.
That source receives only the ordinary divisor column, a positive log-shell
extension degree at each column, and the object-level labelled log-link
transport.  \Lean{} constructs the theta copy by normalizing the
\(\log(\Theta)\)-generator to \(1\), constructs the log-shell copy by taking the
local Frobenius reading equal to the extension degree, proves the normalized
log-shell reading is \(1\), and derives the full labelled local-object equality
from object transport plus the column realified-log-volume translation.  The
ordinary column has now also been lowered by
\texttt{FiniteDivisorRealizedNormalizedExample35ColumnLogKummerDivisorFamilySource}.
Instead of receiving a realified divisor column and three realization laws, the
source receives finite divisor-monoid data in each vertical column--prime
multiplicities, prime degrees, and the finite degree-sum identity against the
column Frobenioid/log-Kummer degree object.  \Lean{} constructs the ordinary
divisor column using the compatibility object's local object and unit
log-volume; the object and unit realization laws become definitional, and the
divisor-degree realization is exactly the finite sum formula.  The labelled
object equality consumed by this source has now been lowered again: instead of
supplying the equality of the base and labelled compatibility objects directly,
one supplies a vertical log-Kummer/log-link object transport whose source and
target are realized as the corresponding Frobenioid degree objects.  \Lean{}
derives the labelled compatibility equality from this transport and then enters
the finite-divisor ordinary-column construction.  The Frobenioid degree column
itself has now also been constructed from finite divisor components: the source
supplies the local object, prime multiplicities, prime degrees, and unit
log-volume in each vertical column, and \Lean{} builds the corresponding
realified Frobenioid degree object.  Its divisor degree is definitionally the
finite sum over the prime components.  The upper-semi comparison boundary has
also been tightened by
\texttt{FrobenioidDivisorColumnUpperSemiCalibratedBaseVolume}: the source now
calibrates the upper-semi source and target coordinates choice-wise against the
constructed Frobenioid base volumes.  \Lean{} derives the older
\((\Ind3)\)-indexed source/target equalities and proves the one-sided
\((\Ind3)\) base-volume inequality from the upper-semi log-volume
compatibility.  This has now been lowered once more by
\texttt{FrobenioidDivisorColumnConstructedUpperSemiBaseVolume}: the upper-semi
state itself is constructed with its log-volume compatibility datum equal to
the Frobenioid base volume.  A further representative-section layer,
\texttt{FrobenioidDivisorColumnRepresentativeConstructedUpperSemiBaseVolume},
now uses the theta-pilot representative section to recover the choice-level
upper-semi identification: the representative's upper-semi state is transported
to the constructed Frobenioid base-volume state, and each concrete choice is
identified with its selected theta-pilot representative.  This has now been
lowered to component data by
\texttt{FrobenioidDivisorColumnComponentRepresentativeConstructedUpperSemiBaseVolume}:
the finite \(F_\ell\)-label, procession state, local tensor state, and
non-volume upper-semi data are supplied class-wise, while \Lean{} constructs
the representative section, inserts the Frobenioid base volume into the
upper-semi log-volume compatibility datum, derives the direct-summand
cardinality, and enters the same Step~(xi) source.  The remaining payload has
moved below these component functions: construct them from the paper-native
log-link and local Frobenioid geometry and prove the concrete choice
identification.  The component boundary has also been separated from the
ambient concrete choice space by
\texttt{FrobenioidDivisorColumnComponentRepresentativeKernel}: from the same
class-wise component data, \Lean{} generates a canonical theta-pilot choice
space whose elements are exactly the constructed representatives.  On this
generated space, the identification with the representative section, the
direct-summand cardinality, and the Frobenioid base-volume upper-semi
compatibility are theorems rather than global assumptions about all arbitrary
concrete choices.
This generated-choice layer has now been refined to keep the full finite
label procession.  The kernel constructs, for each theta-pilot class and each
label \(j\in Z/\ell Z\), a concrete Hodge-theater/log-theta choice with the
same generated procession, local tensor, and upper-semi data.  The resulting
\texttt{FullLabelGeneratedChoice} space is closed under the \(Z/\ell Z\)
translation action, and \Lean{} proves that its projection to the ambient
concrete choice space is exactly the existing \texttt{flProcessionTranslate}
operation.  Thus the generated boundary no longer trades the full \(F_\ell\)
procession for a single representative; the representative choice is now only
the distinguished label inside a larger generated procession space.
The generated full-label space now also has its own typed
\((\Ind1),(\Ind2),(\Ind3)\) core and quotient possible-image audit.  On this
generated space, \((\Ind1)\) is finite-label translation, \((\Ind2)\) is
same-theta-pilot-class transport at the lowered component boundary, and
\((\Ind3)\) is retained only as the Frobenioid base-volume upper-semi
inequality.  Possible images are pulled back from theta-pilot-class images,
and the generated equality relation is characterized at the source boundary:
it preserves the forgotten theta-pilot class, while equality of theta-pilot
classes enters the quotient through the generated \((\Ind2)\) step.  The
finite \(F_\ell\)-procession orbit is now also a named source object: for a
generated choice, every label of \(Z/\ell Z\) occurs in its orbit, every orbit
member is an \((\Ind1)\) equality move, and the equality-quotient index,
procession-normalized log-volume, and pulled-back possible image are unchanged
along the orbit.  Thus the quotient audit proves the pullback for every
generated choice, with the selected q-region as a specialization, while
\((\Ind3)\) remains outside the equality quotient.  This replaces the previous
ambient ``every concrete choice is a representative'' assertion at the
generated-choice quotient layer.
This generated quotient has now entered the public Step~(xi) constructor layer:
\texttt{ofGeneratedFullLabelQuotientSource} constructs a one-sided
Theorem~3.11 multiradial source whose index is
\texttt{FullLabelGeneratedChoice}.  Its \(F_\ell\)-procession action is the
generated label translation, its possible-image family is the theta-pilot
class family pulled back to generated choices, and its endpoint proves both
selected-region containment in the record union and projection compatibility
with the ambient \texttt{flProcessionTranslate}.  Thus the public constructor
now consumes the generated quotient itself, rather than reintroducing a global
ambient representative assumption.  The corresponding corridor audit now also
records the generated-kernel audit, the theta-class characterization of the
generated equality relation, the all-choice quotient pullback, and the typed
action-law audit for the constructed core.  Thus the public boundary exposes
the source-pattern \((\Ind1),(\Ind2)\)-equality and
\((\Ind3)\)-upper-semi laws before entering Remark~3.9.5.
The same generated source is now threaded through the downstream
Remark~3.9.5 and \(C_\Theta\) corridor.  The declarations
\[
\begin{array}{l}
\texttt{GeneratedFullLabelQuotientCorridorSource.toHullCompatibility},\\
\texttt{GeneratedFullLabelQuotientCorridorSource}\\
\quad\texttt{.toRemark395ConstructedHolomorphicHullDeterminantSource},\\
\texttt{GeneratedFullLabelQuotientCorridorSource}\\
\quad\texttt{.toRemark395ConstructedGlobalCThetaScaleComparisonAudit}
\end{array}
\]
construct the Remark~3.9.5 hull compatibility, select the generated
quotient \(q\)-region as the hull/determinant source, and pass it to the
current global \(C_\Theta\)-comparison audit.  Their endpoint exposes the same
region as the selected generated quotient image and as the pullback of the
theta-pilot-class possible image, then records the \(q\leq\Theta\) comparison,
the global \(C_\Theta\) bound, and the present Corollary~3.12 dichotomy.
The generated route now also carries a Remark~3.9.5 hull-compatibility audit:
after quotienting by \((\Ind1,\Ind2)\), every possible region still pulls back
to the corresponding theta-pilot-class region, equality-related generated
choices have the same possible region and hull log-volume, and \((\Ind3)\)
enters only through the one-sided upper-semi log-volume inequality.  The
selected \(F_\ell\)-procession orbit is now part of this same hull boundary:
\texttt{selectedProcessionOrbitRemark395HullEndpoint} proves that every
generated full-label translate of the selected \(q\)-choice has the same
Remark~3.9.5 possible region, the same hull log-volume, and the same selected
\(q\)-region.  Thus the hull boundary sees the full finite procession, not
only the distinguished selected label.
This has been sharpened to the concrete finite-label statement
\[
\texttt{selectedConcreteLabelsRemark395HullEndpoint}.
\]
For every label \(j\in Z/\ell Z\), the generated choice
\((\Theta\text{-class},j)\) has the selected Remark~3.9.5 possible region,
the same hull log-volume as the selected \(q\)-choice, and the same
theta-pilot-class pullback region.  Thus the concrete no-omission/full-label
procession audit now survives to the Remark~3.9.5 hull source, instead of
stopping at the generated quotient layer.
The experiment surface now exposes this generated route as
\[
\texttt{generatedFullLabelQuotientRemark395GlobalCThetaExperimentAudit}.
\]
This audit keeps the generated full-label quotient evidence and the
Remark~3.9.5 hull-compatibility audit next to the q-region equalities and the
global \(C_\Theta\) dichotomy.  It does not by itself identify the
generated-choice package with the finite-divisor
vertical-\(IQ\) package; that handoff is treated at the finite theta-class
fiber.  At this fiber boundary, the raw tensor-label endpoint is now an
intermediate audit below calibrated local tensor packets, which construct the
typed local-tensor symmetry-source boundary before projecting to raw labels.
The current lowest compact endpoint, and now also the constructed
Step~(x)-to-hull upper-ray gluing endpoint, consume the
five-component calibrated local-tensor source consisting of a same-theta
midpoint packet, an \((\Ind1)\) procession step, the source-level
nonarchimedean \(\mathrm{Ism}\) action step, and the two local
nonarchimedean \(\mathrm{Ism}\) calibrations.  From these components Lean
assembles the calibrated transport datum and derives the packet-label and
identified \((\Ind2)\) packet-action witnesses used by the finite
\(C_\Theta\) corridor.  In the constructed gluing form, the same source also
feeds the finite Step~(x) upper-ray datum before the generated/finite
q-region comparison is invoked.
The stronger public route passes through the transported packet-label, retained
label-transport, and matched identified \((\Ind2)\) packet-action endpoints,
culminating in
\[
\begin{array}{l}
\texttt{generatedFullLabelFiniteDivisorVerticalIQFiniteThetaClassFiber}\\
\quad\texttt{ComponentProcessionNonarchimedeanIsmMatchedIdentified}\\
\quad\texttt{Ind2ActionPacketSourceImageLawSource\_compact\_cThetaDichotomy}.
\end{array}
\]
Thus same-theta-class finite packets are no longer compared by a primitive
record-image equality or by an ambient quotient hypothesis.  Lean builds the
comparison through an explicit midpoint packet, a procession leg, a retained
nonarchimedean \(\mathrm{Ism}\) action-entry step, raw source and target tensor
\(\mathrm{Ism}\) labels, and the target summand-kind certificate.  From these
raw labels it constructs the local label transport and then a retained
\(\texttt{NonarchimedeanInd2ActionPacketSymmetrySource}\) whose action place and
transformed family are definitionally matched to the source \(\mathrm{Ism}\)
action-entry step.  From this matched boundary Lean derives the generated
\((\Ind1,\Ind2)\) relation, the place-audited quotient relation, record-image
invariance, selected q-region equalities, and finally the finite \(C_\Theta\)
dichotomy.  The remaining payload at this boundary is the paper-native
construction of the raw tensor-label witnesses from local
Frobenioid/log-Kummer geometry.  The signed pre-ledger transfer has been
factored through a Step~(xi) log-volume source: finite and generated q-values
are compared by their q-region log-volumes, and finite and generated
\(\theta\)-values by their theta-hull log-volumes, before Lean derives the old
q/theta signed equalities.
The finite handoff audit has now been lowered to this matched identified source.
Its audit records the finite signed equalities, the finite possible-image
identification, the raw tensor-label witness, the induced matched packet-action
witness for same-theta finite packets, the source-level nonarchimedean
\((\Ind2)\) packet-action audit, and the recovered local label-transport audit.
Thus the preferred review point is now the five-component local-tensor
calibration boundary, before the raw tensor-label and matched
\((\Ind2)\) packet-action witnesses are assembled and before the ordered-real
dichotomy is invoked.
The theta-pilot possible-image boundary has also been tightened.  The
class-indexed and lattice-key image-law constructors now have
procession-normalized entry points: instead of receiving an arbitrary
\texttt{IndeterminacyData} record, they consume the finite
\(F_\ell\)-averaged procession log-volume source.  Lean then derives the old
typed indeterminacy package, including \((\Ind1)\) and \((\Ind2)\)
log-volume preservation and the \((\Ind3)\) upper-semi inequality, before
constructing the quotient possible-image family and the selected \(q\)-region.
This boundary has now been lowered one step further by
\texttt{LogThetaLabelProcessionUpperSemiSource}: for each theta-pilot class it
supplies label-wise log-theta procession values indexed by \(Z/\ell Z\), and
\Lean{} constructs the finite average, proves the \(\#(Z/\ell Z)=\ell\)
normalization, derives the upper-semi comparison source, and enters the same
one-sided Theorem~3.11 constructors.  Thus the remaining mathematical payload
is no longer an averaged indeterminacy object; it is the paper-native source of
the label-wise log-volume family and its source/target average alignments from
the log-Kummer/log-link geometry.
The Remark~3.9.5 hull boundary has also been lowered from an abstract
intersection-closed predicate to a product-hull source that matches the
paper's \(\lambda\cdot O\) description.  The declaration
\[
\texttt{IUTStage1Remark395ProductHullSystemSource}
\]
carries a family of product hulls, their log-volumes, and for each region a
distinguished parameter whose product hull is the intersection of all product
hulls containing that region.  From this data \Lean{} constructs the ordinary
\texttt{IUTStage1Remark395HolomorphicHullSystem}; the experiment endpoint proves
that \(\phi(P)\) is exactly this selected product hull, contains \(P\), is
minimal among product hulls containing \(P\), and has the stated product-hull
log-volume.
There is now a direct-product constructor for this boundary,
\[
\texttt{IUTStage1Remark395DirectProductHullSystemSource}.
\]
Here a product hull is a literal coordinate product and the selected
intersection parameter is the family of coordinate projections of \(P\).
\Lean{} proves that this coordinate-projection product is the intersection of
all product hulls containing \(P\), then projects to
\texttt{IUTStage1Remark395ProductHullSystemSource}.  Thus this layer no
longer supplies the product-hull intersection law as an independent field.
This product-hull source now has a principal scalar-multiple refinement,
\[
\texttt{IUTStage1Remark395PrincipalProductHullSystemSource}.
\]
It records the local integer/direct-product region \(O\), scalar maps
\(\lambda\cdot(-)\), nonzero-parameter witnesses, and principal hulls of the
source-paper form \(\lambda\cdot O\).  It then derives the previous
\texttt{IUTStage1Remark395ProductHullSystemSource}.  Thus the hull boundary
can distinguish a genuinely Remark~3.9.5(i)-shaped product hull from an
arbitrary family of subsets before the analytic construction of the scalars is
completed.
The supplied principal-minimality law has now been narrowed further by
\[
\texttt{IUTStage1Remark395DirectProductPrincipalHullSystemSource}.
\]
This constructor starts from the direct-product hull theorem and a scalar
presentation of each principal region.  Its remaining source equality is the
pointwise identification \(\lambda\cdot O=\prod_v H_v(\lambda)\); once that is
available, \Lean{} derives the principal intersection/minimality law from the
coordinate-projection product-hull theorem.  Thus the principal layer no longer
has to restate the whole ``smallest \(\lambda\cdot O\) containing \(P\)''
property when its scalar images have already been matched to direct-product
hulls.
This equality boundary has now been factored once more by
\[
\texttt{IUTStage1Remark395ScalarImageDirectProductHullSource}.
\]
Instead of accepting the extensional equality
\(\lambda\cdot O=\prod_v H_v(\lambda)\), this source records the two
directional scalar-image laws: scalar multiples of local-integer points land in
the corresponding direct-product hull, and every direct-product-hull point has
a scalar preimage in \(O\).  \Lean{} proves the set equality from these two
laws and then constructs the direct-product principal hull source above.  Thus
the next valuation/local-ring layer can target concrete image and preimage
statements rather than a monolithic equality of subsets.
The product-level image/preimage laws have now been pushed down to coordinate
factors by
\[
\texttt{IUTStage1Remark395CoordinateScalarImageDirectProductHullSource}.
\]
Here \(O\) is the literal product of local integer factors \(O_v\), and
\(\lambda\cdot(-)\) is assembled coordinatewise from local scalar maps
\(\lambda_v\cdot(-)\).  The source only supplies the one-place assertions
\(\lambda_v O_v\subseteq H_v(\lambda)\) and the corresponding local preimage
statement for points of \(H_v(\lambda)\).  \Lean{} combines these coordinate
witnesses by dependent choice to prove the global scalar-image landing and
preimage laws, then constructs the scalar-image direct-product hull source.
Thus the next finite-extension valuation step can work one local factor at a
time.
There is now a stricter scalar-parameter version of this coordinate boundary:
\[
\texttt{IUTStage1Remark395ScalarParameterDirectProductHullSource}.
\]
This source no longer asks for local image/preimage laws for arbitrary subsets.
Instead each coordinate has an actual scalar-parameter type and a named local
region \(H_v(\lambda_v)\) satisfying the source-shaped equality
\[
H_v(\lambda_v)=\lambda_v\cdot O_v .
\]
\Lean{} derives the product landing law, product preimage law, and equality
between the principal scalar-image hull and the direct-product hull for the
product scalar parameter.  This is the current lowest scalar-image boundary
before the finite-extension valuation model supplies the concrete local
parameters and proves the equality \(H_v(\lambda_v)=\lambda_v O_v\).
The principal hull presentation is now tied to the valuation-ball local-ring
cover.  The declaration
\[
\texttt{IUTStage1Remark395PrincipalValuationBallProductHullCoverSource}
\]
carries a valuation-ball factor-calibrated Haar tensor-packet cover together
with a principal product-hull source, identifies the valuation cover's hull
system with the principal hull system, and identifies \(O\) with the anchor
valuation-ball direct-product cell.  Its endpoint proves that the selected
principal hull \(\lambda\cdot O\) is the same subset as the valuation-ball
direct-product cell union, that its log-volume is the calibrated cell sum, and
that the same valuation cover still projects to the adjusted Ob3/Ob5
determinant source.  This does not construct the analytic scalar parameters
from the source papers, but it removes a previous separation between the
\(\lambda\cdot O\) hull notation and the nonarchimedean local-ring/Haar cover
used by the determinant route.
There is now also a product-carrier version of this valuation-ball bridge,
\[
\texttt{IUTStage1Remark395DirectProductPrincipalValuationBallProductHullCoverSource}.
\]
Its valuation cover lives on an actual dependent product, and its principal
hull source is the direct-product-backed scalar source above.  The endpoint
therefore identifies the selected \(\lambda\cdot O\) hull first with the
coordinate/direct-product hull selected by the projection construction, then
with the valuation-ball direct-product cell union, and finally carries the same
adjusted Ob3/Ob5 determinant normalization handoff.  The remaining scalar
obligation is now just the per-parameter analytic equality between the source
paper's scalar image \(\lambda\cdot O\) and the corresponding valuation/direct
product hull.
This valuation-ball bridge has also been lowered to the scalar-image source:
\[
\texttt{IUTStage1Remark395ScalarImageValuationBallProductHullCoverSource}.
\]
It consumes the two directional scalar-image laws, constructs the
direct-product principal hull source internally, and then projects through the
same valuation-ball determinant route.  Its endpoint therefore keeps the
valuation cover, calibrated cell-sum log-volume, and adjusted Ob3/Ob5 handoff,
but the scalar trust boundary exposed at this product-carrier level is no
longer a subset equality.  It is precisely the landing and preimage pair that
the next finite-extension valuation/local-ring construction must prove.
The coordinate-local version of this same valuation bridge is now exposed as
\[
\texttt{IUTStage1Remark395CoordinateScalarImageValuationBallProductHullCoverSource}.
\]
It starts with the coordinate source above, constructs the scalar-image
valuation cover internally, and keeps the selected principal hull identified
with both the direct-product hull and the valuation-ball direct-product cell
union.  Consequently the adjusted Ob3/Ob5 determinant handoff can now be
reviewed at a boundary whose remaining scalar hypotheses are one-place
statements for the local factors \(O_v\) and \(H_v(\lambda)\), rather than
global statements about \(\lambda\cdot O\).
The selected scalar-parameter version of this valuation bridge is now exposed
as
\[
\texttt{IUTStage1Remark395SelectedScalarParameterValuationBallProductHullCoverSource}.
\]
It combines the scalar-parameter source with the valuation-ball cover by
choosing the product scalar parameter \((\lambda_v)_v\) whose local regions
\(H_v(\lambda_v)\) are exactly the coordinate projections of the current
possible-image union.  \Lean{} then proves that the selected scalar image
\(\lambda\cdot O\) is the direct-product hull selected by the holomorphic hull
operator and hence the valuation-ball direct-product cell union used by the
adjusted Ob3/Ob5 determinant source.  This leaves the next finite-extension
valuation task in its sharpest current form: construct the actual local
parameters \(\lambda_v\) and prove \(H_v(\lambda_v)=\lambda_v O_v\) from the
local IUT source data.
This scalar-parameter source has now been lowered once more to actual local
multiplication by nonzero elements:
\[
\texttt{IUTStage1Remark395NonzeroScalarMultiplicationDirectProductHullSource}.
\]
Here the parameter type at a place \(v\) is the subtype of nonzero local
scalars, the scalar action is the local multiplication map
\(x\mapsto \lambda_v x\), and the region \(H_v(\lambda_v)\) is defined as the
image of \(O_v\) under this map.  Consequently the equality
\[
H_v(\lambda_v)=\lambda_v O_v
\]
is no longer a supplied field at this boundary; it is the defining
construction from which \Lean{} derives the product landing, product preimage,
and principal-hull/direct-product equality.
The valuation-ball determinant handoff has the corresponding nonzero-scalar
form
\[
\texttt{IUTStage1Remark395NonzeroScalarMultiplicationValuationBallProductHullCoverSource}.
\]
Its endpoint verifies that the selected nonzero scalar image is still the
holomorphic family hull and the valuation-ball direct-product cell union used
by the adjusted Ob3/Ob5 determinant source.  The remaining local-field task is
therefore more specific: identify the source-paper scalar parameters as
nonzero elements of the local factors and connect the local integer factors
\(O_v\) to the valuation-ring/unit-ball construction already present in the
Haar normalization branch.  This second connection has now been formalized at
the product-cover boundary by
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalarMultiplication}\\
\quad\texttt{ProductHullCoverSource}.
\end{array}
\]
This source keeps the valuation-cover place index explicit and records a
coordinate-to-place selector.  At the anchor chart it requires each selected
compact-open valuation ball to be the unit ball \(\mathcal{O}_v=\{x\mid
\|x\|_v\leq 1\}\), proves that the anchor local factor is the realized ring of
integers, derives the global equality
\[
  O=\prod_v O_v=\text{anchor valuation direct-product cell},
\]
and then constructs the previous nonzero-scalar valuation cover.  Thus the
\(\lambda_v O_v\) hull now enters the adjusted Ob3/Ob5 determinant route
through valuation-unit-ball provenance, not through a separately supplied
global anchor-cell equality.  What remains is to construct the
coordinate-to-place selector and the nonzero scalars from the source-paper
Frobenioid/Kummer local data rather than pass them as source fields.
This valuation-ball provenance has now been lifted to the finite-divisor
vertical-\(IQ\) endpoint.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395PrincipalValuationBallBackedConstructorBacked}\\
\quad\texttt{ConstructedHullDeterminantFiniteDivisorVerticalIQSource}
\end{array}
\]
requires the constructor-backed adjusted Ob3/Ob5 source to be the
record-canonical form of the adjusted determinant source projected from the
principal valuation-ball cover.  From this equality \Lean{} derives the
principal hull-operator equality, the equality between the valuation-ball
possible-image union and the Theorem~3.11 possible-image union, and the
identity between the selected route hull and the valuation-ball direct-product
cell union.  The public endpoint
\[
\begin{array}{l}
\texttt{remark395PrincipalValuationBallBackedConstructorBackedConstructed}\\
\quad\texttt{Ob3Ob5AdjustedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_cThetaDichotomyWithPrincipalValuationBallAudit}
\end{array}
\]
then returns this valuation-ball audit next to the same finite-divisor
vertical-\(IQ\) \(C_\Theta\) dichotomy.
There is also a canonical-scale specialization of this endpoint:
\[
\begin{array}{l}
\texttt{remark395PrincipalValuationBallBackedConstructorBackedConstructed}\\
\quad\texttt{Ob3Ob5AdjustedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_canonicalCThetaScaleDichotomyWithPrincipalValuationBallAudit}.
\end{array}
\]
Here the scale is not supplied as an external real number.  It is the local
source-attached value
\[
  C_\Theta^{\mathrm{can}}=
  \frac{\theta_{\mathrm{signed}}}{-q_{\mathrm{signed}}},
\]
and the bound
\[
  \theta_{\mathrm{signed}}\le
  C_\Theta^{\mathrm{can}}\cdot(-q_{\mathrm{signed}})
\]
is derived in \Lean{} from q-pilot positivity by cancellation.  The returned
\texttt{PrincipalValuationBallBackedCanonicalCThetaScaleAudit} keeps both the
valuation-ball record audit and the constructor-backed hull/determinant bridge
audit in the statement, so this endpoint no longer takes
\texttt{thetaSigned\_le\_cTheta\_absLogQ} as a hypothesis at this local source
boundary.  It is still a local canonical scale for the present source package,
not yet a construction or identification of Mochizuki's global
\(C_\Theta\)-constant from the full IUT papers.
The valuation-unit-ball/nonzero-scalar product source now has the analogous
finite-divisor boundary wrapper.  The new source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalarBacked}\\
\quad\texttt{ConstructorBackedConstructedHullDeterminantFiniteDivisor}\\
\quad\texttt{VerticalIQSource}
\end{array}
\]
contains the principal valuation-ball finite-divisor source, the literal
local product scalar source, and an explicit carrier equivalence from the
product carrier to the target real-line carrier.  Its transport audit records
that the product local-integer region, selected nonzero scalar image, and
valuation-unit-ball direct-product cover all transport to the same principal
\(\lambda_v O_v\) hull.  The public experiment endpoint
\[
\begin{array}{l}
\texttt{remark395ValuationUnitBallNonzeroScalarBackedConstructorBacked}\\
\quad\texttt{ConstructedOb3Ob5AdjustedHullDeterminantFiniteDivisor}\\
\quad\texttt{VerticalIQ\_canonicalCThetaScaleDichotomyWithTransportAudit}
\end{array}
\]
therefore exposes the same canonical-scale vertical-\(IQ\) dichotomy together
with the product-carrier/unit-ball transport provenance.  The remaining
source-facing gap has moved to constructing this carrier equivalence, the
coordinate-to-place selector, and the nonzero scalars from the actual
Frobenioid/Kummer local data.
This transport boundary has now been sharpened once more.  The reduced source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{FiniteDivisorTransportSynchronizationSource}
\end{array}
\]
does not ask separately for the transported valuation-cover equality.  It only
records the carrier equivalence, the transport of the local-integer region,
and the transport of the selected nonzero scalar image to the principal hull.
\Lean{} then derives
\[
  e\bigl(\text{valuation unit-ball direct-product cover}\bigr)
  =\text{principal }\lambda_vO_v\text{ hull}
\]
from the product-cover theorem
\[
\begin{array}{l}
\texttt{selectedScalarImageHull\_eq}\\
\quad\texttt{\_valuationBallDirectProductCellUnion}.
\end{array}
\]
The experiment endpoint
\[
\begin{array}{l}
\texttt{remark395ValuationUnitBallNonzeroScalarTransportSynchronized}\\
\quad\texttt{ConstructorBackedConstructedOb3Ob5AdjustedHullDeterminant}\\
\quad\texttt{FiniteDivisorVerticalIQ\_canonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTransportAudit}
\end{array}
\]
therefore reaches the same canonical-scale vertical-\(IQ\) dichotomy with one
fewer transported equality at the trust boundary.
The carrier side of the same route has also been separated into a charted
source.  Instead of supplying an arbitrary equivalence from the local product
carrier to the target real-line copy, the new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{TargetCarrierChartSource}
\end{array}
\]
records a product-to-real coordinate, a real-to-product realization, and the
two inverse laws.  \Lean{} derives the carrier equivalence
\[
  ((d:\delta)\to A_d)\simeq \texttt{Point target}
\]
from this chart, and the charted finite-divisor synchronization endpoint then
forwards to the reduced transport-synchronization route.  Thus the current
trust boundary has moved from an unstructured carrier equivalence to the
construction of the product real-coordinate chart itself.  The remaining
source-facing task is to build that chart from the actual Frobenioid/Kummer
local valuation data, together with the coordinate-to-place selector and
nonzero scalar preimage laws.
For the finite-divisor endpoint itself, this carrier requirement has now been
weakened once more to the actual data used by the comparison: a forward
transport into the target real-line copy.  The source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{TargetPointTransportSource}
\end{array}
\]
keeps the same valuation-unit-ball/nonzero-scalar product source and principal
valuation-ball source, but replaces the equivalence or inverse chart by a map
\[
  ((d:\delta)\to A_d)\longrightarrow \texttt{Point target}.
\]
The transported valuation-cover equality is again derived from the selected
scalar-image/product-cover theorem, and the public endpoint reaches the same
canonical-scale vertical-\(IQ\) dichotomy while returning a
\texttt{TargetPointTransportAudit}.  Thus inverse reconstruction of the local
product carrier is no longer part of the finite-divisor trust boundary.  The
remaining source-facing construction is the forward target log-coordinate map
itself, with proofs that it sends the local integer region and selected
nonzero scalar image to the corresponding principal \(\lambda_vO_v\) regions.
This has now been sharpened to a coordinate-derived target transport source.
The new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{CoordinateTargetTransportSource}
\end{array}
\]
does not accept an arbitrary map to \(\texttt{Point target}\).  It takes a real
coordinate map
\[
  ((d:\delta)\to A_d)\longrightarrow \mathbb{R}
\]
together with coordinate descriptions of the target principal local-integer
region and selected principal hull.  \Lean{} proves the elementary wrapper
lemma that the induced map \(x\mapsto\{\texttt{coord}:=f(x)\}\) has the
required point-level image if and only if the coordinate image has the required
real-region image.  The coordinate-derived endpoint then forwards through
\texttt{TargetPointTransportSource}.  Thus the remaining transport obligation
is now stated at the real log-coordinate level: construct the coordinate map
from the local valuation/Kummer data and prove the two coordinate image
equalities.
The selected-hull half of this obligation has now been pushed one layer closer
to Remark~3.9.5(i).  The source-core theorem
\[
\texttt{selectedScalarImageHull\_eq\_selectedNonzeroScalar\_image}
\]
proves that the selected product hull is literally the image
\(\lambda\cdot O\) of the local integer product region under the selected
coordinatewise nonzero scalar multiplication.  The new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{SelectedImageCoordinateTargetTransportSource}
\end{array}
\]
therefore asks for the target coordinate image of this explicit
\(\lambda\cdot O\) region, not for the already-packaged
\texttt{selectedScalarImageHull} image.  \Lean{} rewrites through the
source-core equality and then applies the coordinate-derived endpoint.  The
remaining selected-hull transport payload is now the real-coordinate image law
for an explicit nonzero-scalar multiplication image.
The local-integer half has now been pushed down in the same way.  The
valuation-unit-ball product source already proves
\[
  \texttt{localIntegerRegion}=
  \texttt{valuationCover.directProductCell valuationCover.anchor},
\]
i.e., the local integer product is the anchor product of valuation unit balls
\(O=\prod_v O_v\).  The new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{ValuationAnchorCoordinateTargetTransportSource}
\end{array}
\]
therefore states the local-integer coordinate image for this explicit anchor
valuation-cell product and states the selected-hull coordinate image for the
explicit \(\lambda\cdot O\) image.  \Lean{} derives the previous selected-image
coordinate transport source by rewriting through these two source equalities.
Thus both coordinate-image transport obligations are now attached to concrete
Remark~3.9.5(i) regions \(O\) and \(\lambda O\), rather than to packaged
endpoint regions.
The target coordinate map itself has now been restricted one step further.  The
new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{FiniteLocalLogCoordinateTargetTransportSource}
\end{array}
\]
does not accept an arbitrary real-valued coordinate functional on the source
product carrier.  It carries local readings
\[
  \ell_v:((d:\delta)\to A_d)\longrightarrow \mathbb{R}
\]
for the finite valuation-place set and defines the target coordinate by
\[
  x\longmapsto \sum_v \ell_v(x).
\]
\Lean{} then projects this finite local log-coordinate source to the
valuation-anchor coordinate transport source.  The remaining image laws are
therefore the two explicit statements
\[
  \Big(\sum_v\ell_v\Big)(O)=R_O,\qquad
  \Big(\sum_v\ell_v\Big)(\lambda O)=R_{\lambda O},
\]
where \(R_O\) and \(R_{\lambda O}\) are the real-coordinate descriptions of the
principal local-integer region and selected principal hull on the target
real-line copy.  Thus the arbitrary target-coordinate-map freedom has been
removed from this boundary; the next mathematical task is to construct the
local log-coordinate readings from the valuation/Kummer model and prove these
two image equalities.
The scalar finite-sum image laws have now been reduced to a product-image
statement for the tuple of local coordinates.  The helper
\[
  \texttt{finiteLocalLogCoordinateSumRegion}
\]
defines the real region obtained from local coordinate regions
\(R_v\subseteq\mathbb{R}\) by
\[
  \Big\{\sum_v r_v\mid r_v\in R_v\Big\}.
\]
The theorem
\[
  \texttt{finiteLocalLogCoordinateSumRegion.image\_sum\_eq\_of\_vector\_image}
\]
proves that if
\[
  x\longmapsto (v\mapsto \ell_v(x))
\]
maps a source region onto the product of the local coordinate regions, then
\(x\mapsto\sum_v\ell_v(x)\) maps the same source region onto the corresponding
sum region.  The new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinateProductImageTargetTransportSource}
\end{array}
\]
therefore supplies the vector-valued image laws for \(O\) and \(\lambda O\);
\Lean{} derives the finite-sum transport source and then enters the same
valuation-anchor finite-divisor endpoint.  The remaining source-facing problem
is now the local product-coordinate theorem for
\((\ell_v)_v(O)\) and \((\ell_v)_v(\lambda O)\), rather than an unstructured
image theorem for the scalar sum.
That product-coordinate theorem has now been split into its two source-facing
halves.  The lemma
\[
  \texttt{localLogCoordinateVector\_image\_eq\_product\_of\_landing\_and\_preimage}
\]
proves the vector-valued product image equality from coordinatewise landing
\[
  x\in S\Rightarrow \ell_v(x)\in R_v\quad\text{for all }v
\]
and simultaneous realization
\[
  (r_v)_v\in\prod_vR_v\Rightarrow
  \exists x\in S,\ \ell_v(x)=r_v\quad\text{for all }v.
\]
The corresponding
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinatePreimageTargetTransportSource}
\end{array}
\]
now supplies these landing and simultaneous-preimage laws for \(O\) and
\(\lambda O\); \Lean{} derives the product-image source, then the finite-sum
source, and finally the valuation-anchor endpoint.  Thus the remaining
mathematical construction is the actual local analytic/Kummer realizer for
compatible tuples of valuation-place log coordinates, not a supplied
vector-valued image equality.
The simultaneous-preimage half has now been lowered once more to a direct
product assembly theorem.  The generic lemma
\[
  \texttt{simultaneousLocalLogCoordinatePreimage\_of\_placewise\_factor\_preimages}
\]
states that if each placewise coordinate value \(r_v\in R_v\) has a local
factor preimage \(b_v\), and if admissible choices \((b_v)_v\) assemble to a
source point whose local log-coordinate readings are exactly the factor
coordinates, then the whole tuple \((r_v)_v\) has a simultaneous preimage.  The
source record
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinatePlacewisePreimageTargetTransportSource}
\end{array}
\]
uses this lemma for both the anchor region \(O\) and the selected scalar image
\(\lambda O\).  Thus the remaining preimage payload is no longer a global
existential statement over the product carrier; it is the placewise local
scalar-image/preimage theorem together with the direct-product assembly law
that identifies the assembled point with the prescribed log-coordinate tuple.
The coordinatewise landing half has also been lowered to local factor data.
The lemma
\[
  \texttt{localLogCoordinate\_lands\_of\_placewise\_factor\_landing}
\]
proves landing in \(\prod_vR_v\) from a point-to-factor projection, membership
of that factor in the appropriate local source region, agreement of the source
local coordinate with the factor coordinate, and the local factor landing
theorem.  The new
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinateFactorwiseTargetTransportSource}
\end{array}
\]
uses this landing lemma together with the placewise-preimage assembly theorem,
so the public route now derives both sides of the vector-valued product-image
equality from factorwise local data.
The projected factorwise refinement further removes the abstract
point-to-factor and assembly maps from this boundary.  A valuation-place/product
index equivalence \(e:\gamma_{\mathrm{loc}}\simeq\delta\) identifies each local
place with an actual coordinate of the dependent product \(\prod_{d:\delta}A_d\).
The source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinateProjectedFactorwiseTargetTransportSource}
\end{array}
\]
sets the local factor carrier at \(v\) to \(A_{e(v)}\), takes projection to be
evaluation at \(e(v)\), and takes assembly to be the standard dependent-product
reindexing equivalence \(\texttt{Equiv.piCongrLeft}\).  The corresponding public
endpoint therefore routes to Corollary 3.12 after proving the factorwise
transport laws from product evaluation and reindexing.  The remaining local-log
payload at this boundary is the source-facing image description of the coordinate
regions \(O_v\) and \(\lambda_vO_v\) under the chosen local logarithmic
coordinate, together with the valuation-place/product-index identification.
This image-description boundary has now been lowered once more.  The source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{ValuationLogImageProjectedFactorwiseTargetTransportSource}
\end{array}
\]
defines the local real regions themselves as
\[
  \ell_v(O_v),\qquad \ell_v(\lambda_vO_v),
\]
where \(\ell_v\) is the selected local valuation/log-coordinate map.  The
previous projected-factorwise source is obtained by projection, and the image
equalities for \(O_v\) and \(\lambda_vO_v\) are now definitional theorems.
Thus this boundary no longer asks for separate local coordinate-image laws;
at that level, the remaining inputs were the actual construction of the local
maps \(\ell_v\) from the valuation/Kummer model and the global finite-sum
identifications of the target real-line principal regions.
The finite-sum target boundary has now been lowered another step.  The source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{ValuationLogFiniteSumTargetPointSource}
\end{array}
\]
defines the target point of a local product element \(x\) by the coordinate
\[
  \sum_v\ell_v(x_v).
\]
It carries the typed compatibility saying that the source's coordinate-place map
agrees with the chosen valuation-place/product-index equivalence, then proves
internally that the coordinate images of \(O=\prod_vO_v\) and
\(\lambda O=\prod_v\lambda_vO_v\) are exactly the finite-sum regions
\(\sum_v\ell_v(O_v)\) and \(\sum_v\ell_v(\lambda_vO_v)\).  The remaining
synchronization at this lower boundary is point-level transport of these two
source regions to the principal finite-divisor target regions; the real-line
finite-sum equalities are no longer independent fields of the exact-theta
constructor.
This boundary has now been lowered again by
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{CoordinatePlaceValuationLogFiniteSumTargetPointSource}.
\end{array}
\]
Here the valuation-cover coordinate-place map is represented source-side by an
equivalence \(\delta\simeq\gamma_{\mathrm{local}}\).  Lean derives the previous
finite-sum synchronization law
\[
  \texttt{coordinatePlace}(e^{-1}(v))=v
\]
from the source equality \(\texttt{coordinatePlace}=e\).  Thus the remaining
coordinate-index work is no longer an arbitrary target-boundary compatibility;
it is the construction of this equivalence from the actual local valuation
indexing.
The local coordinate itself has now been lowered to a Haar log-volume source.
The new local source
\[
  \texttt{IUTStage1Remark395LocalFactorHaarLogCoordinateSource}
\]
assigns to a local factor \(x_v\) a local compact-open region \(U_{v,x_v}\) and
defines
\[
  \ell_v(x_v)=\mu_{\log,v}(U_{v,x_v})
\]
using the normalized finite-extension Haar log-volume source already present in
the valuation/Haar branch.  The corresponding finite-sum source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointSource}
\end{array}
\]
therefore projects to the coordinate-place finite-sum route with
\(\ell_v\) no longer a bare function.  Lean proves that the \(O_v\) and
\(\lambda_vO_v\) coordinate regions are images under normalized Haar
log-volume of the assigned local regions.
This has now been strengthened to a compact-open Haar source.  The local
declaration
\[
  \texttt{IUTStage1Remark395LocalFactorCompactOpenHaarLogCoordinateSource}
\]
uses the finite-extension compact-open topology/Haar normalization object,
requires every assigned \(U_{v,x_v}\) to satisfy the compact-open predicate,
and then projects to the normalized Haar log-coordinate source.  The finite
product declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{CompactOpenHaarLogCoordinateFiniteSumTargetPointSource}
\end{array}
\]
threads this compact-open provenance through the same target-point finite-sum
endpoint and exposes the compact-open Haar route at the experiment surface.
This has now been lowered one more step to centered valuation balls.  The local
declaration
\[
  \texttt{IUTStage1Remark395LocalFactorCenteredValuationBallHaarLogCoordinateSource}
\]
takes a proper ultrametric local factor together with the valuation-ball Haar
normalization source, defines
\[
  U_{v,x_v}:=\overline B(x_v,r_v),
\]
where \(r_v\) is the compact-open radius of the valuation-ball Haar source, and
proves that this closed ball is open by the ultrametric inequality and compact
by properness.  Thus the compact-open predicate is no longer supplied at this
boundary; it is constructed from the valuation-ball topology.  The finite product
source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPointSource}
\end{array}
\]
threads these centered balls through the same finite-sum target map and projects
to the compact-open Haar route at the experiment surface.
This local boundary has now been lowered to the valued-field integer source.
The declaration
\[
  \texttt{IUTStage1Remark395LocalFactorValuedFieldIntegerCenteredValuationBallHaarLogCoordinateSource}
\]
starts from a valued-field integer proper-ultrametric Haar normalization source:
the local ring is the actual valued-field integer subring \(\mathcal O_K\), the
valuation topology is the valued-field ultrametric topology, and the centered
coordinate is still
\[
  x_v\longmapsto \mu_{\log}(\overline B(x_v,r_v)).
\]
Lean constructs the proper-ultrametric valuation-ball Haar source used by the
centered-ball layer and then constructs the centered local coordinate source.
The finite product source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{ValuedFieldIntegerCenteredValuationBallHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointSource}
\end{array}
\]
threads these valued-field integer local coordinates through the same target
finite sum and exposes the corresponding experiment route and Step~(xi)
constructor.
The same boundary has now been specialized to the concrete base local field
\(\mathbb Q_p\).  The local declaration
\[
  \texttt{IUTStage1Remark395LocalFactorPadicCenteredValuationBallHaarLogCoordinateSource}
\]
starts from the \(p\)-adic proper-ultrametric Haar source: the integer ring is
identified with \(\mathbb Z_p\), the residue prime is \(p\), the normalization
degree is \(1\), and the uniformizer action is multiplication by \(p\).  It
projects to the valued-field integer centered-ball source without adding a new
abstract local-ring field.  It now also projects to the finite-extension
centered-ball source for \(K=\mathbb Q_p\), proving that the same closed-ball
local region and normalized Haar log-coordinate are obtained after passing
through the degree-one finite-extension normalization route.  The finite-product
declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationUnitBallNonzeroScalar}\\
\quad\texttt{PadicCenteredValuationBallHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointSource}
\end{array}
\]
uses valuation places as the product coordinates and assigns to each place
\(v\) an actual local carrier \(\mathbb Q_{p_v}\).  Its target coordinate is
definitionally
\[
  (x_v)_v\longmapsto
    \sum_v \mu_{\log}\bigl(\overline B(x_v,r_v)\bigr),
\]
and the experiment surface now reaches the same topology/Haar Ob5--Ob7
canonical-scale finite-divisor route through this \(p\)-adic source.
The Milestone 2 hull layer now contains a direct formalization of
Remark 3.9.5(ii)--(iii)'s hull-map skeleton and approximant family.  The hull
map \(\phi(P)\) is represented by a closure operator; \Lean{} exposes the
Remark 3.9.5(ii) laws
\[
  \phi(H)=H,\qquad P\subseteq\phi(P),\qquad
  P_1\subseteq P_2\Rightarrow \phi(P_1)\subseteq\phi(P_2),
\]
together with idempotence \(\phi(\phi(P))=\phi(P)\).  For a region \(P\), an
approximant record carries a hull \(H\), proves \(H\subseteq\phi(P)\), and proves
\[
  \mu_{\log}(P)\le \mu_{\log}(H)\le \mu_{\log}(\phi(P)).
\]
For the Corollary 3.12 possible-image union, the public endpoints now also
return \(P\subseteq\phi(P)\), each \(P_i\subseteq\phi(P)\), q-pilot
containment in \(\phi(P)\), and \(\phi(\phi(P))=\phi(P)\).
The \(\Xi(P)\)-part of Remark 3.9.5(iii) is now represented at the same
finite level: an exact hull approximant is a \(\Phi(P)\)-approximant \(H\)
with \(\mu_{\log}(H)=\mu_{\log}(P)\).  When \(P\) is already closed under
the hull operator, \Lean{} constructs the canonical exact approximant.
The possible-image Step (xi) source can now also be built from such an exact
approximant and a weighted determinant source; in that route \Lean{} derives
\(\mu_{\log}(P)=\mu_{\log}(H)=\det_{\log}\), rather than only the inequality
\(\mu_{\log}(P)\le\mu_{\log}(H)\).
Remark 3.9.5(iv)'s statement \(\phi(P)\in\Phi(P)\), hence
\(H_{\Phi(P)}=\phi(P)\), is now represented by a finite approximant-family
object.  Every member of the family is a \(\Phi(P)\)-approximant inside
\(\phi(P)\), and if one distinguished member is the canonical hull, \Lean{}
proves that the family union and its log-volume are exactly those of
\(\phi(P)\).
The corresponding \(\Xi(P)\)-family statement is also represented.  Each
member is an exact approximant with log-volume \(\mu_{\log}(P)\); if the
family contains the canonical hull, its union is \(\phi(P)\).  In the special
case where \(P\) is already closed under hull formation, the canonical
one-point \(\Xi(P)\)-family has union \(P=\phi(P)\) and log-volume
\(\mu_{\log}(P)\), matching Remark 3.9.5(iv)'s closed-region case.
For possible-image families, the exact \(\Xi(P_B)\) boundary has now been
sharpened: \texttt{IUTStage1Remark395PossibleImageExactXiFamilySource}
does not accept an arbitrary exact family, but only the source calibration
\[
  \mu_{\log}(\phi(P_B))=\mu_{\log}(P_B).
\]
From this equality \Lean{} constructs the canonical exact approximant and a
\(\Xi(P_B)\)-family over either the one-point index or the same index type as
a chosen \(\Phi(P_B)\)-family.
At the possible-image-family level, this exact-approximant family now also
interfaces with the Ob5 upper-semi quotient: if a \(\Xi(P_B)\)-family is
available and one possible image is nonempty, \Lean{} proves
\[
  H_{\Xi(P_B)}=\phi(P_B)
\]
and proves that the quotient image of \(H_{\Xi(P_B)}\) is the same collapsed
point as the quotient image of that nonempty possible image.
The same source-facing family now has an explicit Ob6 log-volume endpoint:
for a \(\Phi(P_B)\)-family and an exact \(\Xi(P_B)\)-family either supplied
directly or constructed from
\(\mu_{\log}(\phi(P_B))=\mu_{\log}(P_B)\), \Lean{}
proves
\[
  H_{\Phi(P_B)}=\phi(P_B)=H_{\Xi(P_B)}
\]
and records the inequalities
\[
  \mu_{\log}(P_B)\leq\mu_{\log}(H_{\Phi(P_B)}),\qquad
  \mu_{\log}(P_B)\leq\mu_{\log}(H_{\Xi(P_B)}),
\]
together with the corresponding inequalities for each selected possible image
\(P_\beta\).  Thus Remark~3.9.5(Ob6)'s warning that estimates must pass through
hull-approximant unions, rather than through the raw possible-image region
alone, is now a named checked source endpoint.
The next source-facing checkpoint is also present.  The Ob7 log-Kummer
compatibility source attaches a constructed hull/determinant bridge to a finite
\(F^{\times\mu}\)-prime-strip lift.  Its endpoint proves that the q-region
log-volume is bounded by the retained prime-strip global log-volume, while
also recording the prime/place square, local realified-Frobenioid
log-volume compatibility, and Frobenius-like unit-character compatibility.
This keeps the comparison object in the Frobenioid/log-Kummer language
required by Remark~3.9.5(Ob7), instead of collapsing immediately to a bare
real number.
The canonical hull \(\phi(P)\) is itself an approximant, and every approximant
is fixed by hull formation.  This is the compactness guard emphasized in the
paper: the indeterminacy in choosing a hull approximant remains inside
\(\phi(P)\).
The bounded-family version of Remark 3.9.5(v)--(vi) is now represented by a
family-hull quotient source.  For a family \(P_\beta\), the code forms the hull
of the union, uses it as the collapsed subset in the upper-semi quotient, and
proves that any two nonempty possible regions have the same quotient image.
This quotient source is now connected directly to the typed Theorem~3.11
indeterminacy layer.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1MultiradialThetaImages}\\
\quad\texttt{.remark395Ob5QuotientEndpoint\_of\_related}
\end{array}
\]
starts from a multiradial possible-image package with its explicit
\((\Ind1),(\Ind2),(\Ind3)\) quotient relation, forms the corresponding
Remark~3.9.5 family \(P_B\), and proves that related choices have equal
possible-image regions and equal upper-semi quotient images after collapsing
\(\phi(P_B)\).  The experiment surface exposes the same bridge as
\[
\begin{array}{l}
\texttt{multiradialThetaImages\_remark395IndeterminacyOb5Endpoint}.
\end{array}
\]
This Theorem~3.11 bridge now has a strengthened Ob5--Ob7 endpoint,
\[
\begin{array}{l}
\texttt{IUTStage1MultiradialThetaImages}\\
\quad\texttt{.remark395Ob5Ob6Ob7Endpoint\_of\_related}
\end{array}
\]
with experiment wrapper
\[
\begin{array}{l}
\texttt{multiradialThetaImages}\\
\quad\texttt{\_remark395IndeterminacyOb5Ob6Ob7Endpoint}.
\end{array}
\]
The endpoint forms the same Remark~3.9.5 possible-image family from the
typed \((\Ind1),(\Ind2),(\Ind3)\) quotient, proves the Ob5 quotient collapse for
related choices, threads the family through the Ob6 \(H_{\Phi(P_B)}\) and
\(H_{\Xi(P_B)}\) log-volume inequalities, and then attaches the Ob7
\(F^{\times\mu}\)-prime-strip source.  Two synchronization equalities require the
Ob7 hull/determinant bridge to use the same possible-image family and the same
holomorphic hull operator, so this audit does not allow an unrelated
prime-strip log-volume comparison to masquerade as the Theorem~3.11
possible-image comparison.
As before, equality across an \((\Ind3)\) generator is not inferred from the
one-sided Step~(x) upper-semi inequality; it is precisely the explicit
image-invariance field of the typed multiradial quotient package.
The map statement in Remark 3.9.5(v) is now lifted to this bounded-family
source: any set map from a nonempty possible region \(P_i\) into another
possible region \(P_j\) induces, after quotienting by the family hull, the same
image as the quotient map on \(P_i\) itself.
The ``formal empty set'' extension in the same remark is represented by a
finite formal-intersection system: a family of nonempty subsets of the
collapsed subset \(S\).  \Lean{} proves that every component has quotient image
\(\{S\}\), that all component images agree, and that component maps induce the
same collapsed image after quotienting.
Remark 3.9.5(vi)'s expected-equivalence statement is also represented for the
bounded-family hull: for arbitrary nonempty regions \(A,B\), their quotient
images are both the collapsed point if and only if \(A\subseteq\phi(P_B)\) and
\(B\subseteq\phi(P_B)\).
The Ob5 compatibility of this quotient formalism with
\(\det^{\otimes M}(\phi(P_B))\) and \(\mu_{\log}(\phi(P_B))\) is now represented
at finite log-volume level: the same family hull that collapses the possible
regions is identified with the weighted determinant log-volume, and the
associated tensor-power normalization recovers this family-hull log-volume.
\Lean{} now also derives
\(\mu_{\log}(\bigcup_\beta P_\beta)\le\det_{\log}\) from hull monotonicity and
this determinant identification.  The public Ob5 endpoint exposes these facts
together with the expected-equivalence condition: for nonempty regions \(A,B\),
both quotient images are the collapsed family-hull point if and only if
\(A,B\subseteq\phi(P_B)\).
The Ob9 log-volume passage is now represented at the same finite hull level.
A realified semi-simplification correspondence between two hull shadows sends
closed hulls to closed hulls, has a two-sided inverse on closed hulls, and
preserves hull log-volume.  Applied to the bounded-family hull, \Lean{} proves
that the transported hull still has log-volume \(\det_{\log}\).  This is the
coarse log-volume content of Ob9; it is not yet a construction of the full
log-link or its arbitrary-iterate indeterminacy.
The Corollary 3.12 possible-image approximant source now projects the same
estimate directly, so the upper-ray route can read
\(\mu_{\log}(P)\le\det_{\log}\) from that source object.
Remark 3.9.6 is represented by a finite product-formula theorem: if the
log-link preserves the local log-volume at every place and the source and
target conversion ratios agree, then the weighted global arithmetic degree
sums agree.
This has also been specialized to the Corollary 3.12 possible theta-image
family, so the possible-image hull used by the upper-ray route and the Ob5
family-hull quotient/determinant source are definitionally the same hull.
The canonical specialization now exposes this family-union-to-determinant
estimate at its endpoint.
The Corollary 3.12 possible-image approximant source projects to this
family-hull quotient source, so the possible-image family used in the
upper-ray route also carries the corresponding choice-independence theorem.
Since the q-pilot region is contained in the chosen approximant and the
approximant lies in the same family hull, the code also proves that a nonempty
q-pilot region has the same family-hull quotient image as any nonempty
possible theta-image choice.
The same approximant now feeds the Step (xi) upper-ray constructor.  If the
\(q\)-pilot region lies in an approximant \(H\), and if
\(\mu_{\log}(H)\) is the determinant-normalized log-volume, then \Lean{}
derives
\[
  \mu_{\log}(q)\le \mu_{\log}(H)\le \mu_{\log}(\phi(P)),
  \qquad
  \mu_{\log}(q)\le \det_{\mathrm{norm}} .
\]
Thus this part of the corridor no longer has to use only the canonical hull
itself; it can use any certified hull-approximant inside \(\phi(P)\).
This has now been specialized to the possible-image union in Corollary 3.12.
One source object carries the family of possible theta images, the union \(P\),
a certified approximant \(H\in\Phi(P)\), \(q\subseteq H\), and determinant
normalization of \(\mu_{\log}(H)\).  The Step (x)-to-Step (xi) comparison is
now expressed by a named handoff proposition over this fixed corridor and hull
source.  Thus the two numerical identifications
\(\mu_{\log}(H)=\Ind3_{\mathrm{upper}}\) and
\(\mu_{\log}(q)=\overline{\mu}_{\log}(q)_{\mathrm{pre}\text{-}\Ind}\)
are no longer loose parameters of the endpoint; they are the explicit source
obligation required before the Step (xi-f) upper-ray datum is formed.
\Lean{} then derives the whole chain
\[
  \mu_{\log}(P)\le\mu_{\log}(H)\le\mu_{\log}(\phi(P)),
  \qquad
  \mu_{\log}(q)\le\mu_{\log}(H)\le\det_{\mathrm{norm}}.
\]
The determinant side has also been sharpened at finite log-volume level.
Following Remark 3.9.5(vii), (Ob3-1)--(Ob3-3), a localization summand now
carries a rank \(>1\), a bundle log-volume, a structure-sheaf adjustment, and
a positive weight.  A determinant source forms the finite weighted sum of the
adjusted summands, then derives the positive tensor-power log-volume and the
normalized determinant log-volume by definition.  This replaces supplied
tensor-power and normalized values for this new route, but it remains a
log-volume skeleton rather than a construction of arithmetic vector bundles.
The localization input itself has been refined one step further: a finite
direct-summand source computes the bundle log-volume as a sum of direct
summand log-volumes before projecting to the localization summand interface.
Thus the weighted determinant can now be built from finite direct-summand
localization sources.
The Ob3-1-2 structure-sheaf adjustment is also named explicitly.  A
structure-sheaf adjusted source carries
\[
  L_{\mathrm{adj}}=\sum_\gamma L_\gamma-L_{\mathcal O(-)}
\]
and proves that its weighted value is the same adjusted summand consumed by
the determinant source.  Thus the current determinant route separates direct
summands, subtraction of the \(\mathcal O(-)\) contribution, positive
weighting, tensor-power formation, and normalization as distinct Lean
interfaces.
The possible-image approximant route can now consume this weighted determinant
source directly.  The equality between the approximant log-volume
\(\mu_{\log}(H)\) and the weighted normalized determinant value is now carried
by a named Ob3-3 compatibility certificate.  After this certificate is supplied,
the old determinant record is only a projection used by the common upper-ray
interface.
At the package-ledger boundary, the hull/determinant source data can now be
constructed from a concrete common hull \(K\), a proof
\(P_{\mathrm{out}}\subseteq K\), and a determinant/log-volume estimate
\(\mu_{\log}(K)\le\theta_{\mathrm{signed}}\).  The resulting
\Lean{} endpoint returns target-union containment, the determinant bound,
all-target bounds, and equality between the package's named hull/determinant
bridge and this constructed bridge.  Thus the remaining source obligation is
the construction of \(K\) and its bound, not an opaque common-bound bridge.
A more source-shaped constructor specializes \(K\) to
\(\phi(P_{\mathrm{out}})\) for an abstract hull operator \(\phi\).  Its
endpoint proves that the bridge hull is definitionally this hull of the target
union, and reduces the source input to the determinant/log-volume estimate for
\(\phi(P_{\mathrm{out}})\) plus equality with the package's named bridge.
The Set-based holomorphic-hull shadow now induces the Region-level hull
operator and Region measure used by this package bridge when the underlying
type is the point set of a real-line copy.  The endpoint identifies the
Region hull with the original point-set hull, proves region containment, and
recovers monotonicity of the induced log-volume.
At the package level, this induced hull operator can now be used directly:
if the charted package measure is identified with the induced Region measure
and the point-set hull of \(P_{\mathrm{out}}\) satisfies the determinant
bound, then the hull/determinant source data is constructed from the
holomorphic-hull shadow.  The remaining bridge equality is explicit, so the
package cannot display one hull construction while proving with another.
The source package's theta-pilot possible-image record now also feeds the
canonical hull approximant directly: \Lean{} proves that its set-theoretic
union is exactly the package target union before applying the determinant
comparison.
The possible-image approximant source now feeds this package bridge in the
canonical case.  If its possible-image union is the package target union, its
chosen approximant is the canonical hull, the package measure is the induced
Region measure, and the normalized determinant value is at most
\(\theta_{\mathrm{signed}}\), then \Lean{} constructs the same
hull/determinant source data.  No general containment of an arbitrary
approximant is assumed.
This has been lifted to the Theorem 3.11 source constructor: the approximant
union may be tied to the source record's theta possible-image union, and the
record then supplies the equality with the package target union.  Thus the
constructor no longer needs prebuilt hull/determinant source data in this
canonical case.
The same constructor now accepts the finite weighted determinant source from
Remark 3.9.5(vii), (Ob3), directly.  The determinant bound is stated for the
weighted determinant log-volume, and \Lean{} derives the normalized determinant
bound consumed by the canonical hull bridge.
A further specialization constructs the approximant as the canonical hull
\(\phi(P)\) itself.  In the current route the q-pilot input may be containment
in the possible-image union \(P=\bigcup_i P_i\); \Lean{} then derives
q-pilot containment in \(\phi(P)\) from hull extensivity.  Thus direct
containment in \(\phi(P)\) is no longer a primitive input for this canonical
possible-image specialization.
Remark 3.9.5(vii), (Ob4), is represented at the same finite level: a naive
Frobenius/tensor-power log-volume object records the passage
\(L\mapsto M L\) for \(M>0\), and \Lean{} proves that normalized log-volume
recovers \(L\).  The weighted determinant source projects to this object, so
the \(M\)-th tensor-power copy does not add a further log-volume ambiguity in
the current corridor.  A comparison object also proves that two positive
tensor-power presentations with the same base log-volume have the same
normalized log-volume, even when the tensor degrees differ.  This has now been
upgraded to the Ob4-3 family form:
\texttt{IUTStage1TensorPowerTwistFamily} records a reference tensor-power
presentation and an arbitrary family of reconstructed twisted presentations
over the same base log-volume.  \Lean{} proves that every twist has the
reference normalized log-volume, that any two twists have equal normalized
log-volume, and that all normalized log-volume bounds are equivalent across the
twist family.  This is the finite log-volume reading of the source-paper
statement that tensor-power-twist indeterminacies have no substantive effect on
the estimates used in Corollary~3.12.
The package hull/determinant bridge now has an Ob4-shaped input form: a bound
on the normalized tensor-power log-volume of the weighted determinant source is
converted by \Lean{} to the determinant bound used by the canonical hull bridge.
In the canonical-hull form, this Ob4 input also derives the
approximant-equals-\(\phi(P)\) witness internally.  At the package boundary
the same canonical Ob4 route can now start from q-pilot containment in the
possible-image union \(P\); \Lean{} derives containment in \(\phi(P)\) before
constructing the hull/determinant bridge.
The same endpoint is exposed at the Theorem 3.11 source-record level, so the
possible-image union used by the canonical hull is the record's multiradial
theta-image union before being identified with the package target union.
For arbitrary possible-image families that are later identified with the
Theorem 3.11 record, the constructor now has the same source shape: start from
q-pilot containment in the displayed possible-image union and derive containment
in its canonical hull internally.
The record-native specialization now has the same \(q\subseteq P_{\mathrm{rec}}\)
input form: the hull containment needed by Step (xi) is derived from the
record's own possible-image union.
A record-native specialization removes the arbitrary possible-image-family
input: the family is \(i\mapsto P_i\) from the Theorem 3.11 source record, and
\Lean{} proves that its set-theoretic union is the record's theta-image union.
Below the packet layer, the code now has a first realified Frobenioid degree
source.  A finite Frobenioid object carries a divisor degree, a unit
log-volume, and their realified log-volume.  A finite divisor-product source
now records a tensor-packet product over base valuations whose packet factors
are the real readings of the corresponding divisor-prime contributions plus
base-local unit contributions; when the unit terms sum to the divisor source's
unit log-volume, \Lean{} derives that the packet product log-volume is the
realified divisor log-volume.  A finite divisor-monoid source computes this
divisor degree from prime
multiplicities and prime degrees, matching the finite shadow of the divisor
monoid in \IUT{} I, Example 3.5.  The same source now has a divisor-level
tensor product that adds multiplicities and realified log-volumes when the
prime-degree data agree; its projection to the degree-object layer agrees with
the existing degree-object tensor product.
It also has the Ob4 naive Frobenius tensor-power operation: multiplying the
divisor multiplicities and unit log-volume by \(M\) constructs a new finite
Frobenioid object whose divisor degree and realified log-volume are proved to
be \(M\) times the original values.  The older realified degree-object layer
now has the same Ob4 operation, and the projection from the finite
divisor-monoid source to that degree-object layer is proved to commute with
tensor-power formation.
The theta-version of \IUT{} I, Example 3.5(ii), is now represented at this
finite level: the same divisor degree is read through a formal
\(\log(\Theta)\)-generator, and normalization of this generator to \(1\)
recovers the ordinary finite divisor source.  The Ob4 tensor-power operation
also lifts to this theta copy, where \Lean{} proves that the theta divisor
log-volume is multiplied by \(M\).
The \(D\)-, or log-shell, version of Example 3.5(iii) is represented similarly:
a distinguished local Frobenius/log-shell reading is divided by the extension
degree before it is applied to the finite divisor degree.  Tensor-powering this
copy leaves the normalized Frobenius reading fixed and multiplies the resulting
log-shell divisor log-volume by \(M\).
The three finite copies now have a compatibility package: if they share the
same base divisor source and the theta/log-shell readings are normalized, then
their log-volume readings are equal.  This compatibility package is now stable
under simultaneous Ob4 tensor-powering: the ordinary, theta, and log-shell
copies are tensor-powered over the same object, the base identifications and
normalizations are preserved, and all three finite log-volume readings are
multiplied by \(M\).  The environment/Gaussian realified
Frobenioid comparison of \IUT{} II, Corollary 4.6(v), is represented at the
same finite level by an evaluation package between two such compatible copy
systems.  The package stores only the ordinary divisor-source identification;
\Lean{} derives equality of the ordinary, theta, and log-shell log-volume
readings across the environment and Gaussian sides from that identification
and the copy-compatibility lemmas.  The comparison is also stable under
simultaneous Ob4 tensor-powering: the ordinary-source equality is preserved,
the theta/log-shell comparison is rederived on the tensor-powered evaluation,
and the two ordinary realified log-volume readings are multiplied by \(M\).
The same comparison is now connected to
the finite local-global restriction layer, reflecting the \(F\)-prime-strip
formulation following Corollary 4.6(v): if the environment and Gaussian global
objects are the degree projections of their ordinary divisor sources and their
local restrictions agree pointwise, then \Lean{} derives equality of the
global realified log-volumes and of all local restricted log-volume readings.
The prime-index part of the same \(F\)-prime-strip statement is now explicit:
finite prime-label types for \(C_{\mathrm{env}}\) and \(C_{\mathrm{gau}}\)
come with bijections to the common valuation set \(V\), and the evaluation
map between prime labels is required to commute with these bijections.
\Lean{} then transports the local compatibility theorem along this
prime-place square, deriving equality of restricted and local realified
log-volumes at evaluated primes.
The next functorial step toward the \(\Theta^{\times\mu}\)- and
\(\Theta^{\times\mu}_{\mathrm{gau}}\)-links of Corollary 4.7(iii) is also
represented at finite level.  A lift to an \(F^{\times\mu}\)-prime-strip
stores an environment-side unit character; the Gaussian-side unit character is
defined by transport along the prime-evaluation equivalence.  Thus \Lean{}
proves unit-character compatibility at evaluated primes rather than accepting
it as an independent bridge field.  The coric \(F^{\vdash\times\mu}\)
invariance of Corollary 4.7(iv) is represented by a common unit character on
the valuation set \(V\).  Once the environment unit character is the pullback
of this coric character along \(Prime(C_{\mathrm{env}})\simeq V\), \Lean{}
derives the corresponding Gaussian equality from the prime-evaluation square.
The coric global realified Frobenioid compatibility of Corollary 4.7(v) is
represented by a positive real scale on finite local-global Frobenioid
collections.  This is the finite shadow of the \(R_{>0}\)-orbit language:
given scaled equality of the global realified log-volume and of the restricted
local prime readings, \Lean{} derives the scaled local-object and local-prime
log-volume equalities from the existing local-global collection laws.
The Frobenius-picture graph of Corollary 4.7(vi) is represented by the
directed successor relation \(n\to n+1\) on \(\mathbb{Z}\).  \Lean{} proves
that translations preserve this oriented graph and that any map exchanging
the adjacent vertices \(0\) and \(1\) cannot preserve directed edges.  This
captures the finite order-theoretic content of the paper's statement that the
chain has translation symmetry but not arbitrary permutation symmetry.
Proposition 3.10(ii)'s column log-Kummer correspondence is now represented at
the same finite level.  For each vertical coordinate \(m\in\mathbb Z\), the
source carries a packet of group elements acting on one common \(IQ\)-carrier
labelled by \(n,\circ\).  Translation in the column transports group elements,
and \Lean{} proves that the transported element acts by the same endomorphism
on the common carrier.  This records the translation-invariance of the
log-Kummer action; it does not yet construct the underlying number fields.
The realified-Frobenioid part of Proposition 3.10(iii) is represented at
degree level by a family of realified Frobenioid objects indexed by
\(m\in\mathbb Z\).  The log-link translation law preserves the extracted
realified log-volume, including adjacent \(m\mapsto m\pm1\) shifts.
The associated etale-picture core of Corollary 4.11(i),(ii) is represented by
a common \(D^{\vdash}\)-core projection for all integer-labelled spokes.
\Lean{} proves that this projection is constant across successor steps and is
unchanged by arbitrary permutations of the integer-labelled spokes, capturing
the finite mono-analytic core/permutation-symmetry contrast with the
Frobenius-picture chain.
The value-group restriction discussed in Remark 4.10.3 is exposed as a
combined finite-label endpoint: for a Gaussian degree evaluation, the
canonical full label \(j=1\) has degree equal to the environment \(q\)-degree,
the canonical square weight at \(j=1\) is \(1\), and the singleton
restriction to \(j=1\) is not stable under translation by \(1\).  Thus the
identity/pivotal specialization and the failure of compatibility with the
full label symmetry are checked in the same typed statement.
A finite tensor-product operation on these degree objects adds divisor degrees
and unit log-volumes, and \Lean{} proves that the realified log-volume of the
tensor product is the sum of the two realified log-volumes.  This operation is
also lifted to the tensor-packet source layer: if an existing tensor-packet
product source is certified to carry the tensor-product Frobenioid degree,
\Lean{} derives additivity of its packet product log-volume.  A Frobenioid
Kummer-compatibility certificate then projects to the coric
tensor-packet transfer by deriving equality of product log-volumes from
equality of realified Frobenioid log-volumes, while retaining the
Hodge-theater history guard.  This is still a finite degree-level shadow, not
a construction of Mochizuki's Frobenioids, but it moves one equality source
below the packet-correspondence interface.
The same degree layer now has finite Frobenioid morphisms.  A morphism records
the divisor-degree shift and unit-log-volume shift between two realified
objects; \Lean{} derives the corresponding shift in realified log-volume and
proves identity and composition laws at this degree/log-volume level.  This
models the additive content of the pull-back and structure morphisms appearing
in Remark 3.9.5(ix), (cQ3).  These morphisms now transport across Ob4
tensor-powering: the source and target degree objects are tensor-powered, and
the divisor and unit shifts of the induced morphism are multiplied by \(M\).
The Ob8/Ob9 vertical-shift issue is now attached directly to the Step (xi-g)
handoff.  A log-Kummer vertical-shift calibration pairs the
Step (x)-to-hull upper-ray source with the global realified Frobenioid
calibration.  \Lean{} proves that the calibrated value is the hull boundary
used by the upper ray, that both q-pilot computations are bounded by this
calibrated value, and that a shifted local value coincides with the calibrated
value only when the shift term vanishes.
Remark 3.9.5(ix)'s distinction between (cQ3),(cQ4) and (iQ5) is now represented
by a finite closed-loop guard.  The guard ties the hull/determinant log-volume
obtained from the (sQ3) route and the calibrated log-Kummer log-volume obtained
from the (sQ4) route to the same Step (xi) boundary.  \Lean{} then proves that
the two values coincide, while the direct shifted local log-volume agrees with
this boundary exactly in the zero-shift case.  This does not construct
\(F^{\times\mu}\)-prime-strips; it records the present formal boundary between
the source-faithful route and the log-volume-only quotient.
The global-to-local realified restriction from \IUT{} I, Example 3.5 is also
encoded at degree level: the restricted global prime log-volume is
\([K_v:(F_{\mathrm{mod}})_v]^{-1}\) times the local prime log-volume, and
\Lean{} proves that multiplying by the extension degree recovers the local
prime log-volume.  The same restricted value now normalizes the local
\(p_v^N\)-shift source: the local shift is expressed with this restricted
global prime step, and the automorphism-or-zero-step criterion is restated in
terms of the restricted realified prime log-volume.
Remark 3.9.5(ix)'s local-global collection language is represented at the same
finite degree level.  A collection contains a local realified Frobenioid object
for each \(v\), one global realified Frobenioid object, and localization
restriction factors.  \Lean{} proves that each local log-volume is the
restricted global value and that multiplying by the corresponding extension
degree recovers the global log-volume.  This is a finite log-volume shadow of
the local-global category, not a construction of the category itself.  The
collection and its restriction factors now transport coherently under Ob4
tensor-powering: local objects, the global object, restricted prime log-volumes,
and local prime log-volumes are all multiplied by \(M\), while extension-degree
rescaling remains valid.
This local-global collection now also backs the finite cQ3/cQ4 closed-loop
guard: if the collection's global realified log-volume is the cQ3
hull/determinant boundary, then \Lean{} proves that every localized value
rescales to both the cQ3 boundary and the cQ4 calibrated log-Kummer boundary.
Thus the Step (xi) boundary can be read from the local-global collection rather
than from a bare real number alone.
The local-global collection has also been refined by structure morphisms in
the finite Frobenioid degree category.  For each \(v\), a degree morphism from
the local object to the global object records divisor and unit shifts.
\Lean{} proves that the resulting morphism shift is exactly the additive form
of the localization rescaling.  This models the degree/log-volume content of
the ``structure poly-morphism'' language in Remark 3.9.5(ix), (cQ3).  The
structure-morphism collection now transports through Ob4 tensor-powering:
the underlying local-global collection is tensor-powered, and every structure
morphism acquires divisor and unit shifts multiplied by \(M\).
The same finite category now has compatible morphisms between two such
local-global structure collections.  A compatible morphism consists of local
morphisms at each \(v\), one global morphism, and a commutativity condition:
the local-then-structure path and the structure-then-global path have the same
divisor and unit shifts.  \Lean{} derives equality of the total realified
log-volume shift along these two paths.  The same compatible morphism now
transports through Ob4 tensor-powering: the global morphism, all local
morphisms, and the two paths in the compatibility square acquire shifts
multiplied by \(M\), and the square remains commutative.
\IUT{} I, Example 5.1 and Remark 5.1.1 distinguish the diagonal Frobenioid
\(F_{\langle J\rangle}\) from the product of underlying categories \(F_J\):
the former carries constant distributions in \(j\), while the latter allows
arbitrary distributions.  The code now models this finite realified
log-volume distinction.  A diagonal distribution has total log-volume
\(|J|\) times its common value, with the realified restriction factor
propagated through this sum; a distribution with two unequal coordinates is
proved not to come from a diagonal constant distribution.
\IUT{} I, Example 5.4(vii) and Remark 5.4.2 are represented by a finite
pivotal distribution object: a chosen pivotal index supplies the common
diagonal log-volume, the summed interpretation gives total
\(|J|\) times this pivotal value, and the averaged interpretation recovers the
pivotal value itself.
\IUT{} I, Definition 5.5 is now represented at finite log-volume level by an
NF-bridge mode object: the bridge target is either the summed capsule
log-volume or the normalized averaged capsule log-volume.  For the same
capsule distribution, \Lean{} proves that the summed bridge target is
\(|J|\) times the averaged bridge target; for a pivotal distribution, these
specialize to \(|J|\) times the pivotal value and to the pivotal value itself.
The adjacent \(\Theta\)-bridge and \(\Theta\mathrm{NF}\)-gluing condition of
Definition 5.5(iii) are formalized at the same finite level: the \(\Theta\)
side reads the common capsule total, and a compatibility record requires the
NF- and \(\Theta\)-bridge morphisms to use the same index bijection and the
same capsule distribution.  Lean then proves that a summed NF target equals
the \(\Theta\)-target, while an averaged NF target becomes the \(\Theta\)-target
after multiplication by \(|J|\).
Corollary 5.6(iii) is represented by a finite gluing torsor: once compatible
NF and \(\Theta\) bridge halves have been fixed, the gluing parameter is modeled
by the additive \(F_\ell\)-torsor on \(\mathbb{Z}/\ell\mathbb{Z}\).  Lean proves
zero action, additivity of the action, existence and uniqueness of the
translation between two gluing parameters, and preservation of the shared
index-bijection and capsule data.
This layer is now connected to the nonarchimedean packet correspondence:
a realified-Frobenioid log-Kummer packet source projects the Frobenioid
compatibility data to the Kummer \(F\to D\) transfer and to the
mono-analytic forgetting transfer, and then feeds the existing packet
correspondence endpoint.  Thus the Step (x) source equality used by the route
can be obtained from realified Frobenioid log-volume compatibility plus the
remaining packet source/target calibrations.
\IUT{} III, Remark 3.11.4 further says that the root-of-unity and cyclotomic
indeterminacies arising from forgetting Frobenius-like labels are invisible
for the objects under consideration.  The present code formalizes the finite
sign-unit part of this assertion: a unit in the subgroup \(\{1,-1\}\subset
(\mathbb{Z}/\ell\mathbb{Z})^\times\) preserves the zero/nonzero full cusp
label, every full-label log-volume expression, and the averaged Gaussian
log-volume.  This is not yet a construction of the full cyclotomic rigidity
isomorphism; it is the finite-label component that the current Stage 1
interface can prove without an additional Frobenioid/cyclotome layer.
The same finite-label layer now also proves the corresponding exclusion:
an affine coordinate change \(j\mapsto t+a j\) preserves the full cusp label
if and only if \(t=0\) and \(a\) is represented by such a sign-unit
invisibility certificate.  For nonzero Gaussian environment degree, the same
classification is equivalent to pointwise preservation of the Gaussian
degree profile.  Thus the current code has a finite analogue of the
``no further indeterminacies'' assertion of Remark 3.11.4(ii).
It also separates this cyclotomic invisibility from the stronger
square-weight preservation used by the factored \(\SHE\) layer: a root-unit
invisibility action always preserves the full-label map, but it preserves the
raw representative-square profile, equivalently the combined
square/full-label preservation package, if and only if the root unit is the
identity.
The integrated route now composes the Hodge--Arakelov theta-value sources with
this packet-target nonarchimedean source.  The resulting theorem derives the
same boundary/strict \(C_\Theta\) dichotomy from source-facing Gaussian
evaluation data and source-facing upper-semi data, rather than from two
unrelated collections of raw equalities.
For the target side, the strongest route now uses a target-only Step (x)
alignment
\[
  \Theta_{\mathrm{avg}}=U_{\Ind3}
\]
together with calibration of the local entry target against \(U_{\Ind3}\).
The direct equality \(\Theta_{\mathrm{avg}}=\mathrm{entry}_{\mathrm{target}}\)
is then derived.
When the theta-source average is identified with the packet-normalized capsule
log-volume, this target alignment is itself derived from calibration of
\(U_{\Ind3}\) with the same packet-normalized value.
The local entry target may now also be calibrated against this packet-normalized
value, so the equality
\(\mathrm{entry}_{\mathrm{target}}=U_{\Ind3}\) is derived rather than supplied
directly in the strongest route.

\subsection{Step (xi-f) algebra}

The final real algebra is fully formalized.  In informal notation, the main
theorem is:

\begin{theorem}[Formal Step (xi-f)]
Assume \(q<0\), \(q\le\theta\), and \(\theta\le C(-q)\).  Then \(C\ge -1\).
If \(q<\theta\), then \(C>-1\).  If \(C=-1\), then \(q=\theta\) and
\(\theta<0\).
\end{theorem}

This theorem is instantiated by the Step (x)-to-Step (xi) route whenever the
hull/log-volume upper-ray comparison and the displayed \(C_\Theta\)-bound are
available.
It is also instantiated by the current nonarchimedean
\((\Ind3)\)-plus-factored-\SHE{} route, subject to the same positivity and
displayed-bound hypotheses.  Thus the remaining gap is not the final
ordered-real implication, including its strict and boundary branches, but the
construction of the source hypotheses consumed by that implication.

\section{Boundary Quotient Experiment}

The most developed diagnostic concerns Step (xii), where local Frobenioid
\(p_v^N\)-ambiguity is compared with the globally calibrated log-volume.  The
formal model records a local shift
\[
  L_N=L_0+N\delta,\qquad N\in\mathbb{Z},\ \delta\in\mathbb{R},
\]
and a global calibration that fixes exponent \(0\).  \Lean{} proves
\[
  L_N=L_0 \quad\Longleftrightarrow\quad N\delta=0,
\]
and, if \(\delta\ne0\),
\[
  L_N=L_M \quad\Longleftrightarrow\quad N=M .
\]

At the boundary branch \(C_\Theta=-1\), the formal corridor identifies
\[
  q_{\mathrm{pilot}}=\Theta_{\mathrm{hull}}=L_0 .
\]
The local shift model is now source-facing: a local Frobenioid log-shell
submodule carries a \(p_v^N\)-action whose log-volume effect is
\(L_0\mapsto L_0+N\delta\).  The local action records whether the
\(p_v^N\)-endomorphism is an automorphism, and in the current model this is
equivalent to \(N=0\).  The global realified Frobenioid calibration package
selects exponent \(0\), hence its calibrated value is \(L_0\).  If the local
endomorphism is not an automorphism and \(\delta\ne0\), \Lean{} proves that the
local shifted value cannot equal the globally calibrated value.  The same
calibration can now be built from the restriction-normalized local source, so
the local step is the restricted global prime log-volume rather than an
independent real parameter.
For the actual upper-ray quotient that collapses
\(\{x\mid x\le \Theta_{\mathrm{hull}}\}\), \Lean{} proves the exact
classification
\[
  [L_N]=[q_{\mathrm{pilot}}]
  \quad\Longleftrightarrow\quad
  N\delta\le0,
\]
and the complementary separation criterion
\[
  [L_N]\ne[q_{\mathrm{pilot}}]
  \quad\Longleftrightarrow\quad
  N\delta>0.
\]
If \(\delta>0\), this becomes:
\[
  [L_N]=[q_{\mathrm{pilot}}]\Longleftrightarrow N\le0,\qquad
  [L_N]\ne[q_{\mathrm{pilot}}]\Longleftrightarrow 0<N .
\]

This is not a proof for either side of the Mochizuki--Scholze--Stix dispute.
It is a precise reading of one simplified quotient mechanism inside the current
formal corridor.  It shows that quotient collapse can identify unequal
underlying log-volumes if they lie in the collapsed upper ray, while positive
local shifts remain separated.  The decisive question is therefore not the
ordered-real algebra; it is whether the source \IUT{} constructions actually
supply the required calibrated hull/log-volume comparison without making an
illicit identification of histories or comparison levels.

\section{Current Results}

The project currently proves the following source-facing results in \Lean{}:

\begin{enumerate}
\item The finite \(q^{j^2}\) degree rule, sign quotient, half-range
  representatives, zero/nonzero split, and average formulas are formalized.
\item The bad-local theta-root quotient-\(\mathbb{Z}\) package now feeds the
  Stage 1 \(|F_\ell|\) full-label model through its canonical coordinate; the
  concrete \(Z/\ell Z\) case yields the canonical nonzero full label.
\item A single label-independent scalar cannot absorb all representative
  \(j^2\)-degrees when \(\deg(q)\ne0\).
\item The raw representative branch does not descend to the sign quotient,
  while the balanced full-label Gaussian branch does.
\item The Step (x) averaged-log-volume corridor feeds a Step (xi) upper-ray
  comparison once determinant/hull identifications are supplied.
\item A nonarchimedean \((\Ind3)\) entry with factored square/full-label
  preservation now directly supplies the final weighted-theta route and the
  signed \(C_\Theta\ge-1\) endpoint, once \(q\)-positivity and the displayed
  \(C_\Theta\)-bound are supplied.
\item The same nonarchimedean route now exposes the strict branch
  \(C_\Theta>-1\) and the boundary consequence
  \(C_\Theta=-1\Rightarrow q_{\mathrm{signed}}=\Theta_{\mathrm{signed}}<0\).
  It also packages these as one dichotomy at the route level.
\item Gaussian degree evaluations with preserved environment degree now feed
  directly into this nonarchimedean \(C_\Theta\) dichotomy, constructing the
  factored square/full-label \SHE{} package internally.
\item In the identity-coordinate Gaussian route, equality at the canonical full
  label \(1\) supplies the environment-degree preservation needed by the same
  nonarchimedean \(C_\Theta\) dichotomy.
\item The Hodge--Arakelov theta-value evaluation source now constructs the
  Gaussian degree evaluation from a theta-monoid degree and the bad-local
  theta-root label source; canonical-label preservation feeds the factored
  \SHE{} square/full-label obligations.
\item The same finite Hodge--Arakelov layer now has an audited theta evaluation
  wrapper matching the current IUT II shadow: it keeps the theta-root source,
  bad-local quotient identification, Gaussian degree evaluation, full-label
  compatibility, canonical \(j=1\) behavior, and the canonical square-weight
  profile as one source-facing object.  A pair of these objects constructs the
  \(\SHE\) synchronization source and can also construct the finite
  Hodge/\(\SHE\) transport source once the allowed-forgetting witness is given.
\item A nonarchimedean upper-semi object equipped with 1-column q-pilot
  log-Kummer data now supplies the raw nonarchimedean \((\Ind3)\) entry
  alignment used by the canonical Gaussian route.
\item The source-side equality in that compatibility can be derived from
  product-log-volume preservation along the finite Kummer-plus-forgetting
  tensor-packet chain.
\item A theta-root attached Kummer/forgetting source package now combines the
  canonical bad-local \(|F_\ell|\)-label source with a source-side
  packet/product calibration object and that finite chain, deriving the
  nonarchimedean source equality.
\item Source-side and target-side packet calibrations are now joined by one
  nonarchimedean log-Kummer packet-correspondence source carrying the q-pilot
  non-interference guard.  Its projections derive the theta-to-packet,
  theta-to-entry, entry-to-\((\Ind3)\)-target, and packet-normalized target
  equalities used by the route; the target calibration now refers directly to
  the packet-normalized capsule value rather than to a separate real
  representative.
\item The strongest Gaussian first-pass route can now consume this single
  packet-correspondence source and project both its source and target faces,
  instead of taking source packet equalities and target calibration as separate
  route inputs.
\item A realified-Frobenioid log-Kummer entry source now bundles the selected
  upper-semi inclusion with the realified packet source; the strongest Step (x)
  route projects Kummer transfer, mono-analytic forgetting, source/target
  packet calibration, and q-pilot non-interference from this single source.
\item A theta-root attached realified entry source now combines the canonical
  bad-local theta-root label package with that realified Step (x) source, and
  the Hodge--Arakelov route can consume this attached source directly.
\item The Hodge/\(\SHE/\IPL\)/hull route now also has a realified endpoint:
  route alignment supplies the Hodge--Arakelov and q-pilot data, and Step (x)
  enters through the theta-root attached realified source.
\item Remark 3.9.5(iii)'s hull-approximant family is now represented directly:
  an approximant lies inside the canonical hull \(\phi(P)\), has log-volume
  between \(P\) and \(\phi(P)\), and is fixed by hull formation.
\item The bounded-family upper-semi quotient of Remark 3.9.5(v)--(vi) is
  represented: each possible region lies in the hull of the family union, and
  any two nonempty possible regions have identical images in the quotient that
  collapses this family hull.
\item The Ob5 determinant/log-volume compatibility of this family quotient is
  represented at finite level: the same \(\phi(P_B)\) quotient source is paired
  with a weighted determinant certificate, and \Lean{} proves that the
  determinant log-volume and normalized tensor-power log-volume are the
  family-hull log-volume.
\item This Ob5 compatibility is specialized to the Corollary 3.12 possible
  theta-image family: the upper-ray source hull and the family quotient
  determinant/log-volume source share the same \(\phi(P_B)\).
\item The canonical possible-image Ob5 endpoint now returns the
  family-union-to-determinant estimate, not only the quotient collapse and
  determinant equality.
\item The Corollary 3.12 possible-image approximant source now projects to
  this bounded-family quotient source, yielding the same quotient-image
  equality for nonempty possible theta-image choices.
\item In that same source, q-pilot containment in the chosen approximant
  implies q-pilot containment in the family hull; if the q-pilot region is
  nonempty, its quotient image agrees with the quotient image of any nonempty
  possible theta-image choice.
\item Such a certified hull-approximant now also constructs the Step (xi)
  upper-ray datum: if the \(q\)-pilot region is contained in the approximant
  and the approximant log-volume is determinant-normalized, then \Lean{}
  derives the \(q\)-pilot bound by the approximant, by the canonical hull, and
  by the determinant log-volume.
\item The approximant route is now specialized to the Corollary 3.12
  possible-image union.  A single source object binds the possible theta-image
  family, its union, the chosen hull-approximant, q-pilot containment in that
  approximant, and determinant normalization; the experiment endpoint returns
  the union/approximant/hull and q-pilot/determinant inequalities.
\item The determinant input can now be produced from a finite weighted
  localization source: adjusted vector-bundle summand log-volumes are summed,
  the positive tensor-power value is derived, and normalization is proved to
  return the determinant log-volume before projecting to the determinant
  interface.
\item Each localization summand can now itself be produced from a finite
  direct-summand source: the bundle log-volume is the sum of direct-summand
  log-volumes, then the structure-sheaf adjustment and positive weight produce
  the adjusted localization contribution.
\item The Ob3-1-2 structure-sheaf adjusted source makes the
  \(\mathcal O(-)\) subtraction explicit before projection to the localization
  summand.  A corresponding determinant constructor proves that summing these
  weighted adjusted sources gives the determinant log-volume used by the
  route.
\item The possible-image hull-approximant endpoint now has a weighted
  determinant-source constructor.  The route consumes the weighted summand
  source and projects to the common upper-ray interface only after a named
  Ob3-3 compatibility certificate identifies the approximant log-volume with
  the weighted normalized determinant value.
\item The weighted determinant route now has a canonical-hull specialization:
  the approximant is constructed as \(\phi(P)\), q-pilot containment is stated
  directly in this hull, and the approximant-equals-hull proof is derived by
  \Lean{} rather than supplied as a separate route input.
\item The Ob4 tensor-power passage is now represented at log-volume level:
  \(M\)-th tensor-power formation multiplies by \(M>0\), and normalization
  recovers the base log-volume.  The weighted determinant source projects to
  this tensor-power object, and two tensor-power presentations with the same
  base log-volume have equal normalized log-volume.  The new
  \texttt{IUTStage1TensorPowerTwistFamily} extends this from a pairwise
  comparison to a family of Ob4-3 tensor-power-twist reconstructions: all twists
  share the reference normalized log-volume, and normalized log-volume bounds
  are invariant under replacing one twist by another.
\item The bounded-family hull/determinant source now proves the direct
  estimate from possible-image union to determinant log-volume:
  \(\mu_{\log}(\bigcup_\beta P_\beta)\le\det_{\log}\).
\item The Corollary 3.12 possible-image approximant source now exposes the
  same possible-image-union-to-determinant estimate directly.
\item The all-in-one target-charted Hodge/\(\IPL\) determinant possible-image
  route now has a named Step (xi) comparison-chain audit,
  \texttt{targetChartedHodgeIPLDeterminantPossibleImageRoute\_stepXIComparisonChainAudit}.
  This audit derives, at the route boundary, the chain
  \[
    \mu_{\log}(q_{\mathrm{pilot}})
      \le \mu_{\log}(P_B)
      \le \mu_{\log}(\phi(P_B))
      = \det_{\mathrm{norm}}
      = \det_{\log}
      \le \theta_{\mathrm{signed}},
  \]
  together with \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).  Thus the
  public route no longer exposes only the final signed comparison; it also
  records the possible-image containment and determinant-normalization chain
  that produces it.
\item This comparison-chain audit is now threaded through the finite-divisor
  vertical-\(IQ\) \(C_{\Theta}\) endpoint as
  \texttt{targetChartedHodgeIPLDeterminantPossibleImageRouteFiniteDivisorVerticalIQ\_stepXIComparisonChainAuditEndpoint}.
  The endpoint returns the same Step (xi) log-volume chain next to the
  conditional Corollary~3.12 dichotomy, so the finite Step (x) boundary can be
  audited through the constructed possible-image/determinant comparison rather
  than only through a coarse Gaussian-to-Step (xi) summary.
\item The package-level hull/determinant bridge can now be built from the
  Ob4-normalized tensor-power bound associated to a weighted determinant
  source.  The conversion to the determinant bound is a Lean theorem, not a
  separate bridge assumption.
\item A first realified Frobenioid degree layer is present: equality of
  realified Frobenioid log-volumes now derives the product-log-volume equality
  used by the tensor-packet coric transfer, with theater histories still kept
  distinct.  The degree object also has a finite tensor-product operation:
  divisor degree, unit log-volume, and realified log-volume are proved to add.
  A tensor-packet source certified by this Frobenioid product inherits
  product-log-volume additivity.
\item The realified Frobenioid degree object can now be constructed from a
  finite divisor-monoid source: \Lean{} computes the divisor degree as
  \(\sum_p m_p\deg(p)\) before adding the unit log-volume.
\item A finite divisor-product source now turns a base-valuation tensor-packet
  product into a realified Frobenioid packet source when every packet factor is
  the real reading of its divisor-prime contribution plus a base-local unit
  contribution, and the unit contributions sum to the divisor source's unit
  log-volume.
  The equality between packet product log-volume and realified Frobenioid
  log-volume is derived from the finite sum, not supplied as a separate field.
\item The Step (x) packet-local source alignment can now consume this finite
  divisor-product source: after identifying the packet-local object with the
  local entry source and the divisor realified log-volume, \Lean{} derives the
  entry-source/mono-analytic-product equality used by the log-Kummer source
  calibration.
\item The procession-normalized Step (x) average now has an
  \(\mathbb{F}_\ell\)-labelled source object: \Lean{} computes the total as
  \(\sum_{j\in ZMod(\ell)} v_j\), the normalized value as
  \(\ell^{-1}\sum_j v_j\), and proves this average is unchanged by translating
  all labels.
\item The corresponding finite-label indeterminacy endpoint proves that two
  successive label translations preserve the normalized average by finite
  reindexing; an upper bound on the twice-translated summands then yields the
  \((\Ind3)\) upper bound for the original average.
\item A target-side Step (x) calibration constructor now derives
  \(\theta_{\mathrm{avg}}=\mathrm{packetNormalized}\) from the
  \(\mathbb{F}_\ell\)-labelled procession average, instead of taking this
  equality as an unclassified direct input.
\item The realified Frobenioid packet source has the same labelled-average
  constructor: Kummer/forgetting compatibility, source calibration, and
  labelled Step (x) average construct the full packet source and expose the
  ordinary log-Kummer packet correspondence endpoint.
\item The labelled-average constructor now reaches the theta-root attached
  Step (x) entry source and the Hodge/\(\SHE/\IPL\)/hull route.  The route
  derives the packet-normalized theta calibration by composing
  theta-source-to-labelled-average with labelled-average-to-packet-normalized
  equality.
\item The labelled-average Hodge/\(\SHE/\IPL\)/hull route now has a
  source-aligned form: packet-local source alignment and Kummer/forgetting
  transfers construct the source calibration internally.
\item The theta-source-to-labelled-average equality can now be derived from
  labelwise agreement between the capsule-labelled source and the
  Hodge-descent theta-source \(ZMod(\ell)\)-average.
\item The labelled-average-to-packet-normalized equality can now be derived
  from labelled capsule local-object equality plus direct packet-normalization;
  the integrated route exposes this stricter source boundary.
\item The direct-labelled route now has an exact vertical-\(IQ\) target form:
  the target-side \((\Ind3)\) equality is derived through the common
  packet-normalized value, not passed as ordered-real alignment data.
\item The direct-labelled vertical-\(IQ\) route now has a finite-divisor form:
  source packet-local alignment is constructed from finite divisor/Frobenioid
  product data rather than supplied as a separate alignment record.
\item The Hodge direct-labelled finite-divisor route can now consume the
  all-in-one target-charted Hodge/\(\IPL\)/determinant possible-image route
  source directly: the source-derived Hodge/\(\SHE/\IPL\)/hull bridge is
  projected from that route source before the labelled Step (x) boundary is
  entered.
\item The direct-labelled and finite-divisor routes no longer require
  labelwise equality with the theta-source \(ZMod(\ell)\)-average as route
  input; it is derived from Hodge-descent label-local-object transport.
\item The theta-root attached Step (x) source can now be constructed from the
  same finite divisor-product source and an exact vertical-\(IQ\) target.  The
  endpoint exposes the canonical bad-local theta-root label, Kummer/forgetting
  product equalities, finite divisor product equality, target packet
  normalization, q-pilot non-interference, and the upper-semi bound.
\item The finite divisor-monoid source now has its own tensor product:
  multiplicities and unit log-volumes add, and \Lean{} proves additivity of the
  induced divisor degree and realified log-volume.
\item The same finite divisor-monoid source now has an Ob4-style naive
  Frobenius tensor-power operation: multiplicities and unit log-volume are
  multiplied by \(M\), and \Lean{} proves the induced divisor degree and
  realified log-volume are multiplied by \(M\).
\item The older realified degree-object layer now has the same Ob4 tensor-power
  operation, and the projection from a finite divisor-monoid source to this
  layer commutes with tensor-power formation.
\item The projection of this divisor-level tensor product to the realified
  degree-object layer agrees with the existing degree-object tensor product,
  preventing these two Frobenioid shadows from drifting apart.
\item The theta-version of the finite divisor source is now represented: a
  formal \(\log(\Theta)\)-generator scales the divisor degree, normalization to
  \(1\) recovers the ordinary source, and tensor products preserve additivity
  when the theta generators match.  The Ob4 tensor-power operation also lifts
  to this copy, multiplying the theta divisor log-volume by \(M\).
\item The \(D\)/log-shell version is also represented at finite level:
  \Lean{} normalizes a distinguished local Frobenius log-volume by the
  extension degree, recovers the ordinary source when this normalized value is
  \(1\), and proves tensor-product additivity when normalized values match.
  The Ob4 tensor-power operation preserves the normalized Frobenius reading and
  multiplies the log-shell divisor log-volume by \(M\).
\item The ordinary, theta, and log-shell divisor copies now have a compatibility
  package: shared base divisor data plus normalized readings imply equality of
  all three finite log-volume readings.  Simultaneous Ob4 tensor-powering of
  the three copies preserves this compatibility package and multiplies all
  three finite log-volume readings by \(M\).
\item The finite environment/Gaussian realified Frobenioid comparison attached
  to \IUT{} II, Corollary 4.6(v), is now encoded as an evaluation package
  between two compatible copy systems.  The only stored bridge is equality of
  the ordinary divisor source; \Lean{} derives equality of the ordinary,
  theta, and log-shell readings across the two sides.  Simultaneous Ob4
  tensor-powering preserves the stored ordinary-source equality, rederives the
  theta/log-shell comparison, and multiplies the two ordinary realified
  log-volume readings by \(M\).
\item This evaluation package is now tied to the existing finite local-global
  restriction layer: if the two global objects are the degree projections of
  the ordinary environment/Gaussian divisor sources and the local restrictions
  agree at every \(v\), then \Lean{} derives equality of the global realified
  log-volume and of the pointwise local restricted log-volume readings.
\item The prime-index skeleton of the corresponding \(F\)-prime-strip
  evaluation is now explicit: finite prime-label types for
  \(C_{\mathrm{env}}\) and \(C_{\mathrm{gau}}\) carry bijections to \(V\), and
  the evaluation equivalence between prime labels must commute with these
  bijections.  \Lean{} transports the local compatibility theorem along this
  square to obtain equality at evaluated primes.
\item The finite \(F^{\times\mu}\)-prime-strip lift used by the
  \(\Theta^{\times\mu}\)- and \(\Theta^{\times\mu}_{\mathrm{gau}}\)-links is
  now represented by transport of a unit character along the prime-evaluation
  equivalence.  The Gaussian unit character is constructed from the
  environment unit character, and \Lean{} proves compatibility at evaluated
  primes.
\item The coric \(F^{\vdash\times\mu}\) invariant of Corollary 4.7(iv) is now
  represented at finite level: a common unit character on \(V\) pulls back to
  the environment side, and \Lean{} derives the Gaussian-side pullback equality
  from the prime-evaluation square.
\item The coric global realified Frobenioid compatibility of Corollary 4.7(v)
  is now represented by a positive real scale on finite local-global
  Frobenioid collections.  From scaled global and restricted-local readings,
  \Lean{} derives the scaled local-object and local-prime log-volume readings.
\item The Frobenius-picture graph of Corollary 4.7(vi) is now represented as
  the directed successor graph on \(\mathbb{Z}\).  \Lean{} proves translation
  invariance and rules out edge preservation by any map that swaps adjacent
  vertices \(0\) and \(1\).
\item The etale-picture \(D^{\vdash}\)-core of Corollary 4.11(i),(ii) is now
  represented as a common core projection for all integer-labelled spokes.
  \Lean{} proves successor-step constancy and invariance under arbitrary
  permutations of the spoke labels.
\item The value-group restriction of Remark 4.10.3 is now a single endpoint:
  the Gaussian degree at \(j=1\) equals the environment \(q\)-degree, the
  square weight at \(j=1\) is \(1\), and the singleton-\(1\) restriction is
  not translation-invariant.
\item The realified Frobenioid degree layer now has finite morphisms: divisor
  and unit shifts determine the target realified log-volume, identity has zero
  shift, and composition adds both shifts.  These morphisms are stable under
  Ob4 tensor-powering, with divisor and unit shifts multiplied by \(M\).
\item The Ob8/Ob9 vertical-shift guard is now tied to the Step (xi-g)
  two-computation handoff: global realified Frobenioid calibration selects the
  hull upper-ray boundary, both q-pilot readings are bounded by it, and shifted
  local coincidence is equivalent to a zero shift term.
\item The cQ3/cQ4 portion of Remark 3.9.5(ix) now has a finite closed-loop
  guard: the hull/determinant value and the calibrated log-Kummer value are
  proved equal as the same Step (xi) boundary, while the direct log-volume-only
  shifted value agrees with that boundary only under the zero-shift condition.
\item The global-to-local realified Frobenioid restriction factor of \IUT{} I,
  Example 3.5 is formalized as inverse-extension-degree scaling of the local
  prime log-volume, with the degree-normalization identity proved in \Lean{}.
  This restricted value is connected to the local \(p_v^N\)-shift source used
  in the Step (xii) diagnostic, and global calibration can now be constructed
  from this restriction-normalized source.
\item A finite local-global realified Frobenioid collection now models the
  degree/log-volume content of Remark 3.9.5(ix): each local object is a
  restricted global value, and extension-degree rescaling recovers the global
  realified log-volume.  The collection and its restriction factors are stable
  under Ob4 tensor-powering, with the realified readings multiplied by \(M\).
\item The cQ3/cQ4 closed-loop guard can now be backed by such a local-global
  collection: the global collection value is identified with the cQ3
  hull/determinant boundary, and every localized value rescales to both the
  cQ3 and cQ4 Step (xi) boundaries.
\item The local-global collection now carries finite structure morphisms from
  local objects to the global determinant object.  The morphism divisor/unit
  shift is proved equal to the additive localization rescaling term.  The
  structure-morphism collection is stable under Ob4 tensor-powering, with every
  structure-morphism shift multiplied by \(M\).
\item Compatible morphisms between local-global structure collections are now
  represented: local-then-structure and structure-then-global paths have equal
  divisor/unit shifts and hence equal total realified log-volume shift.  This
  compatibility is preserved by Ob4 tensor-powering of the source and target
  local-global structure collections.
\item The diagonal/arbitrary distribution distinction of \IUT{} I, Example 5.1
  and Remark 5.1.1 is formalized at finite realified log-volume level:
  diagonal distributions are constant in \(j\), their total is
  \(|J|\) times the common restricted value, and a two-coordinate mismatch
  cannot be represented as diagonal.
\item The pivotal distribution of \IUT{} I, Example 5.4(vii), is modeled by a
  chosen index in a diagonal distribution; \Lean{} proves the summed
  log-volume formula and the normalized averaged formula of Remark 5.4.2.
\item The finite NF-bridge log-volume model of \IUT{} I, Definition 5.5,
  separates summed and averaged bridge targets and proves their \(|J|\)
  scaling relation for a common capsule distribution.
\item The finite \(\Theta\mathrm{NF}\)-bridge compatibility model records the
  same-index-bijection and same-capsule requirements of Definition 5.5(iii),
  and proves the corresponding \(\Theta\)-target equalities for summed and
  averaged NF modes.
\item The finite gluing set of Corollary 5.6(iii) is modeled as the additive
  \(F_\ell\)-torsor on \(\mathbb{Z}/\ell\mathbb{Z}\), with compatibility data
  preserved under gluing translation.
\item The realified Frobenioid layer now feeds the nonarchimedean
  log-Kummer packet source: Kummer and mono-analytic forgetting transfers are
  projected from Frobenioid compatibility before the packet correspondence
  endpoint is applied.
\item A packet-normalized Step (x) entry-target source now constructs the
  target side of a nonarchimedean upper-semi entry from the capsule-family
  normalized log-volume.  The target-calibration constructor derived from this
  source removes the separate entry-target-to-packet-normalized equality.
\item The same target-calibration layer can now derive the
  \((\Ind3)\)-target-to-packet-normalized equality from theta-target alignment
  and theta-average packet normalization, instead of accepting that equality
  directly.
\item A vertical-\(IQ\) target source now models the exact common-target side
  of the log-Kummer correspondence in Proposition 3.10(ii).  It derives the
  theta-average, \((\Ind3)\)-target, and entry-target packet-normalized
  equalities used by the packet target calibration.
\item The vertical-\(IQ\) source carries an \(FMOD\)-exactness guard, reflecting
  Remark 3.10.1's distinction between exact \(FMOD\) Frobenioid
  compatibility and one-sided \(Fmod\) upper semi-compatibility.
\item The exact vertical-\(IQ\) realified entry source now enforces that the
  realified packet target calibration is the calibration induced by the
  retained exact vertical-\(IQ\) target.
\item The canonical exact Step (x) experiment route now constructs this
  refined source internally from theta-root data, realified Frobenioid
  transfer data, packet-local source alignment, and the exact vertical-\(IQ\)
  target.
\item A finite-divisor canonical exact route now derives the packet-local
  source alignment from the finite divisor/Frobenioid packet product before
  constructing the exact source used by the Corollary 3.12 corridor.
\item Its compatibility and audit forms now construct the same finite-divisor
  source object first; the packet-local alignment and audit equalities are
  then projected from that object rather than from a separate alignment
  endpoint.
\item The strongest finite-divisor canonical exact route consumes this
  finite-divisor packet data as one source object: finite divisor packet,
  mono-analytic realization, packet-local/source equality, divisor
  realified-degree equality, and \((\Ind3)\)-source equality are projected
  from that object rather than supplied as unrelated route arguments.
\item The public experiment audit form of this finite-divisor exact route
  exposes the source equality, mono-analytic product equality, divisor-degree
  normalization, \((\Ind3)\)-source equality, and upper-semi inequality used in
  that construction.
\item The source-aligned realified Step (x) entry endpoint now exposes this
  \(FMOD\)-exactness guard at the same level as the Kummer/forgetting transfer
  chain, target packet-normalized equalities, q-pilot non-interference, and
  upper-semi inequality.
\item The theta-root attached source-aligned Step (x) endpoint now carries the
  same \(FMOD\)-exactness guard together with the canonical bad-local
  theta-root label facts.
\item The log-Kummer packet-correspondence source can now be constructed from
  source packet/product calibration plus the packet-normalized entry target and
  theta-target alignment.  The q-pilot non-interference, source equality, and
  target equality endpoint is then recovered from this constructed
  correspondence.
\item The packet-correspondence endpoint now exposes the full finite Step (x)
  transfer chain: Kummer product preservation, mono-analytic forgetting product
  preservation, source equality with the \((\Ind3)\) real source, target
  packet-normalized equalities, and q-pilot non-interference.
\item The source packet/product calibration itself now has a constructor from
  packet-local/source alignment, packet-local \((\Ind3)\)-source alignment,
  and Kummer/forgetting product-log-volume preservation.  The source
  holomorphic-product equality is derived by this constructor.
\item A calibrated source packet/product face can now be projected back to the
  packet-local source-alignment object once the Kummer and mono-analytic
  forgetting transfers are supplied; the packet-local \((\Ind3)\)-source
  equality is reconstructed through that transfer chain.
\item The same projection is now available from a realified-Frobenioid
  log-Kummer packet source itself: its internal Kummer and forgetting
  compatibilities supply the transfer chain needed to recover the packet-local
  source-alignment object.
\item The realified Step (x) entry source now projects the same packet-local
  source alignment while retaining the selected entry's upper-semi membership.
\item The theta-root attached realified Step (x) entry source now projects the
  same packet-local source alignment while retaining the canonical generator
  and nonzero full-label facts.
\item The Hodge/\(\SHE/\IPL\)/hull route has a source-audit endpoint: from one
  theta-root attached realified Step (x) source, \Lean{} returns the recovered
  packet-local alignment equalities together with the \(C_\Theta\) dichotomy.
\item The source-aligned Hodge/\(\SHE/\IPL\)/hull route now derives its
  target-only \((\Ind3)\) alignment from the Step (x) packet-normalized theta
  source and the exact vertical-\(IQ\) target source, retaining the
  \(FMOD\)-exactness guard at the route boundary.
\item The audit form of this vertical-\(IQ\) route also exposes the derived
  equality from the Hodge-descent theta average to the \((\Ind3)\) target
  value, before returning the \(C_\Theta\) dichotomy.
\item The packet-correspondence constructor has a stronger alignment form:
  packet-local source alignment, packet-local \((\Ind3)\)-source alignment,
  packet-normalized entry target, and theta-target alignment generate both
  packet calibrations before projecting the q-pilot endpoint.
\item The realified-Frobenioid log-Kummer packet source has the same reduced
  target-data constructor: Frobenioid compatibility yields the Kummer and
  forgetting transfers, while packet-normalized target data is generated from
  the entry-target source and theta-target alignment.
\item The vertical-\(IQ\) target source has been lifted through the
  realified-Frobenioid entry source and the theta-root attached entry source,
  so their upper-semi endpoints no longer need independent target alignment
  equalities when common-target log-Kummer data is available.
\item The integrated Hodge/SHE/IPL/hull \(C_\Theta\)-dichotomy route now has a
  vertical-\(IQ\) form: exact common-target log-Kummer data supplies the
  target equalities used by Step (x) before the route enters the final
  Corollary 3.12 real inequality.
\item The integrated vertical-\(IQ\) route also has a source-reduced form:
  source packet calibration is constructed internally from packet-local
  alignments and realified Kummer/forgetting compatibility.
\item The same source-reduced vertical-\(IQ\) data now constructs the
  realified Step (x) log-Kummer entry source itself, before any final
  \(C_\Theta\)-dichotomy theorem is invoked.
\item The realified packet source now also has a source-reduced constructor:
  packet-local/source alignment and packet-local \((\Ind3)\)-source alignment
  generate the source packet calibration using the Frobenioid-derived Kummer
  and forgetting transfers.
\item The realified Step (x) entry source has the same reduced boundary:
  entry membership plus source/target alignment data constructs the packet
  source internally and projects q-pilot non-interference, source equality,
  target equality, and the upper-semi inequality.
\item The same realified packet source now exposes a combined calibration
  endpoint: it proves Kummer and forgetting product-log-volume preservation,
  packet-local equality with the entry source, entry-source equality with the
  \((\Ind3)\) source, packet-normalized equality for the theta average,
  \((\Ind3)\) target, and entry target, and q-pilot non-interference.
\item The theta-root attached realified entry source now has the same
  source-reduced vertical-\(IQ\) constructor: the upper-semi packet entry,
  packet-local source alignments, realified Kummer/forgetting compatibility,
  and exact vertical-\(IQ\) target construct one source object that projects
  the canonical nonzero theta-root label facts and the realified Step (x)
  upper-semi endpoint.
\item The packet-correspondence source now has the same source-aligned
  vertical-\(IQ\) constructor: a named packet-local source-alignment object and
  an exact vertical-\(IQ\) target source construct one correspondence object
  before the realified-Frobenioid layer is applied.
\item The packet-correspondence source also has a source-aligned
  packet-normalized ordered-target constructor: the source face is generated
  from the named packet-local alignment object, while the target face is
  generated from the packet-normalized entry and theta-target alignment.
\item The theta-root attached realified entry source now projects the
  underlying packet correspondence endpoint, combining canonical bad-local
  label facts with transfer-chain equalities, packet target calibrations,
  q-pilot non-interference, and the upper-semi bound.
\item The Hodge/\(\SHE/\IPL\)/hull route now consumes this reduced theta-root
  Step (x) data directly: the theorem constructs the realified source internally
  from a named packet-local source-alignment object and exact vertical-\(IQ\)
  target, then concludes the current \(C_\Theta\) dichotomy.
\item The same route has an ordered-real-line form: the packet-source and
  theta-target \((\Ind3)\) real equalities are extracted from one matched-scale
  ordered transport alignment, so they are no longer accepted as unrelated
  route inputs at this boundary.
\item The ordered packet-normalized route now has a source-aligned form:
  packet-local source alignment plus realified Kummer/forgetting compatibility
  construct the source calibration internally before the route enters the
  theta-root attached Step (x) source.
\item The same source-aligned ordered route now has a target-only alignment
  form: the source-side \((\Ind3)\) equality is supplied by the source
  alignment object, and the route consumes only the theta-target
  \((\Ind3)\) equality as ordered-real input.
\item The target-only \((\Ind3)\) alignment can now be constructed from a
  Step (x) packet-normalized theta-source alignment and an exact
  vertical-\(IQ\) target source.
\item The realified-source vertical-\(IQ\) audit recovers the packet-local
  source-alignment object from the theta-root attached realified
  log-Kummer entry source, so this route boundary no longer accepts that
  source alignment as an independent input.
\item The stronger realified-source vertical-\(IQ\) audit also projects
  theta-average packet normalization from that same source, removing the
  separate Step (x) packet-normalized theta-source route from the audit
  boundary.
\item The finite-divisor vertical-\(IQ\) route now constructs this theta-root
  attached realified source internally from the finite divisor/Frobenioid
  packet product, then invokes the realified-source audit.  Thus the integrated
  route no longer reconstructs a packet-local alignment independently of the
  source object.
\item In the ordered form, the packet-normalized theta calibration can now be
  obtained from a constant \(ZMod(\ell)\) packet-normalized route.  The theorem
  requires equality of the Hodge-descent theta source with the packet-normalized
  theta source, preventing a packet-normalization audit for one theta source
  from being used for another.
\item The same source equality is now bundled with the packet-normalized route
  as a Step (x) theta-source alignment, and the Hodge/SHE/IPL/hull endpoint
  consumes that aligned object instead of separate route/equality inputs.
\item The selected packet-normalized nonarchimedean entry is now bundled with
  its membership in the audited upper-semi inclusion family.  The route consumes
  this single source object rather than a constructed entry and separate
  membership proof.
\item The source side of that Step (x) entry can now be supplied by a named
  packet/product source calibration.  The route no longer receives the
  packet-local/source and source/mono-analytic-product equalities separately;
  they are projected from the calibration object before the realified
  Frobenioid source is constructed.
\item Below that calibration, the source/mono-analytic-product equality can now
  be derived from the finite divisor/Frobenioid packet product source whenever
  the packet-local object is identified with the entry source and the finite
  divisor realified log-volume.
\item The Hodge/SHE/IPL/hull vertical-\(IQ\) route has a finite-divisor form:
  it consumes the finite divisor packet source directly and constructs the
  packet-local source alignment internally before deriving the
  \(C_\Theta=-1\) boundary alternative or strict \(C_\Theta>-1\) conclusion.
\item At the entry-source level, the finite-divisor vertical-\(IQ\) constructor
  now first projects the full packet-source calibration from the finite-divisor
  packet source; the packet-local alignment is no longer the primary
  constructor at this boundary.
\item The finite-divisor packet source now also constructs the packet
  correspondence source itself: source calibration, vertical-\(IQ\) target
  calibration, and q-pilot non-interference are bundled before the realified
  packet and entry sources are formed.
\item The same finite-source packet-correspondence boundary now covers the
  entry-target/theta-target branch: the packet-normalized entry target supplies
  the target face while the finite-divisor packet source supplies the source
  face.
\item The ordered Step (x) route itself now has the finite-source boundary:
  the finite-divisor packet source supplies the source alignment before the
  ordered \((\Ind3)\) target comparison enters the Hodge/\(\SHE/\IPL\)/hull
  endpoint.
\item The theta-target branch of the ordered Step (x) route now has the same
  finite-source boundary: the finite-divisor packet source supplies the source
  alignment, while the only remaining ordered target input is the
  theta-target \((\Ind3)\) alignment.
\item The first-pass Corollary 3.12 experiment endpoint now has a finite
  Step (x) source form: the upper-semi packet-normalized entry, finite-divisor
  packet source, realified Kummer/forgetting compatibilities, and exact
  vertical-\(IQ\) target construct the realified log-Kummer entry source before
  the route enters the existing \(C_\Theta\) dichotomy theorem.
\item The public finite-divisor vertical-\(IQ\) experiment surface now includes
  the source-object form and an audit endpoint, so the Step (x) source
  equalities are checked as projections of one finite-divisor/Kummer source.
\item The integrated Hodge/\(\SHE/\IPL\)/hull finite-divisor vertical-\(IQ\)
  route now has the same source-object boundary.  Its compatibility form
  constructs the finite-divisor packet-local source and delegates to the
  source-object route.
\item The direct-labelled finite-divisor vertical-\(IQ\) route and its
  Hodge-derived labelwise specialization now use this source-object boundary
  as well; the finite-divisor compatibility forms no longer build an
  independent packet-local source alignment in their final proof path.
\item The theta-root attached realified Step (x) finite-divisor constructor now
  has the same finite-source form.  The finite-divisor compatibility endpoint
  constructs this source object first and then exposes the theta-root label,
  Kummer/forgetting, product, target-normalization, and upper-semi facts as
  projections from it.
\item The ordered Step (x) vertical-\(IQ\) target route now has the same
  finite-source boundary.  Its finite-divisor compatibility form first bundles
  the finite divisor/Frobenioid data, then derives the source alignment used by
  the ordered target route from that source object.
\item The labelled-average Step (x) route has the same finite-source boundary:
  finite \(ZMod\)-averaging supplies packet normalization, while the
  finite-divisor packet source supplies the source-side packet-local
  alignment.
\item The direct-normalized labelled-average route has the same source
  boundary: direct packet normalization derives the labelled average, and the
  finite-divisor packet source supplies the Step (x) source alignment.
\item The theta-labelled target and vertical-\(IQ\) route now have the same
  finite-source boundary: the labelled finite average supplies the theta-source
  calibration, the exact vertical-\(IQ\) target supplies the target alignment,
  and the finite-divisor packet source supplies the source alignment.
\item The finite sign-unit/root-of-unity part of Remark 3.11.4 is formalized:
  sign-unit action preserves full cusp labels, full-label log-volume readings,
  Gaussian degrees, and averaged Gaussian log-volume.
\item The same finite layer classifies the allowed unit-affine label changes:
  full-label preservation is equivalent to zero translation plus a sign-unit
  invisibility certificate; under nonzero Gaussian environment degree this is
  also equivalent to pointwise Gaussian-degree preservation.
\item The root-unit action preserves the raw representative-square profile,
  equivalently the factored square/full-label package, only for the identity
  unit; root-of-unity invisibility is therefore not silently promoted to
  \(\SHE\) square-weight preservation.
\item The current integrated route composes Hodge--Arakelov theta-value sources
  with the packet-target nonarchimedean source to obtain the same
  \(C_\Theta=-1\) boundary alternative or strict \(C_\Theta>-1\) conclusion.
\item A Theorem 3.11 multiradial source record now packages structured
  \(\IPL/\SHE/\APT\), coric output, possible theta images, pilot-column
  asymmetry, distinct log-shell treatments, and the no-history-identification
  guard.
\item The \(\IPL\) source layer now has an explicit log-volume transport record
  with source and target Hodge-theater sides, prime-strip endpoint
  compatibility, log-volume preservation, and no-history-identification.
\item The \(\SHE\) source layer now derives the current square/full-label
  preservation package from Hodge--Arakelov canonical-one synchronization,
  exposing pointwise representative comparison, transported-average equality,
  and the retained Hodge-history separation.
\item The Step (xi) hull/determinant layer now has a Theorem 3.11 source
  constructor: source obligations are derived from the source record where
  possible, the record's theta possible-image union is tied to the hull endpoint,
  and the determinant bound yields \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).
\item The theta-pilot possible-image family of the source package now feeds the
  canonical holomorphic-hull approximant directly: \Lean{} identifies its
  set-theoretic union with the package target union before the determinant
  comparison is applied.
\item The package-level hull/determinant source bridge can now be constructed
  from a concrete common hull containing the target union and a
  determinant/log-volume bound for that hull.  The experiment endpoint returns
  target-union containment, the determinant bound, all-target bounds, and
  equality with the package's named hull/determinant bridge.
\item The same source bridge has a hull-operator specialization: the common
  hull is \(\phi(P_{\mathrm{out}})\) for the target-union region
  \(P_{\mathrm{out}}\), and the endpoint records this equality before deriving
  containment, determinant, and all-target bounds.
\item The Set-based holomorphic-hull/log-volume shadow now induces a
  Region-level hull operator and Region measure on real-line points.  The
  experiment endpoint proves exact agreement with the original point-set hull,
  containment, and induced log-volume monotonicity.
\item The package-level hull/determinant bridge can now be constructed from
  that holomorphic-hull shadow when the package measure is identified with the
  induced Region measure and the point-set hull satisfies the determinant
  bound.
\item The possible-image approximant source can now construct the package
  hull/determinant bridge in the canonical case: the possible-image union must
  be the package target union, the approximant must be the canonical hull, and
  the normalized determinant value must be bounded by \(\theta_{\mathrm{signed}}\).
\item The Theorem 3.11 hull/determinant constructor can now be built directly
  from the source record plus this canonical approximant data, with the record's
  possible-image union supplying the bridge to the package target union.
\item The same Theorem 3.11 constructor can now be built from a canonical
  possible-image approximant backed by the finite weighted determinant source
  of Remark 3.9.5(vii), (Ob3).  The endpoint exposes the equality between the
  approximant log-volume and the weighted determinant log-volume.
\item The canonical weighted determinant constructor now has the stronger
  canonical-hull input form: the approximant is definitionally \(\phi(P)\),
  q-pilot containment is imposed in this hull, and the endpoint exposes the
  derived approximant-region equality.
\item The canonical possible-image route can now instead consume
  \(q\subseteq P=\bigcup_i P_i\).  The containment \(q\subseteq\phi(P)\) used
  by the upper-ray comparison is derived from hull extensivity, so the source
  interface is closer to the Step (xi) possible-image construction.
\item The canonical-hull route now has the same Ob4 tensor-power input form:
  a normalized tensor-power bound is converted to the determinant bound, while
  \Lean{} derives the approximant-equals-\(\phi(P)\) witness from the canonical
  hull constructor.
\item The package-level canonical Ob4 route now has a \(q\subseteq P\) source
  form: bridge construction, determinant normalization, target-union
  containment, and the signed-volume hull bound are all exposed after \Lean{}
  derives \(q\subseteq\phi(P)\).
\item This canonical-hull Ob4 endpoint is also public for the Theorem 3.11
  source constructor: the source record's theta possible-image union is the
  hull input before the package target-union identification is applied.
\item The arbitrary-family Theorem 3.11 Ob4 constructor now also has a
  \(q\subseteq P\) source form.  The family is then identified with the
  record's theta possible-image union, and \Lean{} derives the hull containment
  consumed by the package-level source data.
\item The record-native Theorem 3.11 Ob4 route can now consume
  \(q\subseteq P_{\mathrm{rec}}\), where \(P_{\mathrm{rec}}\) is the record's
  own possible-image union; \Lean{} derives
  \(q\subseteq\phi(P_{\mathrm{rec}})\) before constructing the final
  hull/determinant source constructor.
\item A record-native specialization now derives that theta-image union from
  the Theorem 3.11 record's own possible-image family, instead of accepting an
  arbitrary image family plus a separate union equality.
\item The Step (x)-to-Step (xi) upper-ray bridge can now be built directly
  from a certified possible-image hull approximant.  The determinant
  normalization is read from the approximant/determinant compatibility, rather
  than supplied as a separate equality at the bridge boundary.
\item The Step (x)-to-Step (xi) hull comparison is now a named handoff
  proposition over a fixed procession corridor and fixed hull source; from this
  handoff \Lean{} derives q-pilot upper-ray membership and determinant
  normalization at the Step (xi-f) boundary.
\item The same upper-ray bridge now has a log-Kummer vertical-shift calibration
  endpoint: the globally calibrated Frobenioid log-volume is the hull boundary
  used in Step (xi-g), not an independently chosen real value.
\item The Step (xi) endpoint now exposes the finite cQ3/cQ4 closed loop:
  hull/determinant passage and log-Kummer calibration produce the same boundary,
  and the shifted local log-volume route is equivalent to a zero-shift
  specialization.
\item A Hodge/\(\SHE/\IPL\)/hull packet-target route now derives the target-side
  log-volume equality from \(\SHE\) synchronization and reads \(q\)-positivity
  from the hull constructor; the source-side theta/Hodge equality is derived
  from a full-label calibration certificate in the route-alignment source
  record.
\item The Hodge/\(\SHE/\IPL\)/hull alignment is now also exposed through a
  source-derived bridge object.  This object keeps the Theorem 3.11
  multiradial record, the \(\IPL\) log-volume transport, the
  finite Hodge--Arakelov \(\SHE\) transport, the Step (xi) hull/determinant
  constructor, and the theta/Hodge calibration certificate as separate source
  components, then constructs the route-level log-volume alignment internally.
  The finite transport records the source and target Hodge-theater sides,
  finite label transport, full-label log-volume preservation,
  transported-average preservation, and the present no-history-identification
  guard.
\item The finite Hodge/\(\SHE\) transport now has a source-boundary layer:
  \Lean{} constructs it from a Hodge-theater descent bridge, a typed
  allowed-forgetting witness, the current Hodge--Arakelov synchronization
  source, and the finite full-label preservation data.  The witness records
  the source theater, target theater, descent operation, permission proof, and
  history-separation guard, separating the history/forgetting obligation from
  the downstream transport object.
\item The allowed-forgetting witness now has a canonical history-separated
  finite-stage form.  Instead of treating the permission predicate as an
  unrelated route input, the public Hodge--Arakelov endpoint can take it to be
  the history-separation condition of the Theorem 3.11 Hodge-theater descent
  bridge carried by the source record.  This removes a loose external
  \(\mathrm{Prop}\) from the public corridor while preserving the trust boundary: the
  full source-paper construction of the Hodge-theater forgetting operation is
  still not claimed.
\item The \(\IPL\) log-volume transport now has a source construction from the
  same finite Hodge/\(\SHE\) transport plus a Theorem 3.11 IPL-link
  construction source.  The construction builds the input-prime-strip link with
  source and target endpoints definitionally equal to the recorded input and
  output prime strips, then aligns the resulting \(\IPL\) datum with the
  pre-ledger certificate.  Its Hodge-theater sides are projected from the
  finite transport, and its log-volume preservation equality is the transported
  average preservation supplied by the finite Hodge/\(\SHE\) layer.
\item The public \(\IPL\) boundary also has a certificate-pinned link-source
  form.  This form consumes the pre-ledger certificate's own \(\IPL\) datum
  together with just the endpoint equalities saying that its link source and
  target are the input and output prime strips.  Thus the strongest
  finite-divisor route no longer has to carry a separate constructed
  \(\IPL\)-datum alignment when the certificate datum itself already satisfies
  the Theorem 3.11 endpoint shape.
\item The Step (xi) holomorphic-hull/determinant route now has a source
  boundary wrapper around the record-native Ob4 constructor.  The wrapper keeps
  the holomorphic hull shadow, \(q\subseteq P_{\mathrm{rec}}\) containment,
  weighted determinant source, tensor-power bound, bridge equality, positivity,
  and normalization as separate auditable fields, then constructs the existing
  Theorem 3.11 hull/determinant constructor and exposes
  \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).
\item The strongest Hodge--Arakelov/history-separated route can now consume
  that Step (xi) holomorphic-hull/determinant source as a single object.  This
  keeps the \(q\)-pilot containment and determinant payload intact, but no
  longer expands the record-native hull fields at the public Hodge--Arakelov
  boundary.
\item The Step (xi) source boundary now also has a choice-linked q-pilot form:
  a named Theorem 3.11 possible-output choice carries
  \(q\subseteq P_{\mathrm{choice}}\), and \Lean{} derives
  \(q\subseteq P_{\mathrm{rec}}\) by the possible-image union inclusion.  Thus
  the strongest Hodge--Arakelov/history-separated endpoint has a variant whose
  q-pilot containment is not an independent public field.
\item That choice-linked Step (xi) source now projects to the existing
  upper-ray and two-computation corridor.  From the canonical hull and
  weighted-determinant compatibility, \Lean{} constructs the
  \(R_{\le -|\log(\Theta)|}\)-style upper-ray datum, proves membership of the
  q-pilot log-volume in this ray, derives the determinant upper bound for that
  q-pilot log-volume, and records equality of the input-prime-strip and
  output-hull q-pilot readings.
\item The choice-linked Step (xi) source now has a stricter exact-theta form.
  Instead of carrying the normalized tensor-power upper bound as a separate
  field, it carries the equality identifying \(\theta_{\mathrm{signed}}\) with
  the normalized Ob4 tensor-power log-volume of the weighted determinant
  source.  \Lean{} then derives the old tensor-power bound, projects back to
  the existing choice-linked hull source, and exposes a public
  Hodge--Arakelov/history-separated finite-divisor endpoint for this stronger
  source shape.
\item That exact-theta Step (xi) source now has a side-conditioned form as
  well.  The q-pilot positivity and source normalization proofs are no longer
  two loose fields in this variant; they are projected from
  \(IUTStage1SourceSideConditions\), the same side-condition boundary used when
  promoting source data to the Stage 1 ledger.
\item The exact-theta Step (xi) source now also has a hull/det-data-backed
  form.  In this variant, the equality with the package's named
  hull/determinant bridge is no longer carried directly.  Instead the source
  consumes \(IUTStage1SourceHullDetData\), projects the package bridge equality
  already stored in that object, and then identifies the stored bridge data
  with the record-canonical Step (xi) hull/tensor-power construction.
\item The same boundary now has a record-native bounded-family hull form.
  This new source object specializes the Ob5 bounded-family hull/determinant
  source to the Theorem 3.11 possible-image family, so the family union
  \(P_{\mathrm{rec}}\), its hull \(\phi(P_{\mathrm{rec}})\), the weighted
  determinant source, and the normalized Ob4 tensor-power log-volume are tied
  to one record-level object.  The strengthened endpoint assumes
  \(\theta_{\mathrm{signed}}=\mu_{\log}(\phi(P_{\mathrm{rec}}))\); \Lean{}
  then derives the older exact tensor-power equality and the tensor-power
  bound from the Ob5 hull/determinant compatibility.
\item The record-native bounded-family source now projects back to the generic
  Ob5 bounded-family hull/determinant source.  Thus the record-level
  possible-image family reuses the existing quotient-collapse theorem,
  possible-region containment in the family hull, determinant/log-volume
  comparison, and normalized tensor-power endpoint instead of duplicating a
  weaker record-specific summary.
\item The history-separated Hodge--Arakelov, certificate-pinned \(\IPL\),
  finite-divisor vertical-\(IQ\) endpoint now consumes this
  family-hull-backed source directly.  The endpoint constructs the
  source-derived Hodge/\(\SHE/\IPL\)/hull bridge from this source, so the
  public route no longer has to present the exact tensor-power equality as the
  Step (xi) source-facing input.  The experiment module exposes the same route
  as the audit theorem
  \texttt{familyHullBackedFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The family-hull-backed endpoint now also has a constructed-\(\IPL\)
  form at the same boundary.  The source-derived bridge is built directly from
  the input-prime-strip link construction source, so the bridge audit retains
  the equality between the package certificate's \(\IPL\) datum and the
  constructed datum, before applying the same finite-divisor vertical-\(IQ\)
  route.  The experiment module exposes this as
  \texttt{constructionFamilyHullBackedFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The same family-hull Step (xi) source now has an obligations-backed
  form.  It consumes one \(IUTStage1SourceHullDetObligations\) object and
  projects the package hull/determinant data, q-pilot positivity, and source
  normalization from that object, rather than carrying them as separate Step
  (xi) fields.  The experiment module exposes this stronger audit route as
  \texttt{obligationsBackedFamilyHullFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The obligations-backed family-hull route now also has the constructed
  \(\IPL\) form.  Thus the public boundary simultaneously keeps the
  input-prime-strip link construction visible and projects the Step (xi)
  hull/determinant data, q-pilot positivity, and normalization from the single
  obligations object.  The experiment module exposes this as the corresponding
  constructed-\(\IPL\), obligations-backed family-hull dichotomy theorem.
\item The exact theta/family-hull identification now also has a
  Hodge-calibrated source form.  Instead of supplying
  \texttt{thetaSigned = familyHullLogVolume} directly, the source object
  factors the equality through the Hodge--Arakelov theta-monoid degree, and the
  experiment module exposes this route as
  \texttt{hodgeCalibratedFamilyHullFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The Hodge-calibrated family-hull route now has a constructed-\(\IPL\)
  form as well.  It keeps the input-prime-strip link construction visible while
  the Step (xi) source still factors the exact theta/family-hull equality
  through the Hodge--Arakelov theta-monoid degree.
\item This Hodge-calibrated route now has a charted refinement.  The source
  object calibrates the transported pre-ledger theta chart coordinate to the
  Hodge--Arakelov theta-monoid degree, and \Lean{} derives the package
  \texttt{thetaSigned} equality from the existing chart theorem.  The
  experiment module exposes this route as
  \texttt{chartedHodgeCalibratedFamilyHullFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The charted Hodge-calibrated route now also has the constructed-\(\IPL\)
  form.  The public boundary keeps the input-prime-strip link construction
  visible while retaining the chart-derived theta/Hodge scalar equality.
\item The charted Hodge/family-hull calibration now has a determinant-factored
  form.  The source object calibrates the Hodge--Arakelov theta-monoid degree
  to the normalized determinant log-volume of the record-native family hull,
  and \Lean{} derives the family-hull equality from the Ob5
  hull/determinant compatibility.  The experiment module exposes this route as
  \texttt{determinantChartedHodgeFamilyHullFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The determinant-factored route now has a summand-factored source form.
  The source object calibrates the Hodge--Arakelov theta-monoid degree to the
  finite sum of adjusted localization summands of the weighted determinant
  source; \Lean{} derives the determinant and normalized determinant
  equalities before entering the same finite-divisor endpoint.  The experiment
  module exposes this route as
  \texttt{summandChartedHodgeFamilyHullFiniteDivisorVerticalIQ\_cThetaDichotomy}.
\item The summand-factored route now also has a source-calibrated
  Hodge--Arakelov input form.  The source Hodge--Arakelov evaluation carries the
  full-label theta/Hodge log-volume calibration and projects the previous
  \texttt{IUTStage1SourceThetaHodgeLogVolumeCalibration} internally.  The
  experiment module exposes this boundary as the source-calibrated variant of
  the summand-charted finite-divisor theorem.
\item The same source-calibrated summand route now has a constructed-\(\IPL\)
  form.  Instead of receiving the certificate-pinned \(\IPL\)-link source and
  its endpoint equalities directly, the boundary consumes the Theorem 3.11
  input-prime-strip link construction source and projects the link source
  internally before entering the finite-divisor vertical-\(IQ\) endpoint.
\item The constructed-\(\IPL\), source-calibrated summand route now also has a
  synchronized Hodge--Arakelov input form.  The source object carries the
  calibrated source evaluation, target evaluation, and canonical one-label degree
  preservation together, so the public finite-divisor boundary no longer receives
  the Hodge/SHE synchronization equality separately.
\item The synchronized summand route now has a target-charted Step (xi) source
  form.  Instead of receiving the charted-theta/source-Hodge scalar equality as
  an immediate summand-calibration field, the source reads the transported theta
  chart as the target Hodge--Arakelov canonical one-label degree and derives the
  source theta-monoid degree equality from the synchronized canonical-one
  preservation.
\item The target-charted summand source now has a possible-image q-pilot form.
  The q-pilot region is fixed to the chosen Theorem 3.11 possible-image region,
  so the public Step (xi) source no longer carries a separate q-region and
  \(q\subseteq P_{\mathrm{choice}}\) proof.
\item The target-charted possible-image summand route now has a Hodge-layer
  charted synchronization form.  The target theta chart/canonical-one equality
  is projected from a target-charted Hodge--Arakelov synchronization object,
  while the Step (xi) source retains only the determinant summand equality and
  record-native possible-image hull data.
\item The target-charted possible-image route now factors the Hodge
  theta/summand comparison through a Hodge/determinant family-hull payload.
  This payload packages the record-native family-hull determinant source, the
  package measure calibration, and the Hodge theta-monoid/summand equality; the
  possible-image Step (xi) source then projects these fields instead of exposing
  them separately.  The source now also exposes the converted
  side-conditioned possible-image hull/determinant endpoint before the
  Hodge/\(\IPL\) wrapper is introduced.  The experiment surface exposes the
  payload endpoint, the determinant possible-image endpoint, this
  side-conditioned hull endpoint, the constructed-\(\IPL\) bridge audit, and
  the finite-divisor vertical-\(IQ\) \(C_\Theta\)-dichotomy route.
\item The synchronized target-charted possible-image summand/family-hull source
  now reduces to the constructor-built Step (xi) boundary.  The named audit
  records the fixed Theorem 3.11 possible-image q-region, target chart/source
  theta-monoid equality, finite adjusted-summand equality, theta/family-hull
  equality, obligations bridge equality, q-positivity, normalization, and the raw
  \(q_{\mathrm{signed}}\leq \theta_{\mathrm{signed}}\) comparison.  A
  product-hull companion audit now carries the Remark~3.9.5 smallest-product-hull
  provenance through this same synchronized source whenever its family-hull
  shadow is induced by a product-hull system.
\item The target-charted Hodge/\(\IPL\) side now has a packaged construction
  source.  It binds the target-charted Hodge--Arakelov synchronization to the
  constructed Theorem 3.11 input-prime-strip link, projects the finite
  Hodge/\(\SHE\) transport, and then projects the \(\IPL\) log-volume transport
  from that same finite transport.  The determinant possible-image bridge and
  finite-divisor vertical-\(IQ\) endpoint can now consume this single
  Hodge/\(\IPL\) payload instead of separate Hodge synchronization and
  constructed-\(\IPL\) arguments.  The construction source now also exposes the
  history-separated finite Hodge/\(\SHE\) transport-source endpoint and the
  constructed \(\IPL\) log-volume transport endpoint itself.  The all-in-one
  route projects these finer audits rather than reaching through the finite
  construction source directly.
\item The strongest target-charted finite-divisor corridor now has an
  all-in-one Step (xi) route source.  It binds the packaged Hodge/\(\IPL\)
  construction source to the determinant possible-image payload, and the
  experiment surface exposes the route-source endpoint, the
  Hodge--Arakelov theta-evaluation/Gaussian endpoint, the
  history-separated Hodge--Arakelov finite Hodge/\(\SHE\) transport-source
  endpoint, the finite Hodge/\(\SHE\) transport endpoint, the constructed
  \(\IPL\) log-volume transport-source endpoint, the constructed
  Hodge/\(\SHE/\IPL\) endpoint, the side-conditioned possible-image
  hull/determinant endpoint, the holomorphic-hull/log-volume endpoint, the
  canonical hull/tensor-power bridge endpoint, the source-boundary raw
  comparison endpoint, source-owned bridge endpoint, the bridge-level raw
  source-derived comparison endpoint, and finite-divisor packet-source and
  finite-divisor \(C_\Theta\)-dichotomy endpoints from this single object.
  It now also exposes a finite-source Step (x) boundary audit before the
  external \(C_\Theta\) numeric bound: the route-owned bridge data, raw
  source comparison, packet-local finite-source equalities, and vertical-\(IQ\)
  target equalities are all projected from the bundled route/source objects.
  The same route now has an exact vertical-\(IQ\) finite-source form: the
  realified log-Kummer Step (x) source retains the exact vertical-\(IQ\) target
  and transfer data, and the route projects its Kummer/forgetting
  compatibilities and \(FMOD\)-exact target internally.  This exact finite
  route is now also bundled as a single source package joining the Step (xi)
  route source, upper-semi entry, finite packet-local source, and exact
  vertical-\(IQ\) realified Step (x) source before the \(C_\Theta\) bound is
  applied.  The bundle also exposes the realified Step (x) correspondence
  audit: theta-root canonical-label data, Kummer/Frobenioid product
  preservation, mono-analytic forgetting, q-pilot non-interference, and the
  upper-semi inequality are projected from the retained exact source.  A
  compact source-derived corridor audit now records one load-bearing fact from
  each stage of the strongest chain: theta root, history-separated
  Hodge/\(\SHE\), constructed \(\IPL\), possible-image hull containment,
  raw comparison, exact vertical-\(IQ\), non-interference, and Step (x)
  upper-semi control.  A companion Gaussian-front audit starts one step
  earlier, at the Hodge--Arakelov theta-evaluation source: canonical theta
  labels, Gaussian zero degree, square-weighted degree formula, full-label
  log-volume compatibility, and target chart comparison are tied to the same
  corridor facts.
\item The finite-divisor vertical-\(IQ\) Hodge/\(\SHE/\IPL\)/hull endpoint now
  has a source-derived form: it consumes this separated bridge object instead
  of a prebuilt route alignment before constructing the same finite-divisor
  Step (x) source and proving the \(C_\Theta=-1\) boundary alternative or
  strict \(C_\Theta>-1\) conclusion.
\item The same finite-divisor vertical-\(IQ\) endpoint now also has the
  milestone-facing constructor form: it consumes the finite Hodge/\(\SHE\)
  transport source, a Theorem 3.11 \(\IPL\)-link construction source,
  record-native Step (xi) hull data, and the theta/Hodge calibration
  certificate directly.  The Step (xi) inputs are the record's possible-image
  union, \(q\subseteq P_{\mathrm{rec}}\), the holomorphic hull shadow, weighted
  determinant source, tensor-power bound, and bridge equality.  The endpoint
  constructs the \(\IPL\) log-volume transport, the hull/determinant source,
  and the source-derived Hodge/\(\SHE/\IPL\)/hull bridge internally, then
  applies the finite-divisor vertical-\(IQ\) route.
\item The constructor-backed finite-divisor endpoint now preserves the
  Remark~3.9.5 product-hull provenance.  A product-hull-backed wrapper records
  that the measured hull operator is induced by the product-hull system, and the
  audit proves selected-product-hull equality, q-pilot containment, minimality
  among product hulls containing \(P_{\mathrm{rec}}\), product-hull log-volume
  equality, and the same raw \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\)
  comparison before returning the downstream \(C_\Theta\) dichotomy.  The same
  wrapper now also exposes the Ob5 quotient/determinant compatibility at this
  product-hull boundary: for any nonempty comparison possible image, the q-choice
  possible image and comparison possible image have the same collapsed
  upper-semi quotient image modulo the selected product hull, and the selected
  hull log-volume is identified with the normalized determinant, determinant
  log-volume, and normalized tensor-power value.  The Ob5 scalar companion is
  now explicit as well: after quotienting the real line by the singleton
  \(\{\mu_{\log}(\phi(P_B))\}\), the normalized determinant scalar, ordinary
  determinant scalar, normalized tensor-power scalar, and family-hull
  log-volume scalar all have the same collapsed image.  This records the
  Remark~3.9.5(Ob5) assertion that the upper-semi formalism applies compatibly
  to \(\phi(P_B)\), \(\det^{\otimes M}(\phi(P_B))\), and
  \(\mu_{\log}(\phi(P_B))\).  Finally, the product-hull
  wrapper now projects to the source-facing possible-image family package: the
  Theorem~3.11 family \(P_B\), its canonical \(\Phi(P_B)\) approximant, and any
  supplied exact \(\Xi(P_B)\) family are audited at the same boundary, with
  \(H_{\Xi(P_B)}\) identified with the selected product hull.  The Ob6
  hull-approximant log-volume audit is also exposed at this boundary:
  \(H_{\Phi(P_B)}\) and \(H_{\Xi(P_B)}\) are both identified with the selected
  product hull, while the raw family union, comparison possible image, and
  q-pilot region are estimated by the corresponding hull-approximant
  log-volumes before the normalized determinant equality is invoked.  The same
  boundary now carries an exact-theta bridge audit: the package value
  \(\theta_{\mathrm{signed}}\) is identified with the Remark~3.9.5 family-hull
  log-volume, the normalized tensor-power/determinant upper bound is derived
  from this equality, and the q-pilot log-volume comparison is threaded through
  the selected product hull into \(\theta_{\mathrm{signed}}\).
\item The milestone-facing endpoint has a Hodge--Arakelov source form as well:
  it consumes source and target Hodge--Arakelov theta-evaluation sources,
  canonical one-label degree preservation, and a typed allowed-forgetting
  witness, then constructs the finite Hodge/\(\SHE\) transport internally.  In
  this form the canonical square-weight profile and theta-root source are read
  directly from the Hodge--Arakelov source side before the endpoint applies the
  same Theorem 3.11 \(\IPL\), record-native Step (xi), and finite-divisor
  vertical-\(IQ\) route.
\item A stronger Hodge--Arakelov endpoint removes even that explicit
  allowed-forgetting argument: it builds the finite Hodge/\(\SHE\) transport
  with the record's history-separated descent-bridge permission, then follows
  the same \(\IPL\), record-native Step (xi), and finite-divisor
  vertical-\(IQ\) path.
\item The strongest Hodge--Arakelov/history-separated endpoint can now use the
  certificate-pinned \(\IPL\)-link source.  Its public assumptions no longer
  include an arbitrary finite Hodge/\(\SHE\) transport, a free
  allowed-forgetting predicate, a free square-weight profile, a separate
  theta-root source, a constructed-\(\IPL\)-datum alignment, or the raw
  record-native Step (xi) hull/determinant field list.
\item The target-side theta-to-entry equality is no longer a direct input in the
  strongest route.  It is derived from a Step (x) theta-target alignment and
  calibration of the entry target with the upper-semi target value.
\item The Step (x) theta-target alignment can itself be derived from
  packet-normalized theta-source equality and calibration of the upper-semi
  target with the packet-normalized value.
\item The entry-target calibration can likewise be expressed by equality to the
  packet-normalized value, deriving equality with the upper-semi target.
\item The Step (xi-f) real algebra proves \(C_\Theta\ge-1\), strictness under
  strict upper-ray membership, and equality constraints in the boundary case.
\item The final route rejects the balanced sign-compatible comparison level as
  sufficient; it requires hull/log-volume comparison data.
\item The local Frobenioid shift model is now sourced by a \(p_v^N\)
  log-volume action package and a global realified calibration package; a
  non-automorphic local shift with nonzero step is separated from the calibrated
  value, and the upper-ray quotient experiment gives the exact threshold for
  collapse versus separation in the boundary upper ray.
\item Several downstream \IUT{} IV numerical estimates are formalized as
  ordered-real algebra conditional on the Corollary 3.12 input.
\end{enumerate}

The first-pass experiment report evaluates the route-theorem, finite Gaussian,
collapse-obstruction, upper-ray, and \IUT{} IV algebra flags to
\texttt{true}.  The flag \texttt{disputeSettledByCurrentStage} remains
\texttt{false}.

The current code base is large enough to distinguish three meanings of
``available''.  First, pure ordered-real consequences are proved outright.
Second, route theorems prove that certain named source-facing records imply the
desired endpoint.  Third, the records themselves remain obligations when they
stand for Hodge-theater, Frobenioid, log-Kummer, hull, determinant, or
multiradial constructions not yet formalized from \IUT{} I--III.  Only the first
two meanings are currently achieved.

\section{What Is Not Yet Proved}

No formal statement currently proves \IUT{} III, Corollary 3.12 from
Mochizuki's published hypotheses.  The following mathematics is still external
to the code:

\begin{enumerate}
\item initial \(\Theta\)-data and its arithmetic hypotheses from \IUT{} I;
\item Hodge theaters, Frobenioids, log-shells, prime strips, and theta links;
\item the Hodge--Arakelov theta evaluation and Gaussian monoids of \IUT{} II;
\item the construction of the actual \((\Ind1),(\Ind2),(\Ind3)\) data in
  Theorem 3.11;
\item the genuine holomorphic hull and determinant constructions used in
  Step (xi), beyond the present source-data constructor and ordered-real
  upper-ray model;
\item the full proof that the typed \SHE{} and Hodge-descent transport
  obligations follow from Mochizuki's source constructions, beyond the current
  Hodge--Arakelov canonical-one synchronization shadow;
\item the construction of the input prime-strip link \((\IPL)\), simultaneous
  holomorphic expressibility \((\SHE)\), and algorithmic parallel transport
  \((\APT)\) properties as actual consequences of Theorem 3.11 rather than
  records;
\item the arithmetic-divisor, height, log-different, and log-conductor
  constructions behind the \IUT{} IV Diophantine applications.
\end{enumerate}

\section{Implementation Audit}

The code contains no explicit placeholder proofs or project-level trust-boundary declarations in the
Stage 1 corridor.  The current risk is not hidden unsoundness of this form, but
mathematical incompleteness: several records are deliberately named
obligation interfaces.  These interfaces are acceptable only as temporary
boundaries.  The next phase must replace them by constructions from the source
papers or mark them as unresolved.

For the Source-Derived Step (xi) Bridge milestone, the checked public endpoint is
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ}.
\end{array}
\]
Its direct audit companion is
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ}\\
\quad\texttt{\_withDirectMilestoneAudit}.
\end{array}
\]
Both declarations have been added to the \texttt{checkdecls} list.  A kernel
\texttt{\#print axioms} check for these two declarations, the explicit
constructed-\(\IPL\) alias, and the underlying namespaced constructed-\(\IPL\)
endpoint reports only \texttt{propext}, \texttt{Classical.choice}, and
\texttt{Quot.sound}; in particular, no \texttt{sorryAx} appears.  Thus the
milestone is kernel-clean at the usual Lean classical/quotient trust boundary.

The Remark~3.9.5 holomorphic-hull/determinant milestone has now started at the
source-object level.  The new declaration
\texttt{IUTStage1Remark395HolomorphicHullOperator} records the source-facing
\(\phi\)-operator laws directly: closed hulls are fixed, \(P\subseteq\phi(P)\),
inclusions are preserved, \(\phi(\phi(P))=\phi(P)\), and log-volume is
monotone.  It projects to the older closure-operator shadow used by the
existing bridge code, but the public source object no longer begins with that
shadow.  This has now been backed by the earlier construction in
Remark~3.9.5(ii): \texttt{IUTStage1Remark395HolomorphicHullSystem} defines
\(\phi(P)\) as the intersection of all hulls that contain \(P\).  Its only
source closure input is that this intersection is again a hull; \Lean{} then
derives P1--P3, idempotence, and
\(\mu_{\log}(P)\leq\mu_{\log}(\phi(P))\), before projecting to the existing
\(\phi\)-operator interface.
The possible-image family layer has also been made source-facing:
\texttt{IUTStage1Remark395PossibleImageFamilySource} records the family
\(P_B=\{P_\beta\}_{\beta\in B}\), its union, the canonical hull
\(\phi(P_B)\), the \(\Phi(P_B)\) and \(\Xi(P_B)\) approximant types projected
from this \(\phi\)-operator, and the Remark~3.9.5(Ob5) upper-semi quotient
collapse.  The experiment-surface declaration
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.remark395PossibleImageFamilySource\_endpoint}
\end{array}
\]
proves that the family union and each possible image lie in \(\phi(P_B)\), that
the canonical \(\Phi\)-approximant is \(\phi(P_B)\), and that any two nonempty
possible regions have the same quotient image after collapsing \(\phi(P_B)\).
The exact-approximant companion
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.remark395PossibleImageFamilySource}\\
\quad\texttt{\_XiFamilyOb5Endpoint}
\end{array}
\]
proves the same Ob5 collapse for \(H_{\Xi(P_B)}\), while recording that each
chosen exact approximant has log-volume \(\mu_{\log}(P_B)\).
This supplied-family endpoint is now accompanied by the more source-local
constructor
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.remark395PossibleImageExactXiFamilySource}\\
\quad\texttt{\_toXiFamilyOb5Endpoint}
\end{array}
\]
and its Ob6 companion.  These endpoints start only from the exactness
calibration \(\mu_{\log}(\phi(P_B))=\mu_{\log}(P_B)\), build the canonical
exact \(\Xi(P_B)\)-family, and then recover the same quotient collapse and
log-volume comparison.  Thus this part of the corridor now records the
specific mathematical equality needed to make \(\phi(P_B)\) exact, instead of
treating the whole \(\Xi(P_B)\)-family as primitive.
The same boundary has now been lowered to the concrete Hodge-theater/log-theta
quotient source.  The declaration
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaConcreteCalibratedExactXi}\\
\quad\texttt{SelectedQRemark395GlobalCThetaAudit}
\end{array}
\]
constructs the exact \(\Xi(P_B)\)-source from the typed quotient
possible-image family and a single source-local calibration
\(\mu_{\log}(\phi(P_B))=\mu_{\log}(P_B)\).  Hence the remaining analytic
payload is no longer a primitive exact-\(\Xi\) family; it is precisely the
paper-side proof of this calibration for the selected quotient possible-image
union.
For the closed-family case this has been lowered once more.  The source
\texttt{ConcreteClosedFamilyUnionExactXiSource} asks only that the concrete
quotient possible-image union be closed for the Remark~3.9.5 hull operator;
\Lean{} then proves \(\phi(P_B)=P_B\) by the hull fixing law and derives
\(\mu_{\log}(\phi(P_B))=\mu_{\log}(P_B)\).  Thus the exactness obligation is
now split into a closed-region route and the remaining non-closed analytic
calibration route.
The closed-region route now has product-hull provenance.  The source
\texttt{ConcreteProductHullFamilyUnionExactXiSource} replaces bare closedness
by the assertion that the quotient possible-image union is a product hull for
the Remark~3.9.5 product-hull system whose induced holomorphic hull operator is
the corridor operator.  From this product-hull witness, \Lean{} constructs the
closed-family exact-\(\Xi(P_B)\) source and enters the same global
\(C_\Theta\) audit.  This has a principal valuation-ball refinement:
\texttt{ConcretePrincipalValuationBallFamilyUnionExactXiSource} starts from a
Remark~3.9.5 valuation-ball product-hull cover and identifies the resulting
valuation-cover union with the selected principal hull \(\lambda\cdot O\).
The sharper source
\texttt{ConcreteValuationBallIndexedFamilyUnionSource} no longer takes the
quotient-family/valuation-cover union equality as primitive: it requires an
equivalence between the Theorem~3.11 quotient index and the valuation-cover
index, plus pointwise equality of the corresponding possible regions, and
\Lean{} derives the union equality.  This comparison has now been lowered one
more step by
\texttt{ConcreteValuationBallChoiceIndexedFamilyUnionSource}: instead of
supplying the quotient-index equivalence, the source data supplies a
choice-level valuation index map, proves that it is invariant under the
typed \((\Ind1,\Ind2)\) equality quotient, gives a representative
Hodge-theater/log-theta choice over each valuation index, and proves pointwise
equality of the corresponding possible regions.  \Lean{} constructs the
quotient-index equivalence by \texttt{Quot.lift} and then derives the same
valuation-cover union equality.  The current preferred form specializes this
once more to the theta-pilot class itself:
\texttt{ConcreteValuationBallThetaClassIndexedFamilyUnionSource} fixes the
valuation-cover index to the forgotten Hodge-theater/log-theta-lattice class,
proves theta-class invariance across the generated \((\Ind1,\Ind2)\) equality
relation, and derives the choice-indexed valuation source from representative
choices in each theta class.  This has now been lowered to the fiber-backed
source
\texttt{ConcreteValuationBallThetaClassFiberBackedFamilyUnionSource}.  Its
representative fiber relation is no longer supplied: \Lean{} builds the
representative-to-choice relation as the canonical finite \((\Ind1)\)
procession shift followed by the typed post-procession \((\Ind2)\) local
tensor transport already present in the Theorem~3.11 source audit.  The
valuation-indexing payload at this boundary is therefore only the pointwise
equality between quotient possible regions and theta-class valuation cells.
That pointwise quotient comparison has now also been factored through concrete
theta-pilot possible images.  The source
\texttt{ConcreteValuationBallThetaClassImageBackedFamilyUnionSource} supplies a
theta-pilot-class possible-image family, identifies the record's
choice-indexed possible images with the pullback of that class family, and
identifies each class image with the corresponding valuation-ball region.
\Lean{} then uses the Theorem~3.11 equality-quotient pullback theorem to derive
the quotient-region/valuation-region comparison required by the older
fiber-backed boundary.  This has now been lowered through
\texttt{ConcreteValuationBallThetaClassRegionBackedFamilyUnionSource} and
\texttt{ConcreteValuationBallThetaClassLatticeFormulaBackedFamilyUnionSource}.
At this new boundary, the possible images are generated by the
Hodge-theater id, history label, finite-label-forgotten log-theta-lattice
coordinate, and coric datum already present in the concrete
Hodge-theater/log-theta-lattice formula records.  The valuation comparison is
then a source-facing identification between those lattice-formula theta regions
and the corresponding valuation-ball regions, not an arbitrary
choice-indexed quotient comparison.  The boundary has now been lowered one
step further by
\texttt{ConcreteValuationBallThetaClassLatticeImageLawBackedFamilyUnionSource}.
Here \Lean{} constructs the lattice formula and the record-level family
equality from a single lattice-key invariance law: choices with the same
Hodge-theater id, history label, finite-label-forgotten log-theta-lattice
coordinate, and coric datum have the same Theorem~3.11 possible-image region.
The boundary has now been lowered again by
\texttt{ConcreteValuationBallThetaClassFiberTransportBackedFamilyUnionSource}.
The lattice-key image law is no longer the primitive source input: the current
packet/action transport source is first forgotten through the typed
\((\Ind1,\Ind2)\) procession/local-tensor chain to a theta-pilot
fiber-transport invariant possible-image family, and \Lean{} derives the
lattice image law from that fiber-transport invariance.  The valuation-side
payload at this point is therefore the identification of the derived
theta-pilot class regions with the corresponding valuation-ball regions.
The log-volume side of this same concrete choice space has now been lowered by
\texttt{ProcessionNormalizedLogVolumeSource}.  Instead of accepting an
arbitrary \texttt{IndeterminacyData} record, the source assigns to each
theta-pilot class an actual averaged \(Z/\ell Z\)-label procession log-volume.
\Lean{} defines the log-volume of a concrete Hodge-theater/log-theta choice as
this class average, proves the displayed average formula with
\(|Z/\ell Z|=\ell\), derives the old \texttt{IndeterminacyData} record, and
constructs the typed core used by the quotient possible-image machinery.  Thus
the equality side of the indeterminacy layer is now built from finite
procession averages; only the \((\Ind3)\) upper-semi comparison remains a
one-sided source input at this boundary.  The next lowering is now also in
place: \texttt{LogThetaLabelProcessionUpperSemiSource} supplies the
label-by-label log-theta values over the canonical full \(F_\ell\)-procession
of a theta-pilot class, and \Lean{} constructs the averaged source internally.
The open mathematical input below this point is the source-paper construction
of those label-wise values and the two average equalities with the
source/target upper-semi log-volume comparison.
The selected-principal-hull equality has also been lowered:
\texttt{ConcreteValuationBallSelectedPrincipalHullSource}
requires the valuation-cover possible-image union to be a hull for its
Remark~3.9.5 hull system, and \Lean{} combines this fixed-point statement with
the principal-hull selection theorem to derive equality with the selected
\(\lambda\cdot O\) hull.  This has now been lowered to the direct-product-cell
exact source
\texttt{ConcreteValuationBallDirectProductCellUnionExactSource}: it records
that the valuation possible-image union is exactly the finite union of the
valuation-ball direct-product cells, and \Lean{} derives both hull-fixedness
and equality with the selected principal hull from the already formalized
Remark~3.9.5 principal-hull theorem.  The preferred boundary has now been
lowered once more by
\texttt{ConcreteValuationBallDirectProductCellCoverSource}.  Here the formal
direction
\[
  \bigcup P_{\Theta} \subseteq \bigcup_{\beta} H_{\beta}
\]
comes from hull containment together with the valuation-cover theorem
\(\phi(\bigcup P_{\Theta})=\bigcup_{\beta}H_{\beta}\).  The only source-facing
payload is the reverse local cover statement: every valuation-ball
direct-product cell \(H_{\beta}\) lies in the theta possible-image union.
This has now been sharpened by
\texttt{ConcreteValuationBallThetaClassDirectProductCellCoverSource}: each
valuation cell carries a theta-pilot class, and the local cover proof is the
containment of that cell in the corresponding theta-class possible region.
\Lean{} derives the older union-cover interface from these per-cell
containments.  The transported-region version
\texttt{ConcreteValuationBallThetaClassFiberTransportCellCoverSource} states
the containment before forgetting to the valuation cover, i.e. each
\(H_\beta\) lies in the transported theta-class region attached to its
theta-pilot class, and \Lean{} derives both the valuation-region equality
interface and the theta-class cell cover.  The current preferred boundary is
one step lower:
\texttt{ConcreteValuationBallThetaClassFiberTransportLocalFactorCoverSource}.
For each valuation cell it chooses a theta-pilot class and a local place, and
requires containment of the corresponding compact-open valuation-ball factor in
the transported theta-class region.  Since \(H_\beta\) is the direct product of
these local factors, \Lean{} derives the previous whole-cell containment.  The
preferred boundary is now the local predicate source
\texttt{ConcreteValuationBallThetaClassFiberTransportLocalThetaPredicateSource}.
For the selected local place it identifies the transported theta region with
the realization of a local predicate \(T_\beta(x)\), and requires the local
estimate
\[
  \|x\|_v\le r_\beta
  \quad\Longrightarrow\quad
  T_\beta(x),
\]
where \(r_\beta\) is the compact-open radius chosen by the local Haar
normalization.  \Lean{} realizes this predicate region to recover the pointwise
theta membership, then uses
\(\mathrm{realizedRegion}(S)=\mathrm{realization}(S)\) and the valuation-ball
audit \(\mathrm{compactOpenSubset}=\mathrm{valuationBall}(r_\beta)\) to recover
the valuation-radius, local-factor, and direct-product cell covers.  This has
now been lowered one step further by
\texttt{ConcreteValuationBallThetaClassFiberTransportLocalThetaInequalitySource}.
Here the local predicate is not opaque: it is the inequality
\[
  g_\beta(x)\le R_\beta
\]
for a named local theta gauge and threshold, and the source estimate proves
\[
  \|x\|_v\le r_\beta\quad\Longrightarrow\quad g_\beta(x)\le R_\beta.
\]
\Lean{} then reconstructs the local-predicate source definitionally and enters
the same exact-\(\Xi(P_B)\) and global \(C_\Theta\) corridor.  The gauge has now
been specialized to the valuation-ball normalization itself by
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationNormGaugeSource}:
\[
  g_\beta(x)=\|x\|_v,\qquad R_\beta=r_\beta .
\]
Thus the implication
\(\|x\|_v\le r_\beta\Rightarrow g_\beta(x)\le R_\beta\) is no longer a
mathematical assumption.  The equality boundary has also been lowered twice.
First,
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallExactSource}
replaces the two equalities needed by the valuation-norm gauge source with the
two inclusions
\[
  P_{\Theta,\beta}\subseteq \mathrm{realizedRegion}(B_\beta),
  \qquad
  \mathrm{realizedRegion}(B_\beta)\subseteq P_{\Theta,\beta}
\]
and the analogous two inclusions between a transported theta-class region and
the valuation-cover possible-image region.  \Lean{} reconstructs both
equalities by antisymmetry and then enters the same valuation-norm-gauge
endpoint.  The next boundary is the pointwise source
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallPointwiseSource}.
It replaces the set containments by the local lifting law
\[
  y\in P_{\Theta,\beta}\Longrightarrow
  \exists x,\ \|x\|_v\le r_\beta\ \wedge\ \mathrm{realization}(x)=y,
\]
the reverse realization law
\[
  \|x\|_v\le r_\beta\Longrightarrow
  \mathrm{realization}(x)\in P_{\Theta,\beta},
\]
and pointwise membership compatibility with the valuation-cover possible
regions.  The set containments and equalities are now projections from these
local transport laws.  This lifting law has now been lowered once more by
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallLocalChartSource}:
for each transported theta point \(y\), the source names its local coordinate
\(x_\beta(y)\), proves
\[
  \|x_\beta(y)\|_v\le r_\beta,\qquad
  \mathrm{realization}(x_\beta(y))=y.
\]
This removes the existential lift, but at this stage the valuation-radius bound
is still a raw source field.
The image boundary is now an intermediate layer:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallLogShellImageSource}.
\end{array}
\]
It names a local log-shell region \(I_\beta\), a base point used only outside
the transported theta region, the realized-image equality presented as the two
containments
\[
  P_{\Theta,\beta}\subseteq \mathrm{realization}(I_\beta),
  \qquad
  \mathrm{realization}(I_\beta)\subseteq P_{\Theta,\beta},
\]
and the two valuation-ball containments
\[
  I_\beta\subseteq \{x:\|x\|_v\le r_\beta\},
  \qquad
  \{x:\|x\|_v\le r_\beta\}\subseteq I_\beta.
\]
\Lean{} chooses \(x_\beta(y)\) from the image statement when
\(y\in P_{\Theta,\beta}\), proves \(x_\beta(y)\in I_\beta\) and
\(\mathrm{realization}(x_\beta(y))=y\), derives the valuation-radius inequality
from \(I_\beta\subseteq \{x:\|x\|_v\le r_\beta\}\), and then reuses the
local-chart, pointwise, exact, and valuation-norm-gauge routes.
The next boundary replaces these four containments by the two equalities
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallLogShellExactSource}.
\end{array}
\]
It requires
\[
  P_{\Theta,\beta}=\mathrm{realization}(I_\beta),
  \qquad
  I_\beta=\{x:\|x\|_v\le r_\beta\},
\]
and \Lean{} derives the previous log-shell image source, the chosen local
coordinate, the valuation-radius bound, and the same exact-\(\Xi(P_B)\)/global
\(C_\Theta\) audit.  The next boundary is
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallLogShellNonemptyExactSource}.
\end{array}
\]
It replaces the supplied totalizing coordinate by the nonemptiness statement
\(I_\beta\ne\varnothing\); \Lean{} chooses the auxiliary coordinate from this
nonemptiness and then projects to the equality-backed exact source.  The
preferred lower boundary is now
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportValuationBallNonemptyExactSource}.
\end{array}
\]
It moves nonemptiness to the valuation-ball side:
\[
  \{x:\|x\|_v\le r_\beta\}\ne\varnothing.
\]
Using \(I_\beta=\{x:\|x\|_v\le r_\beta\}\), \Lean{} derives
\(I_\beta\ne\varnothing\), then derives the previous nonempty log-shell
boundary and the same exact-\(\Xi(P_B)\)/global \(C_\Theta\) audit.  This
nonemptiness hypothesis has now itself been lowered to a centered valuation
ball source:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportCenteredValuationBall}\\
\texttt{ExactSource}.
\end{array}
\]
For each local factor it supplies a point \(x_\beta\) and proves
\[
  \|x_\beta\|_v \le r_\beta.
\]
After unfolding the valuation-ball definition, \Lean{} obtains
\(x_\beta\in\{x:\|x\|_v\le r_\beta\}\), hence valuation-ball nonemptiness,
log-shell nonemptiness, and the same exact-\(\Xi(P_B)\)/global \(C_\Theta\)
audit.  This has now been lowered once more to the zero-centered source
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportZeroCenteredValuationBall}\\
\texttt{ExactSource}.
\end{array}
\]
Here the center is fixed to \(0\).  The source supplies only
\[
  \|0\|_v \le r_\beta,
\]
and \Lean{} constructs the centered source with \(x_\beta=0\).  The next
boundary is metric-normalized:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportMetricZeroValuationBall}\\
\texttt{ExactSource}.
\end{array}
\]
It no longer supplies the zero inequality.  Instead it records, for each
local factor, the normalization
\[
  \|x\|_v=\operatorname{dist}(x,0).
\]
Together with the already available positivity \(0<r_\beta\), \Lean{} proves
\(\|0\|_v\le r_\beta\) using \(\operatorname{dist}(0,0)=0\), then projects to
the zero-centered endpoint.  The log-shell boundary has also been lowered:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportConstructedLogShell}\\
\texttt{MetricZeroValuationBallExactSource}.
\end{array}
\]
Here the local log-shell attached to a factor is no longer an independent
set.  It is defined to be the compact-open valuation ball
\[
  \{x:\|x\|_v\le r_\beta\},
\]
so the log-shell/valuation-ball equality is definitional.  The remaining
realization equality has now been factored into pointwise local transport:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportPointwiseConstructed}\\
\texttt{LogShellMetricZeroValuationBallExactSource}.
\end{array}
\]
This source no longer supplies
\(\Theta_\beta=\operatorname{realize}(\{x:\|x\|_v\le r_\beta\})\) directly.
It supplies the two local assertions: every transported theta-region point has
a lift in the compact-open valuation ball, and every local point in that ball
realizes back into the transported theta region.  \Lean{} converts these
assertions to the two set inclusions using the factor's
\(\texttt{realizedRegion\_eq\_image}\) law and then obtains the equality by
antisymmetry.  A further source,
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportRegionBackedPointwise}\\
\texttt{ConstructedLogShellMetricZeroValuationBallExactSource},
\end{array}
\]
removes the duplicated pointwise membership assumptions at this boundary.  It
uses the fiber-transport-backed equality
\[
  \Theta_{\mathrm{class}}=
  P_{\Theta_{\mathrm{class}}}
\]
between the transported theta-class region and the valuation-cover possible
region, and \Lean{} derives the two membership directions by rewriting.  The
classwise equality is now itself derived from the sharper source
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{FamilyUnionSource}.
\end{array}
\]
There the valuation-cover possible-region family is identified once with the
transported theta-region family; evaluating this family equality at a
theta-pilot class gives the previous classwise comparison.  The corresponding
pointwise source then reuses this family-level construction when deriving
valuation-cover membership.  The construction boundary has now moved inside
the valuation cover:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{ValuationCoverSource}
\end{array}
\]
builds the Remark~3.9.5 valuation-ball/Haar tensor-packet cover with
\(P_\beta\) fixed definitionally to the transported theta-region family.  Its
principal product-hull wrapper projects to the ordinary principal
valuation-ball source, and the previous family-level equality is then
\texttt{rfl}.  This boundary now also has a source-core constructor: a
Remark~3.9.5 factor-calibrated valuation-ball/Haar cover, or its principal
valuation-ball product-hull wrapper, constructs the theta-region-defined
Step~(xi) cover as soon as its possible-image family is identified with the
transported theta-region family.  The newest constructor derives this
family-level equality from the fiber-transport-backed pointwise comparison by
function extensionality, and there is now a lattice-image-law-backed version:
once the lattice image law used in the valuation comparison is identified with
the one produced by the fiber-transport source, the same principal
theta-region-defined cover is constructed.  When the lattice law is obtained
by projecting a fiber-transport-backed source, this identification is now a
named \texttt{rfl} theorem and the public endpoint routes through the
lattice-image-law constructor without an extra equality argument.  Thus the
finite-additive Haar tensor factors, principal \(\lambda O\) hull,
local-integer region, and selected-hull log-volume identity are inherited from
the source-core object instead of being re-supplied in the Step~(xi) source.
The remaining source-facing payload at this boundary is the construction of
the fiber-transport comparison itself, and for independently supplied lattice
laws the proof that they are the fiber-transport lattice law, from the
paper-native log-theta transport.  The local analytic boundary is now
connected directly to this constructed principal cover:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{PrincipalValuationBallPointwiseConstructedLogShellMetricZero}\\
\texttt{ValuationBallExactSource}.
\end{array}
\]
This source carries the metric normalization \(\|x\|_v=\operatorname{dist}(x,0)\)
and the two pointwise local transport laws between transported theta-region
points and compact-open valuation balls, while the valuation-cover
possible-region family is fixed definitionally by the principal source.  \Lean{}
derives the realized valuation-ball equality, projects it to the
theta-region-defined radius-cover source, obtains direct-product-cell exactness,
and then feeds the principal exact-\(\Xi\) source.  Thus the remaining
paper-side payload has been narrowed to the actual construction of the local
analytic coordinate and the reverse valuation-ball realization law.  The newest
declaration
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{PrincipalValuationBallLocalChartMetricZeroValuationBallExactSource}
\end{array}
\]
replaces the forward existential lifting law by a named map
\(x_\beta(y)\in K_v\).  Its fields assert the valuation-radius bound
\(\|x_\beta(y)\|_v\le r_\beta\), the realization identity
\(\operatorname{real}_\beta(x_\beta(y))=y\), the metric normalization, and the
reverse statement that each selected valuation-ball point realizes back into
the transported theta region.  \Lean{} derives the pointwise lift, recovers the
previous principal pointwise source, and hence recovers the exact realized
valuation-ball identity and selected-principal-hull conclusion.  This boundary
has now been lowered to an image-backed log-shell source:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{PrincipalValuationBallLogShellImageMetricZeroValuationBallExactSource}.
\end{array}
\]
Instead of supplying \(x_\beta(y)\) as chart data, it records the two
containments
\[
  P_{\Theta,\beta}\subseteq \operatorname{real}_\beta(I_\beta),
  \qquad
  \operatorname{real}_\beta(I_\beta)\subseteq P_{\Theta,\beta},
\]
and the two containments identifying \(I_\beta\) with the compact-open
valuation ball.  \Lean{} chooses \(x_\beta(y)\) from the first image
containment, proves \(\operatorname{real}_\beta(x_\beta(y))=y\), derives the
radius bound from \(I_\beta\subseteq\{x:\|x\|_v\le r_\beta\}\), and derives the
reverse realization law from
\(\{x:\|x\|_v\le r_\beta\}\subseteq I_\beta\) together with the second image
containment.  The log-shell itself has now been lowered to the compact-open
local shell:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{PrincipalValuationBallCompactOpenLogShellImageMetricZero}\\
\texttt{ValuationBallExactSource}.
\end{array}
\]
Here \(I_\beta\) is definitionally the selected factor's compact-open subset.
The equality between this compact-open subset and
\(\{x:\|x\|_v\le r_\beta\}\) is read from the valuation-ball additive Haar
normalization audit, so the two log-shell/valuation-ball containments are no
longer source fields.  The preferred boundary has also been lowered once more
to a compact-open local-chart source:
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{PrincipalValuationBallCompactOpenLocalChartMetricZero}\\
\texttt{ValuationBallExactSource}.
\end{array}
\]
This source gives compact-open representatives
\(x_\beta(y)\in U_\beta\) for transported theta-region points and the converse
law that every \(u\in U_\beta\) realizes back into \(P_{\Theta,\beta}\).
Using the valuation-ball additive Haar identity
\(U_\beta=\{x:\|x\|_v\le r_\beta\}\), it now also constructs the pointwise
valuation-ball source that feeds log-shell exactness.
Using the local analytic identity
\(\operatorname{realizedRegion}(U_\beta)=\operatorname{real}_\beta''U_\beta\),
\Lean{} derives the two compact-open image containments
\[
  P_{\Theta,\beta}\subseteq
    \operatorname{real}_\beta(U_\beta),
  \qquad
  \operatorname{real}_\beta(U_\beta)\subseteq P_{\Theta,\beta}
\]
and then enters the source-derived global \(C_\Theta\) audit.  The remaining
frontier has now been lowered to the exact compact-open realized-region source
\[
\begin{array}{l}
\texttt{ConcreteValuationBallThetaClassFiberTransportThetaRegionDefined}\\
\texttt{PrincipalValuationBallCompactOpenRealizedExactSource}.
\end{array}
\]
Its local payload is the single identity
\[
  P_{\Theta,\beta}=\operatorname{real}_\beta(U_\beta).
\]
From this equality and
\(\operatorname{realizedRegion}(U_\beta)=\operatorname{real}_\beta''U_\beta\),
\Lean{} chooses compact-open coordinates, proves the converse realization law,
recovers the compact-open local-chart source, and enters the same global
\(C_\Theta\) audit.  This compact-open boundary is now itself a projection from
the valuation-ball realized-exact source: if
\[
  P_{\Theta,\beta}
    =\operatorname{realizedRegion}\{x:\|x\|_v\le r_\beta\},
\]
then the valuation-ball additive Haar audit identifies the selected
compact-open subset \(U_\beta\) with this closed ball, and \Lean{} derives the
compact-open realized source.  The equality-backed log-shell package is also
now recovered from local containments.  On the compact-open branch, the two
image containments
\[
  P_{\Theta,\beta}\subseteq \operatorname{realizedRegion}(U_\beta),\quad
  \operatorname{realizedRegion}(U_\beta)\subseteq P_{\Theta,\beta}
\]
already construct the compact-open realized-exact source by antisymmetry, so
the preferred \(C_\Theta\) audit no longer has to pass through an arbitrary
log-shell equality package.  The more general log-shell source is still
recovered from the four containments
\[
  P_{\Theta,\beta}\subseteq \operatorname{realizedRegion}(I_\beta),\quad
  \operatorname{realizedRegion}(I_\beta)\subseteq P_{\Theta,\beta},\quad
  I_\beta\subseteq B_\beta(r_\beta),\quad
  B_\beta(r_\beta)\subseteq I_\beta,
\]
so the source need not assert these set equalities at the first boundary.
The compact-open local-chart boundary has also been lowered through a
log-Kummer graph formulation.  First, a graph source may supply a local
realization relation on \(U_\beta\times P_{\Theta,\beta}\); left-totality,
realization compatibility, and right-soundness recover compact-open
coordinates.  Second, and more canonically, the compact-open image source now
defines this relation to be the graph of the selected realization map
\[
  x\sim_\beta y \quad\Longleftrightarrow\quad
  \operatorname{real}_\beta(x)=y .
\]
The two image containments then prove the graph laws.  Thus the local
log-Kummer graph is no longer an independent payload at this boundary.  The
graph source also constructs the pointwise local valuation-ball source:
compact-open graph lifts are converted to valuation-radius lifts by the
additive Haar normalization, and right-soundness gives the converse
valuation-ball realization law.  Thus the graph route can now pass through
pointwise local construction, log-shell exactness, compact-open image
compatibility, and finally the global \(C_\Theta\) audit.
The containments themselves were first lowered to the valuation-cover side by the
single equality
\[
  P_{\mathrm{cover}}(\Theta_\beta)
    =\operatorname{realizedRegion}(U_\beta),
\]
where \(P_{\mathrm{cover}}\) is the Remark~3.9.5 valuation-cover possible
region.  Since the principal cover is constructed with
\(P_{\mathrm{cover}}(\Theta)=P_\Theta\), \Lean{} rewrites this equality to
derive both compact-open image containments, the realized-exact source, and the
canonical graph route.  This equality is now itself derived from a local
log-Kummer image source: every point of
\(P_{\mathrm{cover}}(\Theta_\beta)\) has a lift in \(U_\beta\), and every
point of \(U_\beta\) realizes back into
\(P_{\mathrm{cover}}(\Theta_\beta)\).  That image source now constructs the
map-level local log-Kummer source.  \Lean{} takes the local Kummer realization
map to be the selected valuation-factor realization
\[
  \kappa_\beta:K_\beta\longrightarrow\operatorname{Pt}(\mathbb L_\Theta),
\]
and chooses a section of \(\kappa_\beta\) over the selected
Remark~3.9.5 possible region from canonical graph left-totality.  It then
defines the local correspondence as the graph of \(\kappa_\beta\), derives
realization compatibility, compact-open soundness, the image source, cover
exactness, and the global \(C_\Theta\) audit.  Since the principal cover has
\(P_{\mathrm{cover}}(\Theta_\beta)=P_{\Theta,\beta}\) definitionally, the same
map source now also lowers to the theta-region graph source and hence through
the pointwise valuation-ball, log-shell exact, compact-open image route before
the global \(C_\Theta\) audit.  The compact-open image laws are
now also downstream of a log-shell exact source: the two equalities
\[
  P_{\Theta,\beta}=\operatorname{real}_\beta(L_\beta),
  \qquad L_\beta=U_\beta
\]
construct the compact-open route using the valuation-ball Haar normalization.
These equalities are no longer only accepted as an exact source: the pointwise
local construction, which supplies a local representative of each theta-region
point and the converse realization law for the compact-open valuation ball,
constructs the exact source.  Those pointwise laws are now themselves
constructed from compact-open local-chart data, and the compact-open
log-Kummer graph source projects to that local-chart boundary.  The remaining
frontier is the construction of the graph/local-chart laws from the
paper-native holomorphic hull, log-Kummer, and local log-shell geometry.
There is now also an \texttt{ofHullSystem} constructor and experiment endpoint:
starting from the intersection-defined hull system and a family
\(\{P_\beta\}\), \Lean{} constructs the possible-image source and proves that
the canonical hull is precisely the system's \(\phi(\bigcup_\beta P_\beta)\),
which is a hull by the intersection-closure input.  Thus the Ob5 quotient
collapse for possible images is already downstream of the minimal-hull
construction, not merely of a supplied \(\phi\)-operator.
The product-hull source now has a direct-product constructor as well:
\texttt{IUTStage1Remark395DirectProductHullSystemSource} defines product hulls
as coordinate products, defines the selected hull parameter by coordinate
projections of the region, and proves the ``smallest product hull'' equality
before projecting to the existing product-hull and holomorphic-hull systems.
The determinant side now has a source-facing Ob3/Ob4 package as well:
\[
\begin{array}{l}
\texttt{IUTStage1Remark395Ob3Ob4AdjustedDeterminantSource}.
\end{array}
\]
It records localization summands, the structure-sheaf adjustment \(O(-)\),
weighted adjusted log-volumes, the positive tensor power \(M\), and the
normalized determinant log-volume before projecting to the older weighted
determinant skeleton.  The experiment-surface theorem
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.remark395Ob3Ob4AdjustedDeterminantSource}\\
\quad\texttt{\_endpoint}
\end{array}
\]
checks the adjusted-summand formula, determinant summation, tensor-power
formula, and normalized determinant equality.  The constructed Step~(xi)
source also has a constructor
\texttt{ofOb3Ob4AdjustedDeterminantSource} whose endpoint verifies that this
source-facing Ob3/Ob4 package is the determinant source used by the existing
hull/determinant corridor.
This determinant package now has a lower source-facing constructor layer.  The
new objects
\[
\begin{array}{l}
\texttt{IUTStage1LocalizedArithmeticVectorBundle},\\
\texttt{IUTStage1StructureSheafAdjustedLocalizedVectorBundleSource},\\
\texttt{IUTStage1Remark395Ob3Ob4LocalizedVectorBundleDeterminantSource}
\end{array}
\]
separate the local-ring-labelled vector-bundle localization of Step~(xi-d) from
the later \(O(-)\) structure-sheaf adjustment and determinant/tensor-power
normalization.  Their experiment endpoints prove that the localized
rank-\(>1\) direct-summand log-volume projects to the adjusted localization
source, and that the resulting Ob3/Ob4 determinant source has the same weighted
summand formula and normalized determinant equality as the older adjusted
determinant package.
The Ob3/Ob5 determinant-compatibility input has also been separated from the
low-level certificate:
\[
\begin{array}{l}
\texttt{IUTStage1Remark395Ob3Ob5DeterminantCompatibilitySource}.
\end{array}
\]
This object states, at the possible-image-family level, that
\(\mu_{\log}(\phi(P_B))\) is the normalized weighted-determinant log-volume.
Lean derives the older
\texttt{IUTStage1HullApproximantWeightedDeterminantCompatibility} certificate
from this equality and then derives the ordinary determinant equality from the
Ob3/Ob4 normalization theorem.  The record-canonical Step~(xi) specialization
\texttt{IUTStage1Remark395RecordOb3Ob5DeterminantCompatibilitySource} fixes
\(P_B\) to the Theorem~3.11 possible-image family.  Both the generic and
record-canonical Ob3/Ob5 source objects now project to the bounded-family
hull/determinant source used by the downstream exact-theta Step~(xi) routes:
the endpoints
\texttt{remark395Ob3Ob5DeterminantCompatibilitySource\_boundedFamilyEndpoint}
and
\texttt{remark395RecordOb3Ob5DeterminantCompatibilitySource\_boundedFamilyEndpoint}
verify the family union, canonical hull, determinant log-volume equality, and
normalized tensor-power equality after this projection.
The generic bridge from Ob3/Ob5 compatibility to the Step~(xi) log-volume
chain now also has an exact-theta constructor:
\[
\begin{array}{l}
\texttt{remark395HullDeterminantBridgeSource}\\
\quad\texttt{\_ofOb3Ob5CompatibilitySourceOfThetaEqFamilyHullLogVolume}\\
\quad\texttt{\_endpoint}.
\end{array}
\]
This route no longer takes the Ob4 tensor-power bound as an independent input.
Given \(q\subseteq \bigcup_\beta P_\beta\) and the source calibration
\(\theta_{\mathrm{signed}}=\mu_{\log}(\phi(P_B))\), \Lean{} derives the
tensor-power bound from the bounded-family hull/determinant source and then
proves
\[
  \mu_{\log}(q)\leq \det_{\mathrm{norm}}\leq
  \theta_{\mathrm{signed}}.
\]
The record-canonical Ob3/Ob5 source now also has a public constructor endpoint
from the Ob3/Ob4 adjusted determinant source.  Given the remaining
source-facing equality
\[
  \mu_{\log}(\phi(P_B))
    =
  \det_{\mathrm{norm}}(P_B),
\]
\Lean{} constructs the record Ob3/Ob5 compatibility object, projects the
Ob3/Ob4 localization-summand and tensor-power formulas, derives equality with
the ordinary determinant log-volume, and then projects the resulting object to
the bounded-family Ob5 hull source.  The experiment surface exposes this as
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5DeterminantCompatibilitySource}\\
\quad\texttt{\_ofAdjustedDeterminantSource\_endpoint}.
\end{array}
\]
The remaining equality has now been pushed one level closer to Remark~3.9.5,
(vii), (Ob3-1)--(Ob3-3).  The new source-core object
\[
\begin{array}{l}
\texttt{IUTStage1Remark395Ob3Ob5DeterminantCompatibilitySource}\\
\quad\texttt{.IUTStage1Remark395Ob3Ob5AdjustedDeterminantLogVolumeSource}
\end{array}
\]
does not assume equality with the normalized determinant directly.  Instead it
records the finite Ob3-3 summand formula
\[
  \mu_{\log}(\phi(P_B))
    =
  \sum_{\beta} \operatorname{adj}_{\beta},
\]
where the summands are the Ob3/Ob4 structure-sheaf-adjusted localization
contributions.  Lean then derives equality with the determinant log-volume and
with the normalized determinant log-volume from the adjusted determinant source.
The record-canonical specialization fixes \(P_B\) to the Theorem~3.11
possible-image family and exposes
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{\_endpoint}.
\end{array}
\]
Thus the current open analytic/log-volume input is no longer
\(\mu_{\log}(\phi(P_B))=\det_{\mathrm{norm}}\) as a monolithic assertion, but
the more source-facing finite summand identity
\(\mu_{\log}(\phi(P_B))=\sum_{\beta}\operatorname{adj}_{\beta}\).
This identity can now also be stated at the localized vector-bundle level: the
constructor
\[
\begin{array}{l}
\texttt{IUTStage1Remark395Ob3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.ofLocalizedVectorBundleDeterminantSource}
\end{array}
\]
takes the equality with the sum of local-ring-labelled adjusted vector-bundle
summands and derives the adjusted determinant source, determinant log-volume
equality, and normalized Ob3/Ob5 compatibility from it.
The equality with the localized adjusted sum has now been factored once more.
The source declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395LocalizedHullVectorBundle}\\
\quad\texttt{DecompositionSource}
\end{array}
\]
records a finite decomposition of the canonical family hull into localized
hull-regions together with two source-facing facts: the hull log-volume is the
sum of these localized region log-volumes, and each localized region log-volume
is the corresponding adjusted localized vector-bundle summand.  Lean derives
the Ob3-3 summand identity from these two facts and then constructs the same
Ob3/Ob5 adjusted determinant log-volume source.
The localized-region containment has now been pushed one level lower.  The
source declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395LocalizedHullCover}\\
\quad\texttt{VectorBundleSource}
\end{array}
\]
starts from the intersection-defined Remark~3.9.5 hull system and a finite
cover
\[
  \phi(P_B)=\bigcup_\beta H_\beta
\]
by localized hull-regions.  From this cover identity, \Lean{} proves
\(H_\beta\subseteq\phi(P_B)\) for each \(\beta\), derives the family-hull
log-volume sum from the supplied cover-additivity theorem, and then constructs
the localized hull/vector-bundle decomposition source described above.
The pointwise summand calibration has now been factored as well.  A local
source object
\[
\begin{array}{l}
\texttt{IUTStage1LocalizedHullRegion}\\
\quad\texttt{VectorBundleCalibrationSource}
\end{array}
\]
attaches a single localized hull-region \(H_\beta\) to its
structure-sheaf-adjusted localized arithmetic vector bundle and records the
source equality
\[
  \mu_{\log}(H_\beta)
    =
  w_\beta\cdot
  \bigl(L_{\beta,\mathrm{bundle}}-L_{\beta,\mathcal O(-)}\bigr).
\]
\Lean{} then identifies the right hand side with the weighted adjusted
localized vector-bundle summand.  The aggregate declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395CalibratedLocalized}\\
\quad\texttt{HullCoverVectorBundleSource}
\end{array}
\]
assembles these calibrated local objects, constructs the finite localized
determinant source from them, and then projects to the localized hull-cover
source.  Thus the cover-level pointwise equality
\(\mu_{\log}(H_\beta)=\operatorname{adj}_\beta\) is no longer a bare field.
The finite cover-additivity input has also been separated from this aggregate
object.  The declaration
\[
\texttt{IUTStage1FiniteAdditiveHullLogVolumeSource}
\]
records the source-paper law that a finite pairwise-disjoint family of
localized hull-regions satisfies
\[
  \mu_{\log}\!\left(\bigcup_\beta H_\beta\right)
    =
  \sum_\beta \mu_{\log}(H_\beta).
\]
The refined aggregate source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395FiniteAdditive}\\
\quad\texttt{CalibratedLocalizedHullCoverVectorBundleSource}
\end{array}
\]
assumes pairwise disjointness of the localized regions and this finite
additivity law, then derives the exact cover-sum equality consumed by the
calibrated cover source.
The pairwise-disjointness input has now been pushed one level lower as well.
The source declaration
\[
\texttt{IUTStage1LocalizedHullRegionOwnershipSource}
\]
records a single owner map from hull points to optional localized indices and
states that each localized hull-region is the corresponding owner fiber.  From
this fiber description \Lean{} proves pairwise disjointness of distinct localized
regions.  The aggregate declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395OwnedFiniteAdditive}\\
\quad\texttt{CalibratedLocalizedHullCoverVectorBundleSource}
\end{array}
\]
therefore constructs the finite-additive calibrated cover source without taking
localized-region disjointness as a bare field.
The cover identity itself has now been factored through the same owner map.  The
declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395OwnerTotalFiniteAdditive}\\
\quad\texttt{CalibratedLocalizedHullCoverVectorBundleSource}
\end{array}
\]
assumes that every point of the family hull \(\phi(P_B)\) has a localized owner
and that each owner fiber remains inside \(\phi(P_B)\).  Together with the fiber
description of \(H_\beta\), \Lean{} derives
\(\phi(P_B)=\bigcup_\beta H_\beta\) and then projects to the owner-fiber
finite-additive cover route.
The owner map itself has now been constructed from a lower family-hull indexed
source.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395FamilyHullIndexedFiniteAdditive}\\
\quad\texttt{CalibratedLocalizedHullCoverVectorBundleSource}
\end{array}
\]
takes as primitive data an index function on the subtype of points of
\(\phi(P_B)\), together with the assertion that \(H_\beta\) is the corresponding
index fiber.  \Lean{} defines the ambient owner map to be this index on
\(\phi(P_B)\) and \(\texttt{none}\) off \(\phi(P_B)\), then derives owner-totality,
fiber containment in \(\phi(P_B)\), and the owner-total cover source.
The indexing source has now been pushed down to a direct-product localization
source.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395DirectProduct}\\
\quad\texttt{LocalizedHullCoverVectorBundleSource}
\end{array}
\]
represents \(H_\beta\) as the finite direct-product cell cut out by all local
factor regions at the localization places.  Its separation hypothesis is local:
two distinct indices are separated by at least one disjoint local factor.  From
this \Lean{} proves pairwise disjointness of the direct-product cells, uses the
cover equality
\[
  \phi(P_B)=\bigcup_\beta H_\beta
\]
to choose the unique cell containing a hull point, and then constructs the
family-hull indexed source rather than taking the index map as primitive.
The finite-additivity boundary has also been localized to this same
direct-product cover.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395DirectProductAdditive}\\
\quad\texttt{LocalizedHullCoverVectorBundleSource}
\end{array}
\]
does not assume a universal finite-additive law for arbitrary region families.
Instead it records the cover-specific Step~(xi) equality
\[
  \mu_{\log}\!\left(\bigcup_\beta H_\beta\right)
    = \sum_\beta \mu_{\log}(H_\beta)
\]
for the direct-product localization cells.  \Lean{} transports this equality
across the identification of \(H_\beta\) with the calibrated localized regions,
derives the calibrated cover source, and proves
\(\mu_{\log}(\phi(P_B))\) equals the sum of the adjusted Ob3/Ob4 localization
summands.
This cover-specific equality has now been derived from a lower finite
local-factor volume source.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395LocalFactorVolume}\\
\quad\texttt{DirectProductLocalizedHullCoverVectorBundleSource}
\end{array}
\]
assigns a log-volume contribution to each local factor of each direct-product
cell.  Its source laws compute
\[
  \mu_{\log}(H_\beta)=\sum_v \mu_{\beta,v},
  \qquad
  \mu_{\log}\!\left(\bigcup_\beta H_\beta\right)
    =\sum_\beta\sum_v \mu_{\beta,v}.
\]
\Lean{} then derives the direct-product cover additivity by finite-sum
congruence and projects to the cover-specific additive source.  Thus the
previous cover-additivity assumption is now reduced to the local-factor
log-volume computation for the localized arithmetic-vector-bundle cells.
The local-factor volumes are now also tied to the Ob3 vector-bundle data.  The
declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395VectorBundleLocalFactor}\\
\quad\texttt{DirectProductLocalizedHullCoverSource}
\end{array}
\]
defines the local factor \(\mu_{\beta,v}\) to be the direct-summand
log-volume of the localized arithmetic vector bundle attached to \(\beta\) at
the place \(v\).  Its source laws compute each \(H_\beta\) from the associated
bundle log-volume and compute the cover from the resulting finite bundle sum.
\Lean{} then derives the previous local-factor source and proves that the
local-factor sum agrees with the weighted adjusted Ob3/Ob4 summand already
used by the determinant package.  Thus the local-factor layer is no longer an
independent real-valued family; it is read from the localized vector-bundle
summands.
The factor regions themselves have now been pushed down one more source layer.
The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395LocalRingChartedVectorBundle}\\
\quad\texttt{DirectProductHullCoverSource}
\end{array}
\]
introduces a local-ring chart for each factor of each direct-product
localization cell.  The chart records the local-ring label and the region that
represents the corresponding local factor.  Its source laws identify the chart
local ring with the local-ring label of the localized arithmetic vector bundle,
identify each chart log-volume with the associated direct-summand log-volume,
compute each \(H_\beta\) as the sum of these chart-factor log-volumes, and
compute the cover as the finite sum of charted cell log-volumes.  \Lean{} then
derives the vector-bundle local-factor source.  Thus the regions entering the
direct-product cover are no longer an arbitrary family parallel to the bundle
data; they are read from local-ring localization charts tied to the same
localized vector bundles.
The chart/bundle matching has also been isolated at the individual factor
level.  The new
\[
\begin{array}{l}
\texttt{IUTStage1LocalRingVectorBundleFactorCalibrationSource}
\end{array}
\]
records, for a fixed \((\beta,v)\), that the chart lies over the same local
ring as the localized arithmetic vector bundle and that the chart region's
log-volume is the corresponding direct-summand log-volume.  The aggregate
\[
\begin{array}{l}
\texttt{IUTStage1Remark395CalibratedLocalRingCharted}\\
\quad\texttt{VectorBundleHullCoverSource}
\end{array}
\]
then builds the previous charted direct-product source from these per-factor
calibrations, together with the remaining cell factorization and cover
additivity laws.  This separates the local-ring/direct-summand calibration
obligation from the finite direct-product geometry obligation.
The cover additivity law has now been separated from the calibrated charted
source as well.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395FiniteAdditiveCalibrated}\\
\quad\texttt{LocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
keeps the same per-factor calibrations and cell-factorization law, but replaces
the charted cover log-volume equality by a finite-additive hull log-volume
source.  Distinct direct-product cells are proved disjoint from the local-factor
separation condition, and \Lean{} applies finite additivity to derive
\[
  \mu_{\log}\!\left(\bigcup_\beta H_\beta\right)
    =\sum_\beta \mu_{\log}(H_\beta).
\]
Thus the cover equality consumed by the charted vector-bundle route is no
longer an independent field of that route.
The per-cell direct-product equality has now been factored as well.  The new
source declaration
\[
\begin{array}{l}
\texttt{IUTStage1DirectProductCellLogVolumeSource}
\end{array}
\]
records the Step~(xi-d) tensor/direct-product log-volume law for one finite
localization cell:
\[
  \mu_{\log}\!\left(\bigcap_v H_{\beta,v}\right)
    =\sum_v \mu_{\log}(H_{\beta,v}).
\]
The aggregate
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ProductLogVolumeFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
therefore no longer takes the cell-factorization equality as a bare field.  It
derives the equality for each \(H_\beta\) from the single-cell product
log-volume source, proves disjointness from local-factor separation, applies
finite additivity to the direct-product cover, and then projects to the previous
finite-additive charted source.
This source has now been lowered once more to a tensor/direct-sum datum for the
actual charted cells.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1FiniteTensorDirectSumLogVolumeSource}
\end{array}
\]
records a finite tensor-product region, its identification with the corresponding
direct-product cell, the local factor log-volumes, and the finite direct-sum
formula for the tensor-product log-volume.  From these data, \Lean{} derives the
single-cell law
\[
  \mu_{\log}(H_\beta)
    =\sum_v \mu_{\log}(H_{\beta,v}).
\]
The aggregate
\[
\begin{array}{l}
\texttt{IUTStage1Remark395TensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
assigns such a tensor/direct-sum source to each charted localization cell, derives
the cell log-volume equalities, proves the same pairwise-disjoint cover
additivity, and projects to the finite-additive calibrated charted cover source.
The tensor-cell source has now been lowered to compact-open local factor data.
The declaration
\[
\begin{array}{l}
\texttt{IUTStage1LocalCompactOpenTensorFactorSource}
\end{array}
\]
records the local ring label, compact-open local factor region, and normalized
local log-volume for one nonarchimedean tensor factor.  A second declaration,
\[
\begin{array}{l}
\texttt{IUTStage1CompactOpenTensorRegionDirectSumSource}
\end{array}
\]
records the tensor-product region obtained from a finite family of these
compact-open factors, identifies it with the simultaneous local-factor cell, and
proves the finite direct-sum log-volume formula.  Lean then constructs
\(\texttt{IUTStage1FiniteTensorDirectSumLogVolumeSource}\) from this
compact-open direct-sum datum, including the chart-region transport needed when
the compact-open factor regions are identified with the already charted local
factor regions.
At the packet level,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395CompactOpenTensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
requires one such compact-open tensor direct-sum construction for each charted
localization cell, proves that the compact-open factor regions and local-ring
labels match the charted local factors, constructs the tensor-packet source, and
then derives the same finite-additive cover equality and bundle-log-volume
projection.
The compact-open tensor factor source has now been lowered to a
nonarchimedean local normalized log-volume datum.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1NonarchimedeanLocalCompactOpenLogVolumeSource}
\end{array}
\]
records a local carrier, local-ring label, residue prime, finite-extension
degree, integral structure, compact-open subset, uniformizer-scaled subset, and
their realization as regions in the current real-line copy.  It includes the
IUT~IV Proposition~1.4 normalization laws needed in the present corridor:
the integral structure has normalized log-volume zero, the normalized
log-volume is the degree-normalized raw log-volume, and multiplication by a
uniformizer shifts the normalized log-volume by \(-\log(p)\).  Lean constructs
\(\texttt{IUTStage1LocalCompactOpenTensorFactorSource}\) from this datum.
The finite direct-sum layer
\[
\begin{array}{l}
\texttt{IUTStage1NonarchimedeanLocalTensorRegionDirectSumSource}
\end{array}
\]
then constructs the compact-open tensor-region source from a finite family of
these local nonarchimedean sources and the direct-sum tensor-region formula.
Finally,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395NonarchimedeanLocalTensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
uses one such local tensor source for each charted localization cell, verifies
the local compact-open regions and local-ring labels against the charted factors,
constructs the compact-open tensor-packet source, and inherits the finite-additive
cover and bundle-log-volume conclusions.
The local nonarchimedean source has now been lowered once more to the
finite-extension Haar normalization boundary of IUT~IV, Proposition~1.4.  The
declaration
\[
\begin{array}{l}
\texttt{IUTStage1FiniteExtensionHaarCompactOpenLogVolumeSource}
\end{array}
\]
records the raw Haar/log-volume function on local compact-open subsets of a
finite extension of \(\mathbb{Q}_p\), its degree-normalized version, the
realization of local subsets as real-line regions, the integral structure
\(\mathcal{O}_K\), and the uniformizer-scaled compact-open subset.  Its endpoint
checks the source-paper normalizations
\[
  \mu_{\log}(\mathcal{O}_K)=0,\qquad
  \mu_{\log}(p\cdot U)=\mu_{\log}(U)-\log(p),
\]
and constructs
\(\texttt{IUTStage1NonarchimedeanLocalCompactOpenLogVolumeSource}\).
The declaration
\[
\begin{array}{l}
\texttt{IUTStage1FiniteExtensionTensorProductDirectSumDecompositionSource}
\end{array}
\]
records the IUT~IV direct-sum decomposition step for finite tensor products over
\(\mathbb{Z}_p\): the tensor-product region is identified with the simultaneous
local compact-open cell, and its normalized log-volume is the finite sum of the
degree-normalized Haar log-volumes of the direct summands.  This source constructs
the nonarchimedean local tensor-region direct-sum source.  At the packet level,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395FiniteExtensionHaarTensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
assigns such a finite-extension Haar tensor decomposition to each charted
localization cell and then constructs the nonarchimedean local tensor-packet
source used by the Step~(xi) cover route.
The finite-extension Haar source has now been lowered to compact-open topology
provenance.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1FiniteExtensionCompactOpenTopologyHaarNormalizationSource}
\end{array}
\]
records the compact-open predicate on the local carrier, closure of
compact-opens under finite intersections, the ring-of-integers compact-open, the
chosen compact-open subset, a uniformizer action preserving compact-opens, the
raw Haar measure, and the raw and degree-normalized Haar log-volume functions.
Its endpoint verifies compact-open provenance for
\(\mathcal{O}_K\), \(U\), and \(p\cdot U\), checks
\(\log(\mu_{\mathrm{Haar}}(U))\) at the raw level, and constructs
\(\texttt{IUTStage1FiniteExtensionHaarCompactOpenLogVolumeSource}\).
The tensor layer
\[
\begin{array}{l}
\texttt{IUTStage1CompactOpenTopologyTensorProductDirectSumSource}
\end{array}
\]
constructs the finite-extension tensor-product direct-sum source from these
compact-open topology factors.  Finally,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395CompactOpenTopologyHaarTensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
feeds compact-open topology/Haar normalization data for each charted cell into
the finite-extension Haar tensor-packet source and hence into the same
finite-additive Step~(xi) cover route.
The local compact-open topology source has also been lowered one step further to
a Haar-measure-backed source.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarCompactOpenNormalizationSource}
\end{array}
\]
uses mathlib's additive Haar-measure class on the local additive carrier,
records openness and compactness for the ring of integers and selected
compact-open subset, normalizes the ring of integers to Haar mass \(1\), and
records the finite-extension uniformizer scaling law for real Haar mass.  Lean
then derives the raw logarithmic shift by
\(-[K:\mathbb{Q}_p]\log(p)\), divides by the finite-extension degree, and
obtains the normalized IUT~IV shift \(\mu_{\log}(pU)=\mu_{\log}(U)-\log(p)\).
The companion declaration
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTensorProductDirectSumSource}
\end{array}
\]
feeds these Haar-backed local factors into the compact-open tensor/direct-sum
source, so the tensor summation layer now has a route whose local inputs are
actual additive Haar measures rather than arbitrary real-valued Haar functions.
There is now a valuation-ball refinement below this Haar source.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1ProperUltrametricValuationBallTopologySource}
\end{array}
\]
now starts from a proper ultrametric metric topology on the local additive
carrier.  The ultrametric inequality proves openness of positive-radius closed
balls, while properness supplies compactness by the closed-ball compactness
theorem.  Thus the compact-open valuation-ball theorem is constructed from
two recognizable local topological hypotheses rather than from separate
open/compact fields.  The companion declaration
\[
\begin{array}{l}
\texttt{IUTStage1ProperUltrametricValuationBallAdditiveHaarNormalizationSource}
\end{array}
\]
feeds this proper-ultrametric source into the ultrametric Haar route.
The local ring input has also been sharpened from an abstract unit-ball label
to the valued-field integer subring supplied by \texttt{mathlib}.  The
declaration
\[
\begin{array}{l}
\texttt{IUTStage1ValuedFieldIntegerUnitBallSource}
\end{array}
\]
works over a nontrivially normed ultrametric field and uses
\texttt{Valued.integer.mem\_iff} to prove
\[
  \mathcal{O}_K=\{x\mid \|x\|\leq 1\}=\overline{B}(0,1).
\]
It then identifies this valued-field integer subring with the radius-one ball
in the proper-ultrametric valuation-ball topology.  The companion declaration
\[
\begin{array}{l}
\texttt{IUTStage1ValuedFieldIntegerProperUltrametric}\\
\quad\texttt{HaarNormalizationSource}
\end{array}
\]
uses \(\mathcal{O}_K\) itself as the local-ring label and transports the Haar
mass-one normalization from \(\mathcal{O}_K\) to the radius-one valuation ball
before projecting into the proper-ultrametric Haar normalization route.
There is now a base local-field specialization of this statement.  The
declaration
\[
\begin{array}{l}
\texttt{IUTStage1PadicIntegerUnitBallSource}
\end{array}
\]
works over \(\mathbb{Q}_p\), identifies
\(\mathcal{O}_{\mathbb{Q}_p}\) with \(\texttt{PadicInt.subring}\ p\), and
proves that its underlying set is the image of the coercion
\(\mathbb{Z}_p\hookrightarrow\mathbb{Q}_p\).  This also records the local-ring
instance on \(\mathbb{Z}_p\), so the ring-of-integers object is no longer only
the abstract valued-field subring.  The base residue quotient has now also
been made concrete.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1PadicIntegerResidueQuotientSource}
\end{array}
\]
uses the mathlib reduction map
\(\texttt{PadicInt.toZMod}:\mathbb Z_p\to \mathbb Z/p\mathbb Z\),
proves that its additive kernel is the maximal ideal of \(\mathbb Z_p\), and
applies the first isomorphism theorem to identify
\[
  \mathbb Z_p/\ker(\texttt{toZMod})\simeq_{\rm add}\mathbb Z/p\mathbb Z.
\]
Transporting the \(\mathbb Z/p\mathbb Z\)-vector-space structure across this
additive equivalence gives a one-dimensional residue module, and Lean proves
\[
  \#(\mathbb Z_p/\ker(\texttt{toZMod}))
    =p=p^{\operatorname{finrank}_{\mathbb Q_p}\mathbb Q_p}.
\]
The same source now also constructs
\[
  \texttt{Fin}(p^{[\mathbb Q_p:\mathbb Q_p]})
    \simeq \mathbb Z_p/\ker(\texttt{toZMod})
\]
and finite-index representatives whose quotient classes are definitionally
the indexed residue classes.  This upgrades the base-field residue quotient
from a cardinality result to the representative data needed by the coset
partition layer, without a supplied finite quotient equivalence.  This has now
been threaded into the base local coset/Haar boundary.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1PadicBaseFieldResidueQuotientDilationCoset}\\
\quad\texttt{HaarCharacterNormalizationSource}
\end{array}
\]
constructs the additive equivalence
\[
  \mathbb Z_p \simeq_{\rm add} \mathcal O_{\mathbb Q_p},
\]
proves that the transported \(\ker(\texttt{toZMod})\) is exactly the subgroup
\(p\mathcal O_{\mathbb Q_p}\), applies the first isomorphism theorem to build
\[
  \mathcal O_{\mathbb Q_p}/p\mathcal O_{\mathbb Q_p}
    \simeq_{\rm add}
  \mathbb Z_p/\ker(\texttt{toZMod}),
\]
and then supplies the finite quotient equivalence and representatives consumed
by the quotient-coset partition/Haar-character source.  Thus the base-field
coset decomposition used to derive
\(\mu(p\mathcal O_{\mathbb Q_p})=p^{-1}\) now starts from the concrete
\(\texttt{PadicInt.toZMod}\) residue quotient rather than from a supplied
quotient package.  The companion
declaration
\[
\begin{array}{l}
\texttt{IUTStage1PadicProperUltrametricHaarNormalizationSource}
\end{array}
\]
fixes the residue prime to \(p\), the finite-extension degree to \(1\), and the
uniformizer scale map to \(x\mapsto px\), then projects to the valued-field
integer Haar route.  The Haar mass-one and \(p\)-scaling law are still carried
as analytic local-field inputs, but their ambient field, local ring, residue
prime, degree, and uniformizer map are now the actual \(p\)-adic ones.  This
base local-field source now also projects into the finite-extension Haar
boundary itself by viewing \(\mathbb Q_p/\mathbb Q_p\) as a finite extension.
Lean constructs
\[
\begin{array}{l}
\texttt{IUTStage1PadicProperUltrametricHaarNormalizationSource.}\\
\quad\texttt{toPadicFiniteExtensionProperUltrametricHaarNormalizationSource}
\end{array}
\]
and proves that its valued-field integer projection agrees with the direct
\(\mathbb Q_p\) valued-field Haar source.  Thus the finite-extension degree
appearing in the normalization is not an independent parameter at the base
place: it is \(\operatorname{finrank}_{\mathbb Q_p}(\mathbb Q_p)=1\), with the
same base-prime dilation \(x\mapsto px\).
The declaration
\[
\begin{array}{l}
\texttt{IUTStage1UltrametricValuationBallTopologySource}
\end{array}
\]
starts from an ultrametric metric topology on the local additive carrier and
proves that every positive-radius closed valuation ball
\(\{x\mid d(x,0)\leq r\}\), \(r>0\), is open.  It still carries compactness of
these balls as the local compactness/properness input, but the openness part of
the compact-open assertion is now derived from the nonarchimedean triangle
inequality rather than supplied independently.  The companion declaration
\[
\begin{array}{l}
\texttt{IUTStage1UltrametricValuationBallAdditiveHaarNormalizationSource}
\end{array}
\]
projects this ultrametric source into the positive-radius topology-backed Haar
route.
The declaration
\[
\begin{array}{l}
\texttt{IUTStage1PositiveRadiusValuationBallTopologySource}
\end{array}
\]
isolates the local-field topological theorem that every positive-radius
valuation ball \(\{x\mid \|x\|_v\leq r\}\), \(r>0\), is compact-open.  The
topology-backed declaration
\[
\begin{array}{l}
\texttt{IUTStage1ValuationBallTopologyAdditiveHaarNormalizationSource}
\end{array}
\]
then derives the unit ball and selected ball compact-open predicates from this
single positive-radius theorem before projecting to the older additive Haar
normalization route.  Thus the source boundary has moved from four separate
open/compact fields for two balls to one uniform valuation-ball compact-open
theorem.
The declaration
\[
\begin{array}{l}
\texttt{IUTStage1ValuationBallAdditiveHaarNormalizationSource}
\end{array}
\]
records a nonarchimedean valuation-norm function on the local carrier and defines
the ring of integers as the unit ball \(\{x\mid \|x\|_v\leq 1\}\).  The selected
local compact-open subset is likewise a valuation ball
\(\{x\mid \|x\|_v\leq r\}\) for a positive radius \(r\), and the uniformizer
operation is the image under a pointwise scale map.  Lean derives the compact-open
predicate as \(\texttt{IsOpen}\wedge\texttt{IsCompact}\), proves closure under
finite intersections in a \(T_2\) space, and constructs the additive Haar
normalization source from the valuation-ball data.  The companion tensor source
\[
\begin{array}{l}
\texttt{IUTStage1ValuationBallTensorProductDirectSumSource}
\end{array}
\]
feeds valuation-ball local factors into the additive Haar tensor/direct-sum
source.
The valuation-ball route now also reaches the charted Step~(xi) cover boundary
itself.  The new declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationBallHaarTensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
assigns to each charted localization cell a valuation-ball tensor/direct-sum
source, proves that every local charted region and local-ring label is realized
by the corresponding valuation-ball factor, and then constructs the existing
compact-open topology/Haar tensor-packet cover source.  Its endpoint exposes
the valuation-ball identities for \(\mathcal{O}_K\) and \(U\), compact-openness
of the selected valuation balls, the finite direct-product cell log-volume
formula, the finite-additive cover sum, and the inherited bundle-log-volume
projection.  Thus the current IUT~IV local-volume corridor now proceeds from
valuation balls to additive Haar normalization, then to compact-open topology,
finite-extension Haar log-volume, tensor/direct-sum summation, and finally the
charted Step~(xi) cover route.
The local chart calibration in this valuation-ball route has now been pushed
down another level.  The per-factor declaration
\[
\begin{array}{l}
\texttt{IUTStage1ValuationBallVectorBundleFactorCalibrationSource}
\end{array}
\]
constructs the local-ring chart from a valuation-ball Haar factor itself: the
chart local ring is the valuation-ball factor's local ring, and the chart region
is the realized selected valuation ball.  Its source law identifies the
localized vector-bundle direct summand with the normalized Haar log-volume of
that valuation ball, after which \Lean{} derives the ordinary chart/direct-summand
calibration source.  The packet-level declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ValuationBallFactorCalibratedHaarTensorPacket}\\
\quad\texttt{FiniteAdditiveCalibratedLocalRingChartedVectorBundleHullCoverSource}
\end{array}
\]
uses these per-factor valuation-ball calibrations to build the previous
valuation-ball charted-cover source.  Thus the factor chart is no longer a
separate object merely matched to valuation-ball data; at this boundary it is
constructed from the valuation-ball compact-open region.  This same
factor-calibrated valuation-ball source now also projects into the newer
finite-cover-additive/tensor-measure-backed cover corridor.  The projection
uses the broad finite-additive law only to construct the selected
family-local finite-cover certificate, then \Lean{} derives the tensor-cell
cover sum
\[
  \mu_{\log}\Bigl(\bigcup_\beta H_\beta\Bigr)
    =
  \sum_\beta \mu_{\log}^{\mathrm{tensor}}(H_\beta)
\]
and reads the adjusted Ob3/Ob5 determinant equalities from that constructed
finite-cover source.  This connects the valuation-ball Haar factor route to the
current narrower cover-audit path without treating the tensor-cover theorem as
an independent payload.
The record-canonical valuation-ball handoff has also been tightened at the
source-core boundary.  The theorem
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.ofValuationBallFactorCalibratedHaarTensorPacketFiniteAdditive}\\
\quad\texttt{CalibratedLocalRingChartedVectorBundleHullCoverSource}\\
\quad\texttt{\_toSourceCoreAdjustedLogVolumeSource\_eq}
\end{array}
\]
proves that, once the valuation-ball possible-image family is synchronized
with the Theorem~3.11 record family, the record-canonical Ob3/Ob5 source
forgets back to exactly the valuation-ball adjusted determinant log-volume
source.  Downstream principal valuation-ball finite-divisor sources can
therefore use this equality as a derived synchronization, rather than carrying
the valuation-ball Ob3/Ob5 equality as an unrelated payload.
This summand-calibrated source now feeds the milestone-facing constructed
Step~(xi) source directly.  The new constructor
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.toConstructedHolomorphicHullDeterminantSource}
\end{array}
\]
first derives the record Ob3/Ob5 compatibility object from the finite summand
formula, then uses that derived compatibility to build
\(\texttt{IUTStage1Remark395ConstructedHolomorphicHullDeterminantSource}\).
The experiment endpoint
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{\_toConstructedHolomorphicHullDeterminantSource\_endpoint}
\end{array}
\]
returns the finite-summand equality, the determinant and normalized determinant
identifications, and the chain
\[
  \mu_{\log}(q) \leq \det_{\log}(P_B) \leq \Theta_{\mathrm{signed}},
\]
so the constructed Step~(xi) route no longer receives the canonical
hull--determinant compatibility as an independent input in this constructor.
This constructed-source layer now also has an exact-theta refinement,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.toConstructedHolomorphicHullDeterminantSource}\\
\quad\texttt{OfThetaEqFamilyHullLogVolume}.
\end{array}
\]
For an arbitrary q-region \(q\subseteq P_{\mathrm{rec}}\) contained in the
record possible-image union, this constructor derives the Ob4 normalized
tensor-power bound from
\[
  \theta_{\mathrm{signed}}
    =
  \mu_{\log}(\phi(P_B)),
\]
using the bounded-family hull/determinant source projected from the Ob3/Ob5
compatibility.  Its public endpoint records the exact-theta equality, the
derived tensor-power inequality, the adjusted-summand-to-determinant
identifications, the two-step hull/determinant chain, and
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).  Thus the general
constructed Step~(xi) source has the same no-free-tensor-bound interface that
was previously only available after choosing a possible-image q-region; the
package measure calibration and the record-canonical bridge equality remain
explicit source obligations.
There is now also an obligations-backed form of this arbitrary-q exact-theta
constructor,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.toConstructedHolomorphicHullDeterminantSource}\\
\quad\texttt{OfThetaEqFamilyHullLogVolumeFromObligations}.
\end{array}
\]
It projects the package hull/determinant bridge equality, q-pilot positivity,
and source normalization from one
\(\texttt{IUTStage1SourceHullDetObligations}\) object.  The endpoint still
exposes the synchronization identifying that obligations-backed bridge datum
with the record-canonical Remark~3.9.5 hull/tensor-power construction for the
chosen q-region.  Thus, at the general constructed-source level, the remaining
explicit inputs are the measure calibration, the exact-theta family-hull
identity, q-containment in the record possible-image union, and this single
bridge-synchronization statement.
The measured Ob3/Ob5 adjusted source now removes that separate measure
calibration input as well.  Its constructor
\[
\begin{array}{l}
\texttt{IUTStage1MeasureCalibratedRemark395RecordOb3Ob5Adjusted}\\
\quad\texttt{DeterminantLogVolumeSource.toConstructedHolomorphicHull}\\
\quad\texttt{DeterminantSourceOfThetaEqFamilyHullLogVolumeFromObligations}
\end{array}
\]
projects the package measure equality from the measured family-hull source,
derives the Ob4 tensor-power bound from
\(\theta_{\mathrm{signed}}=\mu_{\log}(\phi(P_B))\), and keeps only the
q-containment, exact-theta identity, obligations object, and
record-canonical bridge synchronization as explicit parameters.
There is also a selected-possible-image specialization,
\[
\begin{array}{l}
\texttt{IUTStage1MeasureCalibratedRemark395RecordOb3Ob5Adjusted}\\
\quad\texttt{DeterminantLogVolumeSource.toPossibleImageConstructed}\\
\quad\texttt{HolomorphicHullDeterminantSourceOfThetaEqFamilyHullLogVolume}\\
\quad\texttt{FromObligations}.
\end{array}
\]
Here the q-region is fixed to
\(\texttt{recordThetaPossibleImage record qChoice}\), and Lean derives its
containment in the Theorem~3.11 possible-image union from the record's
choice-indexed union constructor rather than receiving a separate
q-containment proof.
The same summand source now also feeds the constructor-built possible-image
Step~(xi) source used by the finite-divisor-facing corridor.  The constructor
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.toPossibleImageConstructorBuiltHolomorphicHullDeterminantSource}
\end{array}
\]
fixes the q-pilot region to a chosen Theorem~3.11 possible image, derives its
record-union containment, derives the Ob3/Ob5 compatibility from the finite
summand formula, and then builds
\(\texttt{IUTStage1PossibleImageConstructorBuiltHolomorphicHullDeterminantSource}\).
Its experiment endpoint
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{\_toPossibleImageConstructorBuiltHolomorphicHullDeterminantSource\_endpoint}
\end{array}
\]
therefore exposes the constructor-built source endpoint, the Step~(xi)
bridge-inequality audit, the derived compatibility object, and the
summand-to-determinant equalities at one review boundary.  This removes one
more independent compatibility certificate from the public constructor-built
route, although the package measure calibration and record-canonical
hull/determinant bridge equality are still explicit inputs.
The finite-summand source now also has an exact-theta family-hull constructor,
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.toPossibleImageFamilyHullExactThetaHullDetObligationsBackedSource}.
\end{array}
\]
Here the record Ob3/Ob5 family hull is still derived from the adjusted-summand
identity, but the Ob4 tensor-power bound used in the record-canonical
Step~(xi) bridge is no longer a separate route input.  It is derived from the
exact-theta source equality
\[
  \theta_{\mathrm{signed}}
    =
  \mu_{\log}(\phi(P_B)).
\]
The corresponding experiment endpoint exposes the selected possible-image
q-region, the package hull/determinant bridge, q-positivity, normalization, the
derived weighted determinant source, the adjusted-summand-to-determinant
equalities, the derived tensor-power bound, and
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).
The measured adjusted-summand source
\[
\begin{array}{l}
\texttt{IUTStage1MeasureCalibratedRemark395RecordOb3Ob5}\\
\quad\texttt{AdjustedDeterminantLogVolumeSource}
\end{array}
\]
packages the same finite Ob3--3 adjusted-summand construction together with the
package measure equality for the derived record family hull.  Its exact-theta
endpoint first projects the measured family-hull source and then invokes the
possible-image constructor above.  Thus, in this route, the measure
calibration \(\mu=\mu_{\log}(\phi(\cup_B P_B))\) is no longer a loose
endpoint argument; it is part of the source-facing adjusted-summand object.
This adjusted source is now threaded through the target-charted Hodge
Step~(xi) layer as well.  The declarations
\[
\begin{array}{l}
\texttt{IUTStage1TargetChartedHodgeMeasureCalibrated}\\
\quad\texttt{AdjustedSummandFamilyHullSource},\\
\texttt{IUTStage1TargetChartedHodgeMeasureCalibrated}\\
\quad\texttt{AdjustedPossibleImageHullDetObligationsBackedSource}
\end{array}
\]
project to the older measured determinant routes only internally.  Their
experiment endpoints keep the finite adjusted-summand identity
\[
  \mu_{\log}(\phi(P_B))
    =
  \sum_{\gamma}(\text{localization}_{\gamma}
      - \text{structure sheaf}_{\gamma})
    =
  \det_{\log}
\]
visible next to the Hodge theta-degree calibration, the selected
Theorem~3.11 possible-image q-region, and the obligations bridge equality.
The adjusted-summand payload has also been moved into the constructor-backed
Step~(xi) route.  The source
\[
\begin{array}{l}
\texttt{IUTStage1TargetChartedHodgeConstructorBacked}\\
\quad\texttt{MeasureCalibratedAdjustedPossibleImageHullDetSource}
\end{array}
\]
uses the record-canonical Theorem~3.11 hull/tensor-power constructor to
generate the possible-image hull/determinant obligations, while its determinant
input is projected from the measured adjusted-summand family-hull source.  Its
endpoint exposes, in one checked proposition, the selected q-region, the
measure calibration, the two finite adjusted-summand equalities
\[
  \mu_{\log}(\phi(P_B))
  =
  \sum_{\gamma}(\text{localization}_{\gamma}
      - \text{structure sheaf}_{\gamma})
  =
  \det_{\log},
\]
the equality between generated obligations and the constructor hull/determinant
data, the record-canonical bridge equality, q-positivity, normalization, and
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).  The all-in-one route
\[
\begin{array}{l}
\texttt{IUTStage1TargetChartedHodgeIPLConstructorBacked}\\
\quad\texttt{MeasureCalibratedAdjustedPossibleImageRouteSource}
\end{array}
\]
then combines this constructor-backed adjusted source with the Hodge/IPL
construction.  Its audit projects internally to the constructor-backed measured
route, but keeps the adjusted-summand Step~(xi) audit as public provenance.
The actual log-volume bridge has now been separated as a named source object:
\[
\begin{array}{l}
\texttt{IUTStage1Remark395HullDeterminantBridgeSource}.
\end{array}
\]
It takes q-region containment in the possible-image union, Ob3/Ob5
compatibility between \(\phi(P_B)\) and the determinant-normalized log-volume,
and the Ob4 normalized tensor-power bound by \(\theta_{\mathrm{signed}}\), then
proves the chain
\[
  \mu_{\log}(q_{\mathrm{region}})
  \le
  \mu_{\log}(\phi(P_B))
  =
  \det_{\log}^{\mathrm{norm}}
  =
  \det_{\log}
  \le
  \theta_{\mathrm{signed}} .
\]
The experiment-surface theorem
\texttt{remark395HullDeterminantBridgeSource\_endpoint} exposes this chain.
The direct two-step normalized form is also exposed as
\texttt{remark395HullDeterminantBridgeSource\_normalizedBridge}, which records
\[
  \mu_{\log}(q_{\mathrm{region}})
    \leq
  \det_{\mathrm{norm}}
    \leq
  \theta_{\mathrm{signed}} .
\]
The Step~(xi) specialization
\texttt{IUTStage1Remark395RecordHullDeterminantBridgeSource} fixes the family
to the Theorem~3.11 possible images and the bound to
\texttt{package.preLedger.thetaSigned}; its endpoint verifies the
record-canonical q-to-determinant-to-theta comparison, while
\texttt{remark395RecordHullDeterminantBridgeSource\_normalizedBridge} exposes
the corresponding record-canonical normalized bridge.  The record bridge
constructors from Ob3/Ob5 compatibility and from the adjusted Ob3-3 summand
identity now expose this normalized two-step chain in their endpoint statements,
so a reviewer no longer has to pass through a separate determinant-log endpoint
to see the \(\det_{\mathrm{norm}}\) comparison.  The constructed
summand-charted Hodge/family-hull source now exposes this same comparison as a
separate subgoal-5 audit:
\[
\begin{array}{l}
\texttt{remark395SummandCalibratedStepXILogVolumeChainAudit}.
\end{array}
\]
This endpoint starts from the selected Theorem~3.11 possible-image q-region,
uses the record-family hull containment and monotonicity, applies the Ob3/Ob5
family-hull/determinant equality, and then uses the finite summand calibration to
derive \(\det_{\log}=\theta_{\mathrm{signed}}\).  Thus the theorem returns the
explicit Lean chain
\[
  \mu_{\log}(q_{\mathrm{region}})
  \le
  \det_{\log}
  \le
  \theta_{\mathrm{signed}},
\]
together with the determinant summand-sum equality and the raw
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison.
The same synchronized finite-divisor boundary now also has an Ob5 quotient
refinement:
\[
\begin{array}{l}
\texttt{synchronizedTargetChartedPossibleImageSummandHodgeFamilyHull}\\
\quad\texttt{IPLConstructionFiniteDivisorVerticalIQ\_boundaryEndpoint}\\
\quad\texttt{WithStepXIOb5QuotientBoundaryAudit}.
\end{array}
\]
This audit keeps the no-\(C_\Theta\) finite Step~(x) packet and vertical-\(IQ\)
equalities, the summand-calibrated Step~(xi) chain
\(\mu_{\log}(q_{\mathrm{region}})\leq\det_{\log}
\leq\theta_{\mathrm{signed}}\), the synchronized reduction to the
constructor-built Step~(xi) source, and the Ob1--Ob5 quotient bridge for a
second nonempty Theorem~3.11 possible-image choice.  Thus the strongest current
summand route exposes both the numerical log-volume chain and the Ob5 collapsed
quotient images before the final \(C_\Theta\) estimate is supplied.
The product-hull Ob5--Ob7 route now has the analogous canonical-scale boundary
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{Ob3Ob5AdjustedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_canonicalCThetaScaleDichotomy}\\
\quad\texttt{WithOb5Ob6Ob7SynchronizedAuditOfQPilotRegionNonempty}.
\end{array}
\]
This endpoint keeps the synchronized Ob5 quotient collapse, Ob6
\(\Phi/\Xi\)-approximant comparison, and Ob7 prime-strip log-Kummer
compatibility in the returned audit, but replaces the external numeric
\texttt{thetaSigned\_le\_cTheta\_absLogQ} input by the local scale
\[
  C_{\Theta,\mathrm{can}}=
  \frac{\theta_{\mathrm{signed}}}{-q_{\mathrm{signed}}}.
\]
\Lean{} derives the corresponding bound from q-pilot positivity and then applies
the same finite-divisor vertical-\(IQ\) route at this scale.  As above, this is a
source-attached local scale, not an identification with the global
\(C_\Theta\)-constant of the IUT papers.
The same synchronized finite-divisor boundary now has a remaining-payload
variant:
\[
\begin{array}{l}
\texttt{synchronizedTargetChartedPossibleImageSummandHodgeFamilyHull}\\
\quad\texttt{IPLConstructionFiniteDivisorVerticalIQ\_boundaryEndpoint}\\
\quad\texttt{WithStepXIOb5QuotientRemainingPayloadBoundaryAudit}.
\end{array}
\]
This audit adds the constructor-built
\texttt{ConstructorBuiltRemainingPayloadAudit} to the quotient-refined boundary.
Consequently, the finite Step~(x) packet/vertical-\(IQ\) equalities, the
summand-derived chain
\(\mu_{\log}(q_{\mathrm{region}})\leq\det_{\log}
\leq\theta_{\mathrm{signed}}\), the Ob5 quotient independence, and the still-open
Step~(xi) source-paper payload now sit in one review object.
The constructed
Step~(xi) source also has
\texttt{ofRecordHullDeterminantBridgeSource}, so the bridge payload may now be
passed as one source-level mathematical object instead of as unrelated
compatibility and tensor-bound fields.  There is now a sharper constructor
\texttt{ofRecordOb3Ob5CompatibilitySource} that builds the constructed
Step~(xi) source from the record Ob3/Ob5 source equality plus the remaining
Ob4 tensor-bound, measure-calibration, bridge-equality, positivity, and
normalization data.
The corresponding Step~(xi) source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructedHolomorphicHullDeterminantSource}
\end{array}
\]
combines this \(\phi\)-operator with the Theorem~3.11 possible-image union,
q-pilot containment in that union, the finite Ob3/Ob4 weighted determinant
source, tensor-power normalization, and the record-canonical hull/determinant
bridge equality.  Lean proves inside this source object that the possible-image
union, each possible image, and the q-pilot region lie in \(\phi(P)\), and that
the source object projects the possible-image family to the Ob5
family-hull/determinant log-volume source.  In particular, Lean now also proves
the family-hull log-volume equality with the weighted determinant and the
family-union log-volume bound by that determinant before proving
\[
  \mu_{\log}(q_{\mathrm{region}})
  \le \det_{\log}^{\mathrm{norm}}
  \le \theta_{\mathrm{signed}} .
\]
The experiment-surface theorem
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_remark395ConstructedHullDeterminantFiniteDivisorVerticalIQ}
\end{array}
\]
threads this constructed Remark~3.9.5 source through the finite-divisor
vertical-\(IQ\) corridor.  This ordinary form still accepts a chosen
\(C_\Theta\) and the corresponding numeric estimate as explicit inputs.  The
same source now has a canonical-scale companion
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_remark395ConstructedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_canonicalCThetaScale},
\end{array}
\]
where the constructed Remark~3.9.5 source object defines the scale as
\(\theta_{\mathrm{signed}}/(-q_{\mathrm{signed}})\).  The source-level audit
\texttt{ConstructedCanonicalCThetaScaleAudit} records the
\[
  \mu_{\log}(q_{\mathrm{region}})
  \le \det_{\log}^{\mathrm{norm}}
  \le \theta_{\mathrm{signed}}
  \le C_{\Theta,\mathrm{can}}\cdot(-q_{\mathrm{signed}})
\]
chain and proves the final ordered-real dichotomy without an external
\texttt{thetaSigned\_le\_cTheta\_absLogQ} hypothesis for this local scale.  The
new experiment-surface target
\[
\begin{array}{l}
\texttt{Iut.Stage1.Experiments.remark395ConstructedHolomorphic}\\
\quad\texttt{HullDeterminantSource\_canonicalCThetaScaleChain}
\end{array}
\]
exposes this chain directly from the constructed source object, while
\texttt{remark395ConstructedHolomorphicHullDeterminantSource\_canonicalCThetaScaleAudit}
exposes the full audit record.
The
source equality
\(\mu_{\log}(\phi(P_B))=\det_{\log}^{\mathrm{norm}}\), the Ob4 tensor-bound
input, and the equality with the older algorithmic hull/determinant bridge
remain source obligations rather than full arithmetic vector-bundle
constructions, but the Ob3/Ob5 certificate and ordered log-volume comparison
are now derived from named source-level objects.

The endpoint type \texttt{Stage1Comparison} is not a source proof: its
comparison field is the Corollary-3.12-shaped conclusion, and the corresponding
theorem is only a projection.  The source-facing route must construct this
endpoint from the ledger.  The ledger now records the opaque output
certification and ties the \(\Theta\)-common bound used in the final inequality
to \texttt{chartedContainer.apply certificate}, so the displayed charted
container cannot be paired with an unrelated convenient bound.  Throughout the
current corridor, ``upper ray'' means the signed-log region
\(\{x\mid x\le b\}\), not the ordinary order-theoretic ray \(\{x\mid b\le x\}\).

The largest engineering issue has been reduced to the remaining organization of
the endpoint-route families.  Eight mechanical splits have been made:
\texttt{IUTStage1IUTIVAlgebra.lean} now
carries the Remark 3.12 sign shadows and the conditional \IUT{} IV
real-algebra handoff estimates, while \texttt{IUTStage1FiniteLabels.lean}
carries the finite-label and theta-root cusp-label source layer, and
\texttt{IUTStage1StepX.lean} carries the Step (x) upper-ray corridor together
with its boundary Frobenioid-shift diagnostics.  The Gaussian and
Hodge--Arakelov theta-evaluation shadow layer now lives in
\texttt{IUTStage1Gaussian.lean}, and the Hodge/SHE support layer now lives in
\texttt{IUTStage1HodgeSHE.lean}.  The Theorem 3.11 source-choice and
multiradial possible-image layer now lives in
\texttt{IUTStage1Theorem311.lean}.  The Step (xi) hull/determinant and \(\IPL\)
source layer now lives in \texttt{IUTStage1StepXI.lean}.  The first endpoint
audit family and nonarchimedean realified-Frobenioid/log-Kummer support layer
now live in \texttt{IUTStage1FrobenioidShift.lean}; the original
\texttt{IUTStage1Source.lean} file has now also been split into
\texttt{IUTStage1EndpointAudit.lean}, for the nested LogVolumeChartAudit
refinements, and \texttt{IUTStage1Source.lean}, for the public
source-package audit surface.  Low-risk future refactors are:
\[
\begin{array}{ll}
\text{Structured endpoint route families} & \text{smaller route modules},\\
\text{Generated dependency/audit report} & \text{separate checked target}.
\end{array}
\]
These refactors should be mechanical only: move declarations, preserve names
where possible, and rebuild after each move.

\section{Paper Trace Audit}

The current source map for the Theorem~3.11 to Corollary~3.12 corridor is now
recorded directly in Lean, rather than only in prose.  The namespace
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311ToCorollary312PaperTrace}
\end{array}
\]
contains four obligation records and one assembled trace record.  The first
record covers IUT~III, Theorem~3.11 and Remarks~3.11.2--3.11.4: construction
of the multiradial representation, input-prime-strip link, theta-pilot possible
images, log-theta-lattice procession data, \(F_l\)-label transitions, and the
typed compatibility between possible images and the \((\Ind_1,\Ind_2)\)
equality quotient.  It explicitly keeps the \((\Ind_3)\) contribution as an
upper-semi log-volume inequality.
At the current strict endpoint these trace slots are witnessed by the quotient
equality, the typed-core action-law audit, the quotient-indexed pullback of
possible images, the exact \(|Z/lZ|=l\) cardinality, and the finite procession
transition law, rather than by a single broad quotient-audit wrapper.
The input-prime-strip and Hodge/\(\SHE/\IPL/\APT\) entries are likewise no
longer filled by the whole bridge audit at this strict boundary: the former is
the choice-wise constructed \(\IPL\) link endpoint, and the latter is the
structured \(\IPL/\SHE/\APT\) evidence together with the forbidden
\(\SHE\)-transport guard and the non-forbidden permitted \(\APT\) arrow.
The typed quotient layer now also has a first-class hull/log-volume
compatibility object,
\texttt{EqualityQuotientHullLogVolumeCompatibility}.  It packages the
quotient-indexed possible-image family with a Remark~3.9.5 hull operator,
proves pullback to the original choice-indexed images, proves equality-orbit
invariance for the resulting hull log-volumes under \((\Ind_1)\) and
\((\Ind_2)\), and keeps the \((\Ind_3)\) statement as the typed core's
upper-semi log-volume inequality rather than turning it into a hull equality.
The strict two-point nonvacuity model now instantiates this object as
\texttt{strictFiniteToyEqualityQuotientHullLogVolumeCompatibility}; its audit
endpoint verifies pullback, \((\Ind_1)\)/\((\Ind_2)\) hull-log-volume
invariance, the one-sided \((\Ind_3)\) core inequality, and the fact that the
strict \((\Ind_3)\) step is not collapsed by the equality quotient.  This is a
test of the interface geometry, not a claim that the finite model is a source
model of IUT.
The same strict two-point model now reaches the actual one-sided Theorem~3.11
multiradial construction source through
\[
\begin{array}{l}
\texttt{strictFiniteToyEqualityFLProcessionAction},\\
\texttt{strictFiniteToyOneSidedMultiradialConstructionSource},\\
\texttt{strictFiniteToyOneSidedMultiradialConstructionSource\_}\\
\quad\texttt{ind3\_not\_equalized}.
\end{array}
\]
Given a genuine multiradial source record whose possible-image family is this
strict finite family, Lean constructs the equality-quotient \(F_l\)-procession
action by identity transitions, builds an
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource}, proves its
standard endpoint, and verifies that the strict \(0\to1\) \((\Ind_3)\) step is
still not an equality-quotient identification.  Thus the nonvacuity check now
passes through the same one-sided multiradial source object used by the
preferred \(C_\Theta\) corridor.
It now also reaches the finite-place local-to-global \(C_\Theta\) source through
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedFinitePlaceLocalGlobalCThetaSource},\\
\texttt{StrictFiniteToyOneSidedFinitePlaceLocalGlobalCThetaAudit},\\
\texttt{StrictFiniteToyOneSidedIUTIVArithmeticGapHandoffAudit}.
\end{array}
\]
This constructor takes the strict finite multiradial source together with the
finite Step~(xi)/Haar summation data, derives the usual arithmetic-gap and
\(C_\Theta\) comparison audit, and keeps the strict \((\Ind_3)\) non-collapse
visible inside the same local-to-global source object.  The last audit pins the
new explicit \(\IUT{}\,\mathrm{IV}\) arithmetic-gap handoff to this same
nonvacuity witness: finite-sum identifications, the summed Step~(xi)/Haar
inequality, \(C_\Theta+1=A-M\), cancellation to
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\), and the strict \((\Ind_3)\)
non-equality all live in one checked object.
The bridge has also been lowered to the normalized-Haar Step~(xi) local-term
source:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedNormalizedHaarStepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedNormalizedHaarStepXILocalTermCThetaAudit}.
\end{array}
\]
Here the canonical local terms come from the localized vector-bundle determinant
source, and the global \(+1\) is obtained from a finite-place Haar-defect source,
while the strict \((\Ind_3)\) step remains outside the equality quotient.
The strict finite route has now been pushed one layer further, to the local
\(p\)-adic unit-ball Haar source:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedPadicUnitBallHaarStepXILocalTerm}\\
\quad\texttt{CThetaSource},\\
\texttt{StrictFiniteToyOneSidedPadicUnitBallHaarStepXILocalTerm}\\
\quad\texttt{CThetaAudit}.
\end{array}
\]
This replaces the abstract finite-place Haar-defect input by placewise
unit-ball normalization data \(\mu(\mathcal O_v)=1\), the base-prime dilation
character, and the prime/finrank index
\(p_v^{[K_v:\mathbb Q_{p_v}]}\).  Lean proves local nonnegativity and the
distinguished-place \(\sum_v \delta_v\geq1\) contribution from this source, and
the audit keeps the same strict \((\Ind_3)\) non-equality through the projected
local-to-global \(C_\Theta\) comparison.
Finally, the strict finite witness now reaches the IUT IV arithmetic-defect
surface:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVArithmeticDefectStepXI}\\
\quad\texttt{LocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVArithmeticDefectStepXI}\\
\quad\texttt{LocalTermCThetaAudit}.
\end{array}
\]
At this layer the local defect is named as the IUT IV arithmetic-defect term,
with a placewise proof that it equals the \(p\)-adic unit-ball Haar index.  The
same audit therefore carries the total defect lower bound and the strict
\((\Ind_3)\) non-collapse in the paper-side \(C_\Theta\) vocabulary.
The same strict witness has now been lowered to the IUT IV arithmetic-divisor
evaluation surface:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVArithmeticDivisorEvaluation}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVArithmeticDivisorEvaluation}\\
\quad\texttt{StepXILocalTermCThetaAudit}.
\end{array}
\]
Here the arithmetic upper term and main-log term are no longer supplied as
separate global equalities.  They are read from
\texttt{IUTStage1IUTIVThetaPilotArithmeticDivisorLocalEvaluationSource}, whose
endpoint gives the local different/conductor sums, prime-error sum,
arithmetic-upper sum, and main-log sum.  The remaining handoff is the pointwise
identity matching each local arithmetic upper contribution with the Step~(xi)
canonical term, the IUT IV local defect, and the local main-log contribution.
The strict witness has also been lowered through the first Theorem~1.10
arithmetic-divisor construction layer:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVTheorem110ArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVTheorem110ArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaAudit}.
\end{array}
\]
At this boundary, the older theta-pilot local evaluation data are produced
from effective different, \(q\)-parameter, and conductor arithmetic divisors,
the conductor support comparison with the \(q\)-parameter divisor, and the
Theorem~1.10 Step~(v)--(vii) local estimate gate.  The audit records the
different/conductor degree sums, the prime-error and main-log finite sums, the
local procession upper-bound inequality, and the Step~(vi) vanishing condition
for nondistinguished nonarchimedean places.
The strict witness now also reaches the formula-level Theorem~1.10
arithmetic-divisor source:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVTheorem110FormulaArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVTheorem110FormulaArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaAudit}.
\end{array}
\]
This removes the local estimate gate as a primitive input on the strict route.
The gate is produced from the local case formula source: the Step~(v)
distinguished formula bound, the Step~(vi) nondistinguished nonnegative-gap
formula with zero procession contribution, and the Step~(vii) archimedean
formula bound.
The strict witness has now been lowered one layer further, to the
Proposition~1.4/1.5-backed source:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVTheorem110PropositionArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVTheorem110PropositionArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaAudit}.
\end{array}
\]
This audit records the local Proposition~1.4 distinguished log-shell estimate,
the Proposition~1.4 nondistinguished zero/gap estimate, and the
Proposition~1.5 archimedean metric estimate before projecting to the formula
source.  The distinguished and archimedean formula-to-gap comparisons remain
visible as the current Step~(xi)/IUT IV matching payload.  The next lower
boundary is the local analytic construction of these proposition objects.
This boundary is now also represented on the strict route:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVTheorem110LocalAnalyticArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVTheorem110LocalAnalyticArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaAudit}.
\end{array}
\]
Here the Proposition~1.4/1.5 estimates are produced from local analytic
construction sources: distinguished and nondistinguished finite-extension
Haar/log-volume log-shell constructions, and archimedean direct-sum metric
constructions.  The strict route has also been lowered to the additive-Haar
version of this boundary:
\[
\begin{array}{l}
\texttt{strictFiniteToyOneSidedIUTIVTheorem110AdditiveHaarLocalAnalytic}\\
\quad\texttt{ArithmeticDivisorStepXILocalTermCThetaSource},\\
\texttt{StrictFiniteToyOneSidedIUTIVTheorem110AdditiveHaarLocalAnalytic}\\
\quad\texttt{ArithmeticDivisorStepXILocalTermCThetaAudit}.
\end{array}
\]
This audit exposes the actual additive Haar compact-open normalization
endpoint at each distinguished and nondistinguished finite place, then projects
to the local-analytic strict audit.  Thus the strict finite diagnostic no
longer stops at generic finite-extension log-shell data before entering the
Step~(xi) \(C_\Theta\) comparison.

The Step~(x) record names the finite-divisor packet, realified Frobenioid
log-Kummer source, Kummer/forgetting compatibility, vertical-\(IQ\) target
source, and packet source-target log-volume calibration.  Its constructor
from the typed indeterminacy core proves the equality/equality/inequality
pattern: \((\Ind_1)\) and \((\Ind_2)\) preserve procession-normalized
log-volume, while \((\Ind_3)\) only gives a one-sided bound.  The same
Step~(x) record now carries the relation-level
\texttt{Ind3UpperSemiRelationAudit}, so this one-sided law remains a named
certificate in the paper-trace obligations rather than merely an extracted
function field.  The paper-trace API now also exposes projections for the
typed Theorem~3.11 action-law audit, the relation-level \((\Ind_3)\)
upper-semi audit, the step-level \((\Ind_3)\) transport certificate, and the
fact that \((\Ind_3)\) contributes no generator to the equality quotient.  The
Step~(xi)
record names the remaining Remark~3.9.5 hull/determinant work: holomorphic hull
operator, possible-image family matching, q-region containment, Ob1/Ob2 hull
absorption, Ob3/Ob4 determinant normalization, Ob5 quotient compatibility, Ob7
prime-strip retention, tensor-power bound, and the q-region-to-theta
log-volume chain.  In the current top-level audit, the tensor-power slot is the
constructed normalized determinant bound, while the q-region slot is the
separate inequality obtained by composing q-to-determinant and determinant-to-
theta in the constructed record bridge.

The IUT~IV record names the local-to-global \(C_\Theta\) obligations below the
current additive-Haar boundary: Proposition~1.4 distinguished log-shell
inclusions, now instantiated as per-place arithmetic-divisor-backed component
endpoints; Proposition~1.4 numerical bounds, now instantiated as the local
different/conductor nonnegativity facts; the nondistinguished zero log-volume
result, now instantiated as the per-place nondistinguished additive-Haar
log-shell endpoint; Proposition~1.5 metric containment, now instantiated as
the per-place archimedean metric endpoint; the Theorem~1.10
arithmetic-divisor source; distinguished and archimedean formula-to-gap
comparisons, now instantiated as named per-place comparison endpoints;
additive Haar local normalization; the Step~(xi)-to-IUT~IV local
matching equality; the finite-place arithmetic gap
\(C_{\Theta,\mathrm{can}}+1\leq A_{\mathrm{upper}}-M_{\log}\); and the global
proof of \(C_{\Theta,\mathrm{can}}\leq C_\Theta\).  Its
\texttt{LocalToGlobalArithmeticChainAudit} now has named projections for all
seven chain entries, including the local Step~(xi)-to-IUT~IV arithmetic-term
matching, the finite-place arithmetic gap, and the final
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison.

The trace now also has a separate preferred-boundary record,
\texttt{AdditiveHaarArithmeticDegreePadicObligations}.  This names the
remaining constructions specifically used by the deepest current additive-Haar
endpoint: Theorem~1.10 additive-Haar local analytic construction, local
arithmetic matching, arithmetic-divisor formula splitting, \(p\)-adic
prime-error/defect/main-log splitting, Step~(xi) arithmetic-degree
calibration, unscaled Proposition~1.4/Step~(vii) local degree-bound
identifications, determinant-multiplicity and adjusted-log-volume identifications,
realified packet recovery of the Step~(x) equalities, and the constructed
Hodge/\(\SHE\)/\(\IPL\) provenance now threaded through that endpoint.  Its
\texttt{RemainingPayloadAudit} is included in the assembled corridor audit, so
the preferred route no longer hides these lower source assumptions behind the
generic IUT~IV \(C_\Theta\) record.  Each component also has a named Lean
projection theorem.  This makes the next source-math work precise: the local
analytic additive-Haar construction, arithmetic-divisor splitting,
\(p\)-adic error decomposition, Step~(xi) arithmetic-degree calibration, and
the determinant/log-volume identifications must be constructed individually
before this audit can be discharged.

The assembled
\texttt{Obligations} record adds the endpoint-level requirements that the final
preferred theorem must not expose either the raw
\(\theta_{\mathrm{signed}}\leq C_\Theta(-q_{\mathrm{signed}})\) input or the
raw \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison as public hypotheses.
From the assembled \texttt{RemainingPayloadAudit}, Lean now reconstructs the
whole IUT~IV local-to-global arithmetic-chain audit and separately projects
both raw-hypothesis-removal requirements.  The same assembled audit now also
reconstructs the full additive-Haar/arithmetic-degree-padic subledger and
projects each of its lower source clauses: the Theorem~1.10 local analytic
construction, local arithmetic matching, arithmetic-divisor split,
\(p\)-adic prime-error/defect/main split, Step~(xi) arithmetic-degree
calibration, determinant/coefficient and adjusted-log-volume identifications,
Step~(x) packet equalities, the constructed \(\IPL\) and \(\SHE/\APT\)
transport data, and the strongest additive-Haar endpoint certificate.
Its Theorem~3.11/remarks subledger now also contains a
\texttt{typed\_indeterminacy\_nonvacuity\_witness\_constructed} slot,
discharged at the strongest current boundary by the strict two-point typed
\((\Ind_1)/(\Ind_2)/(\Ind_3)\) witness.

\section{Next Work}

The remaining mathematical work is organized by the trace audit above.  One
major branch is still to construct, rather than assume, more of the
source-facing \SHE{} and Hodge-descent preservation data.  The route is:
\[
\begin{array}{c}
q^{j^2}\text{ finite Gaussian endpoint with pivotal restriction}\\
\Downarrow\\
\text{Gaussian and splitting monoid construction}\\
\Downarrow\\
\text{factored square/full-label preservation}\\
\Downarrow\\
\text{Hodge/SHE transport audit}\\
\Downarrow\\
\text{hull/log-volume comparison}\\
\Downarrow\\
C_\Theta\ge -1 .
\end{array}
\]
The project should continue by replacing the present record fields for
factored \SHE{} preservation and Hodge-descent source-target alignment with
the corresponding constructions from \IUT{} I--III.
The first source-derived bridge layer has now been added: the final
finite-divisor vertical-\(IQ\) route can consume separated \(\IPL\),
\(\SHE\), hull/determinant, and theta/Hodge calibration source components
instead of an opaque route-alignment argument.  The \(\SHE\) component has been
refined to a finite Hodge/SHE transport package that exposes the two theater
sides, the finite label equivalence, full-label log-volume preservation,
transported-average preservation, and the current history-separation guard.
It now also has a typed source boundary that carries the Hodge-theater descent
bridge and a typed allowed-forgetting witness separately from the
synchronization-derived finite preservation data.  The remaining work is to
make each of those components itself follow from the relevant source-paper
constructions, rather than supplying them as records.
The \(\IPL\) component can now be constructed at the public finite-divisor
vertical-\(IQ\) endpoint from the finite Hodge/\(\SHE\) transport together with
a Theorem 3.11 IPL-link construction source.  The endpoint no longer receives a
free-standing \(\IPL\) datum, source/target endpoint equalities, or a separate
\(\IPL\) log-volume transport source: the constructed input-prime-strip link
gives the endpoint equalities definitionally, the source object aligns that
constructed datum with the pre-ledger certificate, and log-volume preservation
is read from the finite Hodge/\(\SHE\) transport.
The foundational qualitative certificate is no longer only a nonempty
bookkeeping triple.  The declarations
\[
\begin{array}{l}
\texttt{HodgeTheaterTransportSystem},\\
\texttt{StructuredSHETransportContext},\\
\texttt{AlgorithmicParallelTransportConstruction}
\end{array}
\]
record permitted Hodge-theater transport arrows, forbidden theater
identifications, and APT data built from a permitted arrow.  Lean proves that a
forbidden domain-to-codomain SHE identification admits no allowed transport
arrow, and that the constructed APT datum has the permitted arrow's mechanism,
the constructed output family, the output-family equality back to the
pre-ledger family, the allowedness proof, and the resulting non-forbiddenness
of the APT arrow.  The Stage~1 wrapper
\(\texttt{ConstructedQualitativeCertificateData}\) pins the pre-ledger
certificate to the certificate constructed from these IPL/SHE/APT objects and
returns both a compact qualitative transport audit and this stricter APT
transport audit.
The finite Hodge/\(\SHE\) transport layer now has the corresponding source
discipline audit
\[
\begin{array}{l}
\texttt{IUTStage1ConstructedQualitativeFiniteHodge}\\
\quad\texttt{SHETransportDisciplineAudit}.
\end{array}
\]
It records, in one object, that the finite Hodge/\(\SHE\) comparison uses only
the history-separated forgetful reading, while the constructed \(\SHE\)
transport system forbids a direct domain-to-codomain identification and the
\(\APT\) arrow is separately proved non-forbidden.  Thus the finite comparison
is no longer documented merely by a side inequality; the typed
allowed/forbidden transport discipline is visible next to it.
The route-facing constructor
\[
\texttt{IUTStage1ConstructedQualitativeFiniteHodgeSHETransportSource}
\]
now packages this as source data: from the constructed qualitative bundle and
the Hodge--Arakelov theta evaluation synchronization, it builds the
history-separated finite Hodge/\(\SHE\) transport source and returns the same
typed discipline audit.  In particular, the finite forgetful comparison is
kept separate from the forbidden direct \(\SHE\) identification while the
permitted \(\APT\) arrow remains part of the constructed qualitative input.
The next bridge,
\[
\texttt{IUTStage1ConstructedQualitativeFiniteHodgeSHEIPLConstructionSource},
\]
adds the constructed Theorem~3.11 \(\IPL\) link to this same source object and
projects to the existing finite Hodge/\(\SHE\)+\(\IPL\) log-volume chain.  Thus
the \(\IPL\) handoff can now be audited from the constructed qualitative
\(\SHE/\APT\) transport boundary through the constructed input-prime-strip
link, with no separate finite Hodge/\(\SHE\) source supplied at that layer.
This is the present typed replacement for the older raw
\(\texttt{HasStructuredIPL/SHE/APT}\) certificate fields.  The Theorem~3.11
source layer now exposes
\(\texttt{IUTStage1Theorem311ConstructedQualitativeInputs}\): its pre-ledger
audit is induced from the constructed qualitative certificate, it projects back
to the existing structured-input route, and it exposes the forbidden
SHE-domain-to-codomain transport guard together with the permitted APT
non-forbiddenness proof.  This has now been promoted to the strengthened SHE
route surface by
\(\texttt{IUTStage1Theorem311ConstructedQualitativeInputsWithSHE}\), which
projects to the existing \(\texttt{StructuredInputsWithSHE}\) route, builds the
current multiradial source record, and exposes public source-obligation and
Corollary~3.12 audit constructors without asking callers to supply a raw
pre-ledger audit.  The same constructed boundary now reaches the named
Theorem~3.11-to-Corollary~3.12 checkpoint layer:
\(\texttt{ConstructedQualitativeStructuredSHERouteSummary}\) and
\(\texttt{ConstructedQualitativeTheorem311ToCorollary312Checkpoints}\) retain the
old structured route only as a projection, while the public boundary carries
the constructed qualitative audit, the forbidden SHE-domain-to-codomain
transport statement, and the APT transport audit identifying the actual datum
with the permitted-arrow construction.  The constructed
finite Hodge/\(\SHE\)+\(\IPL\) bridge audit now also exposes the choice-wise
\(\IPL\) endpoint
\(\texttt{choiceWiseIPLEndpoint}\): for every Theorem~3.11 choice the
constructed link has source equal to the fixed input prime strip and target
equal to the corresponding choice prime strip, while the same audit retains the
certificate-to-constructed-\(\IPL\)-datum equality and finite Hodge/\(\SHE\)
log-volume preservation.
There is now also a certificate-pinned variant of this boundary.  It reads the
\(\IPL\) datum directly from the pre-ledger certificate and asks only for the
two endpoint equalities of that certificate link.  Consequently the public
Hodge--Arakelov/history-separated route may avoid the stronger
certificate-equals-constructed-\(\IPL\)-datum assumption.  The remaining
source-paper task for this layer is to construct those certificate endpoint
equalities, and eventually the input-prime-strip link itself, from the
Theorem 3.11 \(\IPL\) machinery.
At the next source boundary, the same public endpoint can now receive a
synchronized Hodge--Arakelov source object.  This object carries the calibrated
source evaluation, target evaluation, and canonical one-label degree
preservation together, and it projects the finite Hodge/\(\SHE\) transport
used by the route.  The allowed-forgetting predicate is fixed to the
history-separation condition of the record's Hodge-theater descent bridge, so
the public route no longer needs to be handed the finite transport record, a
free square-weight profile, a separate theta-root source, a separate
source/target evaluation synchronization equality, or a free permission
predicate.  These are constructed or projected from the synchronized
Hodge--Arakelov and Theorem 3.11 source data.  The actual Hodge-theater
forgetting operation and the deeper construction of the theta-evaluation
sources remain open source-paper obligations.
The summand-charted Step (xi) input also has a synchronized target-charted
form: the transported theta chart is calibrated against the target
Hodge--Arakelov canonical one-label degree, and \Lean{} derives the
charted-theta/source-Hodge equality using the synchronized canonical-one
preservation before projecting to the previous summand source.  Thus the
public route no longer has to receive that charted source-Hodge scalar equality
as a primitive Step (xi) summand-calibration field.
The same source now has a possible-image q-pilot refinement: the q-region is
definitionally the chosen Theorem 3.11 possible-image region, and the
\(q\subseteq P_{\mathrm{choice}}\) containment is projected by reflexive
membership rather than supplied as an additional Step (xi) field.
The experiment surface exposes this refinement as an audit endpoint before the
finite-divisor route is applied: it reports the definitional q-region equality,
the target-charted Hodge/summand identities, the hull-bridge equality, the sign
and normalization side conditions, and the derived
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison.
This source now also projects to the generic possible-image side-conditioned
holomorphic-hull/determinant source.  In that projection, the Ob4 normalized
tensor-power bound is derived from the Hodge/family-hull calibration, the
record-canonical hull/determinant bridge equality is derived from the package
hull-det obligations, and the q-pilot side conditions are read from the same
obligations object.  The experiment surface therefore has a raw
constructed-\(\IPL\) endpoint for this summand/family-hull route, proving
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) before the later
\(C_\Theta\) numeric bound is invoked.
The summand/family-hull q-comparison payload is now also promoted to a named
audit proposition, bundling the possible-image q-pilot choice, determinant
summand formula, family-hull log-volume identification, obligation-backed
hull/determinant bridge equality, and raw signed comparison.
The source-derived bridge constructor itself now has the same specialized
input form: it consumes the calibrated Hodge--Arakelov synchronization, the
constructed \(\IPL\) source, and the synchronized target-charted possible-image
summand/family-hull Step (xi) source, then performs the generic hull-source
projection internally.  The experiment surface exposes a bridge audit endpoint
for this constructor, so the constructed bridge no longer has to be reviewed via
an intermediate generic holomorphic-hull/determinant source.
The finite-divisor vertical-\(IQ\) \(C_\Theta\) endpoint now has the same
direct bridge form: the public Step (xi) input is the synchronized
target-charted possible-image summand source, and the boundary theorem builds
the source-derived Hodge/\(\SHE/\IPL\)/hull bridge internally before entering
the generic finite-divisor route.  Thus this endpoint no longer has to reach the
bridge through the older target-charted/summand projection chain.
The same summand/family-hull route now has a no-\(C_\Theta\) finite-divisor
boundary returning the named q-comparison audit together with the finite Step
(x) packet equalities and vertical-\(IQ\) target equalities, separating the
summand Step (xi)/Step (x) provenance from the later numeric estimate.
The target chart comparison can now be moved one layer earlier.  A
target-charted Hodge--Arakelov synchronization records that the transported
pre-ledger theta chart is the target Hodge--Arakelov canonical one-label
degree; \Lean{} then derives the source theta-monoid reading from the
synchronized canonical-one preservation.  The associated possible-image summand
Step (xi) source no longer carries this target chart/canonical-one equality as
a hull-side calibration field; it keeps only the determinant-side finite
summand equality plus the record-native possible-image hull data.  The bridge
audit and finite-divisor \(C_\Theta\)-endpoint expose this refined source
boundary.
This refined target-charted route now also has a no-\(C_\Theta\) finite-divisor
boundary: it returns a named bridge audit, including the constructed
\(\IPL\)-datum checks, target-chart synchronization, log-volume preservation,
raw signed comparison, and history-separation guard, together with the finite
Step (x) packet equalities and vertical-\(IQ\) target equalities.
The target-charted possible-image route now has a determinant-payload
refinement.  A dedicated Hodge/determinant family-hull source packages the
record-native family-hull determinant source, the equality between the package
measure and the hull log-volume measure, and the Hodge theta-monoid equality
with the finite sum of adjusted determinant summands.  The possible-image Step
(xi) source consumes this single payload and projects the earlier
family-hull, measure-calibration, and summand-equality fields internally before
entering the same side-conditioned hull/determinant bridge.  The bridge audit
now has a determinant-refined raw finite-divisor boundary as well: it reuses the
target-charted summand bridge audit, adds the family-hull/determinant log-volume
equality, and carries the finite Step (x) packet and vertical-\(IQ\) target
equalities before the \(C_\Theta\) estimate is invoked.
The experiment surface therefore reports the determinant log-volume equality in
addition to the target theta chart, Hodge theta-monoid, possible-image q-region,
hull-det bridge, and raw \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\)
comparison.  The
finite-divisor vertical-\(IQ\) experiment endpoint now exposes this determinant
payload as the strongest public Step (xi) boundary in this corridor.
The Hodge/\(\IPL\) side of this route has also been bundled one layer earlier.
A target-charted Hodge--Arakelov \(\IPL\)-construction source now contains the
target-charted Hodge synchronization and the constructed Theorem 3.11
input-prime-strip link.  From these data \Lean{} constructs the finite
Hodge/\(\SHE\) transport source, reads the \(\IPL\) log-volume transport from
that finite transport, and preserves the target/source log-volume equality
without a separate transport equality field.  The determinant possible-image
bridge and finite-divisor vertical-\(IQ\) experiment endpoints now consume this
single Hodge/\(\IPL\) payload together with the Step (xi) determinant
possible-image source.  This packaged route now also has a no-\(C_\Theta\)
finite-divisor boundary that returns the packaged-source bridge audit together
with the finite Step (x) packet equalities, vertical-\(IQ\) target equalities,
and raw signed comparison before the numeric estimate is supplied.  The
Hodge/\(\IPL\) construction source itself now
exposes the history-separated finite Hodge/\(\SHE\) transport-source audit:
the source and target Hodge--Arakelov value sources, record-native forgetting
permission, pointwise representative comparison level, identity coordinate
equivalence, and Hodge-theater separation are visible before the
constructed-\(\IPL\) layer is formed.
The strongest public target-charted route now packages these two sides into one
source object before the finite Step (x) data are introduced.  This all-in-one
route source exposes the target theta chart comparison, constructed
\(\IPL\)-datum equality, possible-image q-region, determinant summand equality,
family-hull/determinant equality, package hull-det bridge equality, log-volume
transport preservation, positivity, normalization, and raw
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison as projections
from a single source-facing payload.  It now also has a divisor-packet
no-\(C_\Theta\) boundary returning a named all-in-one route bridge audit, the
finite Step (x) packet equalities, the vertical-\(IQ\) target equalities, and the
raw signed comparison; thus the source-derived Step (xi) bridge is reviewed as a
single route object before the finite packet source is constructed.  The same
named route audit now also travels through the exact vertical-\(IQ\) finite-source
boundary, alongside the log-Kummer vertical-\(IQ\) calibration-source equality,
the finite-source equalities, and the exact target equalities.
The same
route now also projects
explicitly to the possible-image side-conditioned holomorphic
hull/determinant source, exposing the chosen Theorem 3.11 possible-image
q-region, containment in the record possible-image union, the Ob4/tensor-power
determinant bound, positivity, normalization, and the raw signed comparison
before the finite Step (x) vertical-\(IQ\) data or the separate \(C_\Theta\)
numeric bound enter.  On the Hodge/\(\SHE\) side, the same route now exposes
the finite transport audit separately: the structured-\(\SHE\) flag,
source/target Hodge theaters, coordinate transport, full-label log-volume
preservation, transported-average preservation, and history-separation guard
are route-level projections.  On the Hodge/\(\IPL\) side, the all-in-one route
also projects directly to the finite Hodge/\(\SHE\) plus constructed-\(\IPL\)
source object and exposes the target theta chart comparison, certificate-pinned
\(\IPL\) datum, constructed-\(\IPL\) datum, log-volume preservation, allowed
forgetful transport, and Hodge-theater history separation as route-level
audits.  The packaged target-charted Hodge--Arakelov/\(\IPL\) source now
exposes both the history-separated finite Hodge/\(\SHE\) transport-source
endpoint and the constructed \(\IPL\) log-volume transport endpoint itself,
including the source/target Hodge--Arakelov value sources, record-native
forgetting permission, pointwise representative comparison level, identity
coordinate equivalence, certificate-pinned \(\IPL\) datum, input/output
prime-strip link endpoints, finite Hodge-theater source and target sides,
log-volume preservation, allowed forgetful transport, and history separation;
the all-in-one route projects these source-level endpoints.  Upstream of these
transport audits, the route now also exposes the
Hodge--Arakelov theta-evaluation layer: the canonical theta-root generator and
full label, zero and canonical Gaussian degrees, the finite \(q^{j^2}\)
square-weight degree formula, source full-label theta calibration, and the
target chart/canonical-one comparison are all route-level projections.  Between
this Gaussian layer and the finite transport object, the route now exposes the
factored \(\SHE\) preservation constructor itself: canonical one-label
preservation for the source and target Hodge--Arakelov theta evaluations
constructs identity coordinate transport, coordinate-square preservation,
full-label map and value preservation, transported-average preservation, and
the Hodge-theater history-separation guard.  The next route projection pins the
finite Hodge/\(\SHE\) transport source itself to
the history-separated constructor from these source and target
Hodge--Arakelov theta-evaluation sources: the source/target value sources,
history-separated forgetful permission, pointwise representative comparison
level, identity coordinate equivalence, and Hodge-theater history separation
are exposed before the constructed-\(\IPL\) layer is used.  The constructed
\(\IPL\) log-volume transport source is now exposed at the same route boundary:
the certificate-pinned \(\IPL\) datum, constructed datum, input/output
prime-strip link endpoints, finite Hodge-theater source and target sides,
log-volume preservation, allowed forgetful transport, and history separation
are all projected before the Step (xi) hull/determinant source enters.  The same
route boundary now also has a constructor-identity endpoint,
\texttt{constructedIPLTransportSourceEqConstructedEndpoint}, which states that
the projected \(\IPL\)/log-volume source is exactly
\texttt{ofTheorem311IPLLinkConstructionSource} applied to the finite
Hodge/\(\SHE\) transport and the carried input-prime-strip-link construction.
The same
boundary now records the provenance of the \(\IPL\) log-volume equality: the
\(\IPL\) source log-volume is the source average of the finite
Hodge/\(\SHE\) transport audit, the \(\IPL\) target log-volume is the
transported target average, and their equality is the transported-average
preservation theorem from the finite Hodge/\(\SHE\) layer.  The same
constructed-\(\IPL\) boundary now also exposes the choice-wise input-prime-strip
links generated by the Theorem~3.11 link construction: for every possible output
choice, the constructed link has source equal to the route's input prime strip
and target equal to that choice's prime strip.  This is exposed by the
experiment suffix
\texttt{thetaMonoidMatchedConstructedIPLChoiceLinkEndpoint}, giving a finite
choice-indexed shadow of the \(\IPL\) condition before Step (xi) hull data is
used.  The bundled exact
vertical-\(IQ\) route now carries this same finite-average provenance together
with the route-owned \(\IPL\) datum, raw Step (xi) comparison, log-Kummer
vertical-\(IQ\) target calibration, Frobenioid precision flag, and Step (x)
upper-semi inequality before the external \(C_\Theta\) numeric bound is used.
The same bundled exact-route boundary now also carries the
Remark~3.9.5(Ob5) family-hull guard: for two nonempty Theorem~3.11 possible
images, both regions lie in the record family hull and have the same
upper-semi quotient image, while the determinant/log-volume identifications,
raw signed comparison, log-Kummer non-interference, and Step (x) upper-semi
bound are projected from the same source package.  This Ob5 guard is now also
threaded through the Gaussian-front audit: the canonical Hodge--Arakelov
theta label, zero Gaussian degree, square-weight formula, two arbitrary
nonempty possible images, their common family-hull quotient image, and the
exact Step (x) log-Kummer/upper-semi facts appear in one endpoint.
The same all-in-one route source now feeds the Hodge direct-labelled
finite-divisor vertical-\(IQ\) endpoint directly: instead of passing the
generic source-derived bridge at the public Step (x) boundary, \Lean{} projects
the bridge from the target-charted Hodge/\(\IPL\)/determinant possible-image
route and then applies the Hodge-derived labelled-average and finite-divisor
packet-local construction.
On the
Step (xi) side, the target-charted Hodge/determinant possible-image source now
exposes the converted side-conditioned hull/determinant endpoint itself: the
chosen Theorem 3.11 possible image, its containment in the record possible-image
union, the tensor-power bound, q-positivity, normalization, and raw comparison
are visible before the Hodge/\(\IPL\) route source is assembled.  The
all-in-one route projects this source-level endpoint.  The route also exposes
the canonical hull/tensor-power bridge
equality itself: the common-container hull/determinant bridge is identified
with the record-canonical Theorem 3.11 possible-image hull data, weighted
determinant, measure calibration, and tensor-power bound before the finite
Step (x) vertical-\(IQ\) source or the external \(C_\Theta\) numeric bound
enter.  This canonical bridge audit is now available at the target-charted
Hodge/determinant Step (xi) source boundary itself; the all-in-one route
endpoint projects it from that source.  The same route now also exposes the
source-paper-shaped
Step (xi) passage from Theorem 3.11 possible images to the holomorphic hull and
then to the log-volume bound: the endpoint records certification, the \(\SHE\)
datum, equality of the theta-pilot possible-image union with the record union,
containment of that union in the applied holomorphic hull, the
\(\theta_{\mathrm{signed}}\) log-volume bound, and the resulting raw
comparison \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).  The route-level
theorem is now a projection of the reusable possible-image Step (xi)
source-level holomorphic-hull/log-volume endpoint; this endpoint is also
available at the target-charted Hodge/determinant possible-image source
boundary before the Hodge/\(\IPL\) construction wraps it into the all-in-one
route.  The same route now also exposes the determinant summand/family-hull
payload as its own audit: the target theta-chart readings, Hodge theta-monoid
summand formula, family-hull/determinant log-volume equality, package
measure-to-hull-log-volume calibration, tensor-power normalization,
determinant tensor bound, and raw
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison are projected at
the all-in-one route boundary before finite Step (x) or the external
\(C_\Theta\) bound enter.  The same all-in-one route now exposes the raw
comparison at the source boundary before the generic bridge is assembled: the
certificate-pinned \(\IPL\) datum, preserved \(\IPL\) log-volume, source
Hodge--Arakelov value source, chosen possible-image q-region, and
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison are all projected
from the route source.  The bridge-level raw comparison endpoint now uses this
source-boundary comparison for its final inequality while still auditing the
assembled bridge's \(\IPL\) and Hodge/\(\SHE\) projections.  The same
all-in-one route now has a direct Gaussian-to-Step (xi) audit endpoint: the
theta-root canonical label and square-weighted Gaussian degree formula, the
finite Hodge/\(\SHE\) history-separated transport, the constructed
\(\IPL\) log-volume preservation, the constructed choice-wise input-prime-strip
links, the chosen possible-image q-region with its union containment, the
determinant summand calibration, the package hull/determinant bridge datum, and the raw
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison are projected
from one route source before any finite Step (x) vertical-\(IQ\) input enters.
This audit has also been promoted to a named route-source proposition, and the
finite-divisor vertical-\(IQ\) boundary now has an audited endpoint that returns
this Gaussian-to-Step (xi) payload together with the \(C_\Theta\) dichotomy.
Consequently the public finite-divisor route exposes the constructed
Hodge--Arakelov/\(\SHE/\IPL\)/hull chain used for the raw comparison at the same
boundary where the Step (x) packet data and external numeric bound enter.
The finite-source form of this boundary now also has a no-\(C_\Theta\) audited
endpoint: before the ordered-real dichotomy is invoked, it returns the named
Gaussian-to-Step (xi) audit together with the route-owned bridge, raw comparison,
finite-source packet equalities, and vertical-\(IQ\) target equalities.
The bundled finite exact vertical-\(IQ\) source now has the same audited
\(C_\Theta\) boundary: one source package returns the named Gaussian-to-Step
(xi) route audit, the exact vertical-\(IQ\) Frobenioid-isomorphism precision
flag, and the final dichotomy.  This moves the strongest finite bad-local
corridor's public endpoint closer to the intended source-derived chain while
still leaving the external numeric \(C_\Theta\) estimate explicit.
The same bundled source now also exposes the corresponding raw audit endpoint
before the \(C_\Theta\) estimate is supplied: it returns the named
Gaussian-to-Step (xi) audit, exact vertical-\(IQ\) precision, target
log-Kummer calibration, the raw \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\)
comparison, q-pilot log-Kummer non-interference, and the Step (x) upper-semi
bound.  This separates the source-derived Step (xi)/Step (x) corridor from the
still-open numerical estimate in the public theorem surface.
The same route
also exposes the Remark~3.9.5(Ob5) bounded-family quotient mechanism: for any
two nonempty Theorem~3.11 possible images, the endpoint proves that both lie
in the record possible-image family hull and have the same image under the
upper-semi quotient by that hull.  The audit carries the determinant
log-volume identification, the family-union-to-family-hull inequality, the
normalized tensor-power equality, and the raw
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison, so the
``do not choose a convenient possible image as canonical'' guard is visible
before the finite Step (x) vertical-\(IQ\) source and the external
\(C_\Theta\) bound enter.  The route source
now owns the assembled source-derived bridge via a
\texttt{toSourceDerivedBridge} projection, and the finite-divisor vertical
\(IQ\) theorem consumes that route-owned bridge instead of spelling out the
generic bridge constructor at the Step (x) boundary.  This separates the
Step (xi) comparison and bridge assembly from the later finite Step (x) and
\(C_\Theta\) boundary.  Its finite Step (x) boundary now also has a
packet-source form: the public all-in-one route can consume a
\texttt{NonarchimedeanFiniteDivisorPacketLocalSource} directly, so the divisor
packet, mono-analytic theater, and packet-local log-volume equalities are
audited inside the named Step (x) source object rather than repeated as loose
endpoint arguments.  The same public route now exposes the finite-source
Step (x) boundary before applying the \(C_\Theta\) numeric bound: the endpoint
records the route-owned \(\IPL\) datum and log-volume preservation, the raw
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison, the
packet-local source log-volume chain, and the vertical-\(IQ\) target
identifications from the supplied finite-source and target-source records.  A
tighter exact vertical-\(IQ\) variant now consumes a
\texttt{NonarchimedeanThetaRootExactVerticalIQRealifiedEntrySource} instead of
a separate target-source record: the endpoint projects the retained
log-Kummer vertical-\(IQ\) calibration source, the Kummer/forgetting transfer
guards, and the exact target before applying the same \(C_\Theta\) boundary.
The current strongest public endpoint packages these data into one bundled
exact-route source object, so the route, upper-semi entry, finite Step (x)
source, and exact vertical-\(IQ\) source are audited as projections before the
external numeric bound enters.  Its realified Step (x) correspondence endpoint
now exposes the theta-root canonical generator, nonzero canonical label,
Kummer/forgetting log-volume preservation, q-pilot log-Kummer
non-interference, and the local-object upper-semi bound from the same bundled
exact source.  Its source-derived corridor endpoint additionally records the
history-separated Hodge/\(\SHE\) transport guard, certificate-pinned
\(\IPL\) datum, \(\IPL\) log-volume preservation, possible-image hull
containment, \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\), exact
vertical-\(IQ\) calibration, and Step (x) non-interference in one audit
statement.  The Gaussian-front corridor endpoint extends this by projecting
the Hodge--Arakelov theta-evaluation source's canonical label, Gaussian degree
normalization, square-weight formula, full-label compatibility, and target
chart comparison before entering the same Hodge/\(\SHE\), \(\IPL\), hull, and
Step (x) chain.  A determinant-refined Gaussian corridor endpoint now keeps the
Step (xi) determinant payload visible in this same bundled exact route: after
the Hodge--Arakelov Gaussian data it projects the target-chart/source
theta-monoid comparison, finite adjusted-summand formula, family-hull
determinant log-volume equality, package measure calibration, determinant
tensor bound, raw \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\)
comparison, exact vertical-\(IQ\) calibration, q-pilot log-Kummer
non-interference, and the Step (x) upper-semi estimate.
The direct-labelled Step (x) finite-divisor route now also has a
source-derived Hodge/\(\SHE/\IPL\)/hull form.  Instead of taking the older
route-alignment record, a free square-weight profile, and a separate theta-root
source, this boundary projects the route alignment and canonical square-weight
profile from the source-derived bridge and reads the theta-root package from the
source Hodge--Arakelov side of the finite Hodge/\(\SHE\) transport.  It still
constructs the finite-divisor packet-local source before entering the exact
vertical-\(IQ\) target route.
The source-calibrated vertical-\(IQ\) route now has this projection form as
well: the log-Kummer packet source-calibration remains explicit, while the
route alignment, canonical square-weight profile, and theta-root package are
obtained from the source-derived bridge before the theta-root realified Step (x)
source is constructed.
The earlier realified-entry vertical-\(IQ\) audit endpoint has also been given
the same source-derived projection boundary.  Its public theorem still takes
the realified Step (x) source and the exact vertical-\(IQ\) target as inputs,
because those are the objects whose target-side \(FMOD\) and packet-local audit
facts are being reported, but the Hodge/\(\SHE/\IPL\)/hull alignment and
canonical square-weight profile are now read from the source-derived bridge
rather than supplied independently.
The theta-root packet-local entry route has the same source-derived form.  The
entry membership, Kummer/forgetting compatibilities, packet-local
source/mono-analytic equalities, and the two \((\Ind3)\) real equalities remain
visible Step (x) inputs, while the theta-root source, canonical square-weight
profile, and Hodge/\(\SHE/\IPL\)/hull route alignment are projected from the
source-derived bridge.
The ordered-real-line packet-local variant now factors through this same
source-derived entry route: the ordered alignment supplies the packet-source and
theta-target \((\Ind3)\) equalities, while the bridge supplies the route
alignment, canonical profile, and theta-root source.
The constant-\(ZMod_l\) packet-normalized variant has the same projection
boundary.  The packet route still supplies the theta-average normalization after
the theta-source guard is applied, and the ordered alignment still supplies the
\((\Ind3)\) real equalities, but the Hodge/\(\SHE/\IPL\)/hull alignment,
canonical profile, and theta-root source are projected from the source-derived
bridge.
The upper-semi \(ZMod_l\) entry specialization now follows this same
source-derived route: the upper-semi source packages the chosen
nonarchimedean entry together with its membership proof, and the bridge supplies
the route alignment, canonical profile, and theta-root source.
The source-calibrated \(ZMod_l\) route has also been projected through the
source-derived bridge.  The packet/source calibration object remains the Step
(x) input, but the Hodge/\(\SHE/\IPL\)/hull alignment, canonical profile, and
theta-root source are no longer separate public arguments.
The labelled-average refinement of this source-calibrated route has the same
projection boundary.  The finite \(ZMod_l\) labelled procession average and its
packet-normalized comparison remain visible Step (x) data, while the route
alignment, canonical profile, and theta-root source are supplied by the
source-derived bridge.
The source-aligned labelled-average route has also been given this bridge
projection.  Its packet-local source-alignment object remains the Step (x)
input, while the source-derived bridge supplies the Hodge/\(\SHE/\IPL\)/hull
alignment, canonical profile, and theta-root source.
The finite-source labelled-average route now follows the same pattern.  The
finite divisor packet source still supplies the packet-local source alignment,
while the source-derived bridge supplies the route alignment, canonical profile,
and theta-root source before entering the source-aligned labelled-average
boundary.
The finite-divisor labelled-average compatibility route now has the same
projection form.  Its divisor/Frobenioid packet data is still bundled into the
finite Step (x) source object, while the source-derived bridge supplies the
route alignment, canonical profile, and theta-root source.
The theta-labelled source-aligned variant now has the same bridge boundary.
The labelled capsule average alignment still derives the theta-source average
from finite labelwise averaging, while the source-derived bridge supplies the
route alignment, canonical profile, and theta-root source.
The named source-aligned vertical-\(IQ\) route now has the same projection
boundary: the packet-local source-alignment object remains the Step (x) input,
but the route alignment, canonical square-weight profile, and theta-root package
are obtained from the source-derived Hodge/\(\SHE/\IPL\)/hull bridge.
The packet-local vertical-\(IQ\) compatibility route has the same
source-derived bridge form.  This variant keeps the packet-local
Kummer/forgetting and \((\Ind3)\) source alignments explicit, but obtains the
Hodge/\(\SHE/\IPL\)/hull alignment, canonical square-weight profile, and
theta-root source by projection from the separated source-derived bridge.
It now also has the all-in-one target-charted Hodge/\(\IPL\)/determinant
possible-image source form: the public packet-local route consumes that source
object directly and projects the source-derived bridge internally before
entering the packet-local vertical-\(IQ\) comparison.  The corresponding
no-\(C_\Theta\) packet-local endpoint is now exposed as well: it returns the
all-in-one source-derived bridge audit, the exact vertical-\(IQ\) target audit,
and the three packet-local Step (x) source equalities before the external
numeric bound is introduced.  A choice-linked variant of this no-\(C_\Theta\)
packet-local endpoint now exposes the constructed \(\IPL\) choice links at the
same boundary: for every possible output choice, the constructed link has
source equal to the bridge's input prime strip and target equal to that choice's
prime strip, before the raw signed comparison and exact vertical-\(IQ\) target
audit are consumed.  The experiment surface exposes this review target with
the suffix \texttt{choiceLinkedBoundaryEndpoint}.
The ordinary finite-divisor Step (x) route now has the same projection boundary:
the finite-divisor packet-local source is still constructed from the
divisor/Frobenioid packet data, while the Hodge/\(\SHE/\IPL\)/hull alignment,
canonical square-weight profile, and theta-root package are read from the
source-derived bridge.  This gives the experiment surface a finite-divisor
vertical-\(IQ\) theorem whose public route inputs no longer include the older
alignment/profile/theta-root triple.
At the Step (xi) boundary, the strongest public Hodge--Arakelov route can now
consume the holomorphic-hull/determinant source object directly.  This is a
review-surface improvement rather than a closure of Step (xi): the source
object still contains the holomorphic hull shadow, weighted determinant source,
tensor-power bound, bridge equality, positivity, and normalization.  The
\(\Lean{}\) source now also names this trust boundary explicitly as a
constructor-built Step (xi) boundary audit: it records the selected
possible-image q-region, the internally built Theorem 3.11 hull/determinant
constructor and obligations object, the record-canonical hull/tensor bridge
equality, the tensor-power determinant bound, q-positivity, normalization, and
the raw signed comparison in one review target.  The corresponding
canonical-one constructed-\(\IPL\) finite-divisor endpoint exposes this named
audit before entering the packet/vertical-\(IQ\) boundary.
The stronger charted Hodge-calibrated family-hull source now reduces to this
constructor-built boundary as well.  In this reduction, the possible-image
q-region is fixed by the Theorem 3.11 record, \(\theta_{\mathrm{signed}}\) is
read through the transported pre-ledger theta chart and the Hodge--Arakelov
theta-monoid degree, the tensor-power bound is derived from the
record-family-hull log-volume calibration, and the bridge datum,
q-positivity, and normalization are projected from one hull/determinant
obligations object.  This gives the constructor-built audit a stronger
source-facing predecessor rather than treating its bound and side conditions as
free fields.
The synchronized target-charted possible-image summand/family-hull source now
feeds the same constructor-built boundary through a named reduction audit.  This
adds the target-chart/source theta-monoid comparison and the finite adjusted
summand equality to the review surface before the data is forgotten to the
charted Hodge/family-hull constructor audit.
The record-hull finite-divisor endpoint can now consume the constructor-built
possible-image Step (xi) source object directly.  Thus the operation
identifiers, selected possible-image q-region, determinant source, Ob3/Ob5
compatibility, measure calibration, tensor-power bound, hull/determinant bridge
equality, q-positivity, and normalization are projected from one constructor
source before the packet-local vertical-\(IQ\) comparison is invoked.  The
experiment wrapper
\texttt{possibleImageConstructorBuiltRecordHullFiniteDivisorVerticalIQ\_cThetaDichotomy}
exposes this as the public \(C_\Theta\)-dichotomy surface.
The \(q\subseteq P_{\mathrm{rec}}\) containment now has a stronger choice-linked
source form, where \(q\subseteq P_{\mathrm{choice}}\) is supplied and
\(q\subseteq P_{\mathrm{rec}}\) is derived from the possible-image union.  This
choice-linked source also projects to the formal Step (xi-e/f/g) upper-ray
record: the q-pilot log-volume is shown to lie in the upper ray, to be bounded
by the determinant log-volume, and to have matching input/output q-pilot
readings.  A stricter exact-theta variant now replaces the free
tensor-power-bound field by the equality
\(\theta_{\mathrm{signed}}=\operatorname{NormVol}(\mathrm{Ob4Det})\), from
which \Lean{} derives the bound used by the older constructor.  The
side-conditioned exact-theta variant additionally projects q-pilot positivity
and normalization from the existing Stage 1 side-condition object, rather than
carrying these as independent Step (xi) fields.  A further
hull/det-data-backed variant projects the package bridge equality from the
existing hull/determinant source-data object and then records only the
compatibility of that stored bridge with the record-canonical Step (xi)
construction.  The exact-theta data-backed source now also has a
possible-image-native form: its q-pilot region is definitionally the chosen
Theorem 3.11 possible image, so \(q\subseteq P_{\mathrm{choice}}\) is projected
by reflexive membership before the same data-backed source is constructed.
The experiment surface exposes both this source audit endpoint and the
corresponding finite-divisor vertical-\(IQ\) \(C_\Theta\) route.  The newest
record-native bounded-family variant replaces the
loose exact tensor-power equality by the source-shaped assertion that
\(\theta_{\mathrm{signed}}\) is the log-volume of the Theorem 3.11
possible-image family hull; the normalized tensor-power equality is then
derived from the Ob5 determinant compatibility.  That variant is now wired into
the finite-divisor vertical-\(IQ\) endpoint chain through a dedicated
source-derived bridge constructor, rather than through the older backed
exact-theta source.  The same bounded-family data-backed source now has a
possible-image-native form: the q-pilot region is definitionally the selected
Theorem 3.11 possible image, while the Ob5-shaped equality
\(\theta_{\mathrm{signed}}=\operatorname{Vol}_{\log}(H_{\mathrm{fam}})\)
remains the source datum.  The constructed-\(\IPL\) finite-divisor endpoint and
the experiment surface expose this stronger family-hull route.  This route is
now visible at the source-derived bridge boundary as well: a calibrated
Hodge--Arakelov synchronization supplies the finite Hodge/\(\SHE\) transport and
theta/Hodge calibration, the constructed-\(\IPL\) source supplies the
input-prime-strip link, and the possible-image family-hull source supplies the
fixed q-region and Ob5 log-volume comparison before the finite-divisor
vertical-\(IQ\) theorem is applied.  The same possible-image family-hull route
now has an obligations-backed source form: the package hull/determinant bridge
data, q-pilot positivity, and normalization are projected from one
\texttt{IUTStage1SourceHullDetObligations} object, while the q-region remains
definitionally the chosen Theorem 3.11 possible image.  The experiment surface
exposes both the bridge audit and the calibrated finite-divisor
\(C_\Theta\)-dichotomy for this obligations-backed route.  A further
Hodge-calibrated possible-image form removes the raw
\(\theta_{\mathrm{signed}}=\operatorname{Vol}_{\log}(H_{\mathrm{fam}})\)
field from this public source: the equality is derived through the
Hodge--Arakelov theta-monoid degree carried by the same synchronization object
that constructs the finite Hodge/\(\SHE\) transport.  The bridge audit and
finite-divisor endpoint now expose this Hodge-calibrated possible-image route.
A charted variant now derives the package theta/Hodge equality through the
transported pre-ledger theta chart before entering the same possible-image
Hodge/family-hull route, and the experiment surface exposes its bridge audit
and finite-divisor \(C_\Theta\)-dichotomy endpoint.
The remaining task is to construct the underlying fields from the source-paper
holomorphic-hull and determinant operations.
The experiment surface now also exposes the record-native Step (xi)
hull/determinant corridor directly.  One endpoint presents the constructed
\(\IPL\) variant from finite Hodge/\(\SHE\) transport plus the record
possible-image union and canonical Ob4/tensor-power hull data.  A stronger
endpoint presents the history-separated, certificate-pinned \(\IPL\) variant:
finite Hodge/\(\SHE\) transport is built from the source and target
Hodge--Arakelov theta-evaluation sources and the record's history-separated
descent permission, while the \(\IPL\) boundary is the certificate link source.
The constructed-\(\IPL\) record-hull endpoint now also has a side-conditioned
form: q-pilot positivity and source normalization are projected from the shared
Stage 1 side-condition object instead of appearing as independent Step (xi)
hull/determinant fields.
The same side-conditioned record-hull endpoint now has a possible-image form:
the q-pilot region is no longer supplied as an arbitrary set with a separate
containment proof in the record possible-image union.  It is fixed to the
possible-image region of a chosen Theorem 3.11 output, and \Lean{} derives the
union containment internally.
This possible-image source now also has its own holomorphic-hull/log-volume
endpoint.  Before any Hodge/\(\SHE/\IPL\) route wrapper is used, \Lean{}
projects certification, the \(\SHE\) datum, equality with the record
possible-image union, containment in the applied holomorphic hull, the
\(\theta_{\mathrm{signed}}\) log-volume bound, q-pilot positivity,
normalization, and the raw comparison
\(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) from the single
possible-image Step (xi) source object.
The target-charted Hodge/determinant possible-image source now also has its own
holomorphic-hull/log-volume endpoint and canonical hull/tensor-power bridge
endpoint.  The first projects certification, the \(\SHE\) datum, equality with
the record possible-image union, containment in the applied holomorphic hull,
the \(\theta_{\mathrm{signed}}\) log-volume bound, and the raw comparison.  The
second identifies the package common-container hull/determinant bridge with the
record-canonical Theorem 3.11 possible-image bridge while retaining the
Hodge-calibrated \(\theta_{\mathrm{signed}}\) equality, tensor-power bound,
side conditions, and raw comparison at the Step (xi) source boundary.
The source-derived bridge itself now has a calibrated Hodge--Arakelov
synchronization constructor.  Given one calibrated source/target
Hodge--Arakelov synchronization object, a constructed Theorem 3.11 \(\IPL\)
link, and a Step (xi) holomorphic-hull/determinant source, \Lean{} constructs
both the finite Hodge/\(\SHE\) transport and the source theta/Hodge
log-volume calibration internally before entering the finite-divisor
vertical-\(IQ\) route.  The experiment surface exposes this as the
calibrated-synchronization \(\IPL\)-construction hull finite-divisor
\(C_\Theta\)-dichotomy endpoint.
The same calibrated route now has side-conditioned and possible-image
side-conditioned Step (xi) variants.  In the side-conditioned form,
q-pilot positivity and source normalization are projected from the
Step (xi) hull source; in the possible-image form, the q-pilot region is also
fixed by the chosen Theorem 3.11 possible-image output.  Thus the strongest
experiment-facing endpoint now receives one calibrated Hodge--Arakelov
synchronization object, one constructed \(\IPL\) link source, and one
possible-image side-conditioned hull/determinant source, rather than separate
Hodge/\(\SHE\) transport, source-calibration, profile, theta-root, q-region,
and side-condition witnesses.
The possible-image side-conditioned source now also has a direct bridge
constructor and experiment-facing bridge audit endpoint.  The constructor keeps
the chosen Theorem 3.11 possible-image q-region visible at the Step (xi)
boundary, then projects internally to the generic holomorphic-hull/determinant
source before assembling the calibrated Hodge/\(\SHE\), constructed-\(\IPL\),
and hull/determinant bridge used by the finite-divisor route.
This strongest possible-image route now also exposes the raw signed
Step (xi) comparison separately from the \(C_\Theta\) dichotomy.  The theorem
named \texttt{\dots qSigned\_le\_thetaSigned} on the experiment surface
constructs the source-derived Hodge/\(\SHE/\IPL\)/hull bridge from the
calibrated Hodge--Arakelov synchronization, the constructed Theorem 3.11
\(\IPL\) link, and the possible-image side-conditioned hull/determinant source,
then derives \(q_{\mathrm{Signed}}\leq \theta_{\mathrm{Signed}}\) without
assuming the later numeric bound
\(\theta_{\mathrm{Signed}}\leq C_\Theta\cdot(-q_{\mathrm{Signed}})\).  A
companion audit endpoint records that the q-pilot region is the chosen
Theorem 3.11 possible-image region, that it lies in the record possible-image
union, and that q-positivity and source normalization are projected from the
shared side-condition object.
This possible-image side-conditioned boundary now has an obligations-backed
refinement.  The new source object still fixes the q-pilot region to the chosen
Theorem 3.11 possible image, but the package hull/determinant bridge datum,
q-pilot positivity, and source normalization are projected from the shared
\texttt{IUTStage1SourceHullDetObligations} object.  The experiment surface
therefore exposes a raw Step (xi) comparison whose audit payload identifies
the package bridge with the obligations bridge datum before deriving
\(q_{\mathrm{Signed}}\leq \theta_{\mathrm{Signed}}\).
The same obligations-backed source has now been lifted through the finite-divisor
vertical-\(IQ\) \(C_\Theta\)-dichotomy endpoint.  Thus the current strongest
calibrated possible-image finite-divisor route no longer takes q-positivity,
source normalization, or the package hull/determinant bridge alignment as
separate Step (xi) fields; these are read from the shared hull/determinant
obligations object before applying the existing finite-divisor corridor.  The
later numeric input
\(\theta_{\mathrm{Signed}}\leq C_\Theta\cdot(-q_{\mathrm{Signed}})\) remains an
explicit hypothesis of the dichotomy theorem.
There is now also an \(\IPL\)-link variant of this same obligations-backed
finite-divisor endpoint.  It replaces the constructed-\(\IPL\) source, and its
certificate-equals-constructed-datum alignment, by the certificate-pinned
Theorem 3.11 \(\IPL\) link source.  This does not construct the input-prime-strip
link machinery; rather, it isolates the remaining \(\IPL\) trust boundary to the
two endpoint equalities identifying the certificate link source and target with
the input and output prime strips, while the log-volume preservation is still
read from the finite Hodge/\(\SHE\) transport.
A further Gaussian-to-Step (xi) audit starts this same comparison at the
Hodge--Arakelov theta-evaluation source itself: canonical theta-root data,
Gaussian zero/canonical/square-weight degree facts, and full-label log-volume
calibration are projected before the constructed finite \(\SHE\) transport,
constructed \(\IPL\) link, possible-image hull source, and raw
\(q_{\mathrm{Signed}}\leq \theta_{\mathrm{Signed}}\) comparison are read from the
assembled bridge.
This Gaussian audit now also has the obligations-backed possible-image form.
Its endpoint starts from the same Hodge--Arakelov theta-evaluation source and
constructed \(\IPL\) link, but the Step (xi) source object additionally records
that the package hull/determinant bridge is the datum supplied by the shared
hull/determinant obligations.  Thus the audit chain from theta-root/Gaussian
data to \(q_{\mathrm{Signed}}\leq \theta_{\mathrm{Signed}}\) now exposes the
obligation-projected hull bridge alignment at the same boundary as the raw
comparison and finite-divisor dichotomy.
The obligations-backed constructed-\(\IPL\) synchronized route now also has a
named Gaussian-to-Step (xi) audit proposition.  This packages the theta-root and
Gaussian data from the calibrated synchronization's source evaluation, the
factored finite Hodge/\(\SHE\) transport, constructed \(\IPL\) transport,
obligations-backed Step (xi) hull data, and raw signed comparison before the
later Hodge--Arakelov history-separated wrappers are applied.
The \(\IPL\)-link refinement has now been lifted to these audit layers as well.
The raw comparison endpoint
\(q_{\mathrm{Signed}}\leq \theta_{\mathrm{Signed}}\) and the Gaussian-to-Step
(xi) endpoint can both use the certificate-pinned Theorem 3.11 \(\IPL\) link
source together with the obligations-backed possible-image hull source.  Thus
the audit chain from theta-root/Gaussian data through finite Hodge/\(\SHE\)
transport to the Step (xi) comparison no longer needs the constructed-\(\IPL\)
certificate-alignment field in this variant; it still keeps the two
certificate link endpoint equalities explicit.
This synchronized certificate-pinned \(\IPL\)-link Gaussian payload now also has
a named audit proposition, parallel to the synchronized constructed-\(\IPL\)
audit but without the constructed-datum equality.  The two synchronized audit
surfaces now mark exactly where the formal route switches from a
certificate-pinned link to a constructed input-prime-strip link.
The finite-divisor \(C_\Theta\)-dichotomy route now has the same unbundled
Hodge--Arakelov source surface.  Instead of receiving a calibrated
Hodge--Arakelov synchronization record, the endpoint takes the source and target
theta-evaluation sources, the canonical-one preservation equality, the
certificate-pinned \(\IPL\) link source, the obligations-backed possible-image
hull source, and the separate theta/Hodge log-volume calibration.  The finite
Hodge/\(\SHE\) transport and source-derived Hodge/\(\SHE/\IPL\)/hull bridge are
assembled internally before the existing finite-divisor vertical-\(IQ\) theorem
is applied.  This removes one synchronization-bundle boundary from the strongest
possible-image finite-divisor route, but it does not derive the later numeric
input
\(\theta_{\mathrm{Signed}}\leq C_\Theta\cdot(-q_{\mathrm{Signed}})\).
This same possible-image route now has a source-calibrated Hodge--Arakelov
variant.  The bridge constructor and experiment-facing finite-divisor theorem
consume a calibrated Hodge--Arakelov theta-evaluation source, project the
full-label theta/Hodge log-volume calibration internally, and then construct the
finite Hodge/\(\SHE\) transport, certificate-pinned \(\IPL\) transport, and
obligations-backed possible-image hull bridge.  Thus the strongest
possible-image finite-divisor surface no longer needs a standalone
\texttt{IUTStage1SourceThetaHodgeLogVolumeCalibration} argument in this variant;
the remaining external Step (xi) inputs are still the certificate-pinned
\(\IPL\) link source, the obligations-backed possible-image hull source, the
finite divisor/log-Kummer data, and the later numeric \(C_\Theta\) bound.
The raw Step (xi) comparison has now been exposed at this same
source-calibrated boundary.  The new \(q_{\mathrm{Signed}}\leq
\theta_{\mathrm{Signed}}\) theorem and its audit endpoint start from the
calibrated Hodge--Arakelov theta-evaluation source, the target evaluation,
canonical-one preservation, the certificate-pinned \(\IPL\) link source, and the
obligations-backed possible-image hull source.  The audit records the projected
theta/Hodge full-label calibration, the selected Theorem 3.11 possible-image
q-region and containment in the record possible-image union, the obligations
hull/determinant bridge alignment, the \(\IPL\) certificate endpoint equalities,
q-positivity, and source normalization before deriving the raw signed
comparison, still without using the later \(C_\Theta\) numeric hypothesis.
This source-calibrated boundary now also has a Gaussian-to-Step (xi) audit
endpoint.  It exposes the canonical theta-root generator and full label,
zero/canonical/square-weight Gaussian degree equations, full-label calibration,
factored \(\SHE\) comparison level and coordinate equivalence, the
certificate-pinned \(\IPL\)-link log-volume preservation, possible-image hull containment and
obligations bridge alignment, q-positivity, normalization, and the same raw
signed comparison in one payload.  This is the most direct current audit chain
from the Hodge--Arakelov theta-evaluation source to
\(q_{\mathrm{Signed}}\leq\theta_{\mathrm{Signed}}\) for the finite
nonarchimedean possible-image route.
This certificate-pinned Gaussian-to-Step (xi) payload is now also promoted to a
named audit proposition, and its finite-divisor route has a no-\(C_\Theta\)
boundary endpoint returning that audit together with the finite-divisor Step
(x) packet equalities, vertical-\(IQ\) target equalities, and raw signed
comparison.  This gives a stable audit surface for the pre-construction
\(\IPL\)-link route, without asserting equality to a separately constructed
\(\IPL\) datum.
The same source-calibrated possible-image route now also has the constructed
\(\IPL\) form.  The bridge constructor, finite-divisor dichotomy, raw
comparison, q-comparison audit, and Gaussian-to-Step (xi) audit can consume an
input-prime-strip link construction source.  The construction projects the
link-source and link-target endpoint equalities internally; the remaining
certificate-facing \(\IPL\) condition at this boundary is the equality between
the pre-ledger certificate datum and the datum generated by the construction.
Thus this route removes another certificate-pinned \(\IPL\)-link assumption from
the finite nonarchimedean possible-image corridor, while still treating the
existence of the input-prime-strip construction itself as Theorem 3.11 source
data.
The constructed-\(\IPL\) Gaussian-to-Step (xi) payload is now also promoted to a
named audit proposition, so later finite-divisor endpoints can cite this
theta-root/Gaussian, history-separated Hodge/\(\SHE\), constructed \(\IPL\), and
obligations-backed hull chain without restating the full conjunction.
This named audit now also records the definitional provenance of the route
components themselves: the bridge's finite Hodge/\(\SHE\) transport is the one
constructed from the history-separated Hodge--Arakelov evaluations, its
\(\IPL\) transport is the one obtained from the Theorem 3.11 construction
source, and its hull constructor is the one induced by the possible-image
obligations-backed Step (xi) source.
The generated full-label to finite-divisor handoff has now been lowered one
more step.  The public experiment endpoint
\texttt{generatedFullLabelFiniteDivisorVerticalIQStepXUpperRayRealization\_cThetaDichotomy}
no longer accepts independent real witnesses for the q-region and theta-hull
log-volumes.  Instead, both sides supply
\texttt{IUTStage1StepXToHullUpperRayLogVolume} computations, so the signed
q-values are read from q-pilot upper-ray log-volumes and the signed theta
values are read from theta-hull log-volumes, with the determinant
log-volume equalities retained in the audit.  The remaining source payload is
therefore sharply localized.  Both sides are now constructor-backed: the
generated side uses
\texttt{GeneratedFullLabelConstructedStepXUpperRaySource}, while the finite
nonarchimedean side uses
\texttt{FiniteDivisorVerticalIQConstructedStepXUpperRaySource}.  In each case a
constructed Remark~3.9.5 hull/determinant source builds the canonical hull
approximant, and a procession-normalized Step (x) corridor turns it into an
\texttt{IUTStage1StepXToHullUpperRayLogVolume}.  The cross-package equality of
the finite and generated q-pilot and theta-hull readings is no longer a bare
upper-ray assumption: \texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedStepXUpperRaySignedGluingSource}
derives it from the two constructed upper-ray signed-value identifications and
the existing theta-class signed realization.  This has now been lowered once
more by
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedStepXUpperRayFiniteThetaClassImageLawGluingSource}:
the selected theta-class realization is derived by specializing the finite
theta-class image law at the selected nonarchimedean packet, constructing the
finite theta-pilot class from its packet coordinates, and promoting the result
to the signed gluing source.  This boundary has been lowered again by
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedStepXUpperRayLabelTransportGluingSource}:
the finite image law is projected from the source-level nonarchimedean
label-transport layer, i.e. from the procession \((\Ind_1)\) leg together with
the retained nonarchimedean \((\Ind_2)\) label-transport/source-packet audit.
The constructed Step (x) endpoint has now been lowered once more by
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedStepXUpperRayPacketLabelGluingSource}:
the completed label transport is reconstructed from packet-label geometry
before the same finite image law and \(C_\Theta\) dichotomy are derived.  The
preferred constructed boundary is now
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedStepXUpperRayRawTensorLabelGluingSource}:
same-theta-class packets supply raw midpoint/target nonarchimedean
\(\mathrm{Ism}\) tensor-label equalities and the target \(\mathrm{Ism}\)
summand-kind law; Lean reconstructs packet labels, local label transport, the
finite image law, and the final dichotomy.  The preferred constructed boundary
has now moved one layer closer to the source papers:
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedStepXUpperRayMatchedIdentifiedInd2ActionPacketGluingSource}
consumes the matched identified source-level \((\Ind_2)\) packet-action source
directly, audits that the retained action agrees with the local
nonarchimedean \(\mathrm{Ism}\) action step, then projects the identified
\((\Ind_2)\), transported packet-label, packet-label, and finite image-law
layers before applying the same \(C_\Theta\) dichotomy.  The remaining Step (x)
source lowering is now the concrete construction of this matched identified
packet-action source from Hodge-theater, log-theta-lattice, and local tensor
data.
The same audit now exposes the finite \(\SHE\) preservation facts used by that
transport: the allowed forgetting predicate is the history-separated permission
attached to the record's Hodge-theater descent bridge, and the transported
full-label log-volume equality and transported-average equality are projected
from the constructed finite Hodge/\(\SHE\) transport.
The constructed-\(\IPL\) log-volume equality is now similarly sourced: the audit
records that the route's \(\IPL\) source log-volume is the finite
Hodge/\(\SHE\) source average and that its target log-volume is the transported
target average, before using transported-average preservation to identify them.
On the Step (xi) side, the same audit now exposes the weighted tensor-power
determinant bound and the equality identifying the route hull/determinant bridge
with the record-canonical possible-image hull/tensor-power construction.
The constructed-\(\IPL\) audit also projects the induced theta-pilot hull endpoint
itself: its possible-image union is the record's theta possible-image union, this
union lies in the constructed holomorphic hull, and the resulting hull has
log-volume at most \(\theta_{\mathrm{Signed}}\).
The synchronized calibrated constructed-route audit now exposes the same Step
(xi) provenance one layer earlier: the record-canonical hull/tensor-power bridge,
the weighted tensor-power determinant bound, and the induced theta-pilot hull
endpoint are projected directly from the obligations-backed possible-image source
before the history-separated source-calibrated wrapper is introduced.
The certificate-pinned \(\IPL\)-link version of this synchronized audit now
exposes the same Step (xi) projections as well, so the pre-construction and
constructed-\(\IPL\) branches have the same visible possible-image
hull/determinant provenance before the final finite-divisor boundary is applied.
The same synchronized audit layer now also exposes the finite Hodge/\(\SHE\)
transport facts themselves: the target Hodge source is the synchronized target
evaluation, the history-separated forgetful transport is allowed, and full-label
log-volumes are preserved across the finite Hodge/\(\SHE\) transport.
Both synchronized audits now also expose the \(\SHE\)-to-\(\IPL\) log-volume
handoff directly: the finite Hodge/\(\SHE\) transported average is preserved,
the route's \(\IPL\) source log-volume is the finite Hodge/\(\SHE\) source
average, and the route's \(\IPL\) target log-volume is the transported target
average.
The same finite-divisor route now has a no-\(C_\Theta\) boundary endpoint
returning this named audit together with the finite-divisor Step (x) packet
equalities, vertical-\(IQ\) target equalities, and raw
\(q_{\mathrm{Signed}}\leq\theta_{\mathrm{Signed}}\) comparison, separating the
source-derived Step (xi)/Step (x) provenance from the later numeric estimate.
The corresponding finite-divisor \(C_\Theta\)-dichotomy endpoint now returns
this named audit proposition together with the dichotomy, keeping the external
numeric \(C_\Theta\) estimate as the only additional input at that boundary.
The experiment surface now also has synchronized finite-divisor review wrappers:
they consume the single Hodge--Arakelov synchronization object and return the
synchronized Gaussian-to-Step (xi) audit directly, together with the same raw
finite-divisor boundary or \(C_\Theta\)-dichotomy conclusion.  This makes the
finite bad-local endpoint display the route
theta-root/Gaussian \(\to\) finite Hodge/\(\SHE\) \(\to\) \(\IPL\)
\(\to\) possible-image hull before entering the later source-calibrated audit
wrapper.
The same bundled synchronized source now has the remaining-boundary ledger
\texttt{SynchronizedRemainingSourceBoundaryAudit}, exposed by the experiment
suffix \texttt{synchronizedRemainingBoundaryAudit}.  It packages the
Gaussian-to-Step (xi) audit, constructed \(\IPL\) log-volume endpoint,
possible-image hull/determinant endpoint, finite Step (x) packet equalities,
vertical-\(IQ\) target facts, and raw signed comparison as projections from
one source object.  This gives the pre-matched synchronized corridor the same
review shape as the later matched and side-conditioned exact corridors.
The certificate-pinned \(\IPL\)-link synchronized source now has the analogous
remaining-boundary ledger
\texttt{SynchronizedIPLLinkRemainingSourceBoundaryAudit}, exposed by the
experiment suffix
\texttt{synchronizedIPLLinkRemainingBoundaryAudit}.  It packages the
IPL-link Gaussian-to-Step (xi) audit, the certificate-pinned link source,
possible-image hull/determinant endpoint, finite Step (x) packet equalities,
vertical-\(IQ\) target facts, and raw signed comparison, while deliberately
leaving the construction of the \(\IPL\) datum outside this pre-construction
review surface.
For review, these strongest finite-divisor endpoints are also exposed under the
compact milestone prefix
\texttt{sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ}, with boundary and
\(C_\Theta\)-dichotomy variants carrying the
\texttt{WithConstructedRouteAudit} suffix.
These wrappers are definitionally just the constructed-route endpoints above;
their purpose is to make the current review boundary easy to locate without
renaming or hiding the longer source-calibrated audit theorem.
The compact milestone prefix now also has all-in-one route variants.  The
no-\(C_\Theta\) wrapper with suffix
\texttt{boundaryEndpointWithAllInOneRouteBridgeAudit}
consumes the target-charted Hodge/\(\IPL\)/determinant possible-image route
source directly and returns the route bridge audit together with the finite
Step (x) packet and vertical-\(IQ\) target equalities.  The corresponding
\(C_\Theta\)-boundary suffix
\texttt{cThetaDichotomyWithAllInOneRouteGaussianStepXIAudit}
returns the all-in-one Gaussian-to-Step (xi) audit before applying the same
external numeric \(C_\Theta\) estimate.  Thus the compact review surface can now
point to the stricter route object that packages the Hodge--Arakelov
synchronization, finite Hodge/\(\SHE\) transport, constructed \(\IPL\) handoff,
and record-native possible-image hull/determinant payload in one source-facing
input.
The same conditional boundary now also has the stronger compact suffix
\texttt{cThetaDichotomyWithAllInOneRouteBridgeAudit}.  This endpoint returns
the full route bridge audit next to the dichotomy, rather than only the
Gaussian-to-Step (xi) subaudit, while still keeping the numeric
\(C_\Theta\)-upper estimate as an explicit external hypothesis.  The
target-charted experiment surface has parallel suffixes
\texttt{routeBridgeAuditEndpoint} and
\texttt{matchedRouteBridgeAuditEndpoint}; the latter records the
theta-monoid-matched route bridge audit beside the same conditional
\(C_\Theta\) conclusion.
The all-in-one route bridge audit now also carries the named
\texttt{TargetChartedHodgeSHEIPLConstructionAudit} as a field, and the compact
experiment suffix
\texttt{allInOneRouteHodgeSHEIPLAudit} exposes it directly.  This means the
milestone-facing route bridge reports the theta-root/Gaussian evaluation,
factored \(\SHE\) preservation, finite Hodge/\(\SHE\) transport, constructed
\(\IPL\) log-volume transport, and finite-transport log-volume provenance
before the Step (xi) hull/determinant payload or finite Step (x) boundary is
used.
At the bridge-constructor level, the calibrated Hodge--Arakelov constructed
\(\IPL\) bridge can now consume the constructor-built possible-image
Step (xi) hull/determinant source directly.  The core constructor
\texttt{ofCalibratedHodgeSynchronizationT11IPLConstructionAndPossibleImage}\\
\texttt{ConstructorBuiltHullSources} exposes, through the experiment suffix
\texttt{calibratedSynchronizationIPLConstructionPossibleImage}\\
\texttt{ConstructorBuiltHull\_bridgeEndpoint}, the constructed \(\IPL\) datum,
finite Hodge/\(\SHE\) synchronization, constructor-built Step (xi) source
endpoint, record-canonical Step (xi) audit, compact boundary audit, and
remaining-payload ledger from the same source object.
The same constructor-built Step (xi) source now separates its Ob1/Ob2
holomorphic-hull absorption passage as
\texttt{ConstructorBuiltOb1Ob2HullAbsorptionAudit}, exposed by the experiment
suffix \texttt{possibleImageConstructorBuiltHullSource\_ob1Ob2HullAbsorptionAudit}
and carried by the bridge endpoint.  This audit records that the selected
q-pilot region is a Theorem~3.11 possible image, lies in the record
possible-image union, and is absorbed by the canonical holomorphic hull before
determinant/tensor-power data enters.
The constructor-built Step (xi) source now also separates its Ob3/Ob4
determinant/tensor-power passage as
\texttt{ConstructorBuiltOb3Ob4DeterminantAudit}, exposed by the experiment
suffix \texttt{possibleImageConstructorBuiltHullSource\_ob3Ob4DeterminantAudit}
and carried by this bridge endpoint.  The audit records weighted determinant
summation, determinant normalization, hull-log-volume compatibility, the naive
Frobenius tensor-power bound, and the determinant upper-ray comparison before
the remaining-payload ledger adds q-choice, record-canonical bridge, positivity,
and normalization fields.
The same boundary now separates the Ob3/Ob5 determinant-compatibility chain as
\texttt{ConstructorBuiltOb3Ob5DeterminantCompatibilityAudit}, exposed by the
experiment suffix
\texttt{possibleImageConstructorBuiltHullSource\_ob3Ob5DeterminantCompatibilityAudit}.
This audit derives the canonical hull-log-volume equality with the determinant
log-volume by composing hull-log-volume compatibility with the normalized
weighted determinant and the Ob3/Ob4 determinant normalization theorem, so this
equality is no longer presented as an independent remaining-payload input.
The theta-monoid-matched all-in-one route now has the same stronger no-\(C_\Theta\)
boundary surface with suffix
\texttt{boundaryEndpointWithMatchedRouteBridgeAudit}.  Its first component
keeps the matched Gaussian audit together with the projected all-in-one route
bridge audit, so the matched finite-divisor vertical-\(IQ\) endpoint no longer
drops the Hodge/\(\SHE/\IPL\) construction payload when it records that
canonical one-label preservation was reconstructed from target/source
theta-monoid degree equality.
The all-in-one Gaussian-to-Step (xi) audit has also been strengthened at the
Step (xi) boundary.  Its public experiment endpoint with suffix
\texttt{gaussianToStepXIHullDetAuditEndpoint} now projects the record
possible-image union, containment in the constructed holomorphic hull, the
holomorphic-hull log-volume bound, the family-hull/determinant and
tensor-power equalities, and the record-canonical hull/tensor-power bridge
equality from the same route audit.  Thus the finite-divisor wrappers that
return this audit now carry more than the final raw comparison: they expose the
holomorphic-hull/determinant provenance used to obtain it.
The same all-in-one route now also exposes the narrower determinant-source
boundary via
\path|targetChartedHodgeIPLDeterminantPossibleImageRoute_determinantSourceBoundaryAuditEndpoint|.
This audit separates the two determinant payload fields still supplied at that
boundary---the package measure calibration and the Hodge theta/summand
equality---from the record-native family-hull facts that \Lean{} derives:
the record possible-image union, the family-hull/determinant equality, the
family-union bound by the hull, tensor-power normalization, and the resulting
tensor-power bound against \(\theta_{\mathrm{Signed}}\).
This has now been tightened by the endpoint
\path|targetChartedHodgeIPLDeterminantPossibleImageRoute_calibratedDeterminantSourceEndpoint|:
the same route determinant payload is first viewed through a calibration-backed
source object, so the Hodge theta/summand equality is projected from the
target-charted summand calibration rather than exposed as a raw determinant
field.  The package measure identification remains the explicit determinant
measure boundary.
The stricter determinant payload has also been pushed through the possible-image
Step (xi) source boundary.  The endpoint
\path|targetChartedHodgeIPLDeterminantPossibleImageRoute_calibratedPossibleImageSourceEndpoint|
shows that the chosen q-region, record possible-image union, target-charted
summand calibration, family-hull determinant facts, theta/family-hull equality,
bridge alignment, and raw comparison are all projected from a
calibration-backed possible-image source object.
There is now also an all-in-one route object whose Step (xi) field is this
calibration-backed possible-image source:
\path|targetChartedHodgeIPLCalibratedPossibleImageRoute_sourceEndpoint|
returns the projected Gaussian-to-Step (xi) audit together with the route's
\(\IPL\) handoff, calibrated q-region, determinant measure calibration,
target-charted summand facts, bridge alignment, and raw comparison.
The finite-divisor boundary can now consume this calibrated route object
directly as well.  The compact suffixes
\texttt{boundaryEndpointWithCalibratedAllInOneRouteGaussianStepXIAudit} and
\texttt{cThetaDichotomyWithCalibratedAllInOneRouteGaussianStepXIAudit}
project to the existing finite Step (x) machinery only after the public route
input has been tightened to the calibration-backed possible-image source.
The calibrated route now also has matching review surfaces with
\texttt{CalibratedGaussianStepXIAudit} suffixes; these return the calibrated
possible-image audit directly, rather than only the projected audit for the
older determinant possible-image route shape.
The same boundary has now been refined once more by a measure-calibrated route
object.  The new source
\path|IUTStage1MeasureCalibratedRecordBoundedFamilyHullDetLogVolumeSource|
packages the record-native family-hull determinant source together with the
identification of the package ledger measure with the induced hull log-volume
measure.  The all-in-one
\path|IUTStage1TargetChartedHodgeIPLMeasureCalibratedPossibleImageRouteSource|
threads this measured family-hull payload through the calibrated possible-image
Step (xi) source, so the determinant payload no longer exposes the package
measure equality as a direct field.  The experiment surface now exposes
\path|targetChartedHodgeIPLMeasureCalibratedPossibleImageRoute_toMeasureCalibratedGaussianStepXIAudit|
and a matching finite-divisor boundary wrapper returning the
measure-calibrated Gaussian-to-Step (xi) audit; both project to the older
calibrated route only internally.
The measure-calibrated boundary now has a constructor-backed refinement as
well.  The new constructor-backed possible-image source constructs its
hull/determinant obligations via
\path|ofRecordCanonicalHullTensorPowerOfQSubsetUnion|, using the
record-canonical possible-image hull/tensor-power bridge.  The matching
all-in-one route therefore no longer carries an arbitrary possible-image
hull/determinant obligations object at this boundary; it projects to the
measure-calibrated route only after the constructor has produced those
obligations.  The experiment surface exposes this as a constructor-backed
Gaussian-to-Step (xi) audit, a matching no-\(C_\Theta\) finite-divisor boundary
wrapper, and now also a matching finite-divisor \(C_\Theta\) dichotomy wrapper.
Thus the final dichotomy surface can display the constructor-backed Step (xi)
hull/determinant route before applying the still-external numeric
\(C_\Theta\) estimate.
The same calibration-backed route has now been pushed into the strongest
bundled finite exact vertical-\(IQ\) source as well.  The experiment-surface
calibrated finite-exact wrappers, with suffixes
\texttt{boundaryEndpointWithCalibratedRouteAudit} and
\texttt{cThetaDichotomyWithGaussianStepXIAudit}, consume one calibrated
route/exact Step (x) package and project to the older exact finite-route
theorem only internally.  Thus the exact vertical-\(IQ\) review boundary now
displays the calibration-backed possible-image payload before the final
external numeric \(C_\Theta\) estimate is supplied.
The constructor-backed refinement has now been pushed through this bundled
finite exact vertical-\(IQ\) boundary too.  Its exact route package exposes a
constructor-backed Gaussian-to-Step (xi) audit, a source-derived corridor audit
linking the constructor-produced hull/determinant data to the exact Step (x)
calibration, and a matching \(C_\Theta\) dichotomy wrapper.  The final
dichotomy can therefore be reviewed from a single package whose Step (xi)
payload is constructor-backed before the exact vertical-\(IQ\) projection and
the still-external numeric estimate are applied.
The adjusted Ob3/Ob4 version of this exact route is now explicit as well.  The
source
\[
\begin{array}{l}
\texttt{IUTStage1TargetChartedHodgeIPLConstructorBacked}\\
\quad\texttt{MeasureCalibratedAdjustedPossibleImage}\\
\quad\texttt{FiniteExactVerticalIQRouteSource}
\end{array}
\]
keeps the adjusted-summand Step (xi) equalities
\[
  \mathrm{familyHullLogVolume}
    = \mathrm{adjustedSummandLogVolume}
    = \mathrm{determinantLogVolume}
\]
visible at the same exact vertical-\(IQ\) boundary.  Its public experiment
wrappers expose the adjusted Gaussian audit, the source-derived corridor
endpoint, and the corresponding \(C_\Theta\)-dichotomy endpoint; projection to
the older constructor-backed exact route is used only to reuse the established
Step (x) vertical-\(IQ\) endpoint.
The same adjusted exact route now has a theta-monoid-matched Hodge/\(\IPL\)
version.  The source
\[
\begin{array}{l}
\texttt{IUTStage1TargetChartedThetaMonoidMatchedHodgeIPL}\\
\quad\texttt{ConstructionConstructorBackedMeasureCalibrated}\\
\quad\texttt{AdjustedPossibleImageFiniteExactVerticalIQSource}
\end{array}
\]
stores the matched Hodge/\(\IPL\) construction source and the adjusted
constructor-backed Step (xi) source as public fields, then projects to the
ordinary adjusted exact source only internally.  Its audit keeps the
target/source theta-monoid degree equality, the adjusted exact-theta Step (xi)
audit, and the exact vertical-\(IQ\) facts together before the still-external
numeric \(C_\Theta\) estimate is supplied.
This matched adjusted source now also projects into the obligations-backed
record-canonical corridor.  The audit
\[
\begin{array}{l}
\texttt{MatchedAdjustedObligationsCorridorAudit}
\end{array}
\]
retains the matched adjusted Gaussian/exact audit and the adjusted exact-theta
Step (xi) audit, then adds the projected matched obligations-backed
record-canonical Gaussian corridor and the constructor-built finite-divisor
route audit.  Thus the strongest matched obligations boundary no longer loses
the Ob3/Ob4 adjusted-summand provenance when it reviews the downstream
finite-divisor route.
This exact boundary now also has an assembled-source variant.  Instead of
storing the all-in-one constructor-backed route as a field, the package stores
the target-charted Hodge/\(\IPL\) construction source and the
constructor-backed possible-image source separately, then builds the route only
as an internal projection.  The review surface therefore shows the constructed
\(\IPL\) datum, the constructor-produced Step (xi) obligations, the raw
comparison, and the exact vertical-\(IQ\) calibration in one source-derived
corridor audit before the \(C_\Theta\) estimate is supplied.
The exact boundary has now been tightened once more to a record-canonical
constructor source.  This source does not store the packaged
constructor-backed possible-image object; it stores the measured determinant
payload, q-choice, hull/determinant operation identifiers, record-canonical
bridge equality, q-positivity, and normalization inputs from which the
Theorem 3.11 hull/determinant constructor produces the Step (xi) source.  Its
experiment wrapper displays these constructor inputs together with the
constructed \(\IPL\) datum and exact vertical-\(IQ\) calibration before the
external numeric \(C_\Theta\) estimate is used.
There is now an intermediate side-condition-backed form of the same
record-canonical exact boundary.  The side-conditioned source in
\path|IUTStage1FrobenioidShift| keeps the measured determinant payload,
q-choice, operation identifiers, and record-canonical bridge equality explicit,
but replaces the separate q-positivity and source-normalization fields by one
\path|IUTStage1SourceSideConditions| object.  Its experiment-surface wrappers
display the same corridor and \(C_\Theta\)-dichotomy payload as the direct
record-canonical constructor route, while making the side-condition source a
single audited dependency before projection to the older endpoint.
An obligations-backed version of this record-canonical exact boundary now
projects q-positivity, source normalization, and the package bridge-data
alignment from a single \texttt{IUTStage1SourceHullDetObligations} object.  It
still exposes the measured determinant payload, q-choice, and record-canonical
hull/tensor bridge equality, but the final Step (xi) constructor no longer
takes q-positivity and normalization as independent fields at this exact
boundary.
The finite-divisor \(C_\Theta\)-route now has the same adjusted Ob3/Ob5 source
form.  The new source declaration with suffix
\texttt{RecordOb3Ob5AdjustedPossibleImageFiniteDivisorVerticalIQ} starts from
the record-canonical adjusted determinant log-volume source, derives the Ob4
tensor-power bound from the exact theta/family-hull equality, and projects the
bridge equality, q-positivity, and normalization from the ambient hull/determinant
obligations object before entering the constructor-built possible-image Step
(xi) route.  The experiment surface exposes this as
\texttt{recordOb3Ob5AdjustedPossibleImageFiniteDivisorVerticalIQ\_cThetaDichotomy}.
This route now has a constructed Remark~3.9.5 source object at the
finite-divisor boundary.  The source
\texttt{IUTStage1Remark395ConstructedHullDeterminantFiniteDivisorVerticalIQSource}
bundles the measured adjusted Ob3/Ob5 determinant source, the exact
\(\theta_{\mathrm{signed}}\)-as-family-hull equality, and the
record-canonical obligations synchronization.  Its endpoint proves that the
package measure calibration, derived Ob4 tensor-power bound, obligations
bridge equality, q-positivity, and source normalization are all projected from
this single source object.  The new finite-divisor theorem with suffix
\[
\begin{array}{l}
\texttt{remark395ConstructedOb3Ob5Adjusted}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}
\end{array}
\]
and experiment wrapper
\[
\begin{array}{l}
\texttt{remark395ConstructedOb3Ob5Adjusted}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ\_cThetaDichotomy}
\end{array}
\]
therefore remove the separate public measure-calibration and bridge
synchronization arguments from this adjusted Ob3/Ob5 route.
The constructed finite-divisor source now also projects the actual constructed
Remark~3.9.5 Step~(xi) object, rather than only the downstream
constructor-built possible-image wrapper.  The projection
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructedHullDeterminantFiniteDivisor}\\
\quad\texttt{VerticalIQSource.toPossibleImageConstructedHolomorphicHull}\\
\quad\texttt{DeterminantSource}
\end{array}
\]
fixes the q-region to the selected Theorem~3.11 possible image, derives its
containment in the record possible-image union, exposes the package
hull/determinant bridge equality, and records the two-step comparison
\[
  \mu_{\log}(qRegion)\le \det_{\mathrm{norm}}\le\theta_{\mathrm{signed}}.
\]
The experiment theorem
\texttt{remark395ConstructedHullDeterminantFiniteDivisorVerticalIQSource\_possibleImageConstructedStepXIAudit}
is the review-facing form of this Step~(xi) projection.
At the same finite-divisor boundary, the source now also carries the
Ob1--Ob5 bridge audit
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructedHullDeterminantFiniteDivisor}\\
\quad\texttt{VerticalIQSource.ConstructedFiniteDivisorOb1ToOb5BridgeAudit}.
\end{array}
\]
It is projected through the constructor-built possible-image Step~(xi) source
and records q-region absorption into the holomorphic hull, Ob3/Ob5
hull-log-volume-to-determinant compatibility, the record-canonical bridge
equality, and \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\).  The
experiment surface exposes it as
\texttt{remark395ConstructedHullDeterminantFiniteDivisorVerticalIQSource\_ob1ToOb5BridgeAudit}.
The same finite-divisor source now also has the Ob5-refined quotient bridge
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructedHullDeterminantFiniteDivisor}\\
\quad\texttt{VerticalIQSource.ConstructedFiniteDivisorOb1ToOb5QuotientBridgeAudit}.
\end{array}
\]
For a comparison possible-image choice, and nonemptiness witnesses for the
selected q-choice image and the comparison image, Lean projects the
constructor-built bounded-family quotient theorem to this boundary.  The audit
records containment of both possible images in the family hull, collapse of
both quotient images to the distinguished upper-semi quotient point, equality
of the quotient images, the quotient-collapse iff statement, and the same
source-derived chain
\[
  \mu_{\log}(q\mathrm{Region})\leq
  \det_{\log}^{\mathrm{norm}}\leq \theta_{\mathrm{signed}}.
\]
The experiment surface exposes this as
\texttt{remark395ConstructedHullDeterminantFiniteDivisorVerticalIQSource\_ob1ToOb5QuotientBridgeAudit}.
This witness burden has been reduced at the same finite-divisor boundary:
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructedHullDeterminantFiniteDivisor}\\
\quad\texttt{VerticalIQSource.qChoiceRegion\_nonempty\_of\_qPilotRegion\_nonempty}
\end{array}
\]
derives nonemptiness of the selected Theorem~3.11 q-choice possible image from
nonemptiness of the constructed q-pilot region, using the source equality
\(q\mathrm{Region}=P_{q\mathrm{Choice}}\).  Consequently
\texttt{remark395ConstructedHullDeterminantFiniteDivisorVerticalIQSource\_ob1ToOb5QuotientBridgeAuditOfQPilotRegionNonempty}
requires only q-pilot-region nonemptiness plus a nonempty comparison possible
image, and the canonical-qChoice specialization
\texttt{remark395ConstructedHullDeterminantFiniteDivisorVerticalIQSource\_ob1ToOb5QuotientBridgeAuditAtQChoiceOfQPilotRegionNonempty}
uses a single q-pilot-region nonemptiness witness for both sides of the Ob5
quotient collapse.
The same route now has a constructor-backed source form.  The source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQSource}
\end{array}
\]
does not take an ambient hull/determinant obligations object.  Instead it
carries the common-container equality with the record-canonical hull/tensor
bridge, q-pilot positivity, and source normalization; Lean then constructs
\texttt{IUTStage1SourceHullDetObligations} from the Theorem~3.11
hull/determinant constructor.  The experiment wrapper
\[
\begin{array}{l}
\texttt{remark395ConstructorBackedConstructedOb3Ob5Adjusted}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ\_cThetaDichotomy}
\end{array}
\]
is therefore the current strongest adjusted Ob3/Ob5 finite-divisor route: it
keeps the final numeric \(C_\Theta\) estimate explicit, but no longer accepts
an arbitrary obligations object together with a separate record-canonical
bridge-data equality.
This obligations-backed record-canonical exact corridor now also has a named
audit proposition.  The proposition packages the constructed \(\IPL\) datum,
the record-canonical Step (xi) bridge equality, the obligations-derived
q-positivity and normalization witnesses, the raw \(q_{\mathrm{signed}}\le
\theta_{\mathrm{signed}}\) comparison, and exact vertical-\(IQ\) Frobenioid
precision.  The experiment surface exposes this compact audit object directly,
so dependency review can target the strongest constructor-obligations route
without replaying the long corridor conjunction.
The same exact corridor now has a combined Gaussian/exact audit.  This audit
joins the constructor-backed Gaussian-to-Step (xi) route audit with the
obligations-backed exact vertical-\(IQ\) corridor audit for the same source
package, and the \(C_\Theta\)-dichotomy wrapper now has a suffix returning this
combined audit as its first conjunct.  Thus the public endpoint can display the
theta-root/Hodge--Arakelov Gaussian data, factored \(\SHE\) preservation,
constructed \(\IPL\) transport, record-canonical Step (xi) constructor,
obligations-derived side conditions, raw comparison, and exact vertical-\(IQ\)
precision through one named source object before the still-external numeric
\(C_\Theta\) estimate is applied.
The Hodge/\(\SHE\)/\(\IPL\) portion of this combined audit is now itself a
named pre-Step (xi) audit on the target-charted Hodge--Arakelov \(\IPL\)
construction source.  It packages the theta-root Gaussian evaluation, factored
\(\SHE\) preservation, finite Hodge/\(\SHE\) transport, constructed
input-prime-strip \(\IPL\) transport, and finite-transport log-volume
provenance before any record-canonical hull/determinant constructor is invoked.
Consequently the strongest Gaussian/exact corridor points back to the same
\texttt{hodgeIPLSource} for both the Hodge/\(\SHE\)/\(\IPL\) construction facts
and the later Step (xi) route audit.
The Hodge synchronization boundary has also been sharpened.  The new
theta-monoid-matched synchronization source replaces the public canonical
one-label preservation proof by an equality of source and target
Hodge--Arakelov theta-monoid degrees.  Lean then reconstructs canonical-one
preservation from the finite Gaussian evaluation theorem that the canonical
\(1\)-label degree equals the theta-monoid degree on both sides.  The compact
finite-divisor wrappers with suffixes
\texttt{WithThetaMonoidMatchedRouteAudit} expose this route before the
external numeric \(C_\Theta\) estimate is used.
This matching has now been pushed one layer further into the target-charted
Hodge/\(\IPL\) construction source.  The matched construction source stores
the theta-monoid degree equality and the constructed Theorem 3.11
input-prime-strip link, projects to the ordinary Hodge/\(\IPL\) source by
reconstructing canonical-one preservation internally, and then feeds the same
determinant possible-image Step (xi) payload.  The experiment surface exposes
the matched source endpoint, its Hodge/\(\SHE\)/\(\IPL\) audit projection, and
a finite-divisor \(C_\Theta\)-dichotomy wrapper.  Thus the public determinant
possible-image corridor can now consume a theta-degree-matched Hodge/\(\IPL\)
source directly, while the final numerical \(C_\Theta\) bound remains an
explicit external input.
The matched Hodge/\(\IPL\) source has also been threaded through the
all-in-one target-charted route source.  The new route object stores the
theta-degree-matched Hodge/\(\IPL\) construction source and the determinant
possible-image Step (xi) payload, then projects to the older all-in-one route
only internally.  Its matched Gaussian-to-Step (xi) audit contains the
projected Hodge/\(\SHE\)/\(\IPL\)/hull chain together with the explicit
target/source theta-monoid degree match and the matched Hodge/\(\SHE\)/\(\IPL\)
construction audit.  The experiment surface now exposes this matched route
endpoint and a finite-divisor \(C_\Theta\)-dichotomy wrapper returning the
matched audit before applying the still-external numerical estimate.
There is now also a no-\(C_\Theta\) finite-divisor boundary for this matched
all-in-one route, exposed by the experiment suffix
\texttt{boundaryEndpointWithMatchedGaussianStepXIAudit}.  It returns the same
matched Gaussian-to-Step (xi) audit together with the finite-divisor packet
equalities, vertical-\(IQ\) target equalities, and raw
\(q_{\mathrm{signed}}\le \theta_{\mathrm{signed}}\) comparison before any
numeric \(C_\Theta\) estimate is introduced.
The matched route has now been carried into the assembled constructor-backed
finite exact vertical-\(IQ\) source.  This source stores the theta-degree-matched
Hodge/\(\IPL\) construction source, the constructor-backed Step (xi)
possible-image source, and the exact Step (x) vertical-\(IQ\) package as
separate public fields; the ordinary assembled constructor-backed exact source
is only a projection.  Its matched Gaussian/exact audit combines the matched
all-in-one Gaussian-to-Step (xi) route audit, the constructor-backed
hull/determinant audit, the exact vertical-\(IQ\) target calibration, and the
raw comparison before the external numerical \(C_\Theta\) estimate is supplied.
The same theta-degree-matched Hodge/\(\IPL\) input has now also reached the
record-canonical constructor source.  The matched record-canonical package
stores the measured Hodge determinant source, the possible-image q-choice, the
hull/tensor/determinant operations, the record-canonical bridge equality, the
q-positivity and normalization side conditions, and the exact Step (x)
vertical-\(IQ\) data, while the ordinary record-canonical source is recovered
only by projection.  Its public audit records the matched assembled
Gaussian/exact route together with the record-canonical hull/tensor bridge, the
raw \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison, and exact
Frobenioid precision.  The numerical \(C_\Theta\) bound remains an explicit
external input at this boundary.
The matched record-canonical package has now been lifted through the
obligations-backed record-canonical exact corridor as well.  The new source
keeps the theta-degree-matched Hodge/\(\IPL\) construction public while
projecting q-positivity, normalization, and bridge-data alignment from a single
Step (xi) obligations object.  Its review audit combines the matched
record-canonical constructor audit with the existing obligations-backed
Gaussian/exact corridor audit, so the strongest current endpoint records both
the theta-monoid provenance of canonical-one preservation and the
obligations-backed hull/determinant side conditions before the external
numeric \(C_\Theta\) estimate is applied.
The same obligations-backed exact corridor now also exposes a named pre-exact
Step (xi) hull/determinant audit.  This audit records the chosen Theorem 3.11
possible-image q-region, its containment in the record possible-image union, the
measured family-hull/determinant provenance, the tensor-power bound, the
record-canonical hull/tensor bridge, the obligations-derived q-positivity and
normalization witnesses, and the raw \(q_{\mathrm{signed}}\le
\theta_{\mathrm{signed}}\) comparison.  The combined Gaussian/exact audit now
contains this Step (xi) hull/determinant audit as a separate field, so the
route can be reviewed between the Hodge/\(\SHE\)/\(\IPL\) construction and the
exact vertical-\(IQ\) fields without unpacking the final \(C_\Theta\)
dichotomy theorem.
The obligations-backed record-canonical source also now has a no-\(C_\Theta\)
raw-comparison endpoint at this same level.  The endpoint returns the combined
Gaussian/exact audit, the exact vertical-\(IQ\) target-calibration and
Frobenioid-precision facts, the finite Step (x) packet/product equalities, the
q-pilot log-Kummer non-interference witness, the upper-semi inequality, and the
raw \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\) comparison, all before
the external numeric \(C_\Theta\) estimate is supplied.  The experiment surface
now exposes this no-\(C_\Theta\) target by the milestone-facing suffix
\texttt{boundaryEndpointWithThetaMonoidMatchedRecordCanonicalGaussianExactCorridorAudit}.
Thus the newest review target separates the source-derived
Hodge/\(\SHE\)/\(\IPL\)/Step (xi) and exact Step (x) corridor from the final
ordered-real dichotomy.
At the same source level, the code now exposes a remaining-boundary ledger
\texttt{ObligationsRecordCanonicalConstructorRemainingSourceBoundaryAudit}.
This ledger does not add a new comparison theorem.  Instead it records, in one
kernel-checked proposition, the constructed \(\IPL\) link and
Hodge/\(\SHE/\APT\) transport audit, the
determinant source-boundary audit, the pre-exact Step (xi) hull/determinant
audit, the exact corridor audit, the finite-divisor packet equalities, and the
vertical-\(IQ\)/log-Kummer boundary facts.  Its purpose is to make the next
paper-facing obligation precise: construct the still-public operation
identifiers, q-choice, measure-calibrated determinant source, hull/determinant
obligations object, upper-semi entry, and exact vertical-\(IQ\) source from
IUT I--III data rather than supplying them as fields of the strongest corridor
source.
The same obligations-backed record-canonical source now also projects directly
to the constructor-backed, measure-calibrated possible-image Step (xi) source.
The new audit
\texttt{ObligationsRecordCanonicalConstructorBackedStepXISourceAudit} records
the constructor-backed Step (xi) endpoint, its measure-calibrated
possible-image projection, and the assembled finite exact source endpoint.  The
combined Gaussian/exact audit and the remaining-boundary ledger include this
constructor-backed Step (xi) audit, so the strongest exact corridor can now be
reviewed either as the expanded record-canonical field list or as the
source-facing Step (xi) object built from that list.
The constructor-backed Step (xi) source itself now has a named audit,
\texttt{ConstructorBackedStepXIHullDetAudit}.  It records the chosen
Theorem 3.11 possible-image q-region, the measure-calibrated determinant
source, the constructed hull/determinant obligations object, the
record-canonical hull/tensor bridge, q-positivity, normalization, and the raw
comparison.  The assembled exact source now also has
\texttt{AssembledConstructorBackedRemainingSourceBoundaryAudit}, exposed on the
experiment surface with suffix \texttt{remainingBoundaryAudit}.
This is the direct review target corresponding to the Step (xi) passage in
\IUT{} III from the Theorem 3.11 multiradial output through holomorphic hulls,
determinants/tensor powers, and log-volume, before the remaining finite
Step (x) and vertical-\(IQ\) inputs are discharged.
There is now also a side-conditioned constructor-backed Step (xi) source.  Its
experiment endpoint, with suffix
\texttt{SideConditionedConstructorBackedMeasureCalibratedPossibleImage\_sourceEndpoint},
projects q-pilot positivity and source normalization from one
\texttt{IUTStage1SourceSideConditions} object before building the
constructor-backed hull/determinant source.  This removes two more flat public
propositions at the low-level Step (xi) constructor boundary.
The same low-level source now has the named audit
\texttt{SideConditionedConstructorBackedStepXIHullDetAudit}.  It packages the
selected possible-image q-region, the constructor-backed hull/determinant
provenance, the side-condition-derived q-positivity and normalization, and the
raw signed comparison as one reusable Step (xi) proposition.  The strongest
matched side-conditioned exact corridor now consumes this audit directly before
projecting to the constructor-backed and obligations-backed exact route.
The theta-monoid-matched obligations-backed record-canonical corridor now has
the same explicit source-facing exposure.  Its new audit
\texttt{MatchedObligationsRecordCanonicalConstructorBackedStepXISourceAudit}
records the matched theta-degree equality, the projected constructor-backed
Step (xi) source audit, and the matched assembled Gaussian/exact route audit.
The matched Gaussian/exact corridor includes this audit as a separate field,
and the experiment surface exposes it directly, so the matched route can be
reviewed at the constructor-backed Step (xi) boundary without first unfolding
the ordinary projection.
It now also has the matched remaining-boundary ledger
\texttt{MatchedObligationsRecordCanonicalConstructorRemainingSourceBoundaryAudit},
exposed by
\path|sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ_thetaMonoidMatchedRecordCanonicalRemainingBoundaryAudit|.
This ledger keeps the matched Gaussian/exact audit and matched
constructor-backed Step (xi) audit next to the ordinary projected ledger of
still-public source-paper inputs.  The point is not to close those inputs, but
to make the strongest theta-monoid-matched corridor display the exact remaining
operation, q-choice, determinant, hull/determinant-obligation,
upper-semi, and exact vertical-\(IQ\) construction boundary.
Finally, this strongest source package now has a milestone-facing
\(C_\Theta\)-dichotomy alias using the existing source-derived finite-divisor
endpoint prefix and the suffix
\texttt{withRecordCanonicalGaussianExactCorridorAudit}.  It specializes the
source-derived endpoint to the obligations-backed record-canonical exact
corridor and returns the combined Gaussian/exact audit.  The experiment surface
exposes the same theorem with the suffix
\texttt{cThetaDichotomyWithRecordCanonicalGaussianExactCorridorAudit}.
The record-native possible-image hull route has also gained an
obligations-derived side-condition form.  The new experiment wrapper uses the
ambient \texttt{IUTStage1SourceHullDetObligations} object to supply q-pilot
positivity and source normalization.  The possible-image choice,
record-canonical hull/tensor bridge equality, determinant source, and external
numeric \(C_\Theta\) estimate remain explicit, but the route no longer takes an
independent \texttt{IUTStage1SourceSideConditions} record at this boundary.
This same tightening now sits behind the history-separated Hodge--Arakelov
surface: the finite Hodge/\(\SHE\) transport is constructed from the source and
target Hodge--Arakelov theta-evaluation sources and the record's separated
descent permission, while the Step (xi) side conditions are still projected
from the ambient hull/determinant obligations.
This history-separated possible-image obligations route now also has an audited
\(C_\Theta\)-surface.  The wrapper returns the Hodge--Arakelov canonical
one-degree match, the containment of the chosen Theorem 3.11 possible image in
the record possible-image union, the record-canonical hull/tensor bridge
alignment, and the obligations-derived q-positivity and normalization witnesses
alongside the final dichotomy.  Thus the strongest currently exposed
record-native finite-divisor endpoint can be reviewed at the source-data
boundary without unpacking the long theorem statement.
The certificate-pinned \(\IPL\)-link record-hull path now has the same
side-conditioned tightening.  The new endpoint suffix
\texttt{IPLLinkRecordHullSideConditionedFiniteDivisorVerticalIQ} projects
q-pilot positivity and source normalization from
\texttt{IUTStage1SourceSideConditions} before calling the older
certificate-pinned record-hull route.  Its history-separated
Hodge--Arakelov wrapper uses the same side-condition object, so this public
\(\IPL\)-link boundary no longer needs those two witnesses as separate
arguments.
The experiment module now exposes both versions directly.  The suffix
\texttt{sideConditionedIPLLinkRecordHullFiniteDivisorVerticalIQ} is the finite
Hodge/\(\SHE\) transport form; the history-separated variant uses the
\texttt{RecordHullSideConditionedFiniteDivisorVerticalIQ} suffix after
constructing the transport from Hodge--Arakelov theta evaluations.  These
wrappers make the review-facing certificate-pinned \(\IPL\)-link surface match
the side-conditioned core theorem.
It now also matches the possible-image obligations tightening available on the
constructed-\(\IPL\) side.  The suffix
\texttt{iplLinkPossibleImageObligationsRecordHullFiniteDivisorVerticalIQ}
uses a chosen Theorem 3.11 possible-image q-choice, derives the q-region's
containment in the record possible-image union internally, and projects
q-pilot positivity and normalization from the ambient
\texttt{IUTStage1SourceHullDetObligations} object.  Its history-separated
Hodge--Arakelov companion,
\texttt{historySeparatedIPLLinkPossibleImageObligationsRecordHullFiniteDivisorVerticalIQ},
constructs the finite Hodge/\(\SHE\) transport from the two theta-evaluation
sources before applying the same certificate-pinned \(\IPL\)-link
possible-image obligations route.
The compact synchronized route suffix now consumes one Hodge--Arakelov
synchronization object at this boundary, so the source calibration, target
evaluation, and canonical one-label preservation no longer appear as separate
public inputs on the review-facing theorem.
The no-\(C_\Theta\) finite-divisor boundary now returns this strengthened audit
as well, via the compact suffix
\texttt{boundaryEndpointWithAllInOneRouteGaussianStepXIAudit}.  This gives a
raw Step (x) endpoint whose payload is the same all-in-one Gaussian-to-Step
(xi) chain used by the later \(C_\Theta\)-dichotomy wrapper, before any numeric
\(C_\Theta\) estimate is supplied.
There is now also a \(C_\Theta\)-boundary suffix
\texttt{cThetaDichotomyWithAllInOneRouteHullDetGaussianStepXIAudit}; it displays
the same holomorphic-hull and determinant bridge fields next to the final
dichotomy.  This keeps the finite-divisor review surface aligned between the
raw and \(C_\Theta\) endpoints.
The synchronized Hodge/\(\SHE\)/constructed-\(\IPL\)/possible-image route now
also has a finite-divisor vertical-\(IQ\) source object.  This source object
stores the calibrated Hodge--Arakelov synchronization, constructed Theorem
3.11 \(\IPL\) source, obligations-backed possible-image Step (xi) hull source,
finite-divisor packet, Kummer/forgetting compatibilities, and vertical-\(IQ\)
target source together.  Its experiment-facing boundary and
\(C_\Theta\)-dichotomy aliases therefore take one source package plus the
external numeric estimate, while projecting the same Gaussian-to-Step (xi)
audit and Step (x) finite-divisor/vertical-\(IQ\) endpoint facts internally.
There is now also a bundled certificate-pinned \(\IPL\)-link version of this
finite-divisor source object.  It packages the synchronized Hodge--Arakelov
data, the Theorem 3.11 \(\IPL\)-link source, the obligations-backed
possible-image Step (xi) source, finite-divisor packet, Kummer/forgetting
compatibilities, and vertical-\(IQ\) target source before the constructed
\(\IPL\) datum is introduced.  The experiment suffixes
\texttt{boundaryEndpointWithIPLLinkGaussianStepXIAudit} and
\texttt{cThetaDichotomyWithIPLLinkGaussianStepXIAudit} expose the raw boundary
and conditional \(C_\Theta\) endpoint through this single source package.  This
keeps the certificate-pinned route auditable in the same form as the
constructed-\(\IPL\) route while preserving the intended distinction: the
certificate-pinned link is still a pre-construction source surface, not a proof
of the constructed input-prime-strip link machinery.
There is now a theta-monoid-matched version of this bundled finite-divisor
source as well.  It stores a matched Hodge--Arakelov synchronization whose
source/target theta-monoid degree equality derives the canonical one-label
Gaussian preservation internally, then projects to the synchronized source
object only inside the endpoint proof.  The experiment aliases expose the
theta-monoid equality, the derived canonical-one equality, the same
Gaussian-to-Step (xi) audit, and either the no-\(C_\Theta\) finite-divisor
boundary facts or the final conditional \(C_\Theta\) dichotomy.  This matched
source now also has a named pre-\(\IPL\) Hodge/\(\SHE\) transport audit:
theta-monoid matching, source full-label calibration, the history-separated
forgetful permission, pointwise representative comparison level, identity
coordinate transport, and Hodge-theater side separation are packaged before the
constructed \(\IPL\) layer is invoked.
The same matched bundled source now also exposes the constructed
\(\IPL\)/log-volume transport before the Step (xi) hull comparison is used.
The new endpoint projects the constructed \(\IPL\) datum, input/output
prime-strip equalities, source/target Hodge-theater sides, log-volume
preservation, allowed forgetting, and no-history-identification from the finite
Hodge/\(\SHE\)+\(\IPL\) construction source.  A separate finite-log-volume
endpoint identifies the \(\IPL\) source and target log-volumes with the finite
Hodge/\(\SHE\) source average and transported target average, making explicit
that this preservation is inherited from the finite transport rather than
supplied as an independent route equality.  The suffix
\texttt{thetaMonoidMatchedConstructedIPLTransportSourceEqConstructedEndpoint}
also exposes the exact constructor identity for this \(\IPL\) source at the
finite-divisor review boundary.
The matched bundled source now also exposes the Step (xi) possible-image
holomorphic-hull/determinant endpoint from the same source object.  This
projection displays the selected Theorem 3.11 possible image, containment in
the record possible-image union, obligations bridge alignment, tensor-power
determinant bound, q-positivity, normalization, and the raw
\(q_{\mathrm{signed}}\le \theta_{\mathrm{signed}}\) comparison.  A companion
record-canonical bridge endpoint identifies the package hull/determinant bridge
with the canonical hull/tensor bridge constructed from the possible-image
region, its record-union containment proof, and the weighted determinant data.
These separate projections are now bundled into one named matched route audit,
\texttt{MatchedSourceDerivedFiniteDivisorRouteAudit}, with experiment-surface
wrapper
\path|sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQSource_thetaMonoidMatchedFullRouteAudit|.
This audit is the compact review target for the current one-source-object
finite-divisor corridor: it contains the pre-\(\IPL\) finite Hodge/\(\SHE\)
transport audit, the constructed \(\IPL\) log-volume endpoints, the
obligations-backed possible-image Step (xi) endpoint, the record-canonical
hull/tensor bridge equality, and the no-\(C_\Theta\) matched Gaussian-to-Step
(xi) boundary.
The target-charted route is stronger than this matched bundled source at the
current review surface.  The compact all-in-one target-charted
Hodge/\(\IPL\)/determinant possible-image route now exposes the target theta
chart, the Hodge--Arakelov theta-monoid degree, the determinant summand sum,
the record possible-image family-hull log-volume, the package
hull/determinant bridge, and the raw signed comparison in one bridge audit.
The same ordinary target-charted all-in-one route now also has a compact
full-route audit, \texttt{TargetChartedFullRouteAudit}, with experiment
wrapper
\path|targetChartedHodgeIPLDeterminantPossibleImageRoute_fullRouteAudit|.
It bundles the Gaussian-to-Step (xi) chain, determinant source-boundary audit,
calibrated determinant endpoint, calibrated possible-image endpoint, and raw
comparison endpoint without changing the underlying assumptions.  This gives
the stronger target-charted route a single review target parallel to the
matched finite-divisor audit.
Its theta-monoid-matched variant additionally records that canonical one-label
preservation on the Hodge/\(\IPL\) side is reconstructed from equality of the
target and source theta-monoid degrees.  Thus the strongest finite-divisor
review endpoint no longer merely assumes a tensor-power upper bound at the
public Step (xi) surface: it routes the equality
\(\theta_{\mathrm{signed}}\) equals the record possible-image family-hull
log-volume through the determinant payload before projecting the bound consumed
by the older holomorphic-hull constructor.
The exact vertical-\(IQ\) record-canonical corridor now also has a
summand/family-hull source form.  This source object stores the
Hodge/\(\IPL\) construction, the target-charted possible-image
summand/family-hull Step (xi) source, the finite Step (x) source, and the
exact vertical-\(IQ\) data.  It projects internally to the older
record-canonical obligations exact source, so the exact corridor no longer
exposes the Step (xi) operation identifiers, family-hull source, measure
equality, q-choice, and obligations bridge equality as separate public fields.
The experiment suffixes
\texttt{boundaryEndpointWithSummandFamilyHullGaussianExactCorridorAudit} and
\texttt{cThetaDichotomyWithSummandFamilyHullGaussianExactCorridorAudit} expose
the raw boundary and conditional \(C_\Theta\) endpoint.  This makes the exact
vertical-\(IQ\) corridor line up more closely with the Step (xi) passage of
\IUT{} III, Remark~3.9.5 and Corollary~3.12, where possible images pass through
holomorphic hulls, determinant/tensor-power data, and log-volume comparison
before the final numerical estimate is invoked.
The possible-image Step (xi) source has also gained a constructor-pinned form.
This new source still stores the selected Theorem~3.11 possible image and the
weighted determinant payload, but it additionally carries the Theorem~3.11
hull/determinant constructor whose hull data is identified with the ambient
source obligations.  Its endpoint exposes the constructor/obligation
identification, the constructor bridge equality, q-positivity, normalization,
the tensor-power bound, and the raw \(q_{\mathrm{signed}}\le
\theta_{\mathrm{signed}}\) comparison together.  The experiment surface now has
theta-monoid-matched raw and \(C_\Theta\) finite-divisor variants with the
\texttt{ConstructorPinnedThetaMonoidMatchedRouteAudit} suffix.  These variants
project internally to the older obligations-backed possible-image source, but
the public Step (xi) input is now pinned to a source constructor rather than
only to a bridge-equality field.
The next tightening removes even that ambient obligations object from the
public Step (xi) source.  The constructor-sourced hull source derives
\texttt{IUTStage1SourceHullDetObligations} as
\texttt{constructor.toHullDetObligations}; algorithm certification, \(\SHE\)
alignment, q-positivity, normalization, and hull/determinant data therefore
enter through the same Theorem~3.11 constructor.  The experiment suffix
\texttt{ConstructorSourcedThetaMonoidMatchedRouteAudit} exposes the
constructor-sourced endpoint, the projected constructor-pinned endpoint, and
the same raw or conditional \(C_\Theta\) finite-divisor boundary.  The remaining
unconstructed Step (xi) inputs are now concentrated in the constructor itself:
the holomorphic hull shadow, weighted determinant payload, measure calibration,
and tensor-power bound.
There is now also a constructor-built source at the same review boundary.  It
does not receive a Theorem~3.11 hull/determinant constructor as public input.
Instead, it applies the record-canonical constructor
\texttt{ofRecordCanonicalHullTensorPowerOfQSubsetUnion} to the chosen possible
image, the canonical hull/tensor bridge equation, q-positivity, and
normalization.  The experiment suffix
\texttt{ConstructorBuiltThetaMonoidMatchedRouteAudit} exposes the built source
endpoint, the projected constructor-sourced endpoint, the projected
constructor-pinned endpoint, and then the same raw or conditional \(C_\Theta\)
finite-divisor boundary.  Thus the remaining Step (xi) public payload has moved
from a constructor object to the actual record-canonical hull/tensor inputs:
holomorphic hull shadow, weighted determinant compatibility, measure
calibration, tensor-power bound, and the bridge equality.
The constructor-built possible-image source now also has the named audit
\texttt{RecordCanonicalStepXIAudit}, exposed on the experiment surface by the
suffix \texttt{recordCanonicalStepXIAudit}.  This audit unfolds the
record-canonical Step (xi) constructor itself: the selected q-pilot region lies
in the Theorem~3.11 possible-image union and hence in the canonical holomorphic
hull, that union agrees with both the Theorem~3.11 record and the package
target union, the tensor-power determinant bound supplies the
\(\theta_{\mathrm{signed}}\) bound, and the constructed hull/determinant source
then provides certification, record-union hull containment, determinant-volume
control, and the raw \(q_{\mathrm{signed}}\le\theta_{\mathrm{signed}}\)
comparison.  This gives reviewers a Step (xi)-native audit target before the
finite-divisor route projects it into the later vertical-\(IQ\) corridor.
The same constructor-built source now exposes a sharper remaining-payload
audit,
\texttt{ConstructorBuiltRemainingPayloadAudit}, with experiment suffix
\texttt{remainingPayloadAudit}.  This ledger separates the still-supplied
Remark~3.9.5/Step~(xi) inputs from the constructor projections: selected
possible-image q-region, holomorphic-hull absorption of the possible-image
union and q-region, the named Ob1/Ob2 hull-absorption audit, the named Ob3/Ob4
determinant/tensor-power audit, the derived Ob3--Ob5 hull-log-volume
compatibility chain, the bridge handoff from the package hull/determinant
source to the constructor bridge datum, the subsequent equality from that
constructor bridge datum to the record-canonical hull/tensor bridge,
q-positivity, normalization, and the derived raw comparison.  The experiment
surface exposes this split as \texttt{remainingPayloadBridgeSplit}, so the
remaining supplied Step~(xi) payload can be audited separately from the
constructor-to-record bridge projection.
This constructor-built Step (xi) source is now also available as a single
theta-monoid-matched finite-divisor route object, not merely as an external
experiment wrapper.  This source object packages the matched Hodge--Arakelov
synchronization, the constructed Theorem~3.11 \(\IPL\) source, the
constructor-built possible-image hull source, finite-divisor packet data,
Kummer/forgetting compatibilities, and vertical \(IQ\) target source.  Its
full-route, boundary, and conditional \(C_\Theta\) audits now carry the
\texttt{RecordCanonicalStepXIAudit} as an explicit component, and the experiment
surface exposes it with suffix
\texttt{ConstructorBuiltRecordCanonicalStepXIAudit}.  Thus the route-level
review target no longer hides the record-canonical Step (xi) constructor audit
behind the compact constructor-built source endpoint.  Its route audit first
exposes the built Step (xi) endpoint, the projected
constructor-sourced endpoint, and the projected constructor-pinned endpoint,
then projects to the established matched finite-divisor audit.  The experiment
surface exposes this as the compact \texttt{ConstructorBuiltFullRouteAudit}
review target.  The same route now also has
\texttt{ConstructorBuiltRemainingPayloadRouteAudit}, exposed with suffix
\texttt{ConstructorBuiltRemainingPayloadRouteAudit}; it pairs the
remaining-payload ledger with the full finite-divisor route audit so the
source-paper Step (xi) obligations remain attached to the bundled source
object.  The same bundled source now also has no-\(C_\Theta\) and
conditional \(C_\Theta\) experiment endpoints with suffixes
\texttt{ConstructorBuiltBoundaryAudit} and
\texttt{ConstructorBuiltCThetaAudit}; these keep the external numeric estimate
separate while ensuring that the Hodge/\(\SHE\), constructed \(\IPL\),
constructor-built Step (xi), and finite vertical-\(IQ\) data all come from one
route object.  The conditional endpoint now also has the sharper suffix
\texttt{ConstructorBuiltRemainingPayloadCThetaAudit}, which carries the same
remaining-payload Step (xi) ledger next to the \(C_\Theta\) dichotomy instead
of exposing it only at the raw route-audit boundary.
There is now also an \(\IPL\)-link version of this constructor-built bundled
route.  The source object
\[
\begin{array}{l}
\texttt{IUTStage1ThetaMonoidMatchedHodgeSHEIPLLink}\\
\texttt{PossibleImageConstructorBuiltFiniteDivisorVerticalIQSource}
\end{array}
\]
keeps the same record-canonical Step (xi) constructor-built hull source, but
uses only the certificate-pinned Theorem~3.11 \(\IPL\) link source rather than
an input-prime-strip link construction source.  Its experiment suffixes
\[
\begin{array}{l}
\texttt{ConstructorBuiltIPLLinkFullRouteAudit},\\
\texttt{ConstructorBuiltIPLLinkRemainingPayloadRouteAudit},\\
\texttt{ConstructorBuiltIPLLinkBoundaryAudit},\\
\texttt{ConstructorBuiltIPLLinkCThetaAudit},\\
\texttt{ConstructorBuiltIPLLinkRemainingPayloadCThetaAudit}
\end{array}
\]
expose the route, no-\(C_\Theta\), conditional \(C_\Theta\), and
remaining-payload conditional audits.  The last suffix carries the same
remaining Step (xi) payload ledger beside the certificate-pinned \(\IPL\)-link
dichotomy.  This separates the Step (xi) constructor-built progress from the
still-open construction of the actual Theorem~3.11 input-prime-strip link
machinery.
This constructor-built \(\IPL\)-link route now also has a Hodge--Arakelov
source endpoint.  Instead of asking the public theorem for the bundled
theta-monoid-matched synchronization record, the endpoint starts from a
calibrated source theta evaluation, a target theta evaluation, and the equality
of their theta-monoid degrees, constructs the matched synchronization
internally, and then enters the same constructor-built Step (xi) finite-divisor
route.  The experiment surface now exposes both the no-\(C_\Theta\) boundary,
which includes the projected \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\)
comparison, and the conditional endpoint, with suffixes
\[
\begin{array}{l}
\texttt{hodgeArakelovHistorySeparatedConstructorBuiltIPLLinkBoundaryAudit},\\
\texttt{hodgeArakelovHistorySeparated}\\
\texttt{ConstructorBuiltIPLLinkCTheta}.
\end{array}
\]
This Hodge--Arakelov constructor-built \(\IPL\)-link route now also has a
canonical-one variant.  Instead of receiving the theta-monoid degree equality
directly, the endpoint assumes preservation of the Gaussian degree at the
canonical \(1\)-label and derives the theta-monoid equality from the
Hodge--Arakelov evaluation laws on the source and target sides.  Its experiment
surface exposes the corresponding boundary and conditional endpoints with
suffixes \texttt{hodgeArakelovCanonicalOneConstructorBuiltIPLLinkBoundaryAudit}
and \texttt{hodgeArakelovCanonicalOneConstructorBuiltIPLLinkCTheta}.
The canonical-one variant is now also available as a single source object,
\[
\begin{array}{l}
\texttt{IUTStage1CanonicalOneHodgeArakelovSHEIPLLink}\\
\texttt{PossibleImageConstructorBuiltFiniteDivisorVerticalIQSource}.
\end{array}
\]
This object stores the calibrated source Hodge--Arakelov evaluation, the target
evaluation, the canonical \(1\)-label Gaussian preservation equality, the
certificate-pinned \(\IPL\) link source, the constructor-built Step (xi)
hull/determinant source, and the finite Step (x) vertical-\(IQ\) data.  Its
projection first reconstructs the theta-monoid-matched source object and then
reuses the existing constructor-built \(\IPL\)-link boundary.  The experiment
surface exposes this compact review target through the suffixes
\[
\begin{array}{l}
\texttt{canonicalOneConstructorBuiltIPLLinkFullRouteAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkRemainingPayloadRouteAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkThetaEvaluationPairAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkBoundaryAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkCThetaAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkRemainingPayloadCThetaAudit}.
\end{array}
\]
The theta-evaluation-pair audit records both source and target
Hodge--Arakelov theta-evaluation endpoints, the source full-label calibration
against the theta-source cusp-log-volume average, canonical \(1\)-label
Gaussian-degree preservation, and the derived theta-monoid degree equality.
The latter is now exposed directly on the experiment surface as
\texttt{canonicalOneConstructorBuiltIPLLinkThetaMonoidDegreeEq}; its proof uses
the source and target Hodge--Arakelov theta-evaluation endpoints'
\texttt{canonicalOneDegree\_eq\_thetaMonoidDegree} theorems rather than an
inline route calculation.
The same source object now exposes the raw Step (xi) comparison before the
finite Step (x) boundary is unfolded.  Its named audit
\texttt{CanonicalOneConstructorBuiltIPLLinkQComparisonAudit} packages the
constructor-built route audit, the pre-Step (xi)
\texttt{CanonicalOneConstructorBuiltIPLLinkHodgeSHEIPLAudit}, and
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\).  The pre-Step audit
records the Hodge--Arakelov theta-root/Gaussian endpoint, finite
Hodge/\(\SHE\) transport, history-separated forgetful transport permission, and
certificate-pinned \(\IPL\)/log-volume transport before the possible-image hull
comparison is used.  The Step (xi) source-object handoff is now exposed as
\texttt{CanonicalOneConstructorBuiltIPLLinkHolomorphicHullDeterminantSourceAudit}:
the canonical-one route projects its constructor-built hull source to the
existing obligations-backed possible-image holomorphic-hull/determinant source,
where the q-pilot choice, record-union containment, obligations bridge,
tensor-power bound, q-positivity, normalization, and raw signed comparison are
read from that one source object.  This is now followed by
\texttt{CanonicalOneConstructorBuiltIPLLinkSourceDerivedBridgeAudit}, which
constructs the source-derived Hodge/\(\SHE\)/\(\IPL\)/hull bridge from the
canonical-one Hodge--Arakelov synchronization, the certificate-pinned
Theorem 3.11 \(\IPL\) link, and that projected possible-image hull source.  Its
endpoint records the \(\IPL\) prime-strip equalities, source/target Hodge
averages, possible-image q-region, obligations bridge, log-volume preservation,
history separation, and \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\).
The field-level Step (xi) hull side remains separated as
\texttt{CanonicalOneConstructorBuiltIPLLinkStepXIHullAudit}, which records the
q-pilot possible image, record-union containment, record-canonical
hull/determinant bridge, tensor-power bound, theta-pilot hull containment and
volume facts, q-positivity, and normalization before the raw signed comparison
is projected.  The same \(\IPL\)-link Step (xi) source side now exposes the
remaining payload in the same review buckets as the constructed-\(\IPL\)
route: Ob1/Ob2 hull absorption, Ob3/Ob4 determinant normalization and
tensor-power control, Ob5 compatibility of the bounded-family hull passage,
and the q-positivity/normalization side conditions.  These buckets are then
threaded into
\texttt{CanonicalOneConstructorBuiltIPLLinkQComparisonAudit}, so the raw
comparison no longer points only to a coarse Step (xi) hull audit.  The
experiment surface adds direct endpoints with suffixes
\[
\begin{array}{l}
\texttt{canonicalOneConstructorBuiltIPLLinkThetaEvaluationPairAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkHodgeSHEIPLAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkHolomorphicHullDeterminantSourceAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkSourceDerivedBridgeAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkStepXIHullAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkOb1Ob2HullAbsorptionAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkOb3Ob4DeterminantAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkOb5CompatibilityAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkSideConditionAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkQComparisonAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLink\_qComparison},\\
\texttt{canonicalOneConstructorBuiltIPLLinkCTheta},\\
\texttt{canonicalOneConstructorBuiltIPLLinkRemainingPayloadCThetaAudit},\\
\texttt{canonicalOneConstructorBuiltIPLLinkMilestoneCThetaAudit}.
\end{array}
\]
The no-\(C_\Theta\) finite boundary is now staged through the named audit
\texttt{CanonicalOneConstructorBuiltIPLLinkFiniteBoundaryAudit}: its first
field is the raw q-comparison audit, followed by the Step (xi) hull audit,
Ob1/Ob2 hull absorption, Ob3/Ob4 determinant, Ob5 compatibility, and
side-condition audits, and then the finite-divisor packet equalities plus the
vertical-\(IQ\) target equalities.
The experiment surface exposes this as
\texttt{canonicalOneConstructorBuiltIPLLinkFiniteBoundaryAudit}.  The new
\texttt{CanonicalOneConstructorBuiltIPLLinkMilestoneCThetaAudit} then packages
the q-comparison audit, fine Step (xi) payload audits, finite-boundary audit,
source-derived bridge audit, conditional \(C_\Theta\) audit, the
remaining-payload \(C_\Theta\) audit, and final ordered-real dichotomy as one
milestone-facing declaration.  Thus this review target separates the raw
source-derived Step (xi) comparison, the finite vertical-\(IQ\) boundary
ledger, the still-supplied Step (xi) payload, and the later numeric
\(C_\Theta\) input while also offering a single audit surface for the
canonical-one constructor-built route.
There is now a stricter canonical-one variant whose middle route constructs
\(\IPL\)/log-volume transport rather than consuming only the certificate-pinned
\(\IPL\)-link source:
\[
\begin{array}{l}
\texttt{IUTStage1CanonicalOneHodgeArakelovSHEIPLConstruction}\\
\texttt{PossibleImageConstructorBuiltFiniteDivisorVerticalIQSource}.
\end{array}
\]
It carries the same calibrated source Hodge--Arakelov evaluation, target
evaluation, canonical \(1\)-label Gaussian preservation equality,
constructor-built Step (xi) hull/determinant source, and finite Step (x)
vertical-\(IQ\) data, but replaces the standalone \(\IPL\)-link source by an
\texttt{IUTStage1Theorem311IPLLinkConstructionSource}.  Lean derives the
theta-monoid match from canonical-one preservation, projects to the existing
theta-monoid-matched constructed-\(\IPL\) route, and exposes the finite
Hodge/\(\SHE\) transport audit, constructed \(\IPL\) prime-strip equalities,
and constructed \(\IPL\) source/target log-volume provenance as fields of
\texttt{CanonicalOneConstructorBuiltIPLConstructionMiddleRouteAudit}.  The
front Hodge--Arakelov Gaussian data is now also separated as
\texttt{CanonicalOneConstructorBuiltIPLConstructionThetaEvaluationAudit}; it
records the source and target theta-evaluation endpoints, the source
theta/log-volume calibration, canonical \(1\)-label degree preservation, and the
derived theta-monoid degree equality before the finite Hodge/\(\SHE\) transport
is constructed.  The equality itself is also available as the compact experiment
target \texttt{canonicalOneConstructorBuiltIPLConstructionThetaMonoidDegreeEq}.
The transport-source handoff is now also named separately as
\texttt{CanonicalOneConstructorBuiltIPLConstructionTransportSourceAudit}: it
packages the theta-evaluation audit with the finite Hodge/\(\SHE\)
transport-source endpoint built from the source/target Hodge--Arakelov
evaluations and history-separated forgetting.  The next audit,
\texttt{CanonicalOneConstructorBuiltIPLConstructionFactoredSHEAudit}, records
the factored square/full-label \(\SHE\) synchronization endpoint, the
transport-source audit, and the finite Hodge/\(\SHE\) transport endpoint:
structured-\(\SHE\) availability, identity-coordinate transport, full-label
log-volume preservation, transported-average preservation, and history
separation all appear before the constructed \(\IPL\) log-volume transport is
read.  The constructed \(\IPL\) segment now has two named subaudits:
\texttt{CanonicalOneConstructorBuiltIPLConstructionLogVolumeTransportAudit}
identifies the finite source's \(\IPL\)/log-volume transport source with the
construction from the Theorem 3.11 input-prime-strip link source, while
  \texttt{CanonicalOneConstructorBuiltIPLConstructionFiniteTransportLogVolumeAudit}
  reads the source and target \(\IPL\) log-volumes from the finite
  Hodge/\(\SHE\) source average and transported target average.  The stronger
  chain audit
  \texttt{CanonicalOneConstructorBuiltIPLConstructionFiniteTransportLogVolumeChainAudit}
  packages the finite Hodge/\(\SHE\) transport endpoint, the constructed
  Theorem 3.11 \(\IPL\) source, the finite-transport log-volume endpoint, and the
  transported-average preservation theorem as a single provenance boundary.  Thus
  the equality between the constructed \(\IPL\) target and source log-volumes is
  read directly from finite transported-average preservation rather than from an
  independent route-level conjunction.  The aggregate
  \texttt{CanonicalOneConstructorBuiltIPLConstructionConstructedIPLAudit}
  then packages these two subaudits together with the choice-wise prime-strip
  links.
The named subaudit
\texttt{CanonicalOneConstructorBuiltIPLConstructionChoiceLinkAudit} now exposes
this choice-wise input-prime-strip link obligation directly and is threaded
through the Hodge/\(\SHE\)/\(\IPL\), middle-route, q-comparison, finite-boundary,
and milestone \(C_\Theta\) audits.  The constructed-\(\IPL\) route now also has
its own bridge-construction audit,
\texttt{CanonicalOneConstructorBuiltIPLConstructionSourceDerivedBridgeAudit}.
This audit records the bridge built from the Hodge--Arakelov theta data,
finite Hodge/\(\SHE\) transport, the constructed Theorem 3.11 \(\IPL\) source,
and the constructor-built possible-image Step (xi) hull source, and then
projects the generic source-derived bridge alignment endpoint from that bridge.
The resulting route alignment is now also named as
\texttt{CanonicalOneConstructorBuiltIPLConstructionRouteLogVolumeAlignmentAudit}.
This audit exposes the concrete
\texttt{IUTStage1HodgeSHEIPLHullRouteLogVolumeAlignment} constructed from the
bridge, including \(\IPL\) log-volume preservation, source theta/Hodge
log-volume calibration, target \(\SHE\)-transported log-volume equality, and
q-pilot positivity.
Its
Step (xi) hull side is now separated as
\texttt{CanonicalOneConstructorBuiltIPLConstructionStepXIHullAudit}, which
records the constructor-built, constructor-sourced, and constructor-pinned
possible-image hull endpoints, the projected possible-image hull/determinant
endpoint, and the record-canonical hull/tensor bridge equality before the
boundary audit is used.  It now also carries the compact
\texttt{CanonicalOneConstructorBuiltIPLConstructionOb1ToOb5BridgeAudit}, whose
source-level core is
\texttt{ConstructorBuiltOb1ToOb5BridgeAudit}.  This audit packages the
Remark 3.9.5(vii) chain from Ob1/Ob2 hull absorption through Ob3/Ob4
determinant and tensor-power normalization, Ob3/Ob5 determinant/log-volume
compatibility, the remaining Step (xi) source payload, and the actual
\texttt{hullDetSource\_endpoint} produced by the Theorem 3.11
hull/determinant constructor.  Thus the record-canonical bridge endpoint is now
reviewable as the output of the Ob1--Ob5 source data, not only as a separate
remaining-payload projection.  The source-level audit is also exposed directly
on the experiment surface as
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource\_ob1ToOb5BridgeAudit}.
\end{array}
\]
This lets the Remark 3.9.5(vii) bridge be reviewed before entering the
finite-divisor vertical-\(IQ\) corridor.  The source-level bridge is now also
joined to the bounded-family Ob5 quotient collapse by
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource\_ob1ToOb5QuotientBridgeAudit}.
\end{array}
\]
This audit carries the Ob1--Ob5 bridge, the Ob5 quotient-independence audit,
the record Ob3/Ob5 bridge, and the local canonical \(C_\Theta\) chain in one
object: two nonempty Theorem~3.11 possible images have the same quotient image,
while the selected q-region still satisfies
\(\mu_{\log}(q\mathrm{Region})\leq \det_{\mathrm{norm}}
\leq\theta_{\mathrm{signed}}\).  Its flat-chain companion
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource\_ob1ToOb5QuotientBridgeChain}
\end{array}
\]
spells out the two family-hull inclusions, the quotient-image equality,
\(\mu_{\log}(q\mathrm{Region})\leq\det_{\mathrm{norm}}\leq
\theta_{\mathrm{signed}}\), the canonical \(C_\Theta\) upper bound, and
the signed comparison \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\)
without requiring reviewers to unfold the audit record.  The same Step (xi)
hull audit now exposes the
\enlargethispage{2\baselineskip}
constructor-built upper-ray log-volume audit
\[
\begin{array}{l}
\texttt{ConstructorBuiltStepXIUpperRayAudit},
\end{array}
\]
which records the q-pilot region's holomorphic-hull containment, the equality
between hull log-volume and normalized weighted determinant, membership of the
q-pilot log-volume in the resulting upper ray, and the projected
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison.  This upper-ray
handoff is now named at the same route level as
\texttt{CanonicalOneConstructorBuiltIPLConstructionUpperRayAudit}, which
projects q-pilot upper-ray membership, theta-hull and determinant bounds,
determinant normalization, and the raw signed comparison from the
constructor-built Step (xi) source.  Its Ob1/Ob2
hull-absorption payload is now isolated as
\texttt{CanonicalOneConstructorBuiltIPLConstructionOb1Ob2HullAbsorptionAudit}:
the selected q-region is identified with a Theorem 3.11 possible image, shown
inside the record possible-image union, and both the union and selected q-region
are absorbed by the canonical holomorphic hull before determinant data enters.
Its Ob3/Ob4 determinant payload is now also isolated as
\texttt{CanonicalOneConstructorBuiltIPLConstructionOb3Ob4DeterminantAudit}:
the audit records weighted determinant summation, determinant normalization,
hull-log-volume compatibility, tensor-power control, measure calibration, and
the record-canonical hull/tensor bridge before the finite Step (x) boundary is
used.  The Ob5 independence-of-possibilities passage is now isolated as
\texttt{CanonicalOneConstructorBuiltIPLConstructionOb5CompatibilityAudit}: the
selected q-region is absorbed by the bounded-family hull, and the
hull-log-volume, determinant normalization, package measure, and
record-canonical bridge remain compatible with that hull-family passage.  This
route-level Ob5 audit now also carries the constructor-built
Ob3/Ob5 determinant-compatibility chain, so the determinant log-volume equality
is read through normalized weighted-determinant compatibility rather than a
standalone remaining-payload projection.  The same route now exposes the
quotient form of this Ob5 passage as
\texttt{CanonicalOneConstructorBuiltIPLConstructionOb5QuotientIndependenceAudit}.
For any comparison possible-image choice, together with nonemptiness of the
selected q-choice image and the comparison image, this audit imports the
constructor-built Remark~3.9.5(v)--(vi) quotient collapse into the
canonical-one constructed-\(\IPL\) finite-divisor route: both possible images
map to the same collapsed bounded-family quotient image, while the Ob1--Ob5
bridge, Ob5 compatibility, family-hull determinant/log-volume equality,
family-union bound, tensor-power normalization, and raw signed comparison
remain attached to the same source object.  The
remaining source side conditions are now split off as
\texttt{CanonicalOneConstructorBuiltIPLConstructionSideConditionAudit}: the
constructor-built hull source's q-pilot positivity and source normalization
are repackaged through the existing
\texttt{IUTStage1SourceSideConditions} interface before the finite Step (x)
boundary consumes the raw signed comparison.  The raw Step (xi) comparison is
now also named directly as
\texttt{CanonicalOneConstructorBuiltIPLConstructionQComparisonAudit}: it keeps
the Hodge/\(\SHE\)/constructed-\(\IPL\) middle-route audit, Step (xi) hull
audit, Step (xi) holomorphic-hull/determinant skeleton, named Ob1/Ob2
hull-absorption audit, named Ob3/Ob4 determinant audit, Ob5 compatibility
audit, and source side-condition audit together before projecting
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\).  The
no-\(C_\Theta\) finite boundary is now separated as
\texttt{CanonicalOneConstructorBuiltIPLConstructionFiniteBoundaryAudit}; it
keeps the middle-route audit, Step (xi) hull audit, the
Step (xi) holomorphic-hull/determinant skeleton, compact boundary audit,
finite-divisor packet equalities, exact vertical-\(IQ\) target equalities, and
raw \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison attached to
the same source object.  The named skeleton
\texttt{CanonicalOneConstructorBuiltIPLConstructionStepXIHolomorphicHullDeterminantSkeleton}
records possible-image containment, holomorphic-hull absorption,
determinant/tensor-power facts, the record-canonical bridge equality, side
conditions, and the raw signed comparison as projections from the
constructor-built hull source.  The
experiment surface exposes this stricter route through suffixes
\[
\begin{array}{l}
\texttt{canonicalOneConstructorBuiltIPLConstructionFullRouteAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionRemainingPayloadRouteAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionThetaEvaluationAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{TransportSourceAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionFactoredSHEAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{LogVolumeTransportAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{FiniteTransportLogVolumeAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{FiniteTransportLogVolumeChainAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionConstructedIPLAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionChoiceLinkAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionHodgeSHEIPLAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{DirectHodgeSHEIPLAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionDirectGaussianToStepXIAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionMiddleRouteAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionDirectMiddleRouteAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionSourceDerivedBridgeAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{RouteLogVolumeAlignmentAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionStepXIHullAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{Ob1ToOb5BridgeAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionUpperRayAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{StepXIHolomorphicHullDeterminantSkeleton},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionOb1Ob2HullAbsorptionAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionOb3Ob4DeterminantAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionOb5CompatibilityAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{Ob5QuotientIndependenceAudit},\\
\end{array}
\]
and
\[
\begin{array}{l}
\texttt{canonicalOneConstructorBuiltIPLConstructionSideConditionAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionQComparisonAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{DirectQComparisonAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction\_qComparison},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionPacketTargetAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionDirectFiniteBoundaryAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{DirectRouteFiniteBoundaryAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionFiniteBoundaryAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionBoundaryAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionCTheta},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionDirectCThetaAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstructionMilestoneCThetaAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{DirectMilestoneCThetaAudit},\\
\texttt{canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{Ob5QuotientMilestoneCThetaAudit}.
\end{array}
\]
The constructed-\(\IPL\) route now also has compact milestone-facing aliases:
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ},\\
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ}\\
\quad\texttt{\_withDirectMilestoneAudit},\\
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullConstructedIPLFiniteDivisorVerticalIQ},\\
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullConstructedIPLFiniteDivisorVerticalIQ}\\
\quad\texttt{\_withMilestoneAudit},\\
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullConstructedIPLFiniteDivisorVerticalIQ}\\
\quad\texttt{\_withDirectMilestoneAudit},\\
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullConstructedIPLFiniteDivisorVerticalIQ}\\
\quad\texttt{\_withOb5QuotientMilestoneAudit}.
\end{array}
\]
The first pair is now the compact subgoal-6 public endpoint and its direct audit
companion; the latter four names keep the more explicit constructed-\(\IPL\)
spelling.  All six aliases return the same canonical-one constructor-built
constructed \(\IPL\) route: Hodge--Arakelov theta evaluation, factored \(\SHE\),
constructed \(\IPL\)/log-volume transport, Step (xi) hull/determinant audits,
source side conditions, raw q-comparison, finite boundary, and conditional
\(C_\Theta\) audit, with the numeric \(C_\Theta\) estimate still explicit.
\texttt{CanonicalOneConstructorBuiltIPLConstructionMilestoneCThetaAudit}
now carries the transport-source, log-volume transport, and finite-transport
log-volume audits directly, together with the constructed source-derived
bridge audit, the constructed route-log-volume alignment audit, a direct
middle-route audit, constructor-built upper-ray audit, and a direct signed
\(C_\Theta\) audit.  The direct middle-route audit bundles the canonical-one
theta-evaluation, finite Hodge/\(\SHE\) transport, factored \(\SHE\),
constructed \(\IPL\) log-volume transport, source-derived bridge, and
route-log-volume alignment chain before the theta-monoid-matched finite
boundary is used for compatibility.  The direct \(C_\Theta\) audit computes the
ordered-real dichotomy from the constructed q-positivity side condition, the constructed
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) Step (xi) comparison, and
the explicit numeric \(C_\Theta\) estimate, rather than projecting that
dichotomy only through the coarser theta-monoid-matched \(C_\Theta\) package.
The Hodge/\(\SHE\)/\(\IPL\) part of this direct path is now also exposed as
\texttt{CanonicalOneConstructorBuiltIPLConstructionDirectHodgeSHEIPLAudit}.
Unlike the broader compatibility audit, this direct audit does not carry the
theta-monoid-matched finite-transport ledger; it records only the
canonical-one theta evaluation, finite Hodge/\(\SHE\) transport, factored
\(\SHE\), constructed-\(\IPL\) log-volume transport, finite-transport
log-volume, and choice-link endpoints.  The direct middle route, raw
q-comparison audit, and direct milestone bundle consume this stricter audit.
The raw comparison itself now also has a no-broad-middle-route form,
\texttt{CanonicalOneConstructorBuiltIPLConstructionDirectQComparisonAudit}.
It removes the older \texttt{MiddleRouteAudit} field from the comparison
payload and reviews \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\)
through the direct Hodge/\(\SHE\)/\(\IPL\) audit, direct middle route,
source-derived bridge, route-log-volume alignment, Step (xi)
hull/determinant audits, Ob1--Ob5 payload, and source side conditions.  The
direct finite-boundary route, direct \(C_\Theta\) audit, and direct milestone
bundle consume this direct q-comparison audit.  The public raw comparison
suffix \texttt{canonicalOneConstructorBuiltIPLConstruction\_qComparison} now
projects through the direct comparison theorem as well.
There is now also
\texttt{CanonicalOneConstructorBuiltIPLConstructionDirectMilestoneCThetaAudit},
which removes the theta-monoid-matched route, remaining-payload, compact
boundary, and matched \(C_\Theta\) compatibility projections from the
milestone bundle.  Its load-bearing route is the direct middle-route audit, the
direct route finite-boundary audit, and the direct signed \(C_\Theta\) audit.
The compact constructed-\(\IPL\) alias with suffix
\texttt{withDirectMilestoneAudit} returns this same direct milestone bundle.
Thus the milestone-facing bundle exposes the pre-\(\IPL\) and
constructed-\(\IPL\) transport chain, the Hodge/\(\SHE\)/\(\IPL\)/hull bridge
constructor, the route alignment it constructs, and the Step (xi-f/g)
upper-ray handoff instead of only the coarser constructed-\(\IPL\) and hull
audits.
The quotient-aware milestone bundle,
\texttt{CanonicalOneConstructorBuiltIPLConstructionOb5QuotientMilestoneCThetaAudit},
attaches the route-level Ob5 quotient-independence audit to this same direct
\(C_\Theta\) milestone surface.  Its compact alias with suffix
\texttt{withOb5QuotientMilestoneAudit} returns the final dichotomy together
with the collapsed Ob5 quotient images for two nonempty possible-image choices,
so the quotient-collapse payload is visible at the same review surface as the
finite-divisor vertical-\(\mathrm{IQ}\) \(C_\Theta\) endpoint.
The same route now has an unbundled canonical-one Hodge--Arakelov source
endpoint,
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeArakelovCanonicalOneT11IPLConstruction}\\
\quad\texttt{ConstructorBuiltFiniteDivisorVerticalIQ},
\end{array}
\]
exposed on the experiment surface with suffix
\[
\begin{array}{l}
\texttt{hodgeArakelovCanonicalOne}\\
\quad\texttt{ConstructorBuiltIPLConstructionCTheta}.
\end{array}
\]
It
constructs the canonical-one source object internally from the calibrated source
theta evaluation, target theta evaluation, canonical \(1\)-label Gaussian
preservation, Theorem 3.11 \(\IPL\)-link construction source,
constructor-built Step (xi) hull source, and finite Step (x)
vertical-\(IQ\) data.
Its audit-returning companion,
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeArakelovCanonicalOneT11IPLConstruction}\\
\quad\texttt{ConstructorBuiltFiniteDivisorVerticalIQ\_withMilestoneAudit},
\end{array}
\]
is exposed on the experiment surface with suffix
\[
\begin{array}{l}
\texttt{hodgeArakelovCanonicalOne}\\
\quad\texttt{ConstructorBuiltIPLConstructionMilestoneAudit}.
\end{array}
\]
It returns the full canonical-one constructor-built constructed-\(\IPL\)
milestone \(C_\Theta\) audit for the internally assembled source object.
The same canonical-one boundary now has a charted Hodge/family-hull Step (xi)
variant,
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeArakelovCanonicalOneT11IPLConstruction}\\
\quad\texttt{ChartedFamilyHullFiniteDivisorVerticalIQ},
\end{array}
\]
with audit companion ending in
\[
\begin{array}{l}
\texttt{ChartedFamilyHullFiniteDivisorVerticalIQ\_withMilestoneAudit}.
\end{array}
\]
Its experiment-surface suffixes are
\[
\begin{array}{l}
\texttt{hodgeArakelovCanonicalOneChartedFamilyHull}\\
\quad\texttt{IPLConstructionCTheta},\\
\texttt{hodgeArakelovCanonicalOneChartedFamilyHull}\\
\quad\texttt{IPLConstructionMilestoneAudit}.
\end{array}
\]
These endpoints no longer receive the constructor-built Step (xi) hull source
directly: they project it from the possible-image charted Hodge-calibrated
family-hull obligations-backed source before assembling the finite-divisor
vertical-\(IQ\) corridor.
The canonical-one boundary now also has a synchronized possible-image
summand/family-hull refinement,
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeArakelovCanonicalOneT11IPLConstruction}\\
\quad\texttt{SynchronizedPossibleImageSummandFamilyHull}\\
\quad\texttt{FiniteDivisorVerticalIQ}.
\end{array}
\]
The experiment surface exposes this as
\[
\begin{array}{l}
\texttt{hodgeArakelovCanonicalOneSynchronizedPossibleImage}\\
\quad\texttt{SummandFamilyHullIPLConstructionCTheta}.
\end{array}
\]
Its no-\(C_\Theta\) audit companion is
\[
\begin{array}{l}
\texttt{boundaryEndpoint\_from}\\
\quad\texttt{\_sourceDerivedHodgeArakelovCanonicalOneT11IPLConstruction}\\
\quad\texttt{SynchronizedPossibleImageSummandFamilyHull}\\
\quad\texttt{FiniteDivisorVerticalIQ\_withQComparisonAudit},
\end{array}
\]
with experiment suffix
\[
\begin{array}{l}
\texttt{hodgeArakelovCanonicalOneSynchronizedPossibleImage}\\
\quad\texttt{SummandFamilyHullIPLConstructionBoundaryAudit}.
\end{array}
\]
Here the Hodge source and target evaluations are bundled into the synchronized
Hodge--Arakelov source object, while the Step (xi) input still remembers the
Theorem 3.11 possible-image q-choice and the determinant summand calibration.
The audit companion exposes the summand/family-hull q-comparison audit and the
finite-divisor packet and vertical-\(IQ\) target equalities before the numeric
\(C_\Theta\) estimate is supplied.  Thus this public endpoint sits one stage
upstream of the charted family-hull variant before projecting to the already
verified finite-divisor corridor.
The corresponding milestone \(C_\Theta\) audit now also carries the
remaining-payload route audit, the theta-evaluation audit, the factored
\(\SHE\) audit, and the constructed \(\IPL\) audit as fields, so the final
canonical-one constructed-\(\IPL\) review target keeps the
theta-root/Hodge--Arakelov Gaussian, factored Hodge/\(\SHE\), constructed
\(\IPL\), direct Gaussian-to-Step (xi), Ob1/Ob2 hull absorption, Ob3/Ob4
determinant, Ob5 compatibility, finite Step (x), vertical-\(IQ\), and Step (xi)
source-paper payload ledgers together.
At the same canonical-one boundary, the finite Hodge/\(\SHE/\IPL\) middle
layer is now constructed directly from the route's source-calibrated and
target Hodge--Arakelov evaluations plus canonical \(1\)-label preservation.
The new Hodge/\(\SHE/\IPL\) audit records that direct finite transport-source
endpoint, the constructed \(\IPL\) log-volume endpoint, and the
finite-transport log-volume provenance before the route is projected through
the theta-monoid-matched corridor.  This keeps the history-separated forgetting
permission and transported-average preservation visible at the canonical-one
source surface.
The same route now also carries a direct Gaussian-to-Step (xi) bridge audit:
starting from the route-owned source-calibrated Hodge--Arakelov theta
evaluation, target evaluation, canonical \(1\)-label preservation, and
constructed \(\IPL\) source, it projects the constructor-built possible-image
hull source to the side-conditioned obligations-backed source consumed by the
source-calibrated Step (xi) bridge audit.  This records the theta-root/Gaussian
payload, constructed finite Hodge/\(\SHE/\IPL\) transport, hull containment,
record-canonical bridge, determinant bound, side conditions, and
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) at the canonical-one
milestone surface.
The canonical-one constructed-\(\IPL\) route now also has a separate
Step (x) packet/vertical-\(IQ\) audit before the compact finite-boundary
ledger.  This audit is projected through the named finite-divisor
packet-local source endpoint and the exact vertical-\(IQ\) target endpoint, so
the packet-local equalities, upper-semi inequality, packet-normalized target
equalities, and target \((\Ind3)\) equality are visible as source-endpoint
facts in the milestone audit rather than only as loose components of the final
boundary tuple.
These pieces are now joined in two stages.  The smaller direct finite-boundary
audit projects the raw comparison from the source-calibrated
Gaussian-to-Step (xi) bridge and the finite packet/vertical-\(IQ\) facts from
the packet/target audit.  The larger
\texttt{CanonicalOneConstructorBuiltIPLConstructionDirectRouteFiniteBoundaryAudit}
then carries the direct middle route, source-derived bridge, route-log-volume
alignment, Step (xi) hull/determinant audits, side conditions, raw
q-comparison, and finite packet/vertical-\(IQ\) target facts together before the
matched compatibility boundary is used.  The older compact matched boundary is
still retained for compatibility with the existing \(C_\Theta\) route, but the
no-\(C_\Theta\) review surface now has a direct source-derived boundary for the
same canonical-one constructed-\(\IPL\) source object.
The constructor-built bundled route can now also be reached from the stronger
theta-monoid-matched obligations-backed record-canonical exact corridor.  The
projection constructs the bundled route internally from the matched
Hodge/\(\IPL\) source, the measured determinant family, the selected possible
image, the finite-divisor source, and the exact vertical-\(IQ\) source.  In
particular, the hull/determinant bridge equality, q-positivity, and
normalization are first projected from the constructor-obligations object and
then used to build the constructor-built Step (xi) source.  The experiment
surface exposes this review target through three suffixes:
\[
\begin{array}{l}
\texttt{MatchedObligationsConstructorBuiltFullRouteAudit},\\
\texttt{MatchedObligationsConstructorBuiltRemainingPayloadRouteAudit},\\
\texttt{MatchedObligationsConstructorBuiltBoundaryAudit},\\
\texttt{MatchedObligationsConstructorBuiltCThetaAudit}.
\end{array}
\]
The remaining-payload variant keeps the obligations-to-record-canonical
Step (xi) bridge together with the constructor-built Step (xi) payload ledger,
so this intermediate corridor now reports the same unresolved
hull/determinant source-paper payload that was previously visible only on the
lower constructor-built route.
The same obligations-backed record-canonical corridor is now also reachable
from the earlier constructor-backed matched exact source.  This projection sets
the corridor's constructor-obligations object to
\texttt{toHullDetSourceConstructor.toHullDetObligations}; consequently the
obligations bridge equality with the record-canonical hull/tensor-power bridge
is definitional at this boundary.  The new review target therefore starts from
constructor-backed Step (xi) data, projects to the obligations-backed
record-canonical corridor, and only then uses the constructor-built
finite-divisor route.  The experiment surface exposes this as:
\[
\begin{array}{l}
\texttt{MatchedConstructorBackedObligationsCorridorAudit},\\
\texttt{MatchedConstructorBackedObligationsRemainingPayloadCorridorAudit},\\
\texttt{MatchedConstructorBackedObligationsBoundaryAudit},\\
\texttt{MatchedConstructorBackedObligationsCThetaAudit}.
\end{array}
\]
The remaining-payload corridor threads the same constructor-built payload
ledger through this projection, so the constructor-backed exact source no
longer hides the unresolved Step (xi) hull operation, determinant source,
bridge, positivity, and normalization payload behind the full-route audit.
There is now a side-conditioned variant of this matched constructor-backed
exact source as well.  Its Step (xi) field is a
\texttt{SideConditionedConstructorBacked} source, so q-pilot positivity and
source normalization are projected from one
\texttt{IUTStage1SourceSideConditions} object before the constructor-backed
source is projected to the obligations-backed record-canonical corridor and the
constructor-built finite-divisor route.  The Hodge/SHE/\(\IPL\) middle layer is
also exposed separately by
\texttt{MatchedSideConditionedHodgeSHEIPLAudit}: this audit records the
theta-monoid degree match and then projects the theta-root evaluation,
factored SHE preservation, history-separated finite Hodge/SHE transport,
constructed \(\IPL\) link, and finite-transport log-volume provenance from the
target-charted Hodge--Arakelov/\(\IPL\) construction source.  The experiment
surface exposes this boundary as:
\[
\begin{array}{l}
\texttt{MatchedSideConditionedHodgeSHEIPLAudit},\\
\texttt{MatchedSideConditionedConstructorBackedObligationsCorridorAudit},\\
\texttt{MatchedSideConditionedConstructorBackedObligationsRemainingPayloadCorridorAudit},\\
\texttt{MatchedSideConditionedConstructorBackedObligationsBoundaryAudit},\\
\texttt{MatchedSideConditionedConstructorBackedObligationsCThetaAudit}.
\end{array}
\]
The same strongest side-conditioned corridor is now exposed under the compact
source-derived milestone names
\[
\begin{array}{l}
\texttt{sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ\_}\\
\quad\texttt{boundaryEndpointWithMatchedSideConditionedConstructorBackedObligationsAudit},\\
\texttt{sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ\_}\\
\quad\texttt{cThetaDichotomyWithMatchedSideConditionedConstructorBackedObligationsAudit}.
\end{array}
\]
These are review-surface aliases rather than new mathematical assumptions:
they return the existing side-conditioned Hodge/SHE/\(\IPL\) audit, the named
side-conditioned Step (xi) hull/determinant audit, and the projected
constructor-backed obligations corridor under the milestone endpoint name.
The matched-obligations conditional endpoint remains exposed under the explicit
audit name
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\quad\texttt{\_sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQ}\\
\quad\texttt{\_withMatchedSideConditionedConstructorBackedObligationsAudit}.
\end{array}
\]
The compact theorem name without this suffix is now reserved for the
constructed-\(\IPL\) constructor-built route described above.  The matched audit
variant uses the strongest side-conditioned constructor-backed corridor, keeps
the numeric \(C_\Theta\) estimate explicit, and returns the same matched
Hodge/SHE/\(\IPL\) and Step (xi) audit package as the longer descriptive theorem.
It now also has a matched side-conditioned remaining-boundary ledger,
\texttt{MatchedSideConditionedConstructorBackedRemainingSourceBoundaryAudit},
exposed on the experiment surface with suffix
\[
\begin{array}{l}
\texttt{matchedSideConditionedConstructorBacked}\\
\quad\texttt{RemainingBoundaryAudit}.
\end{array}
\]
This ledger is the strongest current review target for what is still public at
the source-paper boundary: the matched Hodge--Arakelov/\(\IPL\) source, the
side-conditioned constructor-backed Step (xi) source, the upper-semi
finite-divisor Step (x) source, and the exact vertical-\(IQ\) source.
It now also carries the projected constructor-backed remaining-payload
corridor audit, so the route-level remaining-source ledger explicitly includes
the constructor-built Step (xi) payload audit rather than only the older full
obligations corridor and assembled remaining-boundary ledger.
The matched side-conditioned Hodge/\(\SHE/\IPL\) audit now also carries the
choice-wise input-prime-strip links directly.  The experiment endpoint with
suffix \texttt{matchedSideConditionedConstructedIPLChoiceLinkEndpoint} exposes
that, for every possible output choice, the constructed \(\IPL\) link has
source equal to the route input prime strip and target equal to the
choice-indexed output prime strip, before the Step (xi) hull/determinant source
or exact vertical-\(IQ\) boundary is used.
The constructor-backed Step (xi) audit has likewise been strengthened: it now
records q-pilot containment in the Theorem~3.11 possible-image union, inclusion
of that union in the holomorphic hull, the bounded-family determinant/log-volume
equalities, the tensor-power bound, the record-canonical hull/tensor bridge, and
the raw signed comparison as one source-facing skeleton.  The experiment suffix
\texttt{stepXIHolomorphicHullDeterminantEndpoint} exposes this skeleton before
the finite-divisor vertical-\(IQ\) projection.
The same skeleton is now carried by the strongest matched side-conditioned
finite-exact source ledger itself, via
\texttt{MatchedSideConditionedStepXIHolomorphicHullDeterminantSkeleton}; the
experiment suffix
\texttt{matchedSideConditionedStepXIHolomorphicHullDeterminantSkeleton} exposes
it from the bundled source object that also contains the matched
Hodge/\(\SHE/\IPL\), finite-divisor, and exact vertical-\(IQ\) data.
The no-\(C_\Theta\) and conditional \(C_\Theta\) milestone endpoints now also
have remaining-boundary variants,
\texttt{MatchedSideConditionedConstructorBackedRemainingBoundaryAudit} and
\texttt{MatchedSideConditionedConstructorBackedRemainingCThetaAudit}.  These
variants return the projected obligations boundary together with the
remaining-source ledger, so the public endpoint no longer drops the Step (xi)
holomorphic-hull/determinant skeleton when it reaches the boundary or
\(C_\Theta\) audit surface.

The synchronized possible-image summand finite-divisor boundary now has a
Step (xi) log-volume-chain audit endpoint as well.  The new source declaration
with suffix \texttt{withStepXILogVolumeChainAudit} refines the no-\(C_\Theta\)
q-comparison boundary by retaining the finite Step (x) packet and
vertical-\(IQ\) equalities together with the summand-calibrated chain
\[
  \mu_{\log}(q\mathrm{Region})
    \leq \det_{\log}
    \leq \theta_{\mathrm{signed}} .
\]
This gives a sharper review surface for the current 3.11-to-3.12 corridor:
the source-derived Step (xi) hull/determinant comparison and the finite
Step (x) boundary are visible before the separate numerical
\(C_\Theta\)-estimate is supplied.

The constructor-built possible-image Step (xi) source can now also be
constructed directly from an Ob3/Ob4 adjusted determinant package.  The new
constructor
\texttt{ofOb3Ob4AdjustedDeterminantSource} takes the localization summands,
structure-sheaf subtraction, and positive tensor-power data, projects the
weighted determinant internally, and returns the existing constructor-built
Ob3/Ob4 audit for the resulting possible-image hull source.  Its experiment
endpoint exposes the raw adjusted-localization identities, the weighted
determinant summation, tensor-power normalization, and the
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison.  Thus another
piece of the Step (xi) determinant payload has moved from an already-weighted
determinant input to a source-facing Remark 3.9.5(vii) Ob3/Ob4 construction.

There is now also a minimal-hull-system variant of this constructor,
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource}\\
\quad\texttt{\_ofRemark395HullSystemOb3Ob4AdjustedDeterminantSource}\\
\quad\texttt{\_endpoint}.
\end{array}
\]
This route starts from the intersection-defined
\texttt{IUTStage1Remark395HolomorphicHullSystem}, projects the older
hull/log-volume shadow internally, and identifies the resulting Step~(xi)
hull with
\[
  \phi\bigl(\bigcup_i P_i\bigr)
\]
for the Theorem~3.11 possible-image family.  The endpoint proves that this
object is a source-paper hull, that the chosen q-region is contained in it,
and then returns the same Ob3/Ob4 determinant audit, bridge-inequality audit,
and raw signed comparison.  Thus this constructor form no longer treats the
holomorphic-hull shadow as a supplied Step~(xi) payload.

The constructor-built possible-image route has now been refined one step
further to the product-hull formulation of Remark~3.9.5(i)--(ii).  The new
source constructor
\[
\begin{array}{l}
\texttt{ofRemark395ProductHullSystem}\\
\quad\texttt{Ob3Ob4AdjustedDeterminantSource}
\end{array}
\]
starts from an \texttt{IUTStage1Remark395ProductHullSystemSource}: a family of
product hulls, a parameter selecting the intersection of all product hulls
containing a region, and the corresponding log-volume calibration.  The
endpoint proves that the Step~(xi) hull attached to
\(\bigcup_i P_i\) is exactly the product hull selected by this intersection
parameter, that the chosen q-region is contained in it, and that it is minimal
among product hulls containing \(\bigcup_i P_i\).  It then returns the same
constructor-built Ob3/Ob4 determinant audit, bridge-inequality audit, and raw
signed comparison.  Thus the corridor now reaches the source-paper
``smallest product hull'' formulation before projecting to the older
holomorphic-hull shadow.
This product-hull provenance is now also available for any already constructed
possible-image Step~(xi) source whose hull/log-volume shadow is induced by a
product-hull system:
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource}\\
\quad\texttt{\_productHullBackedConstructorBuiltAudit}.
\end{array}
\]
At the product-hull-backed finite-divisor boundary, the Ob5 quotient passage now
also has a scalar quotient compatibility audit:
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_ob5ScalarQuotientCompatibilityAudit}.
\end{array}
\]
This theorem applies the same upper-semi quotient formalism to the real scalar
\(\mu_{\log}(\phi(P_B))\): the singleton images of
\(\det_{\log}^{\mathrm{norm}}\), \(\det_{\log}\), the normalized
\(\det^{\otimes M}\) tensor-power scalar, and the family-hull log-volume all
collapse to the distinguished quotient point, and hence have the same quotient
image.  Thus the product-hull route now records the compatibility with
\(\det^{\otimes M}(\phi(P_B))\) and \(\mu_{\log}(\phi(P_B))\) that
Remark~3.9.5(Ob5) states alongside the bounded-family hull quotient.
The audit identifies the source's canonical hull of
\(\bigcup_i P_i\) with the selected smallest product hull, proves containment
of both \(\bigcup_i P_i\) and the q-pilot possible image in that hull, records
minimality and product-hull log-volume, and keeps the record-canonical
Step~(xi) and bridge-inequality audits attached.  The synchronized
target-charted possible-image summand/family-hull source has a corresponding
wrapper,
\[
\begin{array}{l}
\texttt{synchronizedTargetChartedPossibleImageSummand}\\
\quad\texttt{HodgeFamilyHull\_productHullConstructorBuiltAudit},
\end{array}
\]
which threads this product-hull audit through the Hodge--Arakelov chart,
finite summand equality, exact theta/family-hull equality, and obligations-backed
constructor reduction.  Thus the strongest Hodge/summand Step~(xi) source can
now be reviewed together with the Remark~3.9.5 product-hull boundary, instead
of reserving product-hull provenance only for the later finite-divisor wrapper.

The same constructor-built source now exposes the Step (xi) bridge inequality
as a named audit
\texttt{ConstructorBuiltStepXIBridgeInequalityAudit}.  This audit records the
selected q-pilot log-volume, the normalized determinant/tensor-power
log-volume, and the package theta scalar in the direct chain
\[
  \mu_{\log}(q\mathrm{Region})
    \leq \det_{\mathrm{norm}}
    \leq \theta_{\mathrm{signed}} .
\]
The first inequality is derived from the upper-ray/hull absorption audit and
the Ob3-3 determinant compatibility; the second is the Ob4 normalized
tensor-power bound.  The experiment surface exposes this as
\texttt{possibleImageConstructorBuiltHullSource\_bridgeInequalityAudit}, and
the Ob3/Ob4-adjusted constructor endpoint now returns this bridge audit next
to the determinant audit.

There is also an exact-theta constructor-built variant of the adjusted-summand
route,
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{\_toPossibleImageConstructorBuiltHolomorphicHullDeterminantSource}\\
\quad\texttt{OfThetaEqFamilyHullLogVolume\_endpoint}.
\end{array}
\]
Here the constructor no longer accepts the Ob4 tensor-power bound as a free
input.  It starts from the finite Ob3-3 summand identity, derives the record
Ob3/Ob5 family-hull determinant source, assumes the source-facing exact-theta
calibration
\[
  \theta_{\mathrm{signed}}
    = \mu_{\log}\!\left(\phi\!\left(\bigcup_i P_i\right)\right),
\]
and then obtains
\[
  \det_{\mathrm{norm}}\leq \theta_{\mathrm{signed}}
\]
from the bounded-family theorem
\texttt{tensorPower\_bound\_of\_theta\_eq\_familyHullLogVolume}.  The package
bridge equality is still an explicit Step~(xi) synchronization boundary, but
the numerical Ob4 inequality is now constructed from the Remark~3.9.5
family-hull/log-volume source in this route.

The adjusted-summand source now also exposes the intermediate bridge itself,
before assembling the final constructed Step~(xi) object.  The generic source
constructor
\[
\begin{array}{l}
\texttt{IUTStage1Remark395HullDeterminantBridgeSource}\\
\quad\texttt{.ofAdjustedDeterminantLogVolumeSource}
\end{array}
\]
starts from the finite Ob3--3 identity
\[
  \mu_{\log}(\phi(\bigcup_i P_i))
    = \sum_\beta \operatorname{AdjLoc}_\beta ,
\]
derives the Ob3/Ob5 determinant compatibility, and then proves the bridge
chain
\[
  \mu_{\log}(q\mathrm{Region})
    \leq
  \det_{\mathrm{norm}}
    =
  \det_{\log}
    \leq \theta_{\mathrm{signed}} .
\]
The record-canonical companion
\texttt{toRecordHullDeterminantBridgeSource} fixes the family to the
Theorem~3.11 possible images, while the normalized experiment endpoints
\[
\begin{array}{l}
\texttt{remark395HullDeterminantBridgeSource\_normalizedBridge},\\
\texttt{remark395RecordHullDeterminantBridgeSource\_normalizedBridge}
\end{array}
\]
make the direct \(\det_{\mathrm{norm}}\)-bridge reviewable without unpacking
the longer endpoint.  The experiment endpoint
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{\_toRecordHullDeterminantBridgeSource\_endpoint}
\end{array}
\]
makes this bridge-level derivation reviewable without unfolding the later
constructed-source route.
The named finite-divisor milestone theorem
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta}\\
\quad\texttt{\_from\_remark395ConstructedHullDeterminant}\\
\quad\texttt{FiniteDivisorVerticalIQ}
\end{array}
\]
now also has the audited companion with suffix
\[
\texttt{\_withRecordBridgeAudit}.
\]
This companion returns the constructed record-canonical Remark~3.9.5 bridge
audit together with the final conditional \(C_\Theta\) dichotomy, so the public
milestone name exposes the chain
\[
  \mu_{\log}(q\mathrm{Region})\leq \det_{\log}\leq
  \theta_{\mathrm{signed}}
\]
beside the finite-divisor vertical-\(IQ\) conclusion.

There is now also an exact-theta bridge-level variant with suffix
\[
\begin{array}{l}
\texttt{toRecordHullDeterminantBridgeSource}\\
\quad\texttt{OfThetaEqFamilyHullLogVolume}
\end{array}
\]
and experiment endpoint
\[
\begin{array}{l}
\texttt{remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{\_toRecordHullDeterminantBridgeSource}\\
\quad\texttt{OfThetaEqFamilyHullLogVolume\_endpoint}.
\end{array}
\]
This version no longer takes the Ob4 tensor-power bound as an argument at the
bridge surface.  The generic bounded-family theorem
\texttt{IUTStage1BoundedFamilyHullDetLogVolumeSource}\\
\texttt{.tensorPower\_bound\_of\_theta\_eq\_familyHullLogVolume}
derives the bound from
\[
  \theta_{\mathrm{signed}}
    = \mu_{\log}(\phi(\bigcup_i P_i)),
\]
after the adjusted-summand source has already produced the Ob3/Ob5
determinant equality.  Thus the intermediate bridge now has both forms: an
ordinary form with an explicit Ob4 bound, and an exact-theta form in which that
bound is constructed from the family-hull calibration.

The same exact-theta constructor-built route now has an obligations-backed
form, with suffix
\[
\texttt{OfThetaEqFamilyHullLogVolumeFromObligations\_endpoint}.
\]
This version consumes an \texttt{IUTStage1SourceHullDetObligations} object and
a single synchronization statement identifying its hull/determinant bridge
datum with the record-canonical Step~(xi) construction.  Lean then derives the
package bridge equality from
\texttt{hullDetData.hullDetBridge\_eq\_bridgeData}, and reads q-pilot
positivity and source normalization from the same obligations object.  Thus,
at this constructor-built boundary, the remaining supplied Step~(xi) data has
been narrowed from four separate fields---tensor-power bound, bridge equality,
q-positivity, and normalization---to the family-hull exact-theta calibration
plus one obligations-backed record-canonical bridge synchronization.

The exact-theta adjusted-summand route has now also been tied to the local
canonical \(C_\Theta\)-scale audit.  The source declaration
\[
\begin{array}{l}
\texttt{IUTStage1Remark395RecordOb3Ob5AdjustedDeterminantLogVolumeSource}\\
\quad\texttt{.toPossibleImageConstructorBuiltHolomorphicHullDeterminantSource}\\
\quad\texttt{OfThetaEqFamilyHullLogVolume\_canonicalCThetaBridgeAudit}
\end{array}
\]
returns the constructor-built Remark~3.9.5 canonical-scale bridge audit
together with the reviewable chain
\[
  \mu_{\log}(q\mathrm{Region})
    \leq \det_{\mathrm{norm}}
    \leq \theta_{\mathrm{signed}}
    \leq C_{\Theta,\mathrm{can}}\cdot(-q_{\mathrm{signed}}).
\]
Its obligations-backed companion, with suffix
\[
\texttt{OfThetaEqFamilyHullLogVolumeFromObligations\_canonicalCThetaBridgeAudit},
\]
adds the facts that the package hull/determinant bridge is the obligations
bridge datum, \(0<-q_{\mathrm{signed}}\), and source normalization, all
projected from the same obligations object.  Thus the no-external-numeric-bound
local scale is now attached directly to the finite adjusted-summand
Ob3/Ob5, exact-theta Ob4, possible-image \(q\)-choice constructor, rather than
only to the later constructed-source wrapper.

This canonical-scale bridge has now been lifted to the target-charted,
measure-calibrated adjusted-summand sources as well.  The audit
\[
\begin{array}{l}
\texttt{targetChartedHodgeMeasureCalibratedAdjustedPossibleImage}\\
\quad\texttt{HullDetObligationsBackedSource\_canonicalCThetaBridgeAudit}
\end{array}
\]
projects the same lower constructor-built Remark~3.9.5 canonical-scale audit
from the obligations-backed adjusted exact-theta source.  Its constructor-backed
companion
\[
\begin{array}{l}
\texttt{targetChartedHodgeConstructorBackedMeasureCalibrated}\\
\quad\texttt{AdjustedPossibleImageHullDetSource\_canonicalCThetaBridgeAudit}
\end{array}
\]
does the same after replacing the obligations bridge by the Theorem~3.11
record-canonical hull/tensor-power constructor.  Thus the charted Hodge
calibration, finite Ob3--3 adjusted summands, measured family hull, possible
image \(q\)-choice, and local no-external-bound \(C_{\Theta,\mathrm{can}}\)
chain now occur in one reviewable audit path.

There is now a named obligations-backed audit for the target-charted,
measure-calibrated adjusted-summand possible-image source:
\[
\begin{array}{l}
\texttt{targetChartedHodgeMeasureCalibratedAdjustedPossibleImage}\\
\quad\texttt{HullDetObligationsBackedSource\_adjustedExactTheta}\\
\quad\texttt{StepXIAudit}.
\end{array}
\]
This audit records the exact-theta source before passing to the
constructor-backed form.  The q-region is the chosen Theorem~3.11 possible
image, the package measure is projected from the measured family hull, the
transported target theta chart is calibrated to the Hodge--Arakelov
theta-monoid degree, that degree is identified with the finite Ob3--3 adjusted
summand sum, and the record family-hull/determinant source yields
\[
  \theta_{\mathrm{signed}}
    =
  \mu_{\log}\!\left(\phi\!\left(\bigcup_i P_i\right)\right).
\]
The same audit keeps the obligations-backed hull/determinant bridge,
q-positivity, source normalization, and the raw
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison visible in one
source-boundary object.

The constructor-backed adjusted-summand source now has a companion audit,
\[
\begin{array}{l}
\texttt{targetChartedHodgeConstructorBackedMeasureCalibrated}\\
\quad\texttt{AdjustedPossibleImageHullDetSource\_adjustedExactTheta}\\
\quad\texttt{StepXIAudit}.
\end{array}
\]
It carries the same target-charted Hodge and Ob3--3 summand provenance for
\(\theta_{\mathrm{signed}}
  =\mu_{\log}(\phi(\bigcup_iP_i))\), but replaces the obligations-backed
bridge boundary by the hull/determinant obligations constructed from the
Theorem~3.11 record-canonical hull/tensor-power constructor.  Thus the
constructor-backed review surface no longer loses the source of the
exact-theta equality when it records the constructed bridge, q-positivity,
normalization, and raw signed comparison.

The same constructor-backed exact-theta source now projects directly into the
current finite-divisor milestone source:
\[
\begin{array}{l}
\texttt{targetChartedHodgeConstructorBackedMeasureCalibrated}\\
\quad\texttt{AdjustedPossibleImageHullDetSource}\\
\quad\texttt{\_toRemark395ConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQSource}.
\end{array}
\]
The projection fills the finite-divisor source's
\(\theta_{\mathrm{signed}}
  =\mu_{\log}(\phi(\bigcup_iP_i))\)
field from the already audited Hodge theta-monoid and finite adjusted
determinant summand chain, rather than accepting this equality again as a
bare boundary input.  Its companion audit
\[
\begin{array}{l}
\texttt{targetChartedHodgeConstructorBackedMeasureCalibrated}\\
\quad\texttt{AdjustedPossibleImageHullDetSource}\\
\quad\texttt{\_toRemark395ConstructorBackedConstructedExactTheta}\\
\quad\texttt{FiniteDivisorAudit}
\end{array}
\]
keeps, in one object, the target-charted theta equality, the theta-monoid
degree equality with the adjusted summand sum, the Ob3/Ob5
summand-to-determinant identities, and the constructed finite-divisor
record-bridge audit proving the raw
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison.  This is the
current Lean bridge from the exact-theta Ob3/Ob5 implementation into the
strongest constructor-backed finite-divisor corridor.

This exact-theta bridge now propagates one level further into the Ob5
product-hull hierarchy.  The new internal constructors
\[
\begin{array}{l}
\texttt{toProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQSource},\\
\texttt{toPrincipalProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQSource},\\
\texttt{toPrincipalValuationBallBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQSource}
\end{array}
\]
start from the same target-charted exact-theta adjusted-summand source.  They
then add, respectively, the Remark~3.9.5 product hull, the principal
\(\lambda\mathcal O\) hull, and the valuation-ball direct-product cover
identification.  Their experiment-surface audits
\[
\begin{array}{l}
\texttt{\_productHullBackedExactThetaFiniteDivisorAudit},\\
\texttt{\_principalProductHullBackedExactThetaFiniteDivisorAudit},\\
\texttt{\_principalValuationBallBackedExactThetaFiniteDivisorAudit}
\end{array}
\]
retain the Hodge theta-monoid/adjusted-summand equality while exposing the
product-hull containment audit, the principal scalar-multiple hull identity,
or the valuation-ball direct-product and calibrated-cell log-volume identities.
Thus the product/principal/Haar corridor can now be reviewed as an extension
of the exact-theta Step~(xi) source rather than as a separate supplied
constructor-backed payload.
The principal valuation-ball projection has a tighter source-core variant as
well.  The named theorem
\[
\begin{array}{l}
\texttt{adjustedSource\_eq\_valuationBall}\\
\quad\texttt{\_ofValuationBallRecordSource}
\end{array}
\]
derives the equality between the exact-theta measured adjusted source and the
principal valuation-ball Ob3/Ob5 source from two narrower inputs: the
valuation-ball possible-image family is synchronized with the Theorem~3.11
record family, and the measured adjusted source is the record-canonical source
constructed from that valuation-ball cover.  The companion constructor and
audit,
\[
\begin{array}{l}
\texttt{toPrincipalValuationBallBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQSource}\\
\quad\texttt{OfValuationBallRecordSource},\\
\texttt{toPrincipalValuationBallBackedExactThetaFiniteDivisorAudit}\\
\quad\texttt{OfValuationBallRecordSource},\\
\texttt{\_principalValuationBallBackedExactThetaFiniteDivisorAudit}\\
\quad\texttt{OfValuationBallRecordSource},
\end{array}
\]
therefore no longer require the valuation-ball source-core equality as a
standalone payload at this boundary.

The exact-theta source now reaches the final product-hull and principal
valuation-ball dichotomy endpoints, not only the intermediate audits.  The
new experiment-surface wrappers
\[
\begin{array}{l}
\texttt{\_productHullBackedCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithOb5Ob6Ob7SynchronizedAuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource},\\
\texttt{\_principalValuationBallCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource},\\
\texttt{\_principalValuationBallCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
take the target-charted exact-theta adjusted-summand source, construct the
product-hull-backed or principal valuation-ball-backed finite-divisor source
internally, and then invoke the strongest current finite product-formula Ob7
route.  Consequently the returned \(C_\Theta\) dichotomy now carries the
exact-theta Step~(xi) provenance through the Remark~3.9.5 product-hull,
principal \(\lambda\mathcal O\), valuation-ball topology/Haar, Ob5 quotient,
Ob6 approximant, and Ob7 log-Kummer/product-formula layers.
The record-canonical valuation-ball variant derives the principal
valuation-ball source-core synchronization from the same possible-image
family equality with the Theorem~3.11 record and the equality with the
record-canonical valuation-ball adjusted source before invoking this final
topology/Haar \(C_\Theta\) endpoint.

The exact-theta route has also been pushed through the projected-factorwise
local log-coordinate refinement.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinateProjectedFactorwiseTargetTransportSource},\\
\texttt{\_toValuationUnitBallNonzeroScalar}\\
\quad\texttt{LocalLogCoordinateProjectedFactorwiseTargetTransportSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
builds the projected-factorwise transport source from the target-charted
Step~(xi) source by first constructing the principal valuation-ball
finite-divisor source and then attaching the literal dependent-product local
factor data.  The record-canonical variant derives the principal valuation-ball
source-core equality from the Theorem~3.11 possible-image synchronization and
the record-canonical valuation-ball adjusted source before adding these local
coordinate factors.  The corresponding final wrappers
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarProjectedFactorwise}\\
\quad\texttt{CanonicalCThetaScaleDichotomyWithTopologyFiniteExtensionHaar}\\
\quad\texttt{Ob5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource},\\
\texttt{\_valuationUnitBallNonzeroScalarProjectedFactorwise}\\
\quad\texttt{CanonicalCThetaScaleDichotomyWithTopologyFiniteExtensionHaar}\\
\quad\texttt{Ob5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
returns the target-point transport audit together with the principal
topology/Haar Ob5--Ob7 audit and the canonical-scale dichotomy.  Thus the
current strongest endpoint carries, simultaneously, exact-theta Step~(xi)
provenance, explicit product-index/valuation-place transport, local
\(\lambda_vO_v\) scalar-image regions, valuation-unit-ball provenance, and
finite product-formula Ob7 provenance.

The same exact-theta final route now has a valuation-log-image form.  The
constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarValuationLogImage}\\
\quad\texttt{ProjectedFactorwiseTargetTransportSource},\\
\texttt{\_toValuationUnitBallNonzeroScalarValuationLogImage}\\
\quad\texttt{ProjectedFactorwiseTargetTransportSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
builds the projected-factorwise source from the target-charted Step~(xi)
source while defining the local coordinate regions as \(\ell_v(O_v)\) and
\(\ell_v(\lambda_vO_v)\).  The record-canonical version derives the principal
valuation-ball source-core equality from the Theorem~3.11 possible-image
family synchronization and the record-canonical valuation-ball adjusted source.
The corresponding final wrappers with suffix
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarValuationLogImage}\\
\quad\texttt{ProjectedFactorwiseCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource},\\
\texttt{\_valuationUnitBallNonzeroScalarValuationLogImage}\\
\quad\texttt{ProjectedFactorwiseCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
returns the same target-point transport audit, principal topology/Haar
Ob5--Ob7 audit, and canonical-scale dichotomy, but no longer accepts separate
per-place image-equality hypotheses for the local coordinate regions.  In the
record-canonical variant it also no longer accepts the valuation-ball
source-core equality as an independent input.

The finite-sum target-point form now has the same record-canonical strengthening.
The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarValuationLog}\\
\quad\texttt{FiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
uses the actual point map
\[
  x \longmapsto
    \left\{\mathrm{coord}=\sum_v \ell_v(x_v)\right\}
\]
and asks only for the two transported target-point synchronizations with the
principal local-integer and selected-hull regions.  The valuation-ball
source-core equality is derived from the same record-canonical valuation-ball
source used above.  The corresponding final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarValuationLog}\\
\quad\texttt{FiniteSumTargetPointCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
returns the target-point transport audit, the principal topology/Haar
Ob5--Ob7 audit, and the canonical-scale dichotomy at this lower boundary.
Thus the source-facing route has descended from per-place image regions to the
finite local valuation/log sum as a point-level transport construction, while
keeping the Theorem~3.11 possible-image synchronization as the source of the
principal valuation-ball comparison.

This record-canonical finite-sum endpoint has also been pushed through the
coordinate-place refinement.  The new constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarCoordinatePlace}\\
\quad\texttt{ValuationLogFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
uses the valuation cover's coordinate-place map as an equivalence
\(\delta\simeq\gamma_{\mathrm{local}}\) and derives the older local-index
compatibility from it.  Its final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarCoordinatePlace}\\
\quad\texttt{ValuationLogFiniteSumTargetPointCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
therefore reaches the same target-point transport audit, topology/Haar
Ob5--Ob7 audit, and canonical-scale dichotomy from the source-facing
coordinate/place synchronization rather than from an arbitrary supplied
index/place compatibility.

The same record-canonical route now descends one step further to normalized
Haar log-coordinates.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
replaces the raw local maps \(\ell_v\) by local Haar-log-coordinate sources:
each \(\ell_v(x_v)\) is the normalized Haar log-volume of the source's local
region attached to \(x_v\).  The transported target-point equalities remain the
two synchronizations with the principal local-integer and selected-hull
regions, and the principal valuation-ball source-core equality is still derived
from the record-canonical valuation-ball source.  The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointCanonicalCThetaScaleDichotomy}\\
\quad\texttt{WithTopologyFiniteExtensionHaarOb5Ob6Ob7AuditAtQChoice}\\
\quad\texttt{OfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
therefore reaches the target-point transport audit, topology/Haar Ob5--Ob7
audit, and canonical-scale dichotomy from a source boundary that records the
Haar-log-volume origin of every local valuation/log coordinate.

The compact-open Haar finite-sum layer has now received the same
record-canonical upgrade.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarCompactOpen}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
starts from local compact-open Haar-log-coordinate sources, so every local
region \(U_{v,x_v}\) carries finite-extension topological Haar provenance
before being sent to the target point
\(\{\mathrm{coord}=\sum_v\ell_v(x_v)\}\).  As in the preceding Haar layer,
the transported target-point equalities are checked against the principal
local-integer and selected-hull regions of the constructed valuation-ball
source, while the source-core equality is derived from the record-canonical
valuation-ball adjusted source.  The corresponding final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarCompactOpen}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointCanonicalCThetaScale}\\
\quad\texttt{DichotomyWithTopologyFiniteExtensionHaarOb5Ob6Ob7}\\
\quad\texttt{AuditAtQChoiceOfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
therefore reaches the target-point transport audit, the principal
topology/Haar Ob5--Ob7 audit, and the canonical-scale dichotomy from the
compact-open local Haar boundary, without accepting the valuation-ball
source-core equality as an independent hypothesis at this level.

The centered valuation-ball Haar finite-sum layer now has the same
record-canonical form.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarCenteredValuationBall}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
specializes each compact-open local factor to a centered closed valuation ball
\(\overline B(x_v,r_v)\) in a proper ultrametric local carrier.  The local
source supplies the centered-ball Haar log-coordinate and proves the
compact-open provenance needed by the preceding layer.  The record-canonical
constructor still derives the principal valuation-ball source-core equality
from the valuation-ball adjusted source, so the two transported target-point
equalities are the only remaining local synchronization data at this boundary.
The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarCenteredValuationBall}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointCanonicalCThetaScale}\\
\quad\texttt{DichotomyWithTopologyFiniteExtensionHaarOb5Ob6Ob7}\\
\quad\texttt{AuditAtQChoiceOfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
returns the same target-point transport audit, topology/Haar Ob5--Ob7 audit,
and canonical-scale dichotomy after projecting through the compact-open Haar
finite-sum route.

The valued-field integer centered-ball layer has also been made
record-canonical.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarValuedFieldInteger}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
replaces the abstract proper-ultrametric local carrier by a
nontrivially-normed valued field with its integer-source Haar normalization.
Thus the local centered ball and its compact-open Haar provenance are read
from valued-field integer data before the source projects to the centered-ball
finite-sum corridor.  The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarValuedFieldInteger}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPoint}\\
\quad\texttt{CanonicalCThetaScaleDichotomyWithTopologyFiniteExtension}\\
\quad\texttt{HaarOb5Ob6Ob7AuditAtQChoiceOfCoricThetaMuProductFormula}\\
\quad\texttt{ConstructionSourceOfValuationBallRecordSource}
\end{array}
\]
returns the same target-point transport audit, topology/Haar Ob5--Ob7 audit,
and canonical-scale dichotomy after deriving the valuation-ball source-core
equality from the record-canonical valuation-ball adjusted source.

The concrete \(p\)-adic centered-ball layer now has the same
record-canonical endpoint.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicCenteredValuationBall}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
fixes the local factor at a valuation place \(v\) to the actual field
\(\mathbb Q_{p_v}\), with the integer ring, residue prime, and Haar
normalization supplied by the \(p\)-adic centered valuation-ball source.  It
still derives the principal valuation-ball source-core equality from the
record-canonical valuation-ball adjusted source, and only retains the two
transported target-point synchronizations with the constructed principal
regions.  The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarPadicCenteredValuationBall}\\
\quad\texttt{HaarLogCoordinateFiniteSumTargetPointCanonicalCThetaScale}\\
\quad\texttt{DichotomyWithTopologyFiniteExtensionHaarOb5Ob6Ob7}\\
\quad\texttt{AuditAtQChoiceOfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
then reaches the target-point transport audit, topology/Haar Ob5--Ob7 audit,
and canonical-scale dichotomy after projecting through the valued-field
integer finite-sum route.

The concrete finite-extension \(p\)-adic centered-ball layer now has the same
record-canonical strengthening.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicFiniteExtension}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
replaces the base local factor \(\mathbb Q_{p_v}\) by an actual
finite-dimensional local extension \(K_v/\mathbb Q_{p_v}\).  The local Haar
coordinate records the finite-extension degree
\(\operatorname{finrank}_{\mathbb Q_{p_v}} K_v\), the residue prime \(p_v\),
and the uniformizer scaling map \(x\mapsto p_v x\) through the algebra map into
\(K_v\).  As in the base \(p\)-adic endpoint, the principal valuation-ball
source-core equality is derived from the record-canonical valuation-ball
adjusted source; the endpoint only retains the two target-point
synchronizations identifying the transported local integer and selected-scalar
images with the constructed principal regions.  The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarPadicFiniteExtension}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPoint}\\
\quad\texttt{CanonicalCThetaScaleDichotomyWithTopologyFiniteExtension}\\
\quad\texttt{HaarOb5Ob6Ob7AuditAtQChoiceOfCoricThetaMuProductFormula}\\
\quad\texttt{ConstructionSourceOfValuationBallRecordSource}
\end{array}
\]
then reaches the same target-point transport audit, topology/Haar Ob5--Ob7
audit, and canonical-scale dichotomy through the finite-extension
valued-field integer projection.

The finite-extension \(p\)-adic endpoint has also been strengthened by
base-prime dilation topology in record-canonical form.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicFiniteExtensionDilation}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPointSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
uses the same record-canonical valuation-ball adjusted source to construct the
principal hull/determinant source, but each local factor now supplies a
homeomorphism-backed Haar source for multiplication by the image of \(p_v\) in
\(K_v\).  Thus the local source carries the finite-extension degree and
residue-prime data of the previous layer together with the open/compact
provenance of the base-prime dilation used by the finite-extension Haar
normalization.  The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarPadicFiniteExtensionDilation}\\
\quad\texttt{CenteredValuationBallHaarLogCoordinateFiniteSumTargetPoint}\\
\quad\texttt{CanonicalCThetaScaleDichotomyWithTopologyFiniteExtension}\\
\quad\texttt{HaarOb5Ob6Ob7AuditAtQChoiceOfCoricThetaMuProductFormula}\\
\quad\texttt{ConstructionSourceOfValuationBallRecordSource}
\end{array}
\]
then projects through the finite-extension layer and returns the same
target-point transport audit, topology/Haar Ob5--Ob7 audit, and canonical-scale
dichotomy.

The same finite-extension local-field boundary now has a record-canonical
constructed dilation-mass refinement.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicFiniteExtensionConstructed}\\
\quad\texttt{DilationMassCenteredValuationBallHaarLogCoordinateFiniteSum}\\
\quad\texttt{TargetPointSourceOfValuationBallRecordSource}
\end{array}
\]
keeps the valuation-ball record source as the origin of the principal
hull/determinant object, while each local factor supplies the constructed
nonzero base-prime dilation and the real-valued Haar scaling law
\[
  \mu_v(p_v S_v)_{\mathbb R}
  =
  \mu_v(S_v)_{\mathbb R}/p_v^{[K_v:\mathbb Q_{p_v}]}
\]
for all local subsets \(S_v\).  The final endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarPadicFiniteExtensionConstructed}\\
\quad\texttt{DilationMassCenteredValuationBallHaarLogCoordinateFiniteSum}\\
\quad\texttt{TargetPointCanonicalCThetaScaleDichotomyWithTopology}\\
\quad\texttt{FiniteExtensionHaarOb5Ob6Ob7AuditAtQChoiceOfCoricThetaMu}\\
\quad\texttt{ProductFormulaConstructionSourceOfValuationBallRecordSource}
\end{array}
\]
therefore exposes the local nonzero scalar facts, pointwise dilation formula,
all-subset Haar mass formula, target-point transport audit, topology/Haar
Ob5--Ob7 audit, and canonical-scale dichotomy in one record-canonical route.

The record-canonical finite-extension boundary has now been lowered one step
further from real-valued mass scaling to the measure-level Haar modulus.  The
new constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicFiniteExtensionConstructed}\\
\quad\texttt{DilationHaarModulusCenteredValuationBallHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointSourceOfValuationBallRecordSource}
\end{array}
\]
uses the same valuation-ball record source for the principal hull/determinant
object, but each local factor now supplies the identity in
\(\mathbb R_{\geq0}\cup\{\infty\}\)
\[
  \mu_v(p_vS_v)
  =
  \operatorname{ofReal}\!\left(p_v^{-[K_v:\mathbb Q_{p_v}]}\right)
  \cdot \mu_v(S_v)
\]
for every subset \(S_v\subseteq K_v\).  The corresponding endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarPadicFiniteExtensionConstructed}\\
\quad\texttt{DilationHaarModulusCenteredValuationBallHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointCanonicalCThetaScaleDichotomyWithTopology}\\
\quad\texttt{FiniteExtensionHaarOb5Ob6Ob7AuditAtQChoiceOfCoricThetaMu}\\
\quad\texttt{ProductFormulaConstructionSourceOfValuationBallRecordSource}
\end{array}
\]
first exposes this all-subset Haar-modulus formula and then projects through
the constructed dilation-mass corridor to the canonical-scale dichotomy.  Thus
the Step~(xi) route now distinguishes the genuine measure identity from its
\(\texttt{toReal}\) mass-shadow at the record-canonical experiment surface.

The same record-canonical route now has the next lower Haar-character
refinement.  The constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicFiniteExtensionConstructed}\\
\quad\texttt{DilationHaarCharacterCenteredValuationBallHaarLogCoordinate}\\
\quad\texttt{FiniteSumTargetPointSourceOfValuationBallRecordSource}
\end{array}
\]
keeps the valuation-ball principal hull/determinant source fixed, but replaces
the local measure identity by the additive Haar-character scalar for
multiplication by \(p_v\):
\[
  \operatorname{addEquivAddHaarChar}(x\mapsto p_vx)
  =
  p_v^{-[K_v:\mathbb Q_{p_v}]} .
\]
The final record-canonical endpoint first exposes this scalar, then the
derived all-subset Haar-modulus formula, and finally the same
canonical-scale dichotomy through the Haar-modulus route.  In this layer the
analytic source datum is therefore the Haar-character evaluation; the
measure-level formula is a derived projection.

The record-canonical local Haar boundary has also been lowered to normalized
valuation-unit-ball mass.  The new constructor
\[
\begin{array}{l}
\texttt{\_toValuationUnitBallNonzeroScalarPadicFiniteExtensionUnitBall}\\
\quad\texttt{HaarCharacterCenteredValuationBallHaarLogCoordinateFiniteSum}\\
\quad\texttt{TargetPointSourceOfValuationBallRecordSource}
\end{array}
\]
retains the same principal valuation-ball hull/determinant source, while each
local factor supplies
\[
  \mu_v(\mathcal O_v)=1,\qquad
  \mu_v(p_v\mathcal O_v)=p_v^{-[K_v:\mathbb Q_{p_v}]} .
\]
The corresponding endpoint exposes these two local mass facts, derives the
additive Haar-character scalar, derives the all-subset Haar-modulus formula,
and then reaches the canonical-scale dichotomy through the Haar-character
route.

The record-canonical surface now also uses the core specialization theorem that
derives the unit-ball Haar-character source from the constructed all-subset
Haar-modulus source.  The new endpoint
\[
\begin{array}{l}
\texttt{\_valuationUnitBallNonzeroScalarPadicFiniteExtensionConstructed}\\
\quad\texttt{DilationHaarModulusDerivedUnitBallHaarCharacterCentered}\\
\quad\texttt{ValuationBallHaarLogCoordinateFiniteSumTargetPointCanonical}\\
\quad\texttt{CThetaScaleDichotomyWithTopologyFiniteExtensionHaarOb5Ob6Ob7}\\
\quad\texttt{AuditAtQChoiceOfCoricThetaMuProductFormulaConstructionSource}\\
\quad\texttt{OfValuationBallRecordSource}
\end{array}
\]
takes the constructed Haar-modulus local source and regularity of the Haar
measure, then derives \(\mu_v(\mathcal O_v)=1\),
\(\mu_v(p_v\mathcal O_v)=p_v^{-[K_v:\mathbb Q_{p_v}]}\), the additive
Haar-character scalar, the all-subset Haar-modulus formula, and the same
canonical-scale dichotomy.  Thus the \(p_v\mathcal O_v\) mass is no longer a
separate record-canonical hypothesis.  The remaining local analytic gap below
this layer is now the source construction of the valuation ring
\(\mathcal O_v\), its normalized Haar mass, Haar regularity, and the
all-subset base-prime Haar-modulus identity from the actual
p-adic/Frobenioid input data.

The milestone-facing constructed source now also factors its log-volume
comparison through the generic record-canonical Remark 3.9.5 bridge source.
The projection \texttt{toRecordHullDeterminantBridgeSource} packages the same
\(\phi\)-hull operator, Theorem 3.11 possible-image family, q-region
containment, Ob3/Ob5 determinant compatibility, and Ob4 tensor-power bound as
the record bridge source.  The new constructed-record bridge audit, exposed on
the experiment surface, records that the constructed source's
q-to-determinant-to-theta chain is read from this generic Remark 3.9.5 bridge
theorem rather than re-proved as an isolated comparison.  This audit now also
has a leaner proof shape: it stores the coarse record-bridge endpoint and
the constructed-source endpoint, while \Lean{} derives the named projection
theorems for q-hull containment, determinant-log comparison, normalized
determinant comparison, and the final \(q_{\mathrm{signed}}\leq
\theta_{\mathrm{signed}}\) comparison.  In particular, the normalized
determinant chain
\[
  \mu_{\log}(q\mathrm{Region})
    \leq
  \det_{\mathrm{norm}}
    \leq
  \theta_{\mathrm{signed}} .
\]
is a theorem projected from the record bridge endpoint, not an additional field
of the audit object.  The experiment surface exposes this two-step normalized
form as
\[
\texttt{remark395ConstructedHolomorphicHullDeterminantSource\_normalizedRecordBridge}.
\]
The public constructor endpoints for the record bridge, the exact-theta bridge,
the constructed source, and the possible-image-choice constructor now include
the same normalized inequalities directly in their returned conjunctions.  Thus
the milestone route displays
\(\mu_{\log}(q\mathrm{Region})\leq\det_{\mathrm{norm}}\leq
\theta_{\mathrm{signed}}\) at the point where the Step~(xi) source is built,
not only after a later audit projection.
The constructor-backed finite-divisor source now exposes the same bridge
projection directly.  Its experiment-surface audit,
\[
\begin{array}{l}
\texttt{remark395ConstructorBackedConstructedHullDeterminant}\\
\quad\texttt{FiniteDivisorVerticalIQ\_recordBridgeAudit},
\end{array}
\]
starts from the constructor-backed adjusted source, constructs the record
Remark~3.9.5 bridge internally, and records
\[
  \mu_{\log}(q\mathrm{Region})
    \leq
  \det_{\mathrm{norm}}
    =
  \det_{\mathrm{log}}
    \leq
  \theta_{\mathrm{signed}}
\]
together with the raw \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\)
comparison projected from the same Theorem~3.11 hull/determinant constructor.
Thus the newest finite-divisor endpoint no longer hides the Step~(xi)
q-to-normalized-determinant-to-theta comparison behind only the constructed
obligations equality; the remaining external input at the \(C_\Theta\)
endpoint is still the global numeric estimate.
The corresponding compact endpoint
\[
\begin{array}{l}
\texttt{remark395ConstructorBackedConstructedOb3Ob5AdjustedHull}\\
\quad\texttt{DeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_cThetaDichotomyWithRecordBridgeAudit}
\end{array}
\]
returns this constructor-backed record bridge audit together with the
finite-divisor vertical-\(IQ\) \(C_\Theta\) dichotomy.  Thus the public
milestone surface now carries the normalized Step~(xi) bridge and the
conditional Corollary~3.12 dichotomy in one theorem.
The finite-divisor constructor-backed source now also has a product-hull-backed
form.  This source records that the measured holomorphic-hull operator used by
the constructed Step~(xi) source is induced by an
\texttt{IUTStage1Remark395ProductHullSystemSource}.  Its audit identifies
\[
  \phi(P_{\mathrm{rec}})
\]
with the selected product hull obtained as the intersection of all product
hulls containing the Theorem~3.11 possible-image union \(P_{\mathrm{rec}}\),
proves \(q\subseteq\phi(P_{\mathrm{rec}})\), proves minimality among such
product hulls, and identifies the hull log-volume with the product-hull
log-volume.  The endpoint
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{Ob3Ob5AdjustedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_cThetaDichotomyWithProductHullAudit}
\end{array}
\]
returns this product-hull audit together with the finite-divisor vertical-\(IQ\)
\(C_\Theta\) dichotomy.  Thus the current finite-divisor milestone no longer
forgets the source-paper ``smallest product hull'' formulation when it enters
the downstream Corollary~3.12 corridor.
The product-hull source now also has a smaller possible-image containment audit,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_possibleImageContainmentAudit}.
\end{array}
\]
This audit separates the Ob1/Ob2 absorption facts from the later Ob5 and
determinant payloads.  It records that the source-facing possible-image family
has union \(P_{\mathrm{rec}}\), that both \(\phi(P_{\mathrm{rec}})\) and the
canonical \(\Phi(P_{\mathrm{rec}})\) approximant are the selected smallest
product hull, and that
\[
  P_{\mathrm{rec}}\subseteq\phi(P_{\mathrm{rec}}),\qquad
  P_i\subseteq\phi(P_{\mathrm{rec}}),\qquad
  q\subseteq P_{\mathrm{rec}}\subseteq\phi(P_{\mathrm{rec}}).
\]
These containments are proved from the product-hull intersection law and the
constructor-backed q-choice possible image; they are no longer hidden inside the
later quotient/determinant audits.
The same finite-divisor surface now has a principal-product-hull refinement.
The source
\[
\begin{array}{l}
\texttt{IUTStage1Remark395PrincipalProductHullBackedConstructorBacked}\\
\quad\texttt{ConstructedHullDeterminantFiniteDivisorVerticalIQSource}
\end{array}
\]
uses a principal \(\lambda\cdot O\) hull system instead of a bare product-hull
system, then forgets to the existing product-hull-backed source.  Its audit
records that the selected hull is the scalar image
\[
  \lambda_{\mathrm{sel}}\cdot O,
\]
that \(\lambda_{\mathrm{sel}}\) satisfies the nonzero-parameter predicate,
that the Theorem~3.11 possible-image union and q-pilot region lie in this
selected principal product hull, and that this selected hull is minimal among
principal product hulls containing the possible-image union.  The public
finite-divisor endpoint
\[
\begin{array}{l}
\texttt{remark395PrincipalProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{Ob3Ob5AdjustedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_cThetaDichotomyWithPrincipalProductHullAudit}
\end{array}
\]
returns this principal-hull audit together with the usual conditional
\(C_\Theta\) dichotomy.  This pushes the product-hull boundary one step closer
to the source-paper formula of Remark~3.9.5(i), where hulls are smallest
regions of the form \(\lambda\cdot O\).
The product-hull-backed source also exposes an Ob5 quotient/determinant audit,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_ob5QuotientDeterminantAudit}.
\end{array}
\]
Given a nonempty q-choice possible image and a nonempty comparison possible
image, this audit proves that both images collapse to the distinguished
upper-semi quotient point modulo the selected product hull and hence have the
same quotient image.  It also identifies
\(\mu_{\log}(\phi(P_{\mathrm{rec}}))\) with the product-hull log-volume, the
normalized determinant, the determinant log-volume, and the normalized
tensor-power log-volume, while retaining the q-pilot log-volume bound into the
selected product hull and the raw
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison.  This is the
first finite-divisor product-hull surface where the source-paper
``smallest product hull'' formulation and the Remark~3.9.5(Ob5)
quotient-compatible determinant formalism are visible in one audit object.
The same Ob5 boundary now has a q-pilot-derived variant:
\[
\begin{array}{l}
\texttt{productHullBackedOb5QuotientDeterminantAudit}\\
\quad\texttt{\_of\_qPilotRegion\_nonempty}.
\end{array}
\]
Here \Lean{} derives nonemptiness of the selected q-choice possible image from
nonemptiness of the q-pilot region and the constructor-backed inclusion
\(q\subseteq P_{q\text{-choice}}\).  Thus the q-side quotient collapse no
longer needs a separate selected-possible-image nonemptiness premise at this
product-hull boundary.
The same source now also has a \(\Phi/\Xi\)-approximant audit,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_phiXiApproximantAudit}.
\end{array}
\]
It constructs the source-facing possible-image family
\(P_B=\{P_\beta\}_{\beta\in B}\) directly from the product-hull system and the
Theorem~3.11 possible-image regions.  \Lean{} proves that the family union is
\(P_{\mathrm{rec}}\), that the canonical hull \(\phi(P_B)\) is the selected
smallest product hull, and that the canonical \(\Phi(P_B)\) approximant is this
same hull.  If an exact \(\Xi(P_B)\) family is supplied, the audit proves
\[
  H_{\Xi(P_B)}=\phi(P_B)
\]
at the selected product-hull boundary, records the exact \(\Xi\)-member
log-volume equality, and proves that \(H_{\Xi(P_B)}\) has the same collapsed
upper-semi quotient image as any nonempty comparison possible image.  This
threads the paper's \(\Phi(P)\), \(\Xi(P)\), and \(H_{\Xi(P)}\) formalism into
the strongest current finite-divisor product-hull route instead of leaving it
only at the generic source-core endpoint.
The same product-hull source now exposes the Ob6 log-volume version of this
audit,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_ob6HullApproximantLogVolumeAudit}.
\end{array}
\]
This audit identifies both \(H_{\Phi(P_B)}\) and \(H_{\Xi(P_B)}\) with the
selected product hull, proves
\[
  \mu_{\log}(P_B)\leq\mu_{\log}(H_{\Phi(P_B)}),\qquad
  \mu_{\log}(P_B)\leq\mu_{\log}(H_{\Xi(P_B)}),
\]
and records the corresponding comparison-region and q-pilot inequalities into
the \(H_{\Xi(P_B)}\) log-volume.  The normalized determinant equality and the
raw \(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison remain in
the same audit object, so the Ob6 passage is now visible directly on the
finite-divisor product-hull route.
This Ob6 boundary now has a canonical exact-\(\Xi\) specialization:
instead of supplying arbitrary \(\Phi(P_B)\) and \(\Xi(P_B)\) families, the
route takes the exact source calibration
\(\mu_{\log}(\phi(P_B))=\mu_{\log}(P_B)\), uses the canonical \(\Phi(P_B)\)
approximant, and constructs the exact \(\Xi(P_B)\) family from that
calibration.  Thus the remaining payload at this point is the source
construction of the exact log-volume equality, not a free choice of
approximant families.
At the concrete Hodge-theater/log-theta boundary, this exact-\(\Xi\) route now
also has a source-derived \(C_\Theta\) variant,
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaConcreteCalibratedExactXi}\\
\quad\texttt{SelectedQRemark395SourceDerivedCThetaAudit}.
\end{array}
\]
Here the global constant is the \(\IUT{}\,\mathrm{IV}\) estimate's
\(C_\Theta\), and the required domination
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) is projected from the
local-to-global arithmetic-gap source.  The public concrete exact-\(\Xi\)
boundary therefore no longer has to expose that domination as a raw scalar
hypothesis.  The same source-derived form now reaches the closed-family and
product-hull exact-\(\Xi\) boundaries: closedness constructs the calibration,
the product-hull witness constructs closedness, and the local-to-global source
supplies the \(C_\Theta\) comparison in both cases.  The construction of the
arithmetic-gap source itself remains part of the local
\(\IUT{}\,\mathrm{IV}\) payload.
This source-derived form now also reaches the principal valuation-ball local
boundary, and that boundary has been lowered through realized-region equality
to a local log-shell exact statement.  Starting from a principal cover whose
possible regions are transported theta regions, \Lean{} now accepts the two
local identities that a transported theta region is the realized image of its
selected log-shell and that this log-shell is the compact-open valuation ball.
It can also derive these identities from the pointwise local construction:
theta-region points have chosen compact-open valuation-ball representatives,
and compact-open valuation-ball points realize back into the transported theta
region.  This pointwise source is now constructed from compact-open
local-chart data, from the compact-open log-Kummer graph source, and from the
possible-region log-Kummer map source after rewriting the cover possible
region as the transported theta region.  The resulting construction builds the
exact \(\Xi(P_B)\) family and uses the local-to-global arithmetic source for
the global \(C_\Theta\) comparison, without reintroducing a caller-supplied
scalar domination after the product-hull lowering.
The same specialization now propagates through the synchronized Ob5--Ob7
review object and the canonical-scale audit: the product-hull route can run
with canonical \(\Phi(P_B)\) and source-constructed exact \(\Xi(P_B)\) while
retaining the Ob7 prime-strip/log-Kummer data.  In the strongest product-hull
surface, the finite product-formula Ob7 construction feeds the canonical
\(C_\Theta\) audit without reintroducing caller-chosen approximant families.
The downstream finite-divisor dichotomy has now been lowered to the same
boundary: from the exact \(\Xi(P_B)\) calibration and the product-formula Ob7
source, \Lean{} selects the canonical approximant index and derives the
canonical-scale \(C_\Theta\) alternative directly.
The product-hull boundary also exposes an exact-theta bridge audit,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_exactThetaBridgeAudit}.
\end{array}
\]
This audit does not add a new comparison possible image.  It packages the
source-facing identities already needed by the determinant route:
\[
  \theta_{\mathrm{signed}}=\mu_{\log}(\phi(P_B)),
  \qquad
  \mu_{\log}(\phi(P_B))=\det_{\mathrm{norm}}=\det,
\]
with \(\phi(P_B)\) the selected smallest product hull.  From the exact
theta/family-hull equality, \Lean{} derives the normalized tensor-power upper
bound into \(\theta_{\mathrm{signed}}\), and the audit records the chain
\[
  \mu_{\log}(q)\leq \mu_{\log}(\phi(P_B))
  = \det_{\mathrm{norm}}\leq\theta_{\mathrm{signed}}.
\]
Thus the strongest current product-hull surface separates the remaining open
source task--constructing the actual IUT product-hull/determinant data--from the
ordered-real and determinant-log-volume consequences already checked by the
kernel.
The same surface now has an Ob7 log-Kummer compatibility audit,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_ob7LogKummerCompatibilityAudit}.
\end{array}
\]
Given a finite \(F^{\times\mu}\)-prime-strip lift whose global realified
Frobenioid log-volume agrees with the determinant log-volume, this audit
identifies the family-hull and normalized determinant log-volumes with that
prime-strip global value and proves
\[
  \mu_{\log}(q)\leq \mu_{\log}(F^{\times\mu}_{\mathrm{global}}).
\]
For every environment prime it also returns the corresponding Gaussian
prime-to-place equality, equality of local realified log-volumes at the
evaluated prime, and equality of Gaussian and environment unit characters.
Thus the product-hull route now retains the Ob7 log-Kummer/Frobenioid data at
the precise boundary where the determinant comparison enters the 3.12 corridor.
The same Ob7 boundary now has a source-object form.  The declarations with
suffixes
\[
\begin{array}{l}
\texttt{Ob7LogKummerCompatibilityAuditOfSource},\\
\texttt{Ob5Ob6Ob7SynchronizedAuditAtQChoiceOfQPilotRegionNonemptyOfOb7Source}
\end{array}
\]
take the typed Remark~3.9.5(Ob7) compatibility source itself, rather than a
loose prime-strip lift together with a separate determinant/global-log-volume
equality.  The only synchronization left at this boundary is the proof that the
Ob7 source's hull/determinant bridge is the constructed product-hull
Step~(xi) bridge.  Thus the determinant-to-prime-strip comparison, local
prime/place square, local realified Frobenioid readings, and unit-character
transport are reviewed as one source-paper object.
There is now a further coric form of the same Ob7 boundary.  The core source
\[
\texttt{IUTStage1Remark395Ob7CoricLogKummerCompatibilitySource}
\]
uses the finite \(F^{\vdash\times\mu}\) invariant: a common unit character on
the valuation set \(V\) whose pullbacks are the environment and Gaussian
unit characters.  It projects to the ordinary Ob7 source, while the product
audit
\[
\texttt{Ob7CoricLogKummerCompatibilityAudit}
\]
keeps the projected Ob7 determinant comparison together with the coric unit
equalities.  The q-choice Ob5--Ob7 synchronized and canonical-scale audits now
also have \texttt{OfCoricOb7Source} forms, so the unit part of Ob7 is no longer
represented only by a transported equality between two prime-strip unit
characters.
This coric boundary has now been lowered one more step toward the source-paper
Corollary~4.7(iv) construction.  The declaration
\[
\begin{array}{l}
\texttt{ProductHullBackedCoricThetaMuOb7ConstructionSource}
\end{array}
\]
does not take a completed \(F^{\vdash\times\mu}\) invariant as input.  It takes
an \(F^{\times\mu}\)-prime-strip lift, a common coric unit character on \(V\),
the environment pullback equality, and the determinant/global log-volume
identification.  Lean constructs the coric invariant by
\[
\begin{array}{l}
\texttt{IUTStage1CoricThetaMuPrimeStripInvariant.}\\
\quad\texttt{ofLiftAndCoricUnitCharacter},
\end{array}
\]
then derives the Gaussian coric pullback equality from the prime-strip
evaluation square.  The product-hull and principal topology/Haar audit surfaces
now have \texttt{OfCoricThetaMuConstructionSource} forms, so this finite
Corollary~4.7(iv) construction is visible at the same Ob5--Ob7 boundary as the
Remark~3.9.5 hull and determinant data.
The product-hull final dichotomy now has the corresponding
\texttt{OfCoricOb7Source} endpoint: the canonical-scale \(C_\Theta\) dichotomy
is returned together with the synchronized Ob5--Ob7 audit while consuming the
single coric \(F^{\vdash\times\mu}\) Ob7 source and its bridge equality with the
constructed Remark~3.9.5 hull/determinant source, rather than a raw
prime-strip lift and determinant-global equality.
The product-hull boundary now also has a synchronized Ob5--Ob7 review object,
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{HullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_ob5Ob6Ob7SynchronizedAudit}.
\end{array}
\]
It packages the Ob6 \(H_{\Phi(P_B)}\)/\(H_{\Xi(P_B)}\) log-volume audit and
the Ob7 finite \(F^{\times\mu}\)-prime-strip audit in one source object, while
also recording that the Ob7 hull/determinant bridge uses exactly the same
Theorem~3.11 possible-image family and the same selected product-hull operator
as the Ob6 approximant boundary.  Thus a prime-strip log-volume comparison can
no longer be reviewed at this surface independently of the product-hull
possible-image family whose Ob5 quotient collapse and Ob6 approximant
inequalities are being used.
This synchronized review object is now threaded through the finite-divisor
vertical-\(IQ\) boundary as well.  The experiment endpoint
\[
\begin{array}{l}
\texttt{remark395ProductHullBackedConstructorBackedConstructed}\\
\quad\texttt{Ob3Ob5AdjustedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_cThetaDichotomyWithOb5Ob6Ob7SynchronizedAudit}
\end{array}
\]
returns the synchronized Ob5--Ob7 audit together with the usual conditional
\(C_\Theta\) dichotomy.  Thus the strongest current product-hull
finite-divisor route no longer reviews the final ordered-real conclusion after
forgetting the Ob5 quotient, Ob6 hull-approximant, and Ob7 log-Kummer
provenance attached to the same Remark~3.9.5 hull.
This route now also has
\[
\begin{array}{l}
\texttt{\_cThetaDichotomyWithOb5Ob6Ob7SynchronizedAudit}\\
\quad\texttt{OfQPilotRegionNonempty},
\end{array}
\]
which replaces the direct q-choice possible-image nonemptiness hypothesis by a
nonempty q-pilot region.  The synchronized audit then obtains the selected
possible-image witness internally from \(q\subseteq P_{q\text{-choice}}\), so
the public finite-divisor review target is closer to the source-paper
q-pilot-object formulation.
There is now a further q-choice-specialized version,
\[
\begin{array}{l}
\texttt{\_cThetaDichotomyWithOb5Ob6Ob7SynchronizedAudit}\\
\quad\texttt{AtQChoiceOfQPilotRegionNonempty},
\end{array}
\]
and its canonical-scale analogue.  In this endpoint the Ob5 comparison
possible image is not an arbitrary extra choice: it is the constructor-backed
q-choice itself.  Hence the single nonempty q-pilot region supplies both
quotient-collapse nonemptiness witnesses through
\(q\subseteq P_{q\text{-choice}}\).  The canonical-scale version therefore
has neither an external numeric \(C_\Theta\) estimate nor a separate
comparison-choice nonemptiness hypothesis.
The constructor-built source-level canonical-scale bridge is now exposed
directly as
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource\_remark395CanonicalCThetaBridgeAudit}.
\end{array}
\]
It records the chain
\(\mu_{\log}(q\mathrm{Region})\leq\det_{\mathrm{norm}}
\leq\theta_{\mathrm{signed}}\leq
C_{\Theta,\mathrm{can}}\cdot(-q_{\mathrm{signed}})\) at the Step~(xi)
source boundary, separate from the downstream finite-divisor wrappers.

The same milestone-facing constructed source now has a possible-image
q-choice constructor.  In this form the q-pilot region is definitionally the
chosen Theorem~3.11 possible image \(P_i\), so \Lean{} derives
\(q\subseteq\bigcup_i P_i\) from the possible-image union rather than accepting
that containment as a separate field.  The endpoint then exposes containment
in the record-canonical holomorphic hull, the Ob3/Ob4 weighted determinant
payload, the q-to-determinant log-volume inequality, and the resulting
\(q_{\mathrm{signed}}\leq\theta_{\mathrm{signed}}\) comparison.  This is a
small but important tightening of the current trust boundary: the generic
Remark~3.9.5 bridge source can now be instantiated in the source-native
possible-image case without an arbitrary q-region containment input.

The constructor-built Step~(xi) source now also exposes the Remark~3.9.5(v)--(vi)
upper-semi quotient passage as
\[
\begin{array}{l}
\texttt{possibleImageConstructorBuiltHullSource}\\
\quad\texttt{\_ob5QuotientIndependenceAudit}.
\end{array}
\]
Given two nonempty Theorem~3.11 possible images, the audit proves that both
images collapse to the same point under the quotient by the bounded-family
holomorphic hull \(\phi(\bigcup_i P_i)\).  The same record carries the
bounded-family determinant/log-volume equality, the family-union log-volume
bound, the normalized tensor-power equality, and the raw Step~(xi) signed
comparison.  Thus Ob5 is now visible on the constructor-built public surface as
the paper's independence-of-possibilities quotient statement, not just as a
background containment lemma.

The constructor-built Step (xi) source now has the same record-canonical
Ob3/Ob5 projection.  A shadow hull/log-volume object is first converted back
to a Remark 3.9.5 \(\phi\)-operator by
\texttt{toRemark395Operator}; the constructor-built source then forms the
record Ob3/Ob5 determinant-compatibility source and the record hull/determinant
bridge source from its own q-region containment, determinant compatibility, and
Ob4 tensor-power bound.  The public
\texttt{recordOb3Ob5BridgeAudit} endpoint records that the q-to-determinant
and determinant-to-theta inequalities are obtained from the generic
record-canonical bridge theorem.  This does not construct the analytic
determinant compatibility, but it removes another ad hoc audit boundary: the
large constructor-built object now factors through the same source object as the
milestone-facing constructed source.

The constructor-built Step~(xi) source now also has a canonical local
\(C_\Theta\)-scale audit.  From q-pilot positivity it defines
\[
  C_{\Theta,\mathrm{can}}
    =
  \theta_{\mathrm{signed}}/(-q_{\mathrm{signed}})
\]
and proves internally that
\[
  \theta_{\mathrm{signed}}
  \le
  C_{\Theta,\mathrm{can}}\cdot(-q_{\mathrm{signed}}).
\]
The canonical-one constructed-\(\IPL\) finite-divisor route therefore has a
no-external-bound endpoint
\[
\begin{array}{l}
\texttt{sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQSource}\\
\quad\texttt{\_canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{CanonicalCThetaScaleDichotomy}.
\end{array}
\]
The same source now exposes the stronger audit
\[
\begin{array}{l}
\texttt{sourceDerivedHodgeSHEIPLHullFiniteDivisorVerticalIQSource}\\
\quad\texttt{\_canonicalOneConstructorBuiltIPLConstruction}\\
\quad\texttt{Remark395CanonicalCThetaBridgeAudit}.
\end{array}
\]
This audit keeps the canonical local scale attached to the constructed
Remark~3.9.5 bridge chain
\[
  \mu_{\log}(q\mathrm{Region})
    \leq \det_{\mathrm{norm}}
    \leq \theta_{\mathrm{signed}}
    \leq C_{\Theta,\mathrm{can}}\cdot(-q_{\mathrm{signed}}).
\]
Thus the local no-external-bound scale is no longer merely a final
ordered-real specialization; it is recorded beside the Ob1--Ob5
holomorphic-hull, determinant, and record Ob3/Ob5 bridge payload that produces
the signed comparison.
The compact constructed-hull finite-divisor endpoint now has the same audited
canonical-scale form,
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_remark395}\\
\quad\texttt{ConstructedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_canonicalCThetaScaleWithCanonicalScaleAudit}.
\end{array}
\]
It returns the constructed Remark~3.9.5 canonical-scale audit together with
the finite-divisor vertical-\(IQ\) dichotomy, so the no-external-bound
finite boundary exposes the normalized determinant bridge and the derived
\(\theta_{\mathrm{signed}}\leq
C_{\Theta,\mathrm{can}}(-q_{\mathrm{signed}})\) estimate instead of only the
final ordered-real conclusion.
This does not yet identify \(C_{\Theta,\mathrm{can}}\) with the global
paper constant \(C_\Theta\).  Its purpose is narrower and useful: the
theta/log-q upper bound is no longer an opaque route hypothesis for this local
scale, and the remaining mathematical task is now isolated as the comparison
between this canonical source scale and the \IUT{} constant from the paper.
This comparison boundary is now a named Lean object rather than prose.  The
constructed source theorem
\[
\begin{array}{l}
\texttt{IUTStage1Remark395ConstructedHolomorphicHullDeterminantSource}\\
\quad\texttt{.constructedGlobalCThetaScaleComparisonAudit}
\end{array}
\]
assumes only
\[
  C_{\Theta,\mathrm{can}}\leq C_\Theta
\]
for the chosen paper/global constant \(C_\Theta\).  From this domination and
q-pilot positivity, Lean derives
\[
  \theta_{\mathrm{signed}}
    \leq
  C_\Theta\cdot(-q_{\mathrm{signed}})
\]
and then applies the standard Corollary~3.12 ordered-real dichotomy.  The
experiment-surface endpoints
\[
\begin{array}{l}
\texttt{remark395ConstructedHolomorphicHullDeterminantSource}\\
\quad\texttt{\_globalCThetaScaleComparisonAudit},\\
\texttt{remark395ConstructedHolomorphicHullDeterminantSource}\\
\quad\texttt{\_globalCThetaScaleChain}
\end{array}
\]
therefore replace the raw final numeric hypothesis by the sharper remaining
source obligation ``global \(C_\Theta\) dominates the constructed local
Remark~3.9.5 scale''.  This is still an obligation, but it is now the correct
one to attack from the source-paper global estimate.
This source-level comparison has now been threaded through the compact
finite-divisor vertical-\(IQ\) boundary as
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_remark395}\\
\quad\texttt{ConstructedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_globalCThetaScaleWithGlobalScaleAudit}.
\end{array}
\]
The endpoint assumes \(C_{\Theta,\mathrm{can}}\leq C_\Theta\), constructs the
global-scale Remark~3.9.5 audit, derives the numeric
\(\theta_{\mathrm{signed}}\leq C_\Theta(-q_{\mathrm{signed}})\) estimate
internally, and then returns the finite-divisor dichotomy.  Thus the
finite Step~(x) boundary no longer needs to expose the raw final numeric
hypothesis when the intended local-to-global \(C_\Theta\) comparison is the
available source obligation.
The paper-side \(C_\Theta\) expression from \IUT{} IV is now connected to this
same boundary.  The experiment-surface audit
\[
\begin{array}{l}
\texttt{Remark395ConstructedIUTIVCThetaHandoffAudit}
\end{array}
\]
takes a constructed Remark~3.9.5 Step~(xi) source and an
\texttt{IUTStage1IUTIVThetaPilotLogVolumeEstimateShadow}.  The latter supplies
the displayed \IUT{} IV expression
\[
  C_\Theta
    =
  \mathrm{arithmeticUpperTerm}
    -
  \mathrm{mainLogTerm}
    -
  1
\]
together with the existing \IUT{} IV handoff endpoint.  The only new comparison
input is again
\[
  C_{\Theta,\mathrm{can}}\leq C_\Theta .
\]
The compact endpoint
\[
\begin{array}{l}
\texttt{remark395ConstructedHolomorphicHullDeterminantSource}\\
\quad\texttt{\_iutIVCThetaHandoffChain}
\end{array}
\]
then records, in one proposition, the \IUT{} IV expression for \(C_\Theta\), the
constructed Step~(xi) chain
\(\mu_{\log}(q\mathrm{Region})\leq\det_{\mathrm{norm}}
\leq\theta_{\mathrm{signed}}\), the derived paper-side bound
\(\theta_{\mathrm{signed}}\leq C_\Theta(-q_{\mathrm{signed}})\), and the final
Corollary~3.12 dichotomy.  Thus the remaining global comparison is no longer
split between the Step~(xi) local scale audit and the separate \IUT{} IV
constant shadow.
This \IUT{} IV handoff has now been lifted to the compact finite-divisor
vertical-\(IQ\) boundary:
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_remark395}\\
\quad\texttt{ConstructedHullDeterminantFiniteDivisorVerticalIQ}\\
\quad\texttt{\_iutIVCThetaWithHandoffAudit}.
\end{array}
\]
The endpoint consumes the constructed Remark~3.9.5 Step~(xi) source, the
\IUT{} IV estimate object, and the single comparison
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\).  It returns the \IUT{} IV handoff
inequalities, the constructed global-scale Remark~3.9.5 audit at
\(\texttt{estimate.cTheta}\), and the finite-divisor dichotomy.  Thus the
paper-side \(C_\Theta\) expression is visible at the same boundary as the
Step~(x) vertical-\(IQ\) data.
The first source-facing replacement of this last comparison is now in Lean.
The structures
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311Ind1Action},\quad
\texttt{IUTStage1Theorem311Ind2Action},\\
\texttt{IUTStage1Theorem311Ind3UpperSemiRelation},\quad
\texttt{IUTStage1Theorem311TypedIndeterminacyCore}
\end{array}
\]
replace the earlier name/boolean indeterminacy shadow on the local-to-global
critical path by typed relations on a Theorem~3.11 choice space.  The formal
payload matches the source-paper asymmetry needed in the Corollary~3.12
corridor: \((\Ind_1)\) and \((\Ind_2)\) preserve procession-normalized
log-volume, while \((\Ind_3)\) supplies only an upper-semi log-volume
inequality.  The core constructs the generated quotient and quotient map, and
the possible-image compatibility record states that \((\Ind_1)\) and
\((\Ind_2)\) identify possible-image regions whereas \((\Ind_3)\) contributes
the one-sided estimate.  A finite one-point witness
\(\texttt{finiteToyCore}\) checks joint satisfiability of this typed interface;
it is deliberately not an \IUT{} model.
The quotient layer is now explicit.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{EqualityQuotientPossibleImages}
\end{array}
\]
indexes possible images by
\(\mathrm{Quot}(\texttt{equalityQuotient.relation})\) and proves that pulling
back along \(\texttt{equalityQuotientMap}\) recovers the original choice-indexed
family.  The direct \((\Ind_1)\) and \((\Ind_2)\) steps are members of this
equality orbit, while the equality quotient's \((\Ind_3)\) generator is empty;
\((\Ind_3)\) remains available only through the upper-semi log-volume theorem.
This quotient now feeds the Step~(xi) hull side directly: the constructor
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{EqualityQuotientPossibleImages.}\\
\quad\texttt{toRemark395PossibleImageFamilySource}
\end{array}
\]
builds a Remark~3.9.5 possible-image family indexed by
\(\mathrm{Quot}(\texttt{equalityQuotient.relation})\).  The checked endpoints
\[
\begin{array}{l}
\texttt{remark395Ob5EqualityQuotientEndpoint\_of\_equalityOrbit},\\
\texttt{remark395Ob5Ob6EqualityQuotientEndpoint\_of\_equalityOrbit}
\end{array}
\]
prove the Ob5 collapse and Ob6 \(\Phi/\Xi\) hull-log-volume inequalities for
\((\Ind_1)/(\Ind_2)\)-orbit choices.  They do not identify \((\Ind_3)\)
choices; the \((\Ind_3)\) contribution is still precisely the separate
one-sided log-volume inequality.
The finite toy witness has been upgraded accordingly to
\(\texttt{finiteToyEqualityQuotientPossibleImages}\).
The same equality-quotient discipline is now available at the generated
full-label Step~(xi) boundary: the public generated constructor keeps
\((\Ind_3)\) outside the equality quotient and exposes the selected
q-region as both a quotient possible image and the pullback of the corresponding
theta-pilot-class image.
The current nonvacuity audit is packaged as
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{FiniteToyTypedIndeterminacyNonvacuityAudit}.
\end{array}
\]
It records a nonempty choice space, self-steps for the three typed
indeterminacies, preservation of log-volume for \((\Ind_1)\) and
\((\Ind_2)\), the one-sided upper-semi estimate for \((\Ind_3)\), absence of an
\((\Ind_3)\) generator in the equality quotient, and pullback compatibility for
the quotient-indexed possible-image family.  This closes only the
interface-level satisfiability check: it prevents the typed indeterminacy layer
from being vacuous, but it is not yet a construction of Mochizuki's full
indeterminacy apparatus.
The witness has also been strengthened from the purely reflexive one-point
case to a strict two-point audit,
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{StrictFiniteToyTypedIndeterminacyNonvacuityAudit}.
\end{array}
\]
This audit now also carries the generic
\texttt{actionLawAudit} certificate used by the main corridor.  Here the
choice space is \(\mathrm{Fin}\,2\), \((\Ind_1)\) and \((\Ind_2)\)
are equality relations, and \((\Ind_3)\) contains the strict step
\(0\to 1\).  The Lean theorem
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{strictFiniteToyTypedIndeterminacyNonvacuityAudit\_}\\
\quad\texttt{ind3\_strict\_not\_equalized}
\end{array}
\]
proves simultaneously that this \((\Ind_3)\) step is present, that its
log-volume inequality is strict, that the target point is not in the
\((\Ind_1)/(\Ind_2)\) equality orbit of the source point, that the two points
have distinct \texttt{equalityQuotientMap} images, and that \((\Ind_3)\) is
still absent from the equality quotient generators.  The quotient-map
separation is proved by a finite quotient representative map
\(\mathrm{Quot}(\texttt{equalityQuotient.relation})\to \mathrm{Fin}\,2\),
whose well-definedness follows from the fact that the strict toy equality
quotient relation is exactly equality.  This is stronger nonvacuity evidence
for the asymmetric typed interface, while retaining the same limitation: it is
a finite audit model of the interface, not an \IUT{} source construction.
The same strict model now also carries
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{StrictFiniteToyEqualityQuotientHullNonvacuityAudit}.
\end{array}
\]
This audit instantiates the quotient-indexed Remark~3.9.5 hull/log-volume
compatibility layer on the strict two-point model.  Its endpoint proves
pullback to the original finite possible-image family, hull-log-volume
invariance along \((\Ind_1)\) and \((\Ind_2)\), the \((\Ind_3)\) upper-semi
core inequality \(0\leq 1\), and the same strict non-equalization statement for
the \(0\to1\) \((\Ind_3)\) step.  Thus the finite audit now reaches through the
same quotient-to-hull interface used by the Step~(xi) corridor, while still
remaining only a nonvacuity check.
The one-sided multiradial source now also exposes this information as the
structured audit
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{OneSidedQuotientAudit}.
\end{array}
\]
The audit records that possible images are indexed through the equality
quotient, that the equality quotient has no \((\Ind_3)\) generator, that
\((\Ind_1)\) and \((\Ind_2)\) preserve procession-normalized log-volume, that
\((\Ind_3)\) remains only an upper-semi relation, and that the selected
q-region is the quotient-indexed Theorem~3.11 possible image.  This audit now
also carries
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.}\\
\quad\texttt{ActionLawAudit},
\end{array}
\]
the compact certificate that the three typed indeterminacy action objects share
the same procession-normalized log-volume, that the \((\Ind_1)/(\Ind_2)\)
quotient maps respect their preserving steps, and that \((\Ind_3)\) is excluded
from the equality quotient.  The local-global \(C_\Theta\) source and its
finite-place version now project this audit directly, so the closed boundary can
cite the one-sided quotient facts without unpacking the Step~(xi) constructor.
The selected q-region now also has a quotient-hull audit,
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{OneSidedSelectedQHullLogVolumeAudit}.
\end{array}
\]
This audit consumes the equality-quotient
\texttt{EqualityQuotientHullLogVolumeCompatibility} and the constructed
Remark~3.9.5 hull/determinant source.  It proves that the selected q-pilot
region is the quotient-indexed possible region, lies in the quotient canonical
hull, and satisfies the constructed source's q-region log-volume bound by
\(\theta\), while retaining \((\Ind_1)/(\Ind_2)\) hull-log-volume equalities
and the separate \((\Ind_3)\) upper-semi core inequality.

The local-to-global comparison itself is now isolated as
\[
\begin{array}{l}
\texttt{ConstructedTheorem311IndeterminacyLocalGlobalCThetaSource}.
\end{array}
\]
This source object ties the typed Theorem~3.11 indeterminacy core to the
constructed Remark~3.9.5 Step~(xi) source and the \IUT{} IV estimate shadow.  It
records the remaining paper-mathematical assembly obligations: local place
log-volume assembly, finite-divisor valuation-ball Haar normalization,
product/sum local-to-global assembly, and compatibility between the
Theorem~3.11 indeterminacy construction and the Step~(xi) determinant/hull
source.  Crucially, it no longer assumes the raw comparison
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\).  Instead Lean derives it from the
paper-shaped arithmetic gap
\[
  C_{\Theta,\mathrm{can}}+1
    \leq
  \mathrm{arithmeticUpperTerm}-\mathrm{mainLogTerm}
\]
together with the \IUT{} IV identity
\[
  C_\Theta =
  \mathrm{arithmeticUpperTerm}-\mathrm{mainLogTerm}-1.
\]
The compact finite-divisor endpoint
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{Theorem311IndeterminacyLocalGlobalCThetaFiniteDivisorVerticalIQ}
\end{array}
\]
therefore consumes this source object and returns both the source-obligation
endpoint and the Corollary~3.12 dichotomy.  This is progress on the disputed
corridor because the last scalar comparison is now a typed Theorem~3.11/\IUT{}
IV local-to-global source obligation, not an exposed final numeric hypothesis.
It remains an obligation until the local place assembly, Haar normalization,
and product/sum comparison are constructed from the corresponding source-paper
objects rather than recorded as proof-carrying fields.
The Theorem~3.11 multiradial source has also been strengthened below this
local-to-global handoff.  The source object
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311QuotientMultiradialSource}
\end{array}
\]
now ties the typed \((\Ind_1),(\Ind_2),(\Ind_3)\) core to an actual
\texttt{IUTStage1MultiradialThetaImages} quotient package.  It records that the
multiradial quotient is the quotient generated by the typed indeterminacy core,
that the possible-image family is the one carried by the Theorem~3.11 record,
and that the selected q-region is literally one of these possible images.  It
also carries the finite \(F_l\)-label layer: a \(\Theta\)NF gluing torsor, the
cardinality \(\#F_l=l\), and procession-label transitions satisfying the zero
and addition laws.  Lean proves that every such label transition has the same
quotient-map class and hence the same multiradial possible-image region.

The source is no longer constructed only by supplying this whole package as a
raw payload.  The finite procession layer is separated as
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311FLProcessionAction},
\end{array}
\]
which records the \(\Theta\)NF gluing torsor, the \(Z/lZ\)-indexed procession
transition on choices, the zero/addition action laws, and the fact that each
transition stays inside the quotient generated by the typed indeterminacy core.
At the generated full-label boundary Lean now also proves
\[
\begin{array}{l}
\texttt{GeneratedFullLabelConcreteProcessionSourceAudit},\\
\texttt{GeneratedFullLabelConcreteProcessionQuotientImageAudit}.
\end{array}
\]
The first audit identifies the generated \(F_l\)-orbit with the concrete
full-label procession source over the same forgotten theta-pilot lattice
coordinate: every finite label occurs, the label is unique over that lattice
node, and generated translation projects to the concrete procession coordinate.
The second audit connects this concrete procession to the selected quotient
possible image: each finite-label representative lies in the selected
\((\mathrm{Ind1})\)-orbit, has the same equality-quotient index, and pulls back
to the same theta-pilot possible image.  Thus the Remark~3.11.2
no-omission/cardinality condition is no longer merely a separate label lemma at
this boundary; it is threaded into the selected Theorem~3.11 possible-image
construction.
The constructor
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311QuotientMultiradialConstructionSource}
\end{array}
\]
then builds the quotient-aware source: the multiradial image object is formed
from the typed quotient and the record's Theorem~3.11 theta possible images,
the selected q-region is defined to be the possible image at the selected
choice, and \(\#F_l=l\) is proved by \texttt{ZMod.card}.  Thus the remaining
paper-side payload at this layer has been narrowed to two mathematical
assertions: possible-image invariance along the typed quotient and the actual
finite procession action on the source choice space.

The preferred source boundary now uses the one-sided equality quotient.  The
typed core exposes
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311TypedIndeterminacyCore.equalityQuotient}
\end{array}
\]
generated by \((\Ind_1)\) and \((\Ind_2)\) alone.  Thus \((\Ind_3)\) is not a
possible-image equality: it remains only the upper-semi log-volume relation.
From a \texttt{PossibleImageQuotientCompatibility} object, Lean proves
\[
  i\sim_{\Ind_1,\Ind_2}j
  \Longrightarrow
  \Theta\mathrm{Image}_i=\Theta\mathrm{Image}_j
\]
as
\texttt{PossibleImageQuotientCompatibility.equalityQuotient\_image\_invariant},
while retaining the separate theorem that an \((\Ind_3)\)-step gives only the
upper-semi log-volume inequality.  The Step~(xi) source
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource}
\end{array}
\]
constructs the multiradial possible-image object from this equality quotient.
It now also exposes the quotient-indexed possible-image family itself: pulling
back along \(\texttt{equalityQuotientMap}\) recovers the original
choice-indexed family, and the selected q-region is the pullback of the selected
quotient class.  The local-to-global experiment endpoint reports the same
factorization, so this quotient passage is visible at the \(C_\Theta\) boundary
instead of remaining a private constructor detail.
The finite \(F_l\)-procession action is now threaded through this same hull
interface.  The endpoint
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{flProcessionRemark395Ob5Ob6\_endpoint}
\end{array}
\]
states that translating a choice by an \(F_l\)-label leaves its
\((\Ind_1,\Ind_2)\)-equality-quotient class unchanged and therefore gives the
Remark~3.9.5 Ob5 collapse together with the Ob6 \(\Phi/\Xi\) hull-log-volume
inequalities for the original and translated possible images.  This is a
source-level bridge from procession label transitions to the Step~(xi)
hull family; it still does not identify \((\Ind_3)\)-related choices.

The anonymous choice index can now be replaced by a concrete
Hodge-theater/log-theta-lattice choice type.  A choice carries a Hodge-theater
identifier, a history label, an \((n,m)\) log-theta coordinate, an \(F_l\)
label, and the current procession, local tensor, and upper-semi data.  The
constructor
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{ofConcreteHodgeTheaterLogTheta}
\end{array}
\]
builds the one-sided multiradial source from concrete \((\Ind_1)\),
\((\Ind_2)\), and \((\Ind_3)\) laws on this choice space.  Lean now constructs
the finite \(F_l\)-procession action itself: it translates the \(F_l\) label by
the canonical \(\mathbb Z/l\mathbb Z\) action, proves the zero and addition
laws, proves \(\#F_l=l\), and derives equality-quotient compatibility from the
concrete \((\Ind_1)\) step.  This has been lowered one step further at the
source-choice boundary.  The constructor now also has the compact audit
\texttt{ConcreteHodgeTheaterLogThetaConstructorAudit}, which packages the
one-sided quotient audit, the selected q-region endpoint, finite
\(F_l\)-cardinality, \((\Ind_1)/(\Ind_2)\) log-volume preservation, and the
no-\((\Ind_3)\)-equality guard as one review object.  The new
\texttt{IUTStage1FLLabelProcessionSource} fixes one forgotten
theta-pilot lattice node and constructs the full
\(\mathbb Z/l\mathbb Z\)-indexed family of finite-label representatives over
it.  Its audit proves \(\#F_l=l\), that every label occurs, that a coordinate
over the same forgotten lattice node has a unique full label, and that label
translation agrees with coordinate translation.  The choice-level source
\texttt{FLLabelProcessionChoiceSource} then turns every full-label
representative into a concrete \((\Ind_1)\) step from the base choice; with the
Theorem~3.11 indeterminacy law, Lean derives preservation of the
procession-normalized log-volume for every such label.

The next transition in Remark~3.11.2 is now explicit as well.  The declaration
\[
\begin{array}{l}
\texttt{IUTStage1AbsoluteFLLabelProcessionSource}
\end{array}
\]
forms the \(|F_l|\) label layer from the full \(F_l\) family by sending
\(j\in \mathbb Z/l\mathbb Z\) to the zero label or to the sign quotient of the
corresponding nonzero cusp label.  Its audit proves that every \(|F_l|\) label is
represented, that nonzero opposite labels \(j\) and \(-j\) have the same
absolute label, that this is exactly the quotient identification, and that
ordinary \(F_l\)-procession translation is compatible with the induced
\(\pm\)-procession label map.  The
choice-level audit
\texttt{AbsoluteLabelProcessionChoiceAudit} attaches this passage to concrete
Hodge-theater/log-theta choices, and the Step~(xi) action audit now records both
the all-full-label source and the induced absolute-label compatibility.  Thus the
formal label layer now follows the source-paper chain
\[
F_l\text{-labels}\longrightarrow |F_l|\text{-labels}\longrightarrow
\pm\text{-processions}
\]
instead of stopping at the ordinary \(F_l\)-procession action.

Remark~3.11.2 also treats the mono-analytic \(\pm\)-procession index sets as
naked finite sets, not as further arithmetic holomorphic data.  Lean now models
the component indexed by \(j\) as \(\mathrm{Fin}(j+1)\), proves that any finite
type of cardinality \(j+1\) is equivalent to this chosen model, and packages the
family of choices
\[
\prod_{j=0}^{l} \mathrm{Fin}(j+1).
\]
The total cardinality is proved to be \((l+1)!\), matching the paper's
\(l^{\pm}!\) count.  This audit is attached to the absolute-label procession
source, so the formal passage to \(\pm\)-processions now records both the
quotient of labels and the naked mono-analytic counting data.

This source is canonical: \texttt{ofCoordinate} builds the full-label family from
a log-theta coordinate, \texttt{ofChoice} attaches it to a concrete
Hodge-theater/log-theta choice, and
\texttt{ConcreteHodgeTheaterLogThetaFullLabelProcessionSource.canonical}
assembles the choice-wise family for the whole concrete source space.

The one-sided constructor has both an explicit and a canonical full-label entry
point,
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{ofConcreteHodgeTheaterLogThetaFullLabelSource},\\
\quad\texttt{ofConcreteHodgeTheaterLogThetaCanonicalFullLabelSource}.
\end{array}
\]
They build the same concrete multiradial source as
\texttt{ofConcreteHodgeTheaterLogTheta}, but their endpoints also audit that each
action translate is backed by the all-label source, is represented by an
\((\Ind_1)\) full-label choice, preserves log-volume, and has the expected
\(Z/lZ\) label.  Thus the \(F_l\)-procession input consumed by the corridor is
now tied to the source-level no-omission statement constructed from the
log-theta coordinate itself, rather than merely to an abstract action law.

The quotient-image constructor
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{ofConcreteHodgeTheaterLogThetaQuotientImages}
\end{array}
\]
takes the theta-pilot possible images as a family on the
\((\Ind_1,\Ind_2)\)-equality quotient and a pullback theorem identifying the
record's choice-indexed images with this quotient family.  Lean derives the
old possible-image compatibility record from these quotient-indexed data.  This
has now been bundled as
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource}.
\end{array}
\]
The source object keeps the supplied quotient family visible, proves that it
agrees with the internally reconstructed quotient family, selects the q-image,
and constructs the corresponding Remark~3.9.5 quotient hull compatibility.  The
canonical constructor
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{ofCompatibility}
\end{array}
\]
now builds this quotient family by \texttt{Quot.lift} from the concrete
\((\Ind_1,\Ind_2)\) possible-image compatibility theorem, with the pullback law
definitionally recovered.  The remaining mathematical input is therefore
sharper: prove that compatibility theorem from the source-paper theta-pilot
apparatus, rather than hand-supply a quotient family or direct
\((\Ind_1,\Ind_2)\) image equalities at the Step~(xi) boundary.
The experiment surface now uses the sharper factorized form at the strongest
valuation-ball endpoint.  The new constructor
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaImageFactorizationSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ValuationBallHaarFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}
\end{array}
\]
starts from
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotImageFactorizationSource}: a
theta-class map, its possible-image family, and proofs that \((\Ind_1)\) and
\((\Ind_2)\) preserve the theta class.  It constructs the quotient theta-pilot
source internally by
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\texttt{ofImageFactorization}, then enters the existing valuation-ball
formula-gap/local-to-global \(C_\Theta\) route.  Thus the public endpoint no
longer asks for a prebuilt quotient theta-pilot source at this boundary.
This has now been refined once more: the theta-class map itself is no longer an
arbitrary field.  The concrete class
\[
\begin{array}{l}
\texttt{IUTStage1ConcreteHodgeTheaterLogThetaChoice.ThetaPilotClass}
\end{array}
\]
keeps the Hodge-theater history, the log-theta lattice column and row, the
log-theta-column, and the coric datum, but forgets the finite \(F_l\) label and
the local tensor representative.  Lean proves
\texttt{ind1\_thetaPilotClass\_eq} and
\texttt{ind2\_thetaPilotClass\_eq} from the concrete source steps.  Thus the
new constructor
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotImageFactorizationSource.}\\
\quad\texttt{ofThetaPilotClass}
\end{array}
\]
only requires a family of possible images on this concrete class and a pullback
identification with the record's choice-indexed possible images.  The direct
one-sided constructor
\[
\begin{array}{l}
\texttt{ofConcreteHodgeTheaterLogThetaThetaPilotClassImages}
\end{array}
\]
then constructs the factorization, derives the \((\Ind_1,\Ind_2)\)
possible-image equalities, builds the \(F_l\)-procession action, and fixes the
selected q-region as the chosen Theorem~3.11 possible image.  It still produces
the quotient theta-pilot source via
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{ofImageFactorization}.
\end{array}
\]
No \((\Ind_3)\) class equality is part of this constructor; the endpoint
explicitly keeps \((\Ind_3)\) out of the equality quotient and uses only the
typed upper-semi log-volume inequality.  This boundary has now been lowered
again by
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassImageLawSource}.
\end{array}
\]
This source supplies a representative concrete choice for each theta-pilot
class and proves that two choices with the same theta-pilot class have the same
possible-image region.  Lean then constructs the class-indexed family, proves
the pullback identity, and feeds the resulting factorization into
\texttt{ofConcreteHodgeTheaterLogThetaThetaPilotClassImageLaw}.  The
representative part has now been made explicit:
\texttt{ThetaPilotClassRepresentativeData} chooses the forgotten \(F_l\)-label,
procession representative, local tensor representative, and upper-semi
representative for each theta-pilot class, and Lean proves that this choice is
a section of the theta-pilot forgetting map.  The lower
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassRegionSource}
\end{array}
\]
then takes a class-level possible-image formula
\(\Theta_{\mathrm{class}}\mapsto P_{\Theta_{\mathrm{class}}}\) and the pointwise
pullback law
\[
P_{\mathrm{record}}(x)=P_{\Theta_{\mathrm{class}}(x)}.
\]
At the quotient boundary this class-region source now feeds
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{ofClassRegionSource}.
\end{array}
\]
Thus the equality-quotient family is constructed from the class-region
formula itself: Lean derives the same-class image law, the
\((\Ind_1,\Ind_2)\) quotient compatibility, the selected q-region, containment
in the Theorem~3.11 possible-image union, and the exclusion of \((\Ind_3)\)
from equality.  This is the source-level quotient possible-image construction
used before entering Remark~3.9.5.
The same construction is now also available at the typed-core level, before the
larger endpoint wrappers enter.  The source
\texttt{ThetaPilotClassPossibleImageSource} takes a possible-image family on
the concrete theta-pilot class itself and pulls it back along the forgetting
map from concrete Hodge-theater/log-theta choices.  Lean derives the
\((\Ind_1)\) and \((\Ind_2)\) region equalities from preservation of this class,
constructs the \((\Ind_1,\Ind_2)\)-equality-quotient possible-image family, and
records that \((\Ind_3)\) remains only the typed upper-semi log-volume
inequality.  This source now lowers directly to both the Step~(xi)
theta-pilot factorization and the quotient theta-pilot source: after one
record-pullback equality, Lean identifies the selected q-region with the
selected equality-quotient image, proves containment in the Theorem~3.11
possible-image union, and again exposes the absence of an \((\Ind_3)\)
equality generator.  Thus the class-indexed possible-image family reaches the
Remark~3.9.5 boundary without a manually supplied quotient-image package.  The
same lowering now has two direct endpoints: one returns the selected q-region
hull/log-volume audit, and the other continues through the constructed global
\(C_\Theta\) comparison to the existing dichotomy.  These two endpoints are now
also available one layer lower, from the lattice-key image law itself: the
Hodge-theater/history/log-theta-lattice invariance reconstructs the
possible-image formula before the selected q-region is sent into
Remark~3.9.5.
The same quotient source now has a direct class-law route,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{ofClassImageLawSource},
\end{array}
\]
which first converts same-class possible-image invariance into typed
fiber-transport invariance via
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassImageLawSource.}\\
\texttt{toFiberTransportSource}.  This uses the Lean theorem that fiber
transport is equivalent to equality of the concrete theta-pilot class, so the
class-image law now feeds the quotient construction without a separate
lattice-key payload.  There is also a lower direct route,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{ofLatticeImageLawSource},
\end{array}
\]
which starts from the Hodge-theater/history/label-forgotten-lattice/coric
same-key image law.  The quotient possible-image family is therefore obtained
after reconstructing the lattice formula from representatives, rather than by
first exposing an independent class-region formula.
The current descent from class formula to quotient source is now organized as a
chain of progressively more concrete boundaries.  At the top,
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassFormulaRecordSource}
identifies the Theorem~3.11 record family with a theta-pilot class formula.
The lattice-formula boundary then factors the class through the
Hodge-theater id, history label, coric datum, and the label-forgotten
\texttt{IUTStage1Theorem311ThetaPilotLatticeCoordinate}; the theorem
\texttt{thetaPilotLatticeCoordinate\_flProcessionTranslate} records that the
\(F_l\)-procession label is invisible to this theta-pilot coordinate.

Below the formula boundaries,
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotLatticeImageLawSource}
uses representatives and a same-lattice-key image law to reconstruct the
lattice formula internally.  The typed fiber-transport source replaces this
same-key law by a transport relation preserving the Hodge theater, history
label, label-forgotten lattice coordinate, and coric datum.  The
choice-space layer now proves that this transport relation is equivalent to
equality of the concrete theta-pilot class:
\texttt{thetaPilotClass\_eq\_iff\_latticeKey\_eq} gives the key-level
characterization, while
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberTransport.}\\
\texttt{iff\_thetaPilotClass\_eq} identifies fiber transport with class
equality.  Thus the same-key and same-class formulations are no longer parallel
payloads.  The equality-quotient source lowers the assumption further: it no
longer assumes fiber-region equality, but derives it from membership in the
\((\Ind_1,\Ind_2)\) equality orbit and the quotient pullback theorem.

The newest boundary is
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberInd12ChainSource}.
\end{array}
\]
It does not supply equality-orbit membership directly.  For each typed
theta-pilot fiber transport it supplies an explicit chain generated by concrete
\((\Ind_1)\) procession steps, concrete \((\Ind_2)\) local tensor steps,
symmetry, and composition.  Lean converts this chain into equality-orbit
membership, then into equality of quotient maps and equality of possible-image
regions.

This has now been refined once more by
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberProcessionTensorSource}.
\end{array}
\]
Here the finite procession part of the chain is no longer supplied.  Lean forms
the label shift
\[
j_2-j_1\in\mathbb{Z}/l\mathbb{Z}
\]
between the two \(F_l\)-labels, translates the source choice by this shift, and
uses \texttt{flProcessionTranslate\_ind1Step} to obtain the \((\Ind_1)\)
segment.  The only remaining chain input is then the concrete \((\Ind_2)\)
local tensor step from this shifted choice to the target choice.  The same
boundary now exposes
\texttt{fiberTransport\_processionShiftLabelAudit}: the canonical shift is the
unique \(F_l\)-translation aligning the two theta-pilot-fiber coordinates, and
its label action sends \(j_1\) to \(j_2\).  Thus the preferred boundary has
moved from ``construct an arbitrary equality chain'' to ``construct the local
tensor symmetry after the canonical procession-label shift''.

This boundary has now been lowered in seven stages.  First,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberLocalTensorDataSource}.
\end{array}
\]
It proves the shifted-coordinate equality from the theta-pilot fiber transport
and the \(\mathbb{Z}/l\mathbb{Z}\) label shift.  The \((\Ind_2)\) step is then
constructed from three local tensor equalities: procession state, direct-summand
count, and upper-semi state after the shift.  Second,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberDirectSummandSymmetrySource}
\end{array}
\]
replaces the direct-summand-count equality by a finite equivalence between the
two summand index sets.  Lean derives equality of the two cardinalities and then
reuses the local-tensor source.  Third,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberProcessionTransportSource}
\end{array}
\]
replaces the procession-state equality by a typed procession transport: equality
of the D-prime-strip procession identifier and equality of the chosen
representative.  The missing column equality is derived from the shifted
coordinate and the two procession-column laws, so Lean reconstructs the full
procession-state equality.  Fourth,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberUpperSemiTransportSource}
\end{array}
\]
replaces the upper-semi-state equality by a typed upper-semi transport.  This
transport preserves the non-column upper-semi compatibility data; the missing
log-theta-column equality is derived from the shifted coordinate and the two
upper-semi-column laws.  Lean then reconstructs the full upper-semi state.
Fifth,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberDirectSummandPacketSource}.
\end{array}
\]
It replaces the direct finite summand equivalence by packet-level data: source
and target local tensor packets, identification of their tensor states with the
two choices under comparison, and an equivalence of the corresponding capsule
index sets.  Since each packet records that its direct-summand count is its
capsule count, Lean reconstructs the direct-summand symmetry consumed by the
\((\Ind_2)\) local tensor step.  Sixth,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberDirectSummandActionPacketSource}
\end{array}
\]
replaces the capsule-index equivalence itself by a direct-summand packet action:
the source supplies direct-summand packet states and an action on the source
summand family whose induced capsule family is the target packet.  The induced
capsule action has the same finite index type as the source family, so Lean
derives the capsule-index equivalence and then the direct-summand symmetry.
Seventh,
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberInd2ActionPacketSource}
\end{array}
\]
replaces this arbitrary direct-summand-family action by the two typed
Theorem~3.11 local tensor-factor actions: the nonarchimedean \(\mathrm{Ism}\)
action and the archimedean order-two action.  Lean forgets either typed action
to the generic packet-action interface, derives the capsule-index equivalence,
and then reconstructs the direct-summand symmetry required by the \((\Ind_2)\)
step.  It now also reconstructs the post-procession concrete \((\Ind_2)\)
step itself from the typed packet symmetry, the procession transport, and the
upper-semi transport.  This reconstruction is now exposed as
\texttt{PostProcessionInd2ActionPacketAudit}, and the
\texttt{ofFiberInd2ActionPacketSource} quotient constructor carries the same
audit together with the selected quotient q-region and the no-\((\Ind_3)\)
equality guard.  At the place-audited boundary, the action-entry steps
now project to this typed packet symmetry through explicit local tensor symmetry-label
certificates.  The matching action, target capsule family, and equality of the
two local tensor symmetry labels are no longer separate generic inputs.  The
certificates have also been lowered one step: they may now be derived from a
packet-label compatibility between the tensor label and the direct-summand
family's typed symmetry kind.  The target kind is now derived from a
symmetry-kind transport law between the source and target packets, rather than
asserted as an independent target-side certificate.  These source-labelled
action-entry steps feed the place-audited possible-image quotient directly, so
region invariance and fiber membership can be proved at this stricter
\((\Ind_2)\) boundary.  The newest source constructors lower this once more:
the nonarchimedean and archimedean label-transport source steps can now be
built from the concrete local tensor \(\mathrm{Ism}\)/order-two labels,
the matching action's source kind, and a direct-summand kind-transport law.
The packet-label and target-kind data have now been
combined into one \texttt{SymmetryLabelTransportSource}: both tensor labels are
read against the source packet's typed summand kind, and the target summand
kind is transported from the source.  Its checked audit packages the whole
projection chain from label transport to transported packet labels, typed
\((\Ind_2)\) packet symmetry, direct-summand symmetry, and summand-count
equality.  The local Hodge/SHE layer now also exposes the smaller audit
\texttt{SymmetryLabelTransportSource.TransportAudit}: from the single
label-transport source it derives the source and target label certificates, the
target-kind transport, and equality of the two local tensor symmetry labels.
Thus the place-audited \((\Ind_2)\) packet audit records the label transport as
one source datum, rather than as separate source-label, target-label, and
target-kind assumptions.  The local tensor layer now retains this same datum in
\texttt{Ind2ActionPacketSymmetrySource}: a nonarchimedean case consists of two
packet states, one \texttt{SymmetryLabelTransportSource}, and an \(\mathrm{Ism}\)
direct-summand action; the archimedean case is the order-two analogue.  Its
projection derives the old \texttt{Ind2ActionPacketSymmetry}, the generic
direct-summand action-packet symmetry, and the summand-count equality.  The
place-audited action-entry layer now separates proof-only and data-carrying
forms: the older label-transport step, whose matching action is stored behind a
propositional existential, proves nonemptiness of this source object, while the
new nonarchimedean and archimedean label-transport source steps retain the
matching action as data and construct the source-level packet/action object
directly.  Step~(xi) uses this stricter source as
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotFiberInd2ActionPacketTransportSource},
then forgets it to the previous typed action-packet source before entering the
selected-\(q\) quotient constructor.  Its audit now retains the procession
transport fields and the non-column upper-semi transport fields that reconstruct
the post-procession \((\Ind_2)\) local tensor comparison, rather than exposing
only the projected packet symmetry.  The possible-image layer packages the next step as a quotient
audit: the same source-labelled transport is a generator of the
\((\Ind_1,\Ind_2)\) equality quotient, so the corresponding theta-pilot
possible-image regions agree and the acting place remains in its finite fiber.
The concrete choice layer now has
matching constructors for the typed transports: \((\Ind_1)\) is built from
\texttt{ProcessionTransport}, \((\Ind_2)\) from procession and upper-semi
transports plus the local summand-count equality, and \((\Ind_3)\) from
\texttt{UpperSemiTransport} together with the explicit log-theta-column
equality.  This transport boundary is now checked against the typed
Theorem~3.11 core itself:
\texttt{typedInd1ProcessionTransportAudit} and
\texttt{typedInd2LocalTransportAudit} produce the corresponding equality
generators, normalized-log-volume preservation, and equality-quotient
identifications, while \texttt{typedInd3UpperSemiTransportAudit} produces only
the one-sided upper-semi audit and the no-\((\Ind_3)\)-equality guard.  The
same boundary now has record-based forms
\texttt{Ind1ProcessionTransportSource},
\texttt{Ind2LocalTensorTransportSource}, and
\texttt{Ind3UpperSemiTransportSource}.  Their checked constructors build the
three concrete indeterminacy steps before the typed core derives the
equality/equality/upper-semi consequences.  Thus this layer no longer exposes a
loose list of Hodge-theater, procession, tensor, and upper-semi hypotheses at
the audit endpoint.  The
Step~(xi) fiber source now constructs the relevant record sources before
composing these checks as \texttt{PostProcessionTypedCoreTransportAudit}: the
canonical \(F_l\)-shift gives an
\texttt{Ind1ProcessionTransportSource}, and the post-shift fiber transport
gives an \texttt{Ind2LocalTensorTransportSource} from procession transport,
upper-semi transport, and direct-summand packet symmetry.  Thus a theta-pilot
fiber transport is first the canonical \(F_l\)-procession \((\Ind_1)\)-shift
and then the post-shift typed \((\Ind_2)\) local-tensor equality.  The finite label
correction is now justified by the \(Z/l\mathbb{Z}\)-torsor law itself:
\texttt{existsUnique\_translateFLLabel\_eq\_of\_toThetaPilotLatticeCoordinate\_eq}
proves that two representatives over the same theta-pilot lattice node are
connected by a unique \(F_l\)-translation, and the Step~(xi) source exposes this
as \texttt{fiberTransport\_processionShiftLabelAudit}.  Thus the whole fiber
transport preserves typed-core log-volume and equality-quotient class, with the
same evidence visible at the selected-\(q\) boundary.  That boundary now also
exports preservation of the concrete theta-pilot class and the one-sided
\((\Ind_3)\) upper-semi relation audit; \((\Ind_3)\) is therefore visible at the
endpoint as upper-semi data, not as an equality-quotient transport.  The
remaining source payload is now lower and sharper: construct the paper-side
label transports for the \(ZMod(\ell)\)-labelled local log-shell
representatives, the \(\mathrm{Ism}\)/order-two actions, procession transports,
and upper-semi transports from the underlying Hodge-theater arithmetic,
log-theta lattice, and Frobenioid packet data.

The experiment surface has been lowered to this boundary as well.  The endpoint
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaThetaPilotClassImages\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ValuationBallHaarFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}
\end{array}
\]
starts from the concrete class-indexed possible-image family, constructs the
factorization source internally, and then reuses the same valuation-ball
formula-gap/local-to-global \(C_\Theta\) corridor.  Its audit exposes the class
pullback, the derived \((\Ind_1)\)/\((\Ind_2)\) class invariance, the selected
q-region's containment in the Theorem~3.11 possible-image union, the
constructed valuation endpoint, and the final Corollary~3.12 dichotomy.  Thus
the strongest public valuation-ball boundary no longer asks for an arbitrary
theta-class map.  This experiment boundary has now also been lowered to the
class image law:
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaThetaPilotClassImageLaw\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ValuationBallHaarFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}.
\end{array}
\]
It consumes \texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassImageLawSource},
constructs the class-indexed family internally, and exposes the representative
law, same-class image invariance, selected q-region containment, constructed
valuation endpoint, local-to-global \(C_\Theta\) handoff, and final dichotomy.
This public valuation boundary now also has a direct class-region endpoint,
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaThetaPilotClassRegion\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ValuationBallHaarFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}\\
\quad\texttt{\_endpoint}.
\end{array}
\]
It consumes \texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassRegionSource},
derives the class-image law internally, and exposes the representative section,
class-region pullback formula, same-class invariance, selected q-region
containment, valuation endpoint, local-to-global \(C_\Theta\) handoff, and
final dichotomy.  The lower source layer feeding this boundary now factors the
class formula through the label-forgotten log-theta lattice coordinate, so the
remaining theorem-side payload is the proof that theta-pilot possible images
are invariant on the corresponding same-key fibers.
The same concrete quotient source now feeds the constructed
Remark~3.9.5 hull/determinant source directly.  The constructor
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{toRemark395ConstructedHolomorphicHullDeterminantSource}
\end{array}
\]
takes the q-region to be the selected Theorem~3.11 quotient possible image.
Thus the containment
\(q\subseteq\bigcup_i\Theta\mathrm{Image}_i\) is derived from the multiradial
source, not passed as an independent Remark~3.9.5 hypothesis.  The endpoint
then identifies this q-region with the quotient theta-pilot image, places it
inside the quotient canonical hull, and carries forward the existing
determinant-to-\(\theta\) log-volume bound.  The selected-q handoff is now
also exposed as
\texttt{toRemark395SelectedQHullLogVolumeAudit\_endpoint}: it packages the
constructed q-region equality, canonical-hull containment, q-region
log-volume bound, \((\Ind_1,\Ind_2)\) hull-log-volume equalities, and the
separate \((\Ind_3)\) upper-semi inequality in one checked statement.
Composing once more with the constructed global-\(C_\Theta\) audit gives
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaQuotientThetaPilotSource.}\\
\quad\texttt{toRemark395ConstructedGlobalCThetaScaleComparisonAudit}.
\end{array}
\]
This endpoint builds the constructed Remark~3.9.5 source internally, reads the
selected q-region and the \(q_{\log}\le\theta_{\log}\) comparison from that
source, and proves the Corollary~3.12 ordered-real dichotomy after the single
remaining global comparison
\(C_{\Theta,\mathrm{can}}\le C_\Theta\).  Thus the current boundary is no
longer the possible-image or q-containment step; it is the local-to-global
comparison of the constructed canonical scale with the paper's global
\(C_\Theta\).
The strict typed \((\Ind_2)\) action-packet source now reaches this same
boundary directly.  The endpoints
\[
\begin{array}{l}
\texttt{ofFiberInd2ActionPacketSource\_toRemark395SelectedQHullLogVolumeAudit}\\
\quad\texttt{\_endpoint},\\[2mm]
\texttt{ofFiberInd2ActionPacketSource\_toRemark395ConstructedGlobalCThetaScale}\\
\quad\texttt{ComparisonAudit\_endpoint}
\end{array}
\]
construct the quotient source internally and return the
\texttt{PostProcessionTypedCoreTransportAudit} together with the selected
q-region hull/log-volume audit and the global \(C_\Theta\) dichotomy.  This
keeps the finite procession shift and post-shift \((\Ind_2)\) packet symmetry
visible at the final handoff, rather than hiding them behind an intermediate
quotient-source argument.
The stricter source-level packet/action transport source now has the same two
handoff endpoints.  Its strict fiber endpoint exposes an audit of the retained
\texttt{Ind2ActionPacketSymmetrySource}, so the packet states, label transport,
and typed \(\mathrm{Ism}\)/order-two action are checked before being forgotten to
the projected \((\Ind_2)\) symmetry.  The quotient-constructor endpoint and both
Remark~3.9.5 endpoints also return the named payload
\texttt{LowerTransportPayload}.  This payload contains the procession transport,
the upper-semi transport, and the field equalities needed to compare the shifted
choice with the target choice.  The local comparison handoff is now summarized
by \texttt{FiberTransportQuotientComparisonAudit}.  This audit starts with the
retained source-level \((\Ind_2)\) packet/action transport object, checks its
packet-source audit, then records the typed post-procession
\((\Ind_1,\Ind_2)\) transport audit, equality-quotient-map preservation,
theta-pilot-class preservation, possible-image region invariance, and the
induced lattice-image law.  It also records explicitly that \((\Ind_3)\)
contributes only the upper-semi relation and no equality-quotient generator.
The same handoff still exposes the selected q-region, the global
\(C_\Theta\) dichotomy, fiber-transport log-volume preservation,
direct-summand-count preservation, and the exclusion of \((\Ind_3)\) from the
equality quotient.
The named audit \texttt{SourceLevelTransportQuotientAudit} now packages this
same lower payload with the one-sided quotient audit before the
Remark~3.9.5 hull/determinant source is introduced.
The subsequent
\texttt{SourceLevelTransportRemark395SelectedQAudit} and
\texttt{SourceLevelTransportRemark395GlobalCThetaAudit} carry this same
source-level quotient audit across the selected-q hull/log-volume comparison
and the global \(C_\Theta\) dichotomy, so the strict transport data is visible
at the actual Corollary~3.12 handoff.
The audit \texttt{SourceLevelTransportFLProcessionRemark395Ob5Ob6Audit}
connects the same strict source to the concrete \(F_l\)-label translation and
the Remark~3.9.5 Ob5--Ob6 \(\Phi/\Xi\) hull estimates.
At the procession boundary itself, the \(\Phi\)-side can now be the canonical
hull family and the \(\Xi\)-side can be built from the exact Remark~3.9.5
log-volume source, instead of being supplied as an arbitrary family.
The same canonical/exact family construction is also exposed at the typed
indeterminacy Ob5--Ob7 experiment surface, where the Ob7 prime-strip
compatibility remains the only additional payload.
The full-label-backed version additionally exhibits the translated label in
the no-omission \(F_l\) family and records the corresponding \((\Ind_1)\)
log-volume preservation before the hull estimates are used.
The selected-q specialization now uses the canonical no-omission full-label
source internally and identifies the selected q-region with the
equality-quotient possible region before applying the same Ob5--Ob6 estimates.
The corresponding global \(C_\Theta\) audit carries this canonical full-label
selected-q evidence through to the final dichotomy.
An exact-\(\Xi\) specialization now constructs the \(\Phi\)-family canonically
and obtains \(\Xi\) from the Remark~3.9.5 exact log-volume source, rather than
accepting arbitrary approximant families at this boundary.
At the strongest current local boundary, the endpoint
\texttt{ConcreteHodgeTheaterLogThetaCompactOpenLogKummerMapClosedCorollary312Endpoint}
starts from compact-open log-Kummer map data over the transported theta-region
family.  It constructs the log-Kummer graph, pointwise log-shell source,
exact-\(\Xi(P_B)\) family, Remark~3.9.5 hull/determinant source, and
source-derived \(\IUT{}\) IV \(C_\Theta\) comparison before exposing the final
Corollary~3.12 dichotomy.  The endpoint also records the derived signed bound
\(\theta_{\rm signed}\leq C_\Theta(-q_{\rm signed})\) and the guard that
\((\Ind_3)\) contributes no equality-quotient generator.  Its finite-place
variant,
\texttt{ConcreteHodgeTheaterLogThetaCompactOpenLogKummerMapFinitePlaceClosedCorollary312Endpoint},
constructs the local-global source from finite local Step~(xi)/Haar summation
data, so the compact-open log-Kummer boundary no longer has to receive the
generic local-global \(C_\Theta\) source directly.  The normalized-Haar variant
lowers this once more: the total Haar defect is derived from a finite-place
lower-bound source, i.e. placewise nonnegativity plus a distinguished normalized
valuation-ball contribution, before the same compact-open Corollary~3.12
boundary is entered.  The p-adic unit-ball variant lowers this lower-bound
source to local Haar-normalization data over the finite places: the defect is
the unit-ball dilation index, and the distinguished-place lower bound is proved
from primality and finite-dimensionality.  A valuation-ball formula-gap matched
variant now enters the same compact-open boundary from the IUT IV
Theorem~1.10 source itself: the audit retains the valuation-ball
formula-gap source, the p-adic prime-error split, and the Step~(xi)
arithmetic-degree calibration before projecting to the closed local-global
\(C_\Theta\) handoff.  The endpoint now also has a checked
\texttt{RemainingPayloadAudit}; this is a projection, not an additional
assumption, and records in one place the closed no-raw-comparison audit, the
source-derived signed bound, the final dichotomy, and the exclusion of
\((\Ind_3)\) from equality transport.
The valuation-ball source below this endpoint now has its own
\texttt{ValuationBallFormulaGapSourceDODAudit}.  This audit keeps the
Theorem~1.10 valuation-ball provenance visible while projecting the finite-place
summation audit, the IUT~IV arithmetic-gap handoff, the coarse local-global
assembly expansion, and the closed no-raw-comparison \(C_\Theta\) dichotomy
from the same source object.  It now also contains the explicit finite-place
\(C_\Theta\) chain: the canonical scale, arithmetic upper term, and main term
are identified with finite sums, the summed Step~(xi)/Haar inequality and unit
Haar defect give the global arithmetic gap, and the IUT~IV handoff yields the
signed \(C_\Theta\) bound.  The same source audit also projects the local
formula-gap estimate audit for the distinguished Proposition~1.4 and
archimedean Proposition~1.5 comparison objects.  The endpoint-level
\texttt{RemainingPayloadAudit} projects this valuation-ball source audit
directly, and its
\texttt{remainingPayloadAudit\_formulaGapLocalEstimateAudit} and
\texttt{remainingPayloadAudit\_finitePlaceCThetaChain} projections now return
the local formula-gap audit and the finite-place \(C_\Theta\) calculation at
the compact-open endpoint itself.  The public compact-open boundary was first
lowered to the calibrated valuation-ball source:
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaCompactOpenLogKummerMap}\\
\texttt{ValuationBallHaarCalibratedFormulaGapMatchedStepXI}\\
\texttt{ClosedCorollary312Endpoint}.
\end{array}
\]
That boundary was then tightened to the derived valuation-ball source, to the
unscaled degree-bound source, to the degree-identified unscaled source, through
the local-degree formula source, to the object-backed local-degree source, and
to the arithmetic-divisor-backed valuation-ball source:
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaCompactOpenLogKummerMap}\\
\texttt{ValuationBallHaarArithmeticDivisorBackedLocalDegreeStepXI}\\
\texttt{ClosedCorollary312Endpoint}.
\end{array}
\]
It consumes a valuation-ball source whose public local payload is the
arithmetic-divisor-backed matched local-degree component source.  At each
distinguished nonarchimedean place the local different and conductor
contributions are the local degrees of the Theorem~1.10 arithmetic divisors,
with nonnegativity supplied by divisor effectivity and with the Proposition~1.4
tensor components identified explicitly.  The archimedean branch is still the
constructed metric component.  A synchronization proof identifies this
additive arithmetic-divisor formula core with the additive projection of the
valuation-ball Theorem~1.10 formula source, after which the object, local
formula, degree-identified, unscaled, derived, and calibrated valuation-ball
sources are constructed internally before the final dichotomy is inherited.
The endpoint audit exposes the arithmetic-divisor-backed source endpoint and
its local-degree audit alongside the inherited Corollary~3.12 dichotomy.
The compact-open boundary has now been lowered one more source step to the
Record Ob3/Ob5 determinant/log-volume handoff:
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaCompactOpenLogKummerMap}\\
\texttt{ValuationBallHaarRecordOb3Ob5ArithmeticDivisorBacked}\\
\texttt{LocalDegreeStepXIClosedCorollary312Endpoint}.
\end{array}
\]
This endpoint consumes the record-canonical adjusted determinant source and a
valuation-ball Record Ob3/Ob5 source.  Lean then derives the Step~(xi)
valuation-ball determinant equality and the canonical-scale finite-sum equality
by projection through
\texttt{RecordOb3Ob5ValuationBallStepXIDeterminantHandoffAudit}, before
entering the arithmetic-divisor-backed compact-open route above.  Thus the
valuation-ball compact-open endpoint no longer accepts the final determinant
and \(C_{\Theta,\mathrm{can}}\)-sum equalities as its public mathematical
payload.
This boundary has now been pushed one step further down to the valuation-cover
source itself:
\[
\begin{array}{l}
\texttt{ConcreteHodgeTheaterLogThetaCompactOpenLogKummerMap}\\
\texttt{ValuationBallHaarValuationCoverRecordOb3Ob5}\\
\texttt{ArithmeticDivisorBackedLocalDegreeStepXIClosedCorollary312Endpoint}.
\end{array}
\]
The endpoint consumes a valuation-ball factor-calibrated Haar tensor-packet
cover and the single synchronization
\(\mathrm{possibleRegion}=\Theta\mathrm{Image}\) with the Theorem~3.11 record
family.  The Record Ob3/Ob5 adjusted determinant/log-volume source is then
constructed internally from the valuation-ball cover before the Record Ob3/Ob5
valuation-ball handoff and compact-open Corollary~3.12 dichotomy are invoked.
This removes \texttt{recordAdjustedSource} as a separate endpoint input at this
boundary.  The same endpoint now also carries the source-level transport
quotient audit produced from the concrete \((\Ind_2)\) packet/action transport
source.  Thus the final compact-open boundary exposes, rather than merely
projects at the end, the pullback of quotient possible images, the selected
q-region as an equality-quotient image, the containment in the Theorem~3.11
union, and the exclusion of \((\Ind_3)\) from equality transport.
Thus the strict quotient boundary already shows the full
equality/equality/upper-semi pattern: \((\Ind_1)\) and \((\Ind_2)\) provide
equality transport, while \((\Ind_3)\) remains only one-sided upper-semi data.

The bridge to the constructed Remark~3.9.5 source is now named as
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311QuotientMultiradialRemark395Compatibility}.
\end{array}
\]
Its essential field identifies the constructed Step~(xi) q-pilot region with
the selected Theorem~3.11 possible image.  From this, Lean re-derives
\[
  q\mathrm{Region}\subseteq
  \bigcup_i \Theta\mathrm{Image}_i
\]
through the quotient-aware Theorem~3.11 source, instead of treating the
record-union containment as an unrelated payload.  The construction-source
endpoint also produces this compatibility and the quotient pullback once the
constructed Remark~3.9.5 q-pilot region is identified with the selected possible
image.
The one-sided version is now also a first-class audit:
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource.}\\
\quad\texttt{OneSidedRemark395CompatibilityAudit}.
\end{array}
\]
It packages the constructed q-pilot equality with the
\((\Ind_1,\Ind_2)\)-equality quotient pullback, the selected quotient possible
image, containment in the Theorem~3.11 possible-image union, the explicit
absence of \((\Ind_3)\) generators from the equality quotient, and the separate
\((\Ind_3)\) upper-semi log-volume inequality.  This is the compatibility
object now exported by the preferred local-to-global \(C_\Theta\) audits.
The same one-sided constructor now has a packet-normalized concrete entry:
\[
\begin{array}{l}
\texttt{ofConcreteHodgeTheaterLogThetaVertical}\\
\quad\texttt{LogKummerPacketAlignment}.
\end{array}
\]
It constructs the public Theorem~3.11 source from theta-pilot class images and
the vertical log-Kummer packet-aligned procession source, and its audit exposes
the packet-normalized average equality together with the inherited selected
q-region endpoint.  This is the current preferred bridge from the concrete
Hodge-theater/log-theta-lattice layer into the Step~(xi) corridor.
The next refinement removes the single opaque arithmetic-gap field from the
preferred source surface.  The Lean structure
\[
\begin{array}{l}
\texttt{ConstructedTheorem311FinitePlaceLocalGlobalCThetaSource}
\end{array}
\]
introduces a finite set of local places and records four local functions:
the local canonical Step~(xi) scale, the local \IUT{} IV arithmetic upper
contribution, the local main-log contribution, and the local Haar-normalization
defect.  Its load-bearing local assertion is the pointwise inequality
\[
  C_{\Theta,\mathrm{can},v}+\delta_v
    \leq
  A_v-M_v .
\]
Lean proves
\[
  C_{\Theta,\mathrm{can}}+1
    \leq
  \mathrm{arithmeticUpperTerm}-\mathrm{mainLogTerm}
\]
by summing these local inequalities with
\(\texttt{Finset.sum\_le\_sum}\), using the equalities
\[
  C_{\Theta,\mathrm{can}}=\sum_v C_{\Theta,\mathrm{can},v},\qquad
  \mathrm{arithmeticUpperTerm}=\sum_v A_v,\qquad
  \mathrm{mainLogTerm}=\sum_v M_v,
\]
and the finite-divisor/Haar normalization condition
\[
  1\leq\sum_v \delta_v .
\]
The resulting conversion theorem
\[
\begin{array}{l}
\texttt{ConstructedTheorem311FinitePlaceLocalGlobalCThetaSource}\\
\quad\texttt{.toConstructedTheorem311IndeterminacyLocalGlobalCThetaSource}
\end{array}
\]
constructs the coarser source object automatically.  The public finite-divisor
endpoint
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{Theorem311FinitePlaceLocalGlobalCThetaFiniteDivisorVerticalIQ}
\end{array}
\]
therefore derives the Corollary~3.12 dichotomy from a finite local-place
assembly source, rather than from a raw numerical bound, a raw
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison, or a single global
arithmetic-gap hypothesis.  The remaining mathematical work has been pushed
down to constructing the local terms \(C_{\Theta,\mathrm{can},v}\), \(A_v\),
\(M_v\), and \(\delta_v\) from the actual Theorem~3.11/Step~(xi)/\IUT{} IV
objects and proving the pointwise local inequalities.

The preferred local-to-global surface has also been tightened to use the
one-sided Theorem~3.11 construction directly.  The route now passes through
localized Step~(xi) determinant terms, normalized Haar defects, \(p\)-adic
unit-ball Haar indices, IUT~IV local arithmetic defects, arithmetic-divisor
evaluation, Theorem~1.10 local case formulas, Proposition~1.4/1.5 construction
sources, and finally the additive-Haar local analytic construction source.  The
public theorem
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{Theorem311OneSidedIUTIVTheorem110}\\
\quad\texttt{AdditiveHaarLocalAnalyticArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaFiniteDivisorVerticalIQ}
\end{array}
\]
is the current preferred finite-divisor endpoint.  The source records carry an
\texttt{IUTStage1Theorem311OneSidedMultiradialConstructionSource}, identify the
constructed Remark~3.9.5 q-pilot region with its selected possible image, and
then feed the same finite-place Step~(xi)/Haar summation into the
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison.  The public endpoint
returns the Corollary~3.12 dichotomy while also reporting the equality quotient
generated only by
\((\Ind_1)\) and \((\Ind_2)\), the separate one-sided \((\Ind_3)\) log-volume
inequality, and the selected q-region containment in the Theorem~3.11
possible-image union.  Thus the current preferred route no longer exposes the
raw numeric \(C_\Theta\) comparison and no longer uses a bare typed
indeterminacy core at the local-to-global boundary.
At the one-sided finite-place closed boundary, Lean now also has a
realified-packet-source variant: the Step~(x) finite-divisor and
\((\Ind_3)\)-source equalities are recovered from the realified Frobenioid
log-Kummer packet source while the local-to-global \(C_\Theta\) comparison
remains closed by the finite-place summation source.
The same Step~(x) lowering is now available at the preferred additive-Haar
local-analytic boundary.  The endpoint with suffix
\texttt{\_ofRealifiedFrobenioidPacketSource} keeps the full Theorem~3.11/\IUT{}
IV Theorem~1.10 additive-Haar \(C_\Theta\) route, but replaces the public
packet-local Kummer/forgetting fields and finite-divisor/\((\Ind_3)\)
equalities by a single realified Frobenioid log-Kummer packet source.  Thus the
currently preferred finite-divisor endpoint exposes the closed local-to-global
comparison and the source-recovered Step~(x) packet equalities at the same
boundary.
The first closed local-to-global \(C_\Theta\) boundary has now also been tied
to the constructed qualitative Hodge/\(\SHE\)/\(\IPL\) source.  The declaration
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{QualitativeHodgeSHEIPLIndeterminacyLocalGlobalCTheta}\\
\quad\texttt{FiniteDivisorVerticalIQ}
\end{array}
\]
projects the \(\IPL\) link from
\texttt{IUTStage1ConstructedQualitativeFiniteHodgeSHEIPLConstructionSource}
and returns
\texttt{ConstructedQualitativeHodgeSHEIPLIndeterminacyLocalGlobalCThetaAudit}.
That audit records the constructed \(\IPL\) link source, structured
Hodge/\(\SHE/\APT\) evidence, transport guards, the local-to-global
\(C_\Theta\) endpoint, the \(\IUT{}\,\mathrm{IV}\) handoff, the global
\(C_\Theta\) comparison audit, and the final dichotomy in one checked
proposition.
The same constructed qualitative provenance is now also available at the
finite-place local-to-global boundary:
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{QualitativeHodgeSHEIPLFinitePlaceLocalGlobalCTheta}\\
\quad\texttt{FiniteDivisorVerticalIQ}
\end{array}
\]
returns an audit recording the finite local-place sums, placewise
Step~(xi)/Haar inequality, total Haar defect lower bound, derived
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison, constructed
Hodge/\(\SHE\)/\(\IPL\) bridge, and final dichotomy.
The one-sided finite-place route now has the same constructed qualitative
entry point:
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{QualitativeHodgeSHEIPLOneSidedFinitePlaceLocalGlobalCTheta}\\
\quad\texttt{FiniteDivisorVerticalIQ}.
\end{array}
\]
Its audit adds the Theorem~3.11 one-sided quotient record to the finite-place
payload: \((\Ind_1)\) and \((\Ind_2)\) supply the equality quotient for
possible images, while \((\Ind_3)\) remains a one-sided upper-semi
log-volume relation.  The deeper additive-Haar route below now reuses this
same one-sided audit rather than returning to a free-standing \(\IPL\)-link
surface.

The newest constructor,
\texttt{ConstructedTheorem311OneSidedStepXILocalTermCThetaSource}, removes one
more arbitrary layer from the finite-place comparison.  Its local canonical
terms are the weighted adjusted localization contributions of an
\texttt{IUTStage1Remark395Ob3Ob4LocalizedVectorBundleDeterminantSource}; the
local arithmetic upper contribution is then definitionally this Step~(xi) term
plus the local Haar defect and local main-log term.  Lean derives the
pointwise Step~(xi)/Haar inequality and constructs the finite-place
local-to-global source from these data.  The remaining source obligations at
this boundary are now explicit: identify \(C_{\Theta,\mathrm{can}}\) with the
sum of the localized Step~(xi) terms, identify the \IUT{} IV arithmetic and
main-log terms with their local sums, and identify the local Haar-defect terms
with the precise \IUT{} IV local arithmetic defects.
The Haar-defect lower-bound input is no longer consumed as a raw sum
inequality:
\texttt{IUTStage1FinitePlaceHaarDefectLowerBoundSource} records nonnegative
local Haar defects and a distinguished normalized valuation-ball place whose
defect is at least one, and Lean proves
\(\sum_v \delta_v\geq 1\) from those facts.  The stricter constructor
\texttt{ConstructedTheorem311OneSidedNormalizedHaarStepXILocalTermCThetaSource}
threads this derived bound into the Step~(xi) local-to-global comparison and
now has its own finite-divisor vertical-\(IQ\) endpoint.
The next constructor
\texttt{IUTStage1FinitePlacePadicUnitBallHaarIndexDefectSource} derives this
finite-place lower-bound source from placewise \(p\)-adic unit-ball Haar
normalization.  For each place \(v\), the local defect is the dilation index
\[
  \delta_v=p_v^{[K_v:\mathbb Q_{p_v}]};
\]
Lean proves \(\delta_v\geq0\) and \(\delta_{v_0}\geq1\) for a distinguished
normalized place from primality of \(p_v\) and the natural finrank exponent.
The wrapper
\texttt{ConstructedTheorem311OneSidedPadicUnitBallHaarStepXILocalTermCThetaSource}
threads this \(p\)-adic Haar-index source into the normalized Step~(xi)
local-to-global surface, and the corresponding finite-divisor vertical-\(IQ\)
endpoint projects through the normalized-Haar route to the same Corollary~3.12
dichotomy.
The new source
\texttt{IUTStage1FinitePlaceIUTIVLocalArithmeticDefectSource} names the
paper-side local arithmetic-defect term in the \IUT{} IV \(C_\Theta\) estimate
and records its placewise equality with the \(p\)-adic unit-ball Haar index.
It therefore derives the same nonnegativity, distinguished-place lower bound,
and total \(\sum_v\delta_v\geq1\) statement for the IUT IV local defects.  The
corresponding Step~(xi) wrapper
\texttt{ConstructedTheorem311OneSidedIUTIVArithmeticDefectStepXILocalTermCThetaSource}
expresses the arithmetic upper sum using these named IUT IV local defects and
projects to the p-adic Haar-index route by the recorded equality.  Its
finite-divisor vertical-\(IQ\) endpoint is now the preferred local-to-global
\(C_\Theta\) surface for this part of the corridor.  The divisor-evaluation
refinement
\texttt{IUTStage1IUTIVThetaPilotArithmeticDivisorLocalEvaluationSource} now
records the local Definition~1.9/Theorem~1.10 arithmetic-divisor degree
evaluation: local different degrees, conductor degrees, absorbed prime/error
contributions, local main-log terms, and finite-sum identities recovering
\(\log\mathrm{Diff}_{F_{\mathrm{tpd}}}\),
\(\log\mathrm{Cond}_{F_{\mathrm{tpd}}}\), the absorbed
\(10(e^\ast_{\mathrm{mod}}l+\eta_{\mathrm{prm}})\) term, the global arithmetic
upper term, and the global main-log term.  The wrapper
\texttt{ConstructedTheorem311OneSidedIUTIVArithmeticDivisorEvaluationStepXILocalTermCThetaSource}
threads this source into Step~(xi), leaving the local matching condition that
the IUT IV arithmetic upper contribution is the Step~(xi) weighted determinant
contribution plus the local IUT IV defect plus the local main-log contribution.
The next source layer now makes this more faithful to Definition~1.9 itself.
\texttt{IUTStage1IUTIVArithmeticDivisorSource} formalizes a finite arithmetic
divisor as coefficients \(c_v\), degree weights, a positive normalizing degree,
support, effectivity, local normalized degree summands, and the theorem that the
global normalized degree is the finite sum of the local summands.
\texttt{IUTStage1IUTIVTheorem110ArithmeticDivisorSource} packages the three
paper divisors \(d_{\mathrm{ADiv}}\), \(q_{\mathrm{ADiv}}\), and
\(f_{\mathrm{ADiv}}\), including effectivity, equality of the conductor and
q-parameter supports, and recovery of
\(\log\mathrm{Diff}_{F_{\mathrm{tpd}}}\) and
\(\log\mathrm{Cond}_{F_{\mathrm{tpd}}}\) from normalized degrees.
\texttt{IUTStage1IUTIVTheorem110LocalEstimateGateSource} names the three local
cases of Theorem~1.10, Steps~(v)--(vii): distinguished nonarchimedean,
nondistinguished nonarchimedean with zero upper bound, and archimedean.  Its
endpoint proves the local upper-semi bound into the arithmetic-minus-main-log
gap and supplies the finite-sum identities for the absorbed prime/error and
main-log terms.  The preferred local boundary now refines this gate through
\texttt{IUTStage1IUTIVTheorem110LocalCaseFormulaSource}.  This source defines
the local procession upper bound by the paper's case split: the distinguished
nonarchimedean Step~(v) formula, zero for the nondistinguished
nonarchimedean Step~(vi) branch, and the archimedean Step~(vii) formula.  Lean
constructs the older gate source from this formula-level source, so the
Step~(vi) zero contribution is a theorem of the constructor rather than a
separate payload field.  The wrapper
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110FormulaArithmeticDivisorStepXILocalTermCThetaSource}
threads this stricter typed Theorem~1.10 layer into the Step~(xi) route.  Thus
the preferred public route no longer exposes the raw total Haar-defect sum
inequality, an unnamed Haar-defect summand, the global arithmetic/main-log sum
identities, bare local degree functions, or a raw nondistinguished local-zero
field as separate endpoint hypotheses.
The most recent refinement moves one layer further into the local analytic
estimates of \IUT{} IV.  The Lean source
\texttt{IUTStage1IUTIVProposition14DistinguishedLocalLogShellEstimate}
records the Proposition~1.4(iii) chain from the distinguished
nonarchimedean log-shell container through the Proposition~1.7 weighted average
to the Step~(v) coarse procession-normalized bound.  The source
\texttt{IUTStage1IUTIVProposition14NondistinguishedLocalLogShellEstimate}
records the Proposition~1.4(iv) zero log-volume statement for the
nondistinguished branch, and Lean derives the corresponding nonnegative local
arithmetic gap.  The archimedean source
\texttt{IUTStage1IUTIVProposition15ArchimedeanLocalMetricEstimate} records the
Proposition~1.5(iii),(iv) metric container estimate and proves the elementary
Step~(vii) exact-to-coarse comparison from \(\log(\pi)\leq2\) and \(l\geq5\).
These three objects feed
\texttt{IUTStage1IUTIVTheorem110PropositionLogShellFormulaSource} and then
\texttt{IUTStage1IUTIVTheorem110PropositionArithmeticDivisorEvaluationSource},
which now projects to the formula-level Theorem~1.10 route.

The preferred boundary now goes one step lower.  The source
\texttt{IUTStage1IUTIVProposition14DistinguishedLocalLogShellConstructionSource}
constructs the distinguished Proposition~1.4 estimate from finite-extension
Haar normalized log-volume data, the displayed Proposition~1.4(iii) first and
second container bounds, the Proposition~1.7 weighted-average comparison, and
the Step~(v) coarse procession-normalized bound.  The source
\texttt{IUTStage1IUTIVProposition14NondistinguishedLocalLogShellConstructionSource}
constructs the nondistinguished Proposition~1.4(iv) estimate from the same
finite-extension Haar normalization, identifying the tensor container with the
normalized integral container and deriving its zero log-volume.  The source
\texttt{IUTStage1IUTIVProposition15ArchimedeanMetricConstructionSource}
records the finite sets \(I,V\), the direct-sum cardinality
\(2^{|I|-1}|V|^{|I|}\), primitive-automorphism preservation of the integral
structure, and the vector containment used in Proposition~1.5(iv), then
projects to the archimedean exact-to-coarse estimate.  These construction
sources feed
\texttt{IUTStage1IUTIVTheorem110LocalAnalyticConstructionFormulaSource} and
\texttt{IUTStage1IUTIVTheorem110LocalAnalyticArithmeticDivisorEvaluationSource}.
This finite-extension construction layer is now an intermediate projection.
The additive-Haar-backed route is now an intermediate projection in the
preferred local-to-global \(C_\Theta\) boundary.  The compact-open declarations
\texttt{IUTStage1IUTIVProposition14DistinguishedCompactOpenHaarLogShellSource}
and
\texttt{IUTStage1IUTIVProposition14NondistinguishedCompactOpenHaarLogShellSource}
lower Proposition~1.4 to compact-open topology/Haar normalization data; the
additive declarations
\texttt{IUTStage1IUTIVProposition14DistinguishedAdditiveHaarLogShellSource}
and
\texttt{IUTStage1IUTIVProposition14NondistinguishedAdditiveHaarLogShellSource}
lower the same estimates to additive Haar normalization on the local additive
carrier.  These feed
\texttt{IUTStage1IUTIVTheorem110AdditiveHaarLocalAnalyticConstructionFormulaSource}
and
\texttt{IUTStage1IUTIVTheorem110AdditiveHaarLocalAnalyticArithmeticDivisorEvaluationSource}.
The newest Lean layer lowers this further to valuation-ball additive Haar data.
The sources
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVProposition14DistinguishedValuationBallAdditiveHaarLogShellSource},\\
\texttt{IUTStage1IUTIVProposition14NondistinguishedValuationBallAdditiveHaarLogShellSource}
\end{array}
\]
replace the generic additive normalization input by
\texttt{IUTStage1ValuationBallAdditiveHaarNormalizationSource}, whose audit
identifies the ring of integers and chosen compact open subset as valuation
balls, proves compact-openness of the unit ball and selected ball, and records
the normalized Haar/log-volume uniformizer shift.  These proposition-level
objects feed
\texttt{IUTStage1IUTIVTheorem110ValuationBallAdditiveHaarLocalAnalyticConstructionFormulaSource}
and
\texttt{IUTStage1IUTIVTheorem110ValuationBallAdditiveHaarLocalAnalyticArithmeticDivisorEvaluationSource},
which project to the additive-Haar, local-analytic, Proposition-level,
formula-level, and theta-pilot arithmetic-divisor evaluation records.  The
valuation-ball layer now also reaches the named formula-to-gap boundary:
\texttt{IUTStage1IUTIVTheorem110ValuationBallAdditiveHaarFormulaGapMatchedArithmeticDivisorEvaluationSource}
retains the distinguished Step~(v) and archimedean Step~(vii) gap comparison
objects while forcing the finite Proposition~1.4 inputs through valuation-ball
Haar normalization, and then projects to the additive-Haar formula-gap matched
source.
The distinguished and archimedean formula-to-gap comparisons have now been
split out as named source objects:
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaarFormulaGapComparisonSource},\\
\texttt{IUTStage1IUTIVTheorem110ArchimedeanMetricFormulaGapComparisonSource}.
\end{array}
\]
The first carries the local Proposition~1.4 additive-Haar log-shell source and
derives the container-to-arithmetic-gap comparison; the second carries the
Proposition~1.5 metric source and derives the corresponding archimedean
container-to-gap comparison.  They assemble into
\begin{center}
\small
\begin{tabular}{l}
\texttt{IUTStage1IUTIVTheorem110AdditiveHaar}\\
\quad\texttt{FormulaGapMatchedArithmeticDivisorEvaluationSource},
\end{tabular}
\end{center}
which is now an intermediate projection from the valuation-ball version and
projects to the existing additive-Haar arithmetic-divisor evaluation source.
Thus these two gap inequalities are no longer only anonymous fields at the
local analytic boundary.  This source is now consumed at the experiment layer
by
\[
\begin{array}{l}
\texttt{IUTStage1ValuationBallHaarTheorem110FormulaGapMatched}\\
\quad\texttt{PrimeErrorPadicDefectMainSource},\\
\texttt{IUTStage1ValuationBallHaarTheorem110StepXIFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicPrimeErrorFormulaMatchingSource}.
\end{array}
\]
The first record keeps the valuation-ball formula-gap Theorem~1.10 source
together with the \(p\)-adic Haar defect/main split; the second adds the
Step~(xi) arithmetic-degree calibration and projects to the additive
formula-matching core.  This valuation-ball payload now reaches the
local-to-global \(C_\Theta\) boundary as
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\quad\texttt{ValuationBallHaarFormulaGapMatchedArithmeticDegree}\\
\quad\texttt{PadicFormulaMatchedStepXILocalTermCThetaSource}.
\end{array}
\]
That source exposes
\texttt{arithmeticGap\_dominates\_canonicalCThetaScale},
\texttt{canonicalCThetaScale\_le\_iutIVCTheta},
\texttt{closedLocalGlobalEndpoint}, and \texttt{localGlobalHandoffAudit}
while retaining the valuation-ball Theorem~1.10 input at the public boundary.
Forgetting valuation-ball provenance recovers the additive gap-matched chain
\begin{center}
\small
\begin{tabular}{l}
\texttt{IUTStage1AdditiveHaarTheorem110FormulaGapMatched}\\
\quad\texttt{PrimeErrorPadicDefectMainSource},\\
\texttt{IUTStage1AdditiveHaarTheorem110StepXIFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicPrimeErrorFormulaMatchingSource},\\
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110AdditiveHaar}\\
\quad\texttt{FormulaGapMatchedArithmeticDegreePadicFormulaMatched}\\
\quad\texttt{StepXILocalTermCThetaSource}.
\end{tabular}
\end{center}
This final wrapper projects to the previous strongest additive-Haar local-global
source and exposes the same arithmetic-gap, global \(C_\Theta\)-comparison,
closed endpoint, and handoff audit.
The public finite-divisor vertical-\(IQ\) endpoint consuming the valuation-ball
wrapper directly is
\begin{center}
\small
\begin{tabular}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\texttt{\_constructedTheorem311OneSidedIUTIVTheorem110ValuationBallHaar}\\
\texttt{\_FormulaGapMatchedArithmeticDegreePadicFormulaMatched}\\
\texttt{\_StepXILocalTermCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{tabular}
\end{center}
It returns the valuation-ball endpoint evidence together with the Step~(x)
packet equalities, the IUT~IV displayed-bound audit, the constructed global
\(C_\Theta\)-scale audit, and the Corollary~3.12 dichotomy.
The corresponding Step~(xi) wrapper therefore exposes the preferred checked
route.  Its finite-divisor
vertical-\(IQ\) endpoint returns the additive-Haar source audit, the IUT~IV
displayed-bound audit, the constructed global \(C_\Theta\)-scale audit, and the
Corollary~3.12 dichotomy.  The preferred public projection is now
\begin{center}
\small
\begin{tabular}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\texttt{\_preferredConstructedTheorem311IndeterminacyLocalGlobalCTheta}\\
\texttt{\_FiniteDivisorVerticalIQ\_ofRealifiedFrobenioidPacketSource}.
\end{tabular}
\end{center}
It consumes the constructed qualitative Hodge/\(\SHE/\IPL\) source, the
constructed Remark~3.9.5 hull/determinant source, and the additive-Haar
arithmetic-degree/p-adic formula-matched Step~(xi) source, then returns only
the Corollary~3.12 dichotomy.  Neither the raw
\(\theta_{\mathrm{signed}}\le C_\Theta|\log q|\) bound nor the raw
\(C_{\Theta,\mathrm{can}}\le C_\Theta\) comparison is a hypothesis of this
preferred endpoint.  The stricter preferred projection
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\texttt{\_preferredFormulaGapMatchedConstructedTheorem311}\\
\texttt{\_IndeterminacyLocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}
\end{array}
\]
has the same constructed qualitative Hodge/\(\SHE/\IPL\) boundary but consumes
the formula-gap-matched additive-Haar source directly.  Its audit
\begin{center}
\small
\begin{tabular}{l}
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaar}\\
\quad\texttt{FormulaGapMatchedArithmeticDegreePadicCThetaAudit}
\end{tabular}
\end{center}
retains both the previous preferred audit by projection and the named
formula-gap endpoint evidence.  The valuation-ball refinement of the same
preferred qualitative boundary is exposed as
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from}\\
\texttt{\_preferredValuationBallFormulaGapMatchedConstructedTheorem311}\\
\texttt{\_IndeterminacyLocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
Its audit
\begin{center}
\small
\begin{tabular}{l}
\texttt{ConstructedQualitativeHodgeSHEIPL}\\
\quad\texttt{ValuationBallHaarFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicCThetaAudit}
\end{tabular}
\end{center}
retains the additive formula-gap audit by projection, but its public endpoint
evidence is the valuation-ball local-to-global source and the valuation-ball
Theorem~1.10 formula-matching object.  Thus finite Proposition~1.4
valuation-ball Haar normalization now survives the constructed qualitative
Hodge/\(\SHE/\IPL\) route all the way to the preferred Corollary~3.12
dichotomy.  The named distinguished and archimedean gap-comparison witnesses
for the additive projection are still constructed from an additive-Haar local
analytic arithmetic-divisor evaluation source by
\begin{center}
\small
\begin{tabular}{l}
\texttt{IUTStage1IUTIVTheorem110AdditiveHaar}\\
\quad\texttt{FormulaGapMatchedArithmeticDivisorEvaluationSource.}\\
\quad\texttt{ofAdditiveHaarLocalAnalyticArithmeticDivisorEvaluationSource}.
\end{tabular}
\end{center}
This removes the separate payload of comparison records once the lower
additive-Haar source has supplied the local formula-to-gap inequalities.  The
same construction is now lifted through the local \(p\)-adic defect and
arithmetic-degree formula chain.  The declarations
\begin{center}
\small
\begin{tabular}{l}
\texttt{IUTStage1AdditiveHaarTheorem110FormulaGapMatched}\\
\quad\texttt{PrimeErrorPadicDefectMainSource.ofPrimeErrorPadicDefectMainSource},\\
\texttt{IUTStage1AdditiveHaarTheorem110StepXIFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicPrimeErrorFormulaMatchingSource.}\\
\quad\texttt{ofArithmeticDegreePadicPrimeErrorFormulaMatchingSource},\\
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110AdditiveHaar}\\
\quad\texttt{FormulaGapMatchedArithmeticDegreePadicFormulaMatched}\\
\quad\texttt{StepXILocalTermCThetaSource.}\\
\quad\texttt{ofAdditiveHaarLocalAnalyticArithmeticDegreePadicFormulaMatched}\\
\quad\texttt{StepXILocalTermCThetaSource}
\end{tabular}
\end{center}
construct the stricter formula-gap-matched route from the previous
additive-Haar arithmetic-degree/\(p\)-adic source boundary.  Thus
formula-gap provenance is now a derived wrapper above that boundary, not a
separate route-level payload.  The derived qualitative audit
\begin{center}
\small
\begin{tabular}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\texttt{QualitativeHodgeSHEIPLDerivedFormulaGapMatched}\\
\texttt{AdditiveHaarArithmeticDegreePadicFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}
\end{tabular}
\end{center}
constructs this stricter audit internally from the additive-Haar
arithmetic-degree/\(p\)-adic source before entering the finite-divisor
vertical-\(IQ\) corridor.  The remaining source obligations are now the actual
local log-shell inclusions and numerical Proposition~1.4 estimates that prove
the formula-to-gap inequalities, construction of the Step~(xi)/\IUT{} IV local
arithmetic matching source from paper-native objects, and replacement of the
remaining lower compatibility projections by paper-native local-to-global
constructions.
The Step~(xi) local matching obligation is separated in Lean as
\texttt{IUTStage1AdditiveHaarTheorem110StepXILocalArithmeticMatchingSource}:
it packages the local equality
\[
  A_v = S_v+\delta_v+M_v
\]
between the IUT~IV local arithmetic upper term, the Step~(xi) weighted
determinant term, the local arithmetic defect, and the main-log term.  Its
endpoint proves the derived local inequalities
\[
  S_v+\delta_v\leq A_v-M_v,\qquad S_v\leq A_v-M_v,
\]
using the nonnegativity of the local defect.  This has now been lowered by
\texttt{IUTStage1AdditiveHaarTheorem110StepXIFormulaGapControlled}\\
\texttt{LocalArithmeticSource}: if the distinguished Proposition~1.4
procession bound and the archimedean Proposition~1.5 procession bound are
bounded by the localized Step~(xi) determinant term \(S_v\), Lean derives the
distinguished and archimedean formula-to-gap inequalities from the local
matching theorem \(S_v\le A_v-M_v\).  This is a genuine reduction of the
formula-gap payload: the remaining local question is now the paper-native
domination of the Prop.~1.4/1.5 formula bounds by the IUT~IV local
arithmetic-degree term, together with the construction of the underlying local
log-shell and metric estimates.
The same reduction is now present before forgetting valuation-ball provenance.
\texttt{IUTStage1ValuationBallHaarTheorem110StepXIFormulaGapControlled}\\
\texttt{LocalArithmeticSource} starts from the valuation-ball local-analytic
Theorem~1.10 source, the localized Step~(xi) term, and the IUT~IV local defect
source.  It constructs the additive local matching source by projection, proves
the distinguished and archimedean valuation-ball formula-to-gap inequalities,
and then builds
\texttt{IUTStage1IUTIVTheorem110ValuationBallAdditiveHaar}\\
\texttt{FormulaGapMatchedArithmeticDivisorEvaluationSource}.  The constructor
\texttt{IUTStage1ValuationBallHaarTheorem110FormulaGapMatched}\\
\texttt{PrimeErrorPadicDefectMainSource.ofStepXIFormulaGapControlled}\\
\texttt{LocalArithmeticSource} threads this derived formula-gap source into the
\(p\)-adic defect/main split.  Thus the current valuation-ball boundary no
longer needs the formula-gap-matched record as primitive data; its remaining
payload is the concrete proof of the per-place procession bounds
\(\mathrm{formula}_v\leq S_v\) and the local prime-error identity from
paper-native valuation-ball/log-shell constructions.
The local arithmetic equality itself has also been lowered by
\texttt{IUTStage1AdditiveHaarTheorem110StepXIArithmeticFormulaMatchingSource}.
That source uses the IUT~IV arithmetic-divisor formula
\[
  A_v=a_l(D_v+C_v)+E_v
\]
and derives the displayed Step~(xi) matching equality from two finer
identifications: \(S_v=a_l(D_v+C_v)\) and
\(E_v=\delta_v+M_v\).  The new source
\texttt{IUTStage1AdditiveHaarTheorem110StepXIArithmeticDegreeControlled}\\
\texttt{FormulaGapSource} uses this equality to turn the remaining
Prop.~1.4/1.5 comparison
\[
  \mathrm{formula}_v\leq a_l(D_v+C_v)
\]
into the Step~(xi)-controlled comparison
\(\mathrm{formula}_v\leq S_v\), and then projects to the formula-gap-matched
arithmetic-divisor evaluation source.
This comparison is now backed by named Proposition~1.4/1.5 construction
records.  The algebra layer adds single-place distinguished and archimedean
arithmetic-degree comparison sources; the experiment layer combines them as
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXIArithmeticDegree}\\
\texttt{ComparisonFormulaGapSource}.
\end{array}
\]
Thus the remaining comparison with \(a_l(D_v+C_v)\) is no longer an anonymous
inequality: it is attached to the same additive-Haar log-shell and
archimedean metric construction witnesses used by the formula-gap source.  The
new calibrated source
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXICalibrated}\\
\texttt{ArithmeticDegreeComparisonFormulaGapSource}
\end{array}
\]
splits this comparison one step further: the public procession formula bound
is first identified with the coarse Step~(v) or Step~(vii) bound produced by
the local construction, and only that coarse bound is compared with
\(a_l(D_v+C_v)\).  This calibrated layer is now synchronized with the
arithmetic-degree/\(p\)-adic formula source by
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarCalibratedFormulaGapMatchedArithmeticDegree}\\
\texttt{PadicFormulaMatchedStepXILocalTermCThetaSource}.
\end{array}
\]
Its synchronization field identifies the calibrated formula-matching source
with the projection of the \(p\)-adic/arithmetic-degree formula source, so the
calibrated comparison data cannot be attached to a different Step~(xi)
local package.  The same synchronization is now available before forgetting
valuation-ball provenance:
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{ValuationBallHaarCalibratedFormulaGapMatched}\\
\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}
\end{array}
\]
keeps the valuation-ball Theorem~1.10 formula-gap source, the calibrated
Proposition~1.4/1.5 arithmetic-degree comparison, and the
\(p\)-adic formula-matching core in one source object.  Its audit projects the
valuation-ball definition-of-done audit and the local formula-gap estimate
while checking that the calibrated formula-matching source is the same
formula-matching core used by the downstream \(p\)-adic route.  The remaining
local payload is therefore not a synchronization issue; it is the construction
of the paper-native valuation-ball/log-shell comparison records themselves.
The valuation-ball version has now been lowered to the same derived comparison
level by
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{ValuationBallHaarDerivedFormulaGapMatched}\\
\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}.
\end{array}
\]
This source keeps the valuation-ball Theorem~1.10 formula-gap package, but its
public Proposition~1.4/1.5 payload is the derived comparison object.  Thus the
calibrated inequality \(\mathrm{coarse}_v\leq a_l(D_v+C_v)\) is obtained by
projection from the unscaled degree-bound/nonnegativity calculation rather
than supplied as the source-facing comparison.  Its audit records both the
derived comparison endpoint and the inherited valuation-ball definition-of-done
audit.
The valuation-ball source has now been lowered through that unscaled step,
through the degree-identification step, through the local formula checks,
through the object-backed local degree-identification source, and further to the
arithmetic-divisor-backed matched local-degree component source:
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{ValuationBallHaarArithmeticDivisorBackedMatchedLocalDegreeComponent}\\
\texttt{ArithmeticDegreePadicFormulaMatchedStepXILocalTermCThetaSource}.
\end{array}
\]
Here the source-facing local payload no longer stops at typed local
degree-identification objects.  It carries the arithmetic-divisor-backed
component source: finite distinguished different/conductor degrees come from
the Theorem~1.10 arithmetic divisors, their effectivity proves the required
nonnegativity, and the tensor-different/tensor-conductor identities connect
those divisor degrees to the Proposition~1.4 log-shell calculation.  The
valuation-ball synchronization proof then recovers the object-backed source by
projection.  The remaining hard local work is narrower: replace the remaining
paper-side component inputs themselves by still more explicit valuation-ball
and log-shell constructions where possible.
In the additive-Haar chain, the corresponding calibrated comparison had already
been lowered by
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXIDerived}\\
\texttt{ArithmeticDegreeComparisonFormulaGapSource}.
\end{array}
\]
For each distinguished additive-Haar place and each archimedean metric place,
the new source derives
\[
  \mathrm{coarse}_v\leq a_l(D_v+C_v)
\]
from the unscaled local degree bound
\(\mathrm{coarse}_v\leq D_v+C_v\), the coefficient lower bound
\(1\leq a_l\), and nonnegativity of \(D_v+C_v\).  This unscaled layer is now
represented explicitly by
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXIUnscaled}\\
\texttt{DegreeBoundFormulaGapSource}.
\end{array}
\]
At a distinguished nonarchimedean place the source names the Proposition~1.4
tensor expression
\(-\lambda+d_I+4\log(p)+\mathrm{Ram}\) as the local
different-plus-conductor bound; at an archimedean place it names the Step~(vii)
coarse bound as the same unscaled degree bound.  Both project to the derived
source above, so the direct payload has been narrowed to the paper-side local
degree identification itself.
The local degree-identification payload has now been factored into two lower
source objects,
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaar}\\
\texttt{UnscaledDegreeIdentificationSource},\\
\texttt{IUTStage1IUTIVTheorem110ArchimedeanMetric}\\
\texttt{UnscaledDegreeIdentificationSource}.
\end{array}
\]
The first identifies the Proposition~1.4 tensor expression with
\(D_v+C_v\) and records the coarse Step~(v) domination by that tensor
degree; the second identifies the Step~(vii) archimedean coarse bound with
\(D_v+C_v\).  Each constructs the older unscaled degree-bound source by
projection.  At the finite-place formula-gap level this is exposed by
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{DegreeIdentifiedUnscaledFormulaGapSource}.
\end{array}
\]
This has now been lowered one step further by
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{LocalDegreeIdentificationFormulaSource}.
\end{array}
\]
This source does not ask for the per-place degree-identification records
directly.  It carries the formula-level local checks: \(1\leq a_l\), the
identification of the distinguished procession bound with the coarse
Step~(v) bound, the Proposition~1.4 tensor expression as \(D_v+C_v\), the
coarse Step~(v) domination by that tensor expression, the archimedean
Step~(vii) coarse-bound identification, and the archimedean
coarse \(D_v+C_v\) equality.  Lean derives the nonnegativity of \(D_v\) and
\(C_v\) from the arithmetic-divisor evaluation source and constructs
\texttt{DegreeIdentifiedUnscaledFormulaGapSource} by projection.
The p-adic/arithmetic formula-matched branch now has a matched version of this
local source,
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeIdentificationFormulaSource}.
\end{array}
\]
Here the local degree-identification formulas are written directly over the
arithmetic formula core projected from
the source
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXIFormulaGapMatched}\\
\texttt{ArithmeticDegreePadicPrimeErrorFormulaMatchingSource}.
\end{array}
\]
Consequently
the endpoint no longer exposes a separate proof that the local-degree formula
source and the p-adic formula source have the same arithmetic-formula core;
that synchronization is internal and definitional.
The scaling input \(1\leq a_l\) has also been factored as
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVThetaPilotArithmeticDegreeCoefficient}\\
\texttt{LowerBoundSource}.
\end{array}
\]
This source records the explicit size condition
\(4|\log(q)|\leq l+1\) and Lean derives \(1\leq a_l\) from the displayed
IUT~IV coefficient formula and \(|\log(q)|>0\).  It now has a separate
\texttt{CoefficientWindowAudit}: Lean proves the base window factor
\((l+1)/(4|\log(q)|)\geq 1\), the theta-error factor
\(1+36d_{\mathrm{mod}}/l\geq 1\), and then multiplies these inequalities to
obtain \(1\leq a_l\).  Thus the matched local-degree source no longer carries
\(1\leq a_l\) as an anonymous proof field; it carries the named paper-side
coefficient-window source.  The same
matched source now exposes
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeIdentificationFormulaSource.}\\
\texttt{CoefficientWindowSynchronizationAudit}.
\end{array}
\]
This audit records that the coefficient-window source's displayed \(a_l\) is
definitionally the arithmetic-divisor evaluation coefficient used by the local
formula source, and that the lower bound \(1\leq a_l\) is transported through
that equality before the local degree-identification formulas are built; it
also exposes the nested \texttt{CoefficientWindowAudit}.
The formula source also now has a named
\texttt{LocalDegreeFormulaAudit}.  It derives, from the Step~(v) formula
bound, the Proposition~1.4 tensor equality, and the tensor domination,
\[
  \mathrm{bound}^{(v)}_v \leq D_v+C_v,
\]
and it derives from the Step~(vii) formula equality the archimedean identity
\[
  \mathrm{bound}^{(vii)}_v = D_v+C_v
\]
together with its inequality form.  These are the local unscaled consequences
used to construct the degree-identification records; they are no longer only
recoverable by inspecting the projection to
\texttt{DegreeIdentifiedUnscaledFormulaGapSource}.
This formula boundary has now been tightened by an object-backed matched source,
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeIdentificationObjectSource}.
\end{array}
\]
It consumes the typed distinguished and archimedean unscaled
degree-identification objects from the \IUT{} IV algebra layer and derives the
five matched Step~(v)/Step~(vii) formula fields by projection.  The preferred
finite-divisor endpoint
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_preferred}\\
\texttt{MatchedLocalDegreeObjectConstructedTheorem311}\\
\texttt{IndeterminacyLocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}
\end{array}
\]
therefore no longer exposes these formula fields as the public boundary; it
exposes the typed local identification objects and projects internally to the
matched formula route.  The remaining local obligation is to construct these
typed Step~(v)/Step~(vii) identification objects from the detailed valuation,
log-shell, and archimedean metric data of the paper.  The
local-to-global surface first had a matching unscaled public wrapper
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarUnscaledDegreeBoundFormulaGapMatched}\\
\texttt{ArithmeticDegreePadicFormulaMatchedStepXI}\\
\texttt{LocalTermCThetaSource}.
\end{array}
\]
It projects to the derived wrapper internally and exposes the same closed
finite-divisor vertical-\(IQ\) endpoint with the unscaled local
different-plus-conductor payload as its public source assumption.  The public
boundary has now been lowered one more step by
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarDegreeIdentifiedUnscaledFormulaGapMatched}\\
\texttt{ArithmeticDegreePadicFormulaMatchedStepXI}\\
\texttt{LocalTermCThetaSource}.
\end{array}
\]
This wrapper carries the finite-place
\texttt{DegreeIdentifiedUnscaledFormulaGapSource}, projects to the unscaled
wrapper internally, and exposes the same
\texttt{arithmeticGap\_dominates\_canonicalCThetaScale},
\texttt{canonicalCThetaScale\_le\_iutIVCTheta},
\texttt{closedLocalGlobalEndpoint}, and
\texttt{localGlobalHandoffAudit} theorems at the degree-identification
boundary.  The matching lower wrapper is
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarLocalDegreeFormulaMatchedArithmeticDegree}\\
\texttt{PadicFormulaMatchedStepXILocalTermCThetaSource}.
\end{array}
\]
It carries \texttt{LocalDegreeIdentificationFormulaSource}, projects to the
degree-identified wrapper internally, and exposes the same closed
local-to-global \(C_\Theta\) handoff theorems at the formula-equality
boundary.  The strict matched wrapper is
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarMatchedLocalDegreeFormula}\\
\texttt{StepXILocalTermCThetaSource}.
\end{array}
\]
It carries the matched local-degree formula source above, projects to the
previous local-degree wrapper with the formula-core equality supplied by
\texttt{rfl}, and now exposes
\texttt{matchedLocalDegreeFormulaAudit} together with the same
\texttt{arithmeticGap\_dominates\_canonicalCThetaScale},
\texttt{canonicalCThetaScale\_le\_iutIVCTheta},
\texttt{closedLocalGlobalEndpoint}, and
\texttt{localGlobalHandoffAudit} theorems.  The object-backed wrapper
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarMatchedLocalDegreeObject}\\
\texttt{StepXILocalTermCThetaSource}
\end{array}
\]
now projects to this strict matched formula wrapper and exposes the same
closed \(C_\Theta\) handoff theorems together with
\texttt{matchedLocalDegreeObjectAudit}.
The distinguished finite-place side has now been lowered below this object
boundary.  The source
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaar}\\
\texttt{TensorDegreeComponentSource}
\end{array}
\]
separates the local tensor expression
\[
  -\lambda+d_I+\mathrm{Ram}+4\log(p)
\]
into a different component \(-\lambda+d_I+\mathrm{Ram}\) and a conductor
component \(4\log(p)\), proves their recombination as
\texttt{tensorFormula\_eq\_different\_conductor}, and then projects to the
older distinguished unscaled degree-identification object.  Its matched
Step~(xi) wrapper,
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeDistinguishedComponentSource},
\end{array}
\]
combines these distinguished component sources with the existing archimedean
degree-identification objects.  The corresponding local-to-global
\(C_\Theta\) wrapper
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarMatchedLocalDegreeDistinguishedComponent}\\
\texttt{StepXILocalTermCThetaSource}
\end{array}
\]
projects to the object-backed route and exposes the same closed handoff,
audit, and final preferred dichotomy endpoint.  Thus the current preferred
finite-divisor endpoint no longer consumes the distinguished local
degree-identification object as primitive; it consumes the finer local
different/conductor decomposition and rebuilds that object internally.
The finite distinguished branch is now lowered beyond the tensor-component
interface to the constructed source
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaar}\\
\texttt{ConstructedTensorDegreeComponentSource}.
\end{array}
\]
This object reads the Proposition~1.4 additive-Haar log-shell source and defines
the finite local components
\[
D_v=-\lambda+d_I+\operatorname{Ram},\qquad
C_v=4\log(p_v).
\]
Lean proves the conductor nonnegativity from the residue-prime bound and
projects the source to the older tensor-degree component and calibrated
unscaled-degree interfaces.  This has now been lowered once more by
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaar}\\
\texttt{EffectiveDifferentConstructedTensorDegreeComponentSource}.
\end{array}
\]
That source reads the nonnegativity of the local arithmetic different degree
from the effective arithmetic-divisor side of Definition~1.9/Theorem~1.10 and
uses the equality between that degree and
\(-\lambda+d_I+\operatorname{Ram}\) to derive the tensor-different
nonnegativity internally.  Thus the remaining finite payload at this boundary
is no longer the raw nonnegativity assertion.  This has now been lowered again
to
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaar}\\
\texttt{EffectiveDifferentConductorConstructedTensorDegreeComponentSource}.
\end{array}
\]
The new source also reads the effective arithmetic local conductor degree and
identifies it with the Proposition~1.4 tensor-conductor term \(4\log(p_v)\).
The matched finite source therefore derives both finite component equalities
\[
D_v=-\lambda+d_I+\operatorname{Ram},\qquad C_v=4\log(p_v)
\]
from arithmetic local degrees before projecting to the closed local-to-global
\(C_\Theta\) route.  This boundary has now been lowered once more to
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110DistinguishedAdditiveHaar}\\
\texttt{ArithmeticDivisorBackedTensorDegreeComponentSource}.
\end{array}
\]
Here \(D_v\) and \(C_v\) are not free arithmetic local degrees: they are
\texttt{differentDivisor.localDegree v} and
\texttt{conductorDivisor.localDegree v} from the Theorem~1.10
arithmetic-divisor source.  Lean derives their nonnegativity from effectivity
of the different and conductor divisors, then uses the remaining paper-side
identifications of those divisor local degrees with the Proposition~1.4 tensor
terms.  The remaining finite payload is therefore narrower: construct the
different, conductor, and \(q\)-parameter divisors from valuation and
ramification data, and construct the Proposition~1.4 log-shell source that
supplies the displayed tensor identities.

The archimedean branch remains lowered beyond the component interface to the
constructed source
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110ArchimedeanMetric}\\
\texttt{ConstructedDegreeComponentSource}.
\end{array}
\]
Here the local different component and local conductor component are defined
from the Proposition~1.5 metric construction source itself: the former is the
exact metric term and the latter is the exact-to-coarse remainder.  Lean then
projects this source to the previous component object and provides a calibrated
projection for externally named Step~(xi) local \(D_v,C_v\) entries.  The
matched source
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeArithmeticDivisorBackedComponentSource}
\end{array}
\]
uses the arithmetic-divisor-backed finite construction at every distinguished
finite place and the metric construction at every archimedean place.  The
local-to-global
wrapper
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarMatchedLocalDegreeArithmeticDivisorBackedComponent}\\
\texttt{StepXILocalTermCThetaSource}
\end{array}
\]
projects it to the effective-different/conductor and then constructed-component
\(C_\Theta\) route.  The
current strongest preferred endpoint is
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_preferred}\\
\texttt{MatchedLocalDegreeArithmeticDivisorBackedComponent}\\
\texttt{ConstructedTheorem311}\\
\texttt{IndeterminacyLocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
It consumes arithmetic-divisor-backed finite local-degree data and
construction-backed archimedean local-degree components, then derives the
finite-divisor vertical-\(IQ\) dichotomy through the closed local-to-global
\(C_\Theta\) source.
The finite distinguished branch is now audited separately by
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeArithmeticDivisorBackedComponentSource.}\\
\quad\texttt{ArithmeticDivisorLocalDegreeAudit}.
\end{array}
\]
For every distinguished nonarchimedean place this audit exposes the
arithmetic-divisor-backed component endpoint, nonnegativity of the local
different and conductor degrees from divisor effectivity, the identifications
of those local degrees with the Proposition~1.4 tensor-different and
tensor-conductor terms, and the projection to the effective
different/conductor component endpoint.
The archimedean branch is now audited at the parallel constructed-component
boundary by
\[
\begin{array}{l}
\texttt{IUTStage1AdditiveHaarTheorem110StepXI}\\
\texttt{MatchedLocalDegreeConstructedArchimedeanComponentSource.}\\
\quad\texttt{ArchimedeanConstructedDegreeComponentAudit}.
\end{array}
\]
For every archimedean place this audit records the Proposition~1.5 metric
construction endpoint, the equality with the Step~(xi) archimedean metric
source, the identifications of the Step~(xi) local different and conductor
entries with the constructed exact metric and coarse-remainder terms, and the
projection to the calibrated local-degree component endpoint.  The top
arithmetic-divisor-backed \(C_\Theta\) certificate now carries this audit
beside the finite arithmetic-divisor local-degree audit.
The same wrapper now exposes the local-to-global arithmetic proof and the
Theorem~3.11 quotient input at this lowest boundary by
\[
\begin{array}{l}
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.}\\
\quad\texttt{arithmeticDivisorLocalDegreeAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.}\\
\quad\texttt{archimedeanConstructedDegreeComponentAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.oneSidedQuotientAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.}\\
\quad\texttt{oneSidedRemark395CompatibilityAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.}\\
\quad\texttt{oneSidedSelectedQHullLogVolumeAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.typedCoreActionLawAudit},\\
\texttt{ArithmeticDivisorBackedLocalGlobalCThetaAudit.selectedQRegionQuotientEndpoint},\\
\texttt{localGlobalCThetaDerivationAudit}.
\end{array}
\]
These declarations project the arithmetic-divisor-backed source to the
formula-gap/additive-Haar summation source, record the one-sided
\((\Ind_1)/(\Ind_2)\) equality-quotient audit, expose its compact typed-core
action-law certificate, carry the selected-q hull/log-volume audit at the same
arithmetic-divisor boundary, record the selected q-pilot possible image both as
a Theorem~3.11 possible image and as an equality-quotient possible image, record
the finite-place Step~(xi) Haar summation audit, derive
\[
  C_{\Theta,\mathrm{can}}+1\le A-M,
\]
and then obtain the displayed
\(C_{\Theta,\mathrm{can}}\le C_\Theta\) handoff from the \IUT{} IV identity
\(C_\Theta+1=A-M\).  Thus the newest endpoint's \(C_\Theta\) comparison is
visible as a derived local-to-global chain rather than only as an inherited
projection through the effective-conductor wrapper.
The determinant and canonical-scale sides of this handoff are now lowered one
more source boundary by
\[
\begin{array}{l}
\texttt{RecordOb3Ob5ArithmeticDivisorBackedComponentSource},\\
\texttt{RecordOb3Ob5StepXIDeterminantHandoffAudit}.
\end{array}
\]
This wrapper no longer stores either the Step~(xi) determinant equality or the
global-scale-to-Step~(xi)-sum equality directly.  It derives the determinant
equality from the record-canonical Ob3/Ob5 adjusted determinant source,
identifies the record Ob3/Ob4 weighted determinant with the localized Step~(xi)
arithmetic-degree determinant, first calibrates
\(C_{\Theta,\mathrm{can}}\) against the record adjusted-summand log-volume, and
then derives the localized weighted Step~(xi) sum from the same Ob3/Ob4
identification.  The broader \(C_{\Theta,\mathrm{can}}\le C_\Theta\) comparison
remains the surrounding local-to-global arithmetic-divisor chain.
The compact theorem
\texttt{arithmeticDivisorBackedFinitePlaceCThetaChain} now packages this
chain as a single source-level review target: finite-place identifications,
the summed Step~(xi)/Haar bound, the total Haar-defect lower bound, the
derived arithmetic gap, the \(C_{\Theta,\mathrm{can}}\le C_\Theta\) handoff,
and the final signed \(C_\Theta\) bound are all returned together.
The finite-place source now also has the explicit
\texttt{IUTIVArithmeticGapHandoffAudit}, which records the finite-sum
identifications, the summed Step~(xi)/Haar inequality, the unit Haar-defect
input, the \(\IUT{}\,\mathrm{IV}\) identity \(C_\Theta+1=A-M\), and the
ordered-real cancellation to \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) in one
checked certificate.
This source-level audit is now pinned at the constructed qualitative
Hodge/\(\SHE/\IPL\) finite-divisor boundary by
\[
\begin{array}{l}
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaar}\\
\texttt{ArithmeticDivisorBackedComponentCThetaAudit}.
\end{array}
\]
The preferred arithmetic-divisor-backed endpoint projects its dichotomy from
that certificate, whose fields include the constructed qualitative bridge,
the source-record constructed transport-guard audit,
the choice-wise constructed \(\IPL\) link law, the forbidden direct
\(\SHE\) domain-to-codomain transport guard, the non-forbidden permitted
\(\APT\) transport guard, the source theta/Hodge log-volume calibration
endpoint, the one-sided Theorem~3.11 quotient audit, the one-sided
Remark~3.9.5 compatibility audit, its typed-core action-law audit, the explicit
exclusion of \((\Ind_3)\) from the equality quotient, the \((\Ind_1)\) and
\((\Ind_2)\) procession-normalized log-volume equalities, the \((\Ind_3)\)
upper-semi log-volume inequality, the \(\mathbb{F}_l\)-procession
equality-quotient law, the selected q-region quotient endpoint, the realified
Frobenioid/log-Kummer packet
endpoint, the recovered finite-divisor packet-local Step~(x) source, the exact
vertical-\(IQ\) target endpoint, the arithmetic-divisor-backed endpoint, the
arithmetic-divisor local-degree audit, the
finite-place local-to-global \(C_\Theta\) derivation audit, the
\texttt{paperTraceRemainingPayloadAudit}, the closed handoff audit, and the
derived arithmetic-gap \(C_\Theta\) chain.  The same endpoint now exposes the
Theorem~3.11 source-record guard as
\[
\begin{array}{l}
\texttt{IUTStage1Theorem311MultiradialSourceRecord.}\\
\texttt{ConstructedQualitativeTransportGuardAudit},
\end{array}
\]
which packages the record/bundle equality, the multiradial source endpoint,
the structured-Hodge history guard, the typed \(\SHE\) forbidden-transport
audit including all-arrow and all-mechanism exclusions, and the
non-forbidden \(\APT\) arrow audit.  This does not yet derive the full
source-paper Hodge-theater reconstruction theorem, but it removes the earlier
boundary where the Theorem~3.11 source record exposed only a side-inequality
history guard while the constructed \(\SHE/\APT\) transport discipline lived
only in a later bridge.
Lean now also exposes the synchronized constructor
\[
\begin{array}{l}
\texttt{ofTransportBaseConstructedQualitativeInputsWithSHE\_}\\
\texttt{synchronizedTransportGuardAudit}.
\end{array}
\]
It builds the structured-\(\SHE\) input from the base context of the
constructed \(\SHE\)-transport system itself, proves the definitional equality
between those contexts, and derives the record's Hodge-history guard by
rewriting the transport audit's
\texttt{history\_sides\_not\_identified} field.  This is the cleaner boundary
for later endpoint lowering: arbitrary constructed bundles still carry the
ordinary guard audit, while transport-base bundles make the source-record
history separation a consequence of the typed transport system.
The finite-divisor \(C_\Theta\) boundary now exposes this cleaner form through
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_transportBase}\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaar}\\
\texttt{ArithmeticDivisorBackedComponentFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}
\end{array}
\]
and the corresponding direct dichotomy projection.  These declarations take
the constructed qualitative inputs as the source data, build the transport-base
structured-\(\SHE\) bundle, the Theorem~3.11 multiradial source record, and the
finite Hodge--\(\SHE\)--\(\IPL\) construction internally, and return the
synchronized transport-guard audit together with the arithmetic-divisor-backed
\(C_\Theta\) certificate.  Thus this public finite-divisor endpoint no longer
has an arbitrary source-record/constructed-bundle pair as part of its exposed
hypothesis surface; the remaining source inputs are the substantive
Remark~3.9.5 hull source, the \(\IUT{}\,\mathrm{IV}\) estimate, and the
arithmetic-divisor-backed component sources.
The same transport-base boundary now has the named audit projection
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_transportBase}\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaar}\\
\texttt{ArithmeticDivisorBackedComponentFiniteDivisorVerticalIQ}\\
\texttt{\_paperTraceLocalGlobalAudit}.
\end{array}
\]
It projects the top-level paper-trace remaining-payload audit from this
transport-base route, so the review surface can cite the constructed
Theorem~3.11 quotient layer, Step~(x), Step~(xi), \(\IUT{}\,\mathrm{IV}\)
local-to-global \(C_\Theta\) handoff, and raw-comparison-free endpoint through
one declaration at the current preferred boundary.  The direct transport-base
dichotomy theorem now takes its final alternative from the
\texttt{ClosedDichotomyEndpoint} field of this certificate, so the public
Corollary~3.12 projection passes through the raw-comparison-free endpoint
rather than reading the broader audit's derived signed-bound field directly.
The companion declaration
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_transportBase}\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaar}\\
\texttt{ArithmeticDivisorBackedComponentFiniteDivisorVerticalIQ}\\
\texttt{\_milestoneCompletionAudit}
\end{array}
\]
collects the same boundary evidence in one requirement-indexed certificate:
the synchronized transport-base source record, a strict finite typed
indeterminacy nonvacuity witness, the
\texttt{PreferredSourceCorridorDODAudit}, and the full
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDivisorBackedComponentCThetaAudit}.
Together these structures contain the typed \((\Ind_1),(\Ind_2),(\Ind_3)\)
quotient laws, selected q-region and selected-q hull/log-volume audits,
constructed \(\IPL/\SHE/\APT\) transport laws, finite-place Step~(xi)/Haar summation, derived
\(C_\Theta\) comparison, closed raw-comparison-free endpoint, and final
dichotomy.  This is the current definition-of-done certificate for the
milestone-level source-interface route; it is not a claim that the full
published \IUT{} source constructions have been formalized from first
principles.
The same endpoint also exposes the
Step~(xi) normalized bridge directly as
\texttt{normalizedRecordBridge} and
\texttt{qRegionLogVolume\_le\_thetaSigned}: the constructed
Remark~3.9.5 source gives
\[
  \mu_{\log}(q\text{-region})\leq \det_{\mathrm{norm}}\leq
  \theta_{\mathrm{signed}},
\]
and hence the q-region log-volume is already bounded by
\(\theta_{\mathrm{signed}}\) before the later \(\IUT{}\,\mathrm{IV}\)
\(C_\Theta\) comparison is invoked.  It also exposes the finite-place
local-to-global arithmetic step directly through
\texttt{finitePlaceLocalGlobalIdentifications},
\texttt{finitePlaceLocalUpperContributionDecomposition},
\texttt{finitePlaceLocalStepXIHaarIdentity},
\texttt{finitePlaceSummedStepXIHaarBound}, and
\texttt{finitePlaceTotalHaarDefect\_ge\_one}: the local canonical scale,
arithmetic upper term, and main-log term are identified with their finite sums,
each local arithmetic upper contribution is identified with the Step~(xi)
weighted determinant contribution plus the \(\IUT{}\,\mathrm{IV}\) arithmetic
defect plus the local main-log term, Lean cancels the main-log term to obtain
the pointwise identity
\[
  A_v-M_v=S_v+N_v,
\]
and these local Step~(xi)/Haar identities are then summed, while the
Haar-normalization defect contributes the global \(+1\).  The
derived consequences are now separate
fields, \texttt{finitePlaceDerivedArithmeticGap} and
\texttt{finitePlaceDerivedCanonicalCThetaScale\_le\_iutIVCTheta}, proving
\[
  C_{\Theta,\mathrm{can}}+1\leq
  A_{\mathrm{upper}}-M_{\log}
\]
and then \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) via the \(\IUT{}\,\mathrm{IV}\)
identity \(C_\Theta+1=A_{\mathrm{upper}}-M_{\log}\).
In particular, the audit now
stores the local-to-global derivation of
\[
  \theta_{\mathrm{signed}}\leq
  C_\Theta\cdot(-q_{\mathrm{signed}})
\]
and the corresponding source-bridge-to-\(\IUT{}\,\mathrm{IV}\)
\(C_\Theta\) inequality, rather than requiring this signed bound as a public
endpoint hypothesis.  The generic local-to-global source also exposes the
named audit
\texttt{ClosedDichotomyEndpoint}, whose proposition contains only the source
assembly obligations, the \(\IUT{}\,\mathrm{IV}\) expression
\(C_\Theta=A_{\mathrm{upper}}-M_{\log}-1\), and the final dichotomy.  The
companion audit \texttt{ClosedNoRawComparisonAudit} carries this endpoint
together with the derived comparison chain, and the constructed qualitative
Hodge--\(\SHE\)--\(\IPL\) certificate carries both directly; its fields project
the arithmetic-gap cancellation, the derived
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison, the derived signed
\(C_\Theta\) bound, and the final dichotomy from the constructed handoff
rather than from raw comparison inputs.  The paper-trace field instantiates the abstract
remaining-payload ledger with the
formula-gap-matched Theorem~1.10 arithmetic-divisor evaluation, the local
arithmetic matching source, the Step~(xi) arithmetic-degree calibration, the
two separated arithmetic-degree calibration laws
\(\mathrm{wt}_v=a_l\) and
\(\ell_{v,\mathrm{adj}}=D_v+C_v\),
Step~(x) packet equalities, the constructed \(\IPL\) choice-link endpoint, the
\(\IPL\)-datum/certificate alignment, the structured \(\IPL/\SHE/\APT\)
evidence, the \(\SHE/\APT\) transport guards, and the arithmetic-divisor-backed
endpoint itself.  The same split is now used in the additive-Haar subledger
rather than only in the outer Theorem~3.11 trace.  The transport-guard split is
also exposed on the arithmetic-degree/p-adic additive-Haar audit, so both the
intermediate additive-Haar route and the final arithmetic-divisor-backed route
carry the same source-record constructed transport certificate.
The same certificate now also
has a top-level
\texttt{topLevelPaperTraceRemainingPayloadAudit} field for the assembled
\texttt{IUTStage1Theorem311ToCorollary312PaperTrace.Obligations} ledger.  This
outer audit records the Theorem~3.11/Remarks~3.11.2--3.11.4 source, Step~(x),
Step~(xi), \(\IUT{}\,\mathrm{IV}\), additive-Haar, and closed-endpoint
obligations together; its last two entries are witnessed by the derived
\(\theta_{\mathrm{signed}}\leq C_\Theta(-q_{\mathrm{signed}})\) bound and the
finite-place-derived \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison, not
by raw endpoint hypotheses.  In the Theorem~3.11 part of this audit, the
multiradial, theta-possible-image, and finite-label/procession slots are now
split into the exact quotient equality/action-law, possible-image pullback,
cardinality, and procession-transition facts; the \(\IPL/\SHE/\APT\) slots are
split into the constructed choice-link endpoint and the explicit structured
transport guards.  The trace also takes the normalized Step~(xi)
bridge directly from the constructed Remark~3.9.5 record bridge: the weighted
determinant/tensor-power slot is witnessed by
\(\det_{\mathrm{norm}}\leq\theta_{\mathrm{signed}}\), and the q-region
log-volume slot by
\(\mu_{\log}(q_{\mathrm{region}})\leq\theta_{\mathrm{signed}}\).  The assembled
\(\IUT{}\,\mathrm{IV}\) obligation list now has a separate
\texttt{finite\_place\_arithmetic\_gap\_constructed} entry, witnessed here by
\texttt{finitePlaceDerivedArithmeticGap}.  This entry has now been refined by
\texttt{LocalToGlobalArithmeticChainAudit}, whose slots separately record the
finite-place sum identifications for the canonical scale, arithmetic upper
term, and main-log term, the summed Step~(xi) Haar bound, the total Haar-defect
lower bound, the \(\IUT{}\,\mathrm{IV}\) identity \(C_\Theta+1=A-M\), and the
ordered-real cancellation of the normalized \(+1\) before the final
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) consequence.  Thus the paper trace
records the actual finite-place summation and cancellation, not only the derived
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison.  Its distinguished
Proposition~1.4
entries are also no longer witnessed by the whole local-degree audit: the
log-shell inclusion slot is filled by the per-place distinguished component
endpoint, and the numerical-bound slot is filled by the local different and
conductor nonnegativity projections.  The same cleanup now applies to the
remaining local IUT~IV case split: the nondistinguished Proposition~1.4 slot
is witnessed by the per-place additive-Haar log-shell endpoint, the
Proposition~1.5 slot by the per-place archimedean metric endpoint, and the
distinguished/archimedean Theorem~1.10 formula-gap slots by the named
per-place comparison endpoints.
The matched boundary now has its own constructed qualitative audit,
\[
\begin{array}{l}
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaar}\\
\texttt{MatchedLocalDegreeFormulaCThetaAudit}.
\end{array}
\]
This audit records the strict source's
\texttt{MatchedLocalDegreeFormulaAudit}: the matched local-degree endpoint, the
coefficient-window endpoint, the nested
\texttt{CoefficientWindowSynchronizationAudit}, the projected local
degree-formula endpoint, the nested \texttt{LocalDegreeFormulaAudit}, the
formula-gap matched arithmetic-degree/\(p\)-adic endpoint, the
\texttt{ArithmeticDegreeCalibrationAudit}, the definitional formula-core
synchronization, and the degree-identified unscaled endpoint.  The calibration
audit records, place by place, that the localized Step~(xi) determinant weight
is the IUT~IV arithmetic-degree coefficient and that the adjusted raw
log-volume is the local different-plus-conductor degree; the displayed
\(S_v=a_l(D_v+C_v)\) formula is then the derived local equality exposed by the
same certificate.  It
also records the closed local-to-global endpoint, the Remark~3.9.5/\IUT{} IV
handoff audit, the derived \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison,
and the final dichotomy.
Thus the paper-trace certificate is attached directly to the current lowest
matched local-degree source rather than only to its older unscaled projection.
The prime-error side has then been lowered another
step by
\texttt{IUTStage1AdditiveHaarTheorem110PrimeErrorPadicDefectMainSource}: it
uses the local \(p\)-adic Haar-index split
\[
  E_v=h_v+M_v
\]
together with the IUT~IV defect identification \(\delta_v=h_v\) to derive
\(E_v=\delta_v+M_v\).  The wrapper
\texttt{IUTStage1AdditiveHaarTheorem110StepXIPadicPrimeErrorFormulaMatchingSource}
handled the prime-error side while still exposing the Step~(xi)
arithmetic-degree identification \(S_v=a_l(D_v+C_v)\).  That last local
formula has now been factored by
\texttt{IUTStage1AdditiveHaarTheorem110StepXIArithmeticDegreeCalibrationSource}.
It derives \(S_v=a_l(D_v+C_v)\) from two source equalities: the localized
determinant multiplicity is the IUT~IV arithmetic-degree coefficient \(a_l\),
and the adjusted raw localization log-volume is the local
different-plus-conductor degree \(D_v+C_v\).  These two equalities are now the
actual witnesses in the additive-Haar paper-trace subledger, rather than both
slots being filled by the whole arithmetic-degree calibration endpoint.  The combined
arithmetic-degree/\(p\)-adic formula source therefore backs both local formula
sides and now enters the finite-place local-global \(C_\Theta\) route at the
same strength.  In particular, the strict source has a finite-divisor
vertical-\(IQ\) boundary theorem after combination with the realified
Frobenioid log-Kummer packet source; at that boundary neither the numerical
\(\Theta\)-bound nor the global \(C_\Theta\) comparison is supplied as a raw
endpoint hypothesis.

The matched additive-Haar wrapper also projects directly to
\texttt{ConstructedTheorem311OneSidedFinitePlaceLocalGlobalCThetaSource}; the
summation theorem there derives
\[
  C_{\Theta,\mathrm{can}}+1\leq A-M
\]
from the local matching source and the global lower bound for the total local
arithmetic defect.  Thus the theorem
\texttt{arithmeticGap\_dominates\_canonicalCThetaScale} is no longer reached
only through a compatibility projection to the older additive-Haar wrapper.
The current strongest finite-divisor boundary therefore combines the strict
Step~(xi)/\IUT{} IV local formula source with the Step~(x) realified
Frobenioid log-Kummer packet source, so both local arithmetic matching and
packet equalities appear as typed source objects rather than loose endpoint
fields.  The calibrated version of this boundary is exposed as
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\texttt{Theorem311OneSidedIUTIVTheorem110AdditiveHaarCalibrated}\\
\texttt{FormulaGapMatchedArithmeticDegreePadicFormulaMatched}\\
\texttt{StepXILocalTermCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
It projects to the formula-gap matched proof for the closed \(C_\Theta\)
comparison, but its public endpoint now retains the calibrated coarse
Step~(v)/(vii) source evidence.
The corresponding unscaled boundary theorem is now also present:
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\texttt{Theorem311OneSidedIUTIVTheorem110AdditiveHaarUnscaled}\\
\texttt{DegreeBoundFormulaGapMatchedArithmeticDegreePadic}\\
\texttt{FormulaMatchedStepXILocalTermCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
It exposes the Proposition~1.4/Step~(vii) unscaled local degree-bound records
at the finite-divisor boundary and projects to the derived/calibrated route
internally.
The corresponding degree-identified boundary theorem is
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\texttt{Theorem311OneSidedIUTIVTheorem110AdditiveHaarDegreeIdentified}\\
\texttt{UnscaledFormulaGapMatchedArithmeticDegreePadicFormulaMatched}\\
\texttt{StepXILocalTermCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
It exposes the Proposition~1.4 tensor-to-\(D_v+C_v\) and archimedean
Step~(vii)-to-\(D_v+C_v\) identifications at the finite-divisor boundary, then
projects to the unscaled theorem internally.
This strongest additive-Haar boundary has now also been tied to the constructed
qualitative Hodge/\(\SHE\)/\(\IPL\) provenance at the same unscaled strength.
The declaration
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_constructed}\\
\quad\texttt{QualitativeHodgeSHEIPLAdditiveHaarUnscaledDegreeBound}\\
\quad\texttt{ArithmeticDegreePadic}\\
\quad\texttt{FiniteDivisorVerticalIQ\_ofRealifiedFrobenioidPacketSource}
\end{array}
\]
projects the \(\IPL\) link from the constructed qualitative source, reuses the
formula-gap qualitative audit obtained from the unscaled source, and records
the unscaled Proposition~1.4/Step~(vii) endpoint, the realified packet
equalities, the \(\IUT{}\,\mathrm{IV}\) handoff, the global
\(C_\Theta\)-scale audit, and the final dichotomy.  The projected top-level
audit therefore exposes the fact that
\((\Ind_1)\) and \((\Ind_2)\) form the equality quotient while \((\Ind_3)\)
remains outside that quotient as an upper-semi log-volume relation; this no
longer has to be recovered by chasing through the nested finite-place audit.
This is now recorded directly on the unscaled audit certificate: the
choice-wise \(\IPL\) links, the typed \(\SHE\) no-domain-to-codomain transport
guard, and the permitted \(\APT\) arrow's non-forbidden-identification proof
are all fields of the preferred additive-Haar certificate.
At the underlying Step~(xi) qualitative bridge these laws are now bundled as
\[
\begin{array}{l}
\texttt{IUTStage1ConstructedQualitativeFiniteHodgeSHEIPLConstructionSource.}\\
\quad\texttt{ConstructedIPLSHEAPTTransportLawAudit}.
\end{array}
\]
This audit records, in one checked object, the choice-wise input-prime-strip
links, constructed/certificate \(\IPL\)-datum alignment, the forbidden direct
\(\SHE\) domain-to-codomain transport, and the permitted \(\APT\) endpoint.
The \(\APT\) endpoint is now quotient-backed: the construction carries a
\texttt{HodgeTheaterTransportQuotient}, and Lean proves that the permitted
\(\APT\) arrow's source and target are equal after passing to this quotient.
The underlying \texttt{APTDatum} has been strengthened accordingly: a structured
\(\APT\) witness now stores the transport system, the quotient, the arrow, its
permission proof, and the quotient endpoint equality, not only the mechanism
and output family.
The \(\SHE\) guard is now also represented by
\texttt{DomainCodomainForbiddenTransportAudit}: it stores the forbidden
domain/codomain theater pair, proves that no allowed arrow with these endpoints
exists for any mechanism, and retains the underlying history-side separation.
It does not prove full \(\SHE\) or \(\APT\) from the source papers; it removes
another loose conjunction from the critical path by making the present
transport laws a named typed certificate.
The remaining-payload ledger now has a separate
\texttt{constructed\_ipl\_she\_apt\_transport\_law\_audit\_threaded} slot,
and the strongest additive-Haar arithmetic-degree and arithmetic-divisor-backed
certificates expose this same typed transport-law audit directly.
The additive-Haar subledger also exposes the components of the old
\(\SHE/\APT\) transport guard separately: the no-domain-to-codomain
\(\SHE\) transport law, the non-forbidden \(\APT\) arrow law, and the
underlying \(\APT\) transport audit are now individual projections as well as
part of the combined guard.
The same certificate directly exposes the local-to-global arithmetic gap
\[
  C_{\Theta,\mathrm{can}}+1\leq A-M
\]
and the local formula-matching subcertificates: unscaled local
different-plus-conductor bounds, formula-gap matched Theorem~1.10 arithmetic
divisor evaluation, Step~(xi) arithmetic-degree calibration, and the
\(p\)-adic prime-error/defect split.  It also carries the closed
local-to-global endpoint and the Remark~3.9.5/IUT~IV handoff audit as named
fields, so the \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) proof is visible at
the strongest unscaled boundary itself.
At the arithmetic-divisor-backed preferred boundary, the same certificate now
also carries the nested
\texttt{ArithmeticDegreeCalibrationAudit} directly.  Thus the local Step~(xi)
formula
\[
  S_v=a_l(D_v+C_v)
\]
is visible from the preferred certificate as the consequence of the two
calibration laws already stored there: determinant multiplicity equals the
\IUT{} IV arithmetic-degree coefficient, and adjusted raw log-volume equals
the local different-plus-conductor degree.
The new
\texttt{StepXIDeterminantCalibrationAudit} records the adjacent global
calibration: the Remark~3.9.5 determinant source is the weighted determinant
obtained from this localized Step~(xi) source, and
\(C_{\Theta,\mathrm{can}}\) is the finite sum of its weighted adjusted
log-volumes.  This makes the determinant handoff an explicit checked component
of both the arithmetic-divisor-backed local-global audit and the preferred
constructed qualitative certificate.
The same preferred certificate now also exposes the \(p\)-adic prime-error
side through its
\texttt{primeErrorPadicDefectMainEndpoint} and
\texttt{padicPrimeErrorFormulaMatchingEndpoint} fields.  These record the
source equality \(E_v=h_v+M_v\), its conversion to
\(E_v=\delta_v+M_v\) via the IUT~IV local arithmetic-defect source, and the
wrapper that recombines this with the Step~(xi) arithmetic formula.
Thus the preferred certificate records how the final
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison is obtained, rather than
only recording that the comparison was available downstream.  Its
\texttt{arithmeticDivisorBackedFinitePlaceCThetaChain} field now packages this
finite-place calculation as a single checked endpoint: the global terms are
identified with finite local sums, the summed Step~(xi)/Haar inequality and
unit Haar defect give the arithmetic gap, and the \(\IUT{}\,\mathrm{IV}\)
handoff yields both \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) and the signed
theta bound used by Corollary~3.12.
The finite-place source also exposes a
\texttt{coarseAssemblyConcreteAudit}: the four coarse assembly slots of the
typed local-global source are definitionally identified with the finite
canonical-scale sum, the total Haar-defect lower bound, the arithmetic-upper and
main-log finite-sum identities, and the placewise Step~(xi)/Haar inequalities.
The source-level
\texttt{theorem311MultiradialFinitePlaceCThetaAudit} now joins this finite
calculation to the Theorem~3.11 multiradial side: the selected \(q\)-region is
an equality-quotient possible image, \((\Ind_1)\) and \((\Ind_2)\) preserve the
procession-normalized log-volume, \((\Ind_3)\) is absent from the equality
quotient and remains upper-semi, and the resulting selected region feeds the
finite-place \(C_\Theta\) chain.
The equality quotient is now also backed by a
\texttt{EqualityQuotientSetoidAudit}: Lean proves that equality of the setoid
quotient maps is equivalent to the generated \((\Ind_1)/(\Ind_2)\) relation,
while the \((\Ind_3)\) generator of this equality quotient remains empty.
The top-level paper-trace \texttt{RemainingPayloadAudit} now also requires the
Theorem~3.11 possible-image quotient compatibility itself.  Its checked
projections now expose the \((\Ind_1)\) and \((\Ind_2)\) possible-image region
equalities separately from the one-sided \((\Ind_3)\) upper-semi log-volume
inequality, and then derive the equality-quotient image invariant from the
first two.  Thus the ledger can no longer satisfy the Theorem~3.11 block while
hiding the distinction between equality-generating indeterminacies and the
non-equality \((\Ind_3)\) upper-semi relation inside a single compatibility
payload.
Its
\texttt{paperTraceRemainingPayloadAudit} field instantiates the abstract
\texttt{AdditiveHaarArithmeticDegreePadicObligations} record with these
concrete endpoints, so the paper-trace ledger now has a checked handoff from
the strongest constructed source object.  The same obligation record now
separates a finer local payload audit,
\texttt{FineLocalPayloadAudit}.  This new audit names three local witnesses
which were previously visible only by inspecting the surrounding certificate:
the Theorem~1.10 formula-gap local estimate audit, the Step~(xi)
arithmetic-degree calibration audit, and the \(p\)-adic prime-error formula
matching endpoint.  All current paper-trace instantiations of
\texttt{AdditiveHaarArithmeticDegreePadicObligations} now supply these slots
from the corresponding constructed source objects, and
\texttt{RemainingPayloadAudit} itself is the conjunction of the coarse
payload audit and this fine local audit.  The top-level
Theorem~3.11-to-Corollary~3.12 ledger therefore has checked projections to
the formula-gap local estimate, arithmetic-degree calibration, and
\(p\)-adic prime-error formula-matching witnesses.
The same ledger now also requires the quotient-backed \(\APT\)-datum endpoint
itself: the additive-Haar payload audit has a separate
\texttt{constructed\_apt\_datum\_quotient\_endpoint\_threaded} slot, projected
from the constructed \(\IPL/\SHE/\APT\) transport-law audit.
The same strict source now has direct
preferred-audit projections
\[
\begin{array}{l}
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDegreePadicCThetaAudit.}\\
\quad\texttt{oneSidedLocalGlobalEndpoint},\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDegreePadicCThetaAudit.}\\
\quad\texttt{indeterminacyLocalGlobalEndpoint},\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDegreePadicCThetaAudit.}\\
\quad\texttt{finitePlaceLocalGlobalCThetaDerivationAudit},\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDivisorBackedComponentCThetaAudit.}\\
\quad\texttt{finitePlaceIUTIVArithmeticGapHandoffAudit},\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDivisorBackedComponentCThetaAudit.}\\
\quad\texttt{equalityQuotientSetoidAudit},\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDivisorBackedComponentCThetaAudit.}\\
\quad\texttt{oneSidedSelectedQHullLogVolumeAudit},\\
\texttt{ConstructedQualitativeHodgeSHEIPLAdditiveHaarArithmeticDivisorBackedComponentCThetaAudit.}\\
\quad\texttt{coarseAssemblyConcreteAudit}.
\end{array}
\]
These expose, from the preferred certificate itself, both the one-sided
Theorem~3.11 quotient endpoint, the exact setoid quotient audit, the
selected-q hull/log-volume bridge induced by equality-quotient compatibility,
the coarse typed-indeterminacy local-to-global endpoint, and the concrete
finite-place meaning of the coarse assembly fields.  The finite-place
derivation projection packages the
derivation itself: the summed Step~(xi)/Haar inequality, the Haar-defect
contribution of the global \(+1\), the \(\IUT{}\,\mathrm{IV}\)
\(C_\Theta+1=A-M\) handoff identity, the named ordered-real cancellation audit
from
\[
  C_{\Theta,\mathrm{can}}+1\leq A-M=C_\Theta+1
\]
to \(C_{\Theta,\mathrm{can}}\leq C_\Theta\), the constructed global
\(C_\Theta\)-scale audit, and the final dichotomy.  The underlying strict
source also projects directly
to \texttt{ConstructedTheorem311IndeterminacyLocalGlobalCThetaSource}, and its
\texttt{closedLocalGlobalEndpoint}, \texttt{closedNoRawComparisonAudit}, and
\texttt{localGlobalHandoffAudit} theorems expose the named closed
\(C_\Theta\) route without passing through an older wrapper in the public audit
surface.  The final preferred arithmetic-divisor-backed certificate now carries
the same \texttt{closedNoRawComparisonAudit} field, so the absence of raw
\(\theta_{\mathrm{signed}}\leq C_\Theta(-q_{\mathrm{signed}})\) and raw
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) endpoint hypotheses can be checked
directly at the strongest current boundary.  Lean also packages this source
route as
\[
\begin{array}{l}
\texttt{ConstructedTheorem311OneSidedIUTIVTheorem110}\\
\texttt{AdditiveHaarMatchedLocalDegreeArithmeticDivisorBacked}\\
\texttt{ComponentStepXILocalTermCThetaSource.}\\
\quad\texttt{PreferredSourceCorridorDODAudit}.
\end{array}
\]
This audit records the arithmetic-divisor-backed endpoint, the typed
Theorem~3.11 multiradial finite-place \(C_\Theta\) audit, the local-to-global
\(C_\Theta\) derivation, the finite-place \(\IUT{}\,\mathrm{IV}\)
arithmetic-gap handoff, the concrete coarse-assembly audit, the arithmetic-gap
\(C_\Theta\) chain, the Remark~3.9.5/\(\IUT{}\,\mathrm{IV}\) handoff, the
closed no-raw-comparison audit, the derived
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison, the derived signed
\(C_\Theta\) bound, the source-bridge bound, and the final dichotomy.  The
strongest finite-divisor certificate now carries this field as
\texttt{preferredSourceCorridorDODAudit}.
The compact preferred theorem is
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_preferred}\\
\texttt{UnscaledDegreeBoundConstructedTheorem311Indeterminacy}\\
\texttt{LocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
and the degree-identified preferred projection is
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_preferred}\\
\texttt{DegreeIdentifiedUnscaledConstructedTheorem311Indeterminacy}\\
\texttt{LocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
The formula-level preferred projection is
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_preferred}\\
\texttt{LocalDegreeFormulaConstructedTheorem311Indeterminacy}\\
\texttt{LocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
The matched formula-level preferred projection is now the lowest public
local-to-global \(C_\Theta\) theorem in this branch:
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_preferred}\\
\texttt{MatchedLocalDegreeFormulaConstructedTheorem311}\\
\texttt{IndeterminacyLocalGlobalCThetaFiniteDivisorVerticalIQ}\\
\texttt{\_ofRealifiedFrobenioidPacketSource}.
\end{array}
\]
It consumes the constructed qualitative Hodge/\(\SHE\)/\(\IPL\) source and
the matched local Step~(v)/Step~(vii) formula-identification additive-Haar
source, and it still does not expose either the raw numerical \(\Theta\)-bound
or the raw \(C_{\Theta,\mathrm{can}}\leq C_\Theta\) comparison as hypotheses.
The same final audit and its strongest top-level paper trace now retain the
constructed \(\APT\) datum audit from the qualitative boundary: the permitted
transport arrow, the induced mechanism, the output family, allowedness, and
non-forbiddenness are still available at the arithmetic-divisor-backed
endpoint.
The matched qualitative audit stores the paper-shaped arithmetic gap
\(C_{\Theta,\mathrm{can}}+1\leq A-M\), the closed handoff audit, the
\texttt{ArithmeticGapCThetaChainAudit}, and the strict-source
\texttt{MatchedLocalDegreeFormulaAudit}, including its nested
\texttt{ArithmeticDegreeCalibrationAudit}.  Its audit-level
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) declaration is therefore a derived
theorem obtained by the exposed \(+1\) cancellation, not a field.  It also now
exposes the one-sided Theorem~3.11 quotient audit and the selected-q quotient
endpoint directly.  The quotient audit includes the typed-core action-law
certificate, so the preferred matched boundary explicitly exposes
\((\Ind_1)\)/\((\Ind_2)\) log-volume preservation, \((\Ind_3)\) upper-semi
one-sidedness, and exclusion of \((\Ind_3)\) from the equality quotient.  The
q-pilot region is identified with a selected
Theorem~3.11 possible image, that image is read through the
\((\Ind_1)/(\Ind_2)\) equality quotient, and the pullback of the
quotient-indexed possible-image family is the original theta-pilot family.
The same concrete quotient source now feeds the finite-place
local-to-global \(C_\Theta\) handoff by
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedFinitePlaceLocalGlobalCThetaSource}
\end{array}
\]
and, more sharply, through the localized Step~(xi) constructor
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedStepXILocalTermCThetaSource}.
\end{array}
\]
The normalized-Haar refinement
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedNormalizedHaarStepXILocalTermCThetaSource}
\end{array}
\]
and its p-adic unit-ball version
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedPadicUnitBallHaarStepXILocalTermCThetaSource}
\end{array}
\]
now sit above the IUT~IV arithmetic-defect version
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVArithmeticDefectStepXILocalTermCThetaSource}.
\end{array}
\]
That defect version is now itself the projection of the arithmetic-divisor
evaluation version
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVArithmeticDivisorEvaluationStepXILocalTerm}\\
\quad\texttt{CThetaSource}.
\end{array}
\]
These constructors build the Remark~3.9.5 hull/determinant source internally
from the selected quotient q-region.  The Step~(xi) refinement removes another
free local input: the canonical local summands are the weighted adjusted
log-volumes of the localized vector-bundle determinant source, and the local
upper contribution is the Step~(xi) term plus the Haar defect and main-log
term.  The normalized-Haar source derives the global Haar \(+1\) from a
finite-place lower-bound source: placewise nonnegativity plus a distinguished
normalized valuation-ball place.  The p-adic unit-ball source replaces that
abstract lower-bound source by the local unit-ball Haar normalization and
dilation character; the local defect is the index \(p_v^{[K_v:\mathbb Q_p]}\).
The new arithmetic-defect source then rewrites the local arithmetic upper sum in
terms of the IUT~IV defect \(\delta_v^{\mathrm{IUT}}\) itself, together with the
placewise equality
\[
  \delta_v^{\mathrm{IUT}}
  =
  \text{the }p_v^{[K_v:\mathbb Q_p]}\text{ unit-ball Haar index}.
\]
The arithmetic-divisor evaluation source goes one step lower: it supplies the
finite sums for the global arithmetic upper term and the global main-log term
from local divisor-evaluation data, leaving only the pointwise identity
\[
  A_v
  =
  S_v^{\mathrm{Step\,(xi)}}+\delta_v^{\mathrm{IUT}}+M_v
\]
as the local Step~(xi)/IUT~IV handoff.  Its endpoint exposes the quotient
q-region facts, the arithmetic-divisor evaluation endpoint, the IUT~IV defect
projection, the induced total defect lower bound, localized determinant
identities, the finite-place \(C_\Theta\) derivation, the signed bound, and the
final Corollary~3.12 dichotomy.
The concrete route now also reaches the Theorem~1.10 arithmetic-divisor source
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ArithmeticDivisorStepXILocalTerm}\\
\quad\texttt{CThetaSource}.
\end{array}
\]
This replaces the generic divisor-evaluation source by typed different,
q-parameter, and conductor divisors together with the Step~(v)--(vii) local
estimate gate.  The endpoint records the different and conductor degree sums,
the prime-error and main-log sums, the local procession-gap inequality, the
nondistinguished zero branch, and the conductor/q-support equality before
projecting to the existing \(C_\Theta\) and Corollary~3.12 endpoint.
The concrete route has now been lowered one step further to the local
case-formula layer
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110FormulaArithmeticDivisorStepXILocalTerm}\\
\quad\texttt{CThetaSource}.
\end{array}
\]
Here the local procession upper bound is not a free gate: it is the
case-defined bound coming from the distinguished nonarchimedean Step~(v),
the nondistinguished Step~(vi) zero branch, and the archimedean Step~(vii)
formula.  The endpoint exposes these three local inequalities, the induced
casewise procession-gap bound, and the same quotient q-region and finite-place
\(C_\Theta\) handoff.
The same concrete route now also reaches the Proposition~1.4/1.5-backed source
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110PropositionArithmeticDivisorStepXILocalTerm}\\
\quad\texttt{CThetaSource}.
\end{array}
\]
It now also has lower local-analytic, additive-Haar, valuation-ball
additive-Haar, and valuation-ball formula-gap matched versions
\[
\begin{array}{l}
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110LocalAnalyticArithmeticDivisorStep}\\
\quad\texttt{XILocalTermCThetaSource},\\
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110AdditiveHaarLocalAnalyticArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ValuationBallAdditiveHaarLocalAnalytic}\\
\quad\texttt{ArithmeticDivisor}\\
\quad\texttt{StepXILocalTermCThetaSource},\\
\texttt{concreteHodgeTheaterLogThetaQuotientThetaPilotSource\_to}\\
\quad\texttt{OneSidedIUTIVTheorem110ValuationBallHaarFormulaGapMatched}\\
\quad\texttt{ArithmeticDegreePadicFormulaMatched}\\
\quad\texttt{StepXILocalTermCThetaSource}.
\end{array}
\]
The endpoint exposes the local analytic construction witnesses themselves:
the distinguished and nondistinguished Proposition~1.4 log-shell construction
sources and the Proposition~1.5 archimedean metric construction source.  The
additive-Haar endpoint further exposes the compact-open Haar normalization
endpoints underlying the finite Proposition~1.4 branches.  The valuation-ball
endpoint keeps this finite-place provenance visible: the distinguished and
nondistinguished additive-Haar log-shell branches are required to arise from
valuation-ball Haar normalization audits before the source forgets to the
additive-Haar route.  The formula-gap matched endpoint goes one level lower:
it consumes named distinguished and archimedean formula-to-gap comparison
objects, the \(p\)-adic prime-error/defect/main split, and the Step~(xi)
arithmetic-degree calibration before projecting to the closed local-to-global
\(C_\Theta\) handoff.  After projection, these routes recover the proposition,
formula, finite local-to-global \(C_\Theta\), and Corollary~3.12 outputs.  Thus
the concrete Hodge/log-theta route no longer stops at a proposition-level
estimate package, nor at an abstract additive-Haar normalization.  The
remaining payload at this boundary is the construction of the valuation-ball
formula-gap comparison and Step~(xi) arithmetic-degree calibration objects from
paper-native local fields, log-shells, and divisor terms, not a raw global
\(C_{\Theta,\mathrm{can}}\leq C_\Theta\) hypothesis or a raw total Haar-defect
inequality.
The preferred certificate now also carries the IUT~IV local formula audit
\[
\begin{array}{l}
\texttt{IUTStage1IUTIVTheorem110AdditiveHaarFormulaGapMatched}\\
\texttt{ArithmeticDivisorEvaluationSource.FormulaGapLocalEstimateAudit}.
\end{array}
\]
This audit proves, place by place, that the distinguished Proposition~1.4
log-shell container bound and the archimedean Proposition~1.5 metric container
bound lie below the local arithmetic-upper-minus-main-log gap used by the
Theorem~1.10 summation.  The strongest arithmetic-divisor-backed certificate
exposes this as \texttt{formulaGapLocalEstimateAudit}.  It now also exposes
the nested coefficient-window synchronization audit from the matched
local-degree formula source, so the displayed coefficient lower bound and its
identification with the local arithmetic-degree coefficient are visible at the
same public certificate.  Thus the remaining payload has moved below these
container-to-gap and coefficient-window checks: it is concentrated in
constructing the local formula comparison sources themselves, including the
paper-native coefficient-window lower-bound source and the calibration
equalities that identify the local arithmetic-degree term with IUT~IV data.

The Theorem~3.11 qualitative checkpoint is now also present at the
finite-divisor \(C_\Theta\) boundary.  The new checkpoint-aware
side-conditioned Hodge/\(\SHE\)/\(\IPL\) declaration requires
\texttt{ConstructedQualitativeTheorem311ToCorollary312Checkpoints} and reports
the constructed public audit, typed no-\(\SHE\)-domain-to-codomain transport
guard, \(\APT\) non-forbidden transport guard, and Hodge-history separation
next to the finite-divisor dichotomy.  Its Lean name has suffix
\texttt{withConstructedQualitativeCheckpoints}.  This does not remove the
downstream local-to-global \(C_\Theta\) comparison; it closes the previous gap
between the constructed qualitative Theorem~3.11 route and the finite Step~(x)
vertical \(IQ\) surface.

At this same boundary, the certificate-pinned \(\IPL\) link has now been
replaced by the constructed input-prime-strip link source.  The construction
version of the side-conditioned record-hull endpoint consumes
\texttt{IUTStage1Theorem311IPLLinkConstructionSource}, exposes the choice-wise
links from the fixed input prime strip to each possible output prime strip, and
only then projects to the certificate-facing link source used by the older
route.  The same replacement is available at the checkpoint-aware boundary, so
the constructed qualitative audit can be read next to the constructed
input-prime-strip link audit.  The history-separated Hodge--Arakelov
record-hull boundary now has the same constructed-\(\IPL\) core theorem
\[
\begin{array}{l}
\texttt{boundarySignedEqualityOrStrictCTheta\_from\_sourceDerived}\\
\texttt{HodgeArakelovHistorySeparatedT11IPLConstructionRecordHull}\\
\texttt{FiniteDivisorVerticalIQ}.
\end{array}
\]
The experiment module exposes this as the review companion
\[
\begin{array}{l}
\texttt{historySeparatedIPLConstructionRecordHullFiniteDivisor}\\
\texttt{VerticalIQ\_cThetaDichotomy}.
\end{array}
\]
Both forms expose the choice-wise links, the constructed/certificate \(\IPL\)
equalities, and then project to the older certificate-facing route.  This closes
the \(\IPL\)-construction gap for the current side-conditioned and
history-separated record-hull finite-divisor surfaces; any remaining
certificate-pinned declarations are retained only as review aliases until they
are migrated or retired.

The generated full-label quotient route now has a typed package handoff to the
finite-divisor vertical-\(IQ\) layer.  The new handoff record
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQPackageHandoff}
\]
does not identify these packages by convention: it requires equality of the
signed q/theta pre-ledger data and requires both the finite-divisor
record-theta possible image and the finite-divisor target region for the chosen
packet to be exactly the generated selected q-region.  Given these source-side
realization fields, the theorem
\[
\texttt{generatedFullLabelFiniteDivisorVerticalIQPackageHandoff\_cThetaDichotomy}
\]
transports the generated full-label \(C_\Theta\) dichotomy to the
finite-divisor package, with the conclusion stated in finite-divisor
pre-ledger variables.  Thus the package-identification step has been made a
kernel-checked boundary; what remains is to construct its equality witnesses
from the paper-native local log-Kummer/Frobenioid data.

This boundary was first sharpened by removing a redundant finite target-region
witness: Lean proves
\[
\texttt{recordThetaPossibleImage\_eq\_targetRegion\_toSet}
\]
from the definition of a Theorem~3.11 source record.  The smaller source object
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQRecordImageRealization}
\]
therefore asks only for equality of the signed q/theta pre-ledger quantities and
for equality between the finite selected record image and the generated selected
record image.  Its projection
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQRecordImageRealization.toHandoff}
\]
constructs the full package handoff, and
\[
\texttt{generatedFullLabelFiniteDivisorVerticalIQRecordImageRealization\_cThetaDichotomy}
\]
derives the finite-divisor dichotomy from this smaller realization source.
The current boundary sharpens the image witness again.  The generated quotient
source now exposes
\[
\texttt{generatedFullLabelSelectedRecordThetaPossibleImage\_eq\_thetaClassRegion\_toSet},
\]
which identifies its selected record image with the theta-pilot-class region
obtained from the selected generated full-label choice.  Thus the finite packet
source can be stated as
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQThetaClassRecordImageRealization}.
\]
It requires the finite selected Theorem~3.11 record image to realize this
theta-class region directly, plus equality of the signed q/theta pre-ledger
quantities.  Its projection to the record-image realization and the endpoint
\[
\begin{gathered}
\texttt{generatedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{ThetaClassRecordImageRealization\_cThetaDichotomy}
\end{gathered}
\]
are now fed by
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQStepXILogVolumeRealization}.
\]
This new source records the Step~(xi-d)--(xi-f) comparison: the q-pilot
log-volume is read as a q-region log-volume on both the finite and generated
sides, while the theta-pilot bound is read as the corresponding theta-hull
log-volume.  Lean proves the old signed q/theta package equalities from these
four log-volume identifications and then invokes the theta-class realization
endpoint, which derives the generated-record match, the package handoff, and
the finite-divisor \(C_\Theta\) dichotomy.  The finite-packet boundary has now
been lowered once more.  The earlier source
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQThetaClassPacketProjection}
\]
is retained as a projection layer.  The constructed packet source
\[
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQConstructedThetaClassPacketSource}.
\]
constructs the finite theta-pilot class from the nonarchimedean packet
coordinates, the upper-semi log-theta column, the coric datum, and explicit
Hodge-theater/history labels.  Its componentwise theorem
\[
\texttt{constructedThetaClass\_eq\_generatedSelected}
\]
then identifies this constructed class with the selected generated full-label
theta class.  This boundary has now been lowered again: the preferred source is
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{RecordBackedConstructedThetaClassPacketSource}.
\end{gathered}
\]
It states realization at the finite Theorem~3.11 record-image level.  The
finite package target-region equality is derived from the record law
\[
\texttt{recordThetaPossibleImage\_eq\_targetRegion\_toSet},
\]
so the handoff no longer asks for that target-region equality directly.  The
projection
\[
\texttt{toConstructedThetaClassPacketSource}
\]
derives the constructed packet source, and
\[
\begin{gathered}
\texttt{generatedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{RecordBackedConstructedThetaClassPacketSource\_cThetaDichotomy}
\end{gathered}
\]
returns the constructed-class equality, the finite record-image realization, the
derived target-region realization, the selected-region identifications, and the
finite-divisor \(C_\Theta\) dichotomy.  The next source boundary is no longer
selected-only.  The finite image-law source
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassImageLawSource}
\end{gathered}
\]
states one finite Theorem~3.11 theta-class image law for all nonarchimedean
finite packets.  Lean specializes this law at the selected packet, constructs
the record-backed packet source, and the endpoint
\[
\begin{gathered}
\texttt{generatedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassImageLawSource\_cThetaDichotomy}
\end{gathered}
\]
derives the same selected-region and \(C_\Theta\) conclusions.  Thus the
remaining record-image payload has moved from a selected equality to a finite
packet image law.  This law is now itself derived from
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassRepresentativeImageLawSource}.
\end{gathered}
\]
The representative source supplies finite packets, proves finite record-image
invariance under equality of the reconstructed theta class, and identifies
representative record images with the class-indexed Theorem~3.11
possible-image regions.  This has now been lowered to the fiber/component
source
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassFiberComponentImageLawSource}.
\end{gathered}
\]
The fiber is determined by the fixed finite Hodge-theater/history labels.  On
that fiber Lean constructs representative finite packets from the procession
state, local direct-summand packet state, upper-semi state, and place-family
compatibility witness; the universal finite image law follows by applying this
fiber representative to the theta class reconstructed from an arbitrary finite
packet.  The component source is now itself obtained from
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassFiberAuditedPacketImageLawSource},
\end{gathered}
\]
which supplies one place-audited nonarchimedean direct-summand packet on each
fiber theta class.  Lean extracts the procession, local packet, upper-semi, and
place-family data from that audited packet, derives the log-theta column
compatibility from the reconstructed theta-class equality, and uses
same-theta-class record-image invariance to pass from the rebuilt component
packet back to the audited packet.  The invariance input has now been factored
once more by
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassFiberQuotientAuditedPacketImageLawSource}.
\end{gathered}
\]
This source aligns the finite possible-image family with the place-audited
Theorem~3.11 multiradial possible images and replaces the raw same-theta-class
record-image equality by the quotient statement that two finite packets with
the same reconstructed theta class are related in the place-audited
multiradial quotient.  Lean derives record-image equality from quotient
invariance.  This has now been sharpened to the source
\[
\begin{gathered}
\texttt{GeneratedFullLabelFiniteDivisorVerticalIQ}\\
\texttt{FiniteThetaClassFiberInd12AuditedPacketImageLawSource}.
\end{gathered}
\]
Here the same-theta-class relation is no longer an ambient quotient input: it
is a relation generated only by finite \((\Ind1)\) procession transports and
\((\Ind2)\) local direct-summand actions.  Lean embeds this
\((\Ind1,\Ind2)\)-relation into the existing place-audited quotient and
explicitly discharges the impossible \((\Ind3)\) equality-generator case.
This has now been sharpened once more at the component boundary.  The preferred
fiber route records same-theta finite packets through the midpoint,
procession, nonarchimedean-\(\mathrm{Ism}\) action, and local calibration data
from which Lean builds the raw tensor labels, the local label transport, the
matched local \((\Ind2)\) packet-action source, the generated
\((\Ind1,\Ind2)\) relation, quotient relation, record-image equality, selected
q-region equalities, and finally the Corollary~3.12 dichotomy.  Thus the
remaining payload is narrower: construct these component witnesses, the finite
Step~(x) upper-ray data, and the Step~(xi) q-region/theta-hull log-volume
identifications from the paper-native vertical log-Kummer/Frobenioid geometry.

The concrete Hodge-theater/log-theta route is now connected to this matched
finite Step~(x) handoff by an explicit bridge
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiniteDivisorVerticalIQMatchedStepXBridge}.
\end{gathered}
\]
The bridge records exactly the cross-package identifications needed at this
boundary: equality of the concrete and generated selected q-regions, equality
of the concrete and finite signed q-values, and equality of the concrete and
finite signed theta-values.  The endpoint
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiniteDivisorVerticalIQMatchedStepXBridge\_cThetaDichotomy}
\end{gathered}
\]
runs the generated/finite matched Step~(x) theorem and transports the resulting
finite \(C_\Theta\) dichotomy back to the concrete Hodge-theater/log-theta
package.  This bridge has now been lowered by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{StepXILogVolumeComparisonSource}.
\end{gathered}
\]
The new source no longer asks for concrete/finite signed equalities.  It
records equality of the concrete and generated selected q-regions and derives
the concrete/generated signed q/theta equalities from common Step~(xi)
q-region and theta-hull log-volume readings.  Lean then composes this with the
matched generated/finite Step~(x) gluing to construct the older bridge
internally, and the endpoint
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{StepXILogVolumeComparisonSource\_cThetaDichotomy}
\end{gathered}
\]
reaches the same concrete \(C_\Theta\) dichotomy.  This has now been lowered
one step further.  A concrete upper-ray source,
\[
\texttt{ConcreteHodgeTheaterLogThetaConstructedStepXUpperRaySource},
\]
is the concrete analogue of the generated full-label upper-ray source: both
read the q-pilot and theta-hull values from constructed Remark~3.9.5
hull/determinant data and a procession-normalized Step~(x) corridor.  The new
comparison source
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{ConstructedStepXIComparisonSource}
\end{gathered}
\]
then promotes equality of the concrete and generated Step~(xi) q-regions,
q-pilot readings, and theta-hull readings to the earlier log-volume comparison
source.  This has now been lowered again by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{UpperRayCalibrationSource}.
\end{gathered}
\]
The calibrated source no longer supplies equality of the Step~(x)-to-hull
upper-ray coordinates directly.  The q equality is obtained from equality of
the hull-approximant q-pilot log-volume readings, while the theta equality is
obtained from equality of the normalized weighted-determinant log-volumes.
Lean proves the promotion to the constructed Step~(xi) comparison source and
then runs the same concrete \(C_\Theta\) endpoint.  This boundary has now been
lowered once more by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiniteSummandUpperRayCalibrationSource}.
\end{gathered}
\]
There the q equality is derived from the selected q-region equality and the
Remark~3.9.5 hull-operator equality.  The theta equality is derived from a
finite equivalence between the concrete and generated determinant index sets,
matching adjusted localization summands, and the existing theorem that
normalization of the positive tensor power recovers the determinant sum.  Thus
the determinant side no longer compares normalized real fields directly.  This
boundary has now been lowered again by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{Ob3Ob4LocalizationUpperRayCalibrationSource}.
\end{gathered}
\]
Here the finite adjusted-summand matching is itself derived from
Remark~3.9.5 Ob3/Ob4 adjusted-localization sources: Lean rewrites the
constructed determinants to their weighted determinant projections and proves
the summand comparison from equality of the weighted adjusted localization
log-volumes after the determinant-index equivalence.  A further localized
vector-bundle boundary,
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LocalizedVectorBundleUpperRayCalibrationSource},
\end{gathered}
\]
now derives that weighted adjusted equality from the finite direct-summand
log-volume comparison, the structure-sheaf term, and the determinant
multiplicity.  The same boundary has now been lowered once more by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LocalizedHullCoverUpperRayCalibrationSource}.
\end{gathered}
\]
This source projects the localized vector-bundle determinant packages from
Remark~3.9.5 localized hull-cover data and derives the common hull operator
from a common holomorphic hull system.  The selected q-region comparison has
also been factored by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{SelectedThetaClassQRegionCalibration}.
\end{gathered}
\]
Instead of asserting equality of the two selected q-regions directly, Lean now
derives it from a common theta-pilot-class image family and equality of the
selected concrete/generated theta-pilot classes.  This boundary has now been
lowered by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{SelectedThetaClassQRegionSource}.
\end{gathered}
\]
The new source constructs the concrete quotient theta-pilot source from the
concrete class-region formula
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassRegionSource}, identifies
that class-region formula with the generated full-label theta-class image
family, and then projects to the older selected-q calibration.  Thus the
selected q-region equality is no longer a bare input.  The same boundary has
now been lowered again by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{RepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
This source chooses the concrete selected q-choice as the representative of
the generated selected theta-pilot class under the concrete representative
section.  Lean therefore derives the selected theta-pilot class match from the
representative-section theorem; the remaining cross-side input at this boundary
is the common class-region comparison.  That comparison has now been lowered
by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FormulaRepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
The formula-backed source starts from the concrete record-level
\texttt{ConcreteHodgeTheaterLogThetaThetaPilotClassFormulaRecordSource} and
identifies the generated full-label theta-class image family with the same
theta-pilot class formula.  The pointwise concrete/generated class-region
agreement is then derived internally before projecting to the
representative-selected q-region calibration.  This has now been lowered to
the lattice level by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LatticeFormulaRepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
The lattice-backed source uses the concrete lattice-formula record source; the
common class formula is obtained from Hodge-theater id, history label, the
finite-label-forgotten log-theta lattice coordinate, and the coric datum.  This
has been lowered once more by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LatticeImageLawRepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
Here Lean constructs the lattice formula from representative concrete choices;
the concrete source-paper input is the invariance of possible-image regions
under equality of the Hodge-theater/history/lattice/coric key.  The generated
side has also been tightened by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LatticeImageLawGeneratedQuotientRepresentative}\\
\texttt{SelectedThetaClassQRegionSource}.
\end{gathered}
\]
This source constructs the generated full-label quotient with its
theta-class image family already fixed to the concrete lattice-image-law
formula, so the previous cross-side image-family equality is definitional.
The generated record-image law has then been lowered by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LatticeImageLawPointwiseGeneratedPullback}\\
\texttt{RepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
It assumes only the pointwise generated pullback: each generated full-label
possible-image region is the common lattice-image-law region attached to its
theta-pilot class.  Lean derives the family-level generated quotient image
equality from this pointwise law.  The concrete side of this boundary has now
also been lowered to the source-level fiber transport layer by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportPointwiseGeneratedPullback}\\
\texttt{RepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
This source starts from the retained post-procession \((\mathrm{Ind}2)\)
action-packet transport object for theta-pilot fibers, forgets it through the
typed transport chain to the lattice-image-law family, and then applies the
pointwise generated-pullback calibration above.  Its audit keeps the
source-level packet transport endpoint, the lower procession/upper-semi
transport payload, the derived fiber-transport image law, and the generated
pullback law visible.  It now also retains
\texttt{FiberTransportQuotientComparisonAudit}, so the public q-region handoff
records the source-level packet audit, typed \((\Ind_1,\Ind_2)\)
equality-quotient preservation, possible-image region invariance, induced
lattice-image law, and no-\((\Ind_3)\)-equality guard in one named object.
The same source now also projects the selected
\(F_\ell\)-procession orbit through the generated quotient Remark~3.9.5 hull
endpoint: at the lattice-image-law, pointwise generated-pullback, and
fiber-\((\Ind2)\) packet-transport boundaries, Lean proves that every generated
full-label translate of the selected \(q\)-choice has the same possible
region, hull log-volume, and selected \(q\)-region.  The generated side has now
been lowered one step further by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportKernelImagePullback}\\
\texttt{RepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
This source identifies the generated record image family with the full-label
kernel image family before comparing that family with the concrete
fiber-lattice image law; the same selected-orbit Remark~3.9.5 endpoint is
available at this kernel-image boundary.  Thus the no-omission finite-label
statement survives the concrete/source handoff, not only the abstract generated
quotient.
This boundary has been sharpened again by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportCommonKernelImagePullback}\\
\texttt{RepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
Here the generated theta-class image family is definitionally the concrete
fiber-lattice image law.  Hence the theta-class match is no longer a separate
input at this boundary: Lean derives the previous kernel and pointwise generated
pullbacks from the common image family and reuses the existing q-region
calibration.  This has now been lowered once more by the target-region variant
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportTargetRegion}\\
\texttt{CommonKernelImagePullbackRepresentativeSelectedThetaClassQRegionSource}.
\end{gathered}
\]
Instead of assuming the generated Theorem~3.11 record-image family directly,
this source identifies the generated package target region of each full-label
choice with the full-label pullback of the common concrete fiber-lattice image
family.  Lean then reconstructs the record-image equality from the record's
target-region realization theorem.  The generated side has now been lowered in
two further steps.  First, the representative target-region source proves that
target regions are invariant under equality of the forgotten theta-pilot class
and calibrates only the generated representative of each theta class against
the common concrete fiber-lattice image law; Lean then derives the all-choice
target-region law.  Second, the quotient target-region source replaces this
same-theta-class invariance field by factorization of the generated package
target-region family through the generated \((\Ind_1,\Ind_2)\) equality
quotient.  Since equality of theta-pilot classes is a generated \((\Ind_2)\)
equality step, Lean derives same-theta-class target-region invariance from the
quotient possible-image interface.  The quotient factorization has now also
been constructed from the all-choice target-region pullback law itself: Lean
builds the generated target-region
\texttt{EqualityQuotientPossibleImages} object by proving \((\Ind_1)\) and
\((\Ind_2)\) target-region invariance from the concrete theta-class
fiber-lattice image law, while keeping \((\Ind_3)\) as the generated upper-semi
log-volume relation.  Thus the remaining q-region obligation is no longer an
arbitrary full-label equality, a primitive same-theta-class invariance
assumption, or an independently supplied quotient image object, but the
construction of the generated target-region pullback law and representative
calibration from local log-Kummer/Frobenioid geometry.  The target-region
pullback itself has now been rederived from the pointwise generated
record-region pullback: Lean combines the record image/fiber-lattice equality
with the source record's target-region realization theorem, and then reuses the
constructed target-region quotient.  Consequently the remaining generated-side
payload is pushed below package target regions.  This has been split again by
the generated-corridor-backed source: the public generated full-label quotient
corridor supplies the record-image equality, and Lean derives the common-kernel
record pullback from the single comparison between generated theta-class
regions and the concrete fiber-lattice image law.  The remaining mathematical
payload is therefore the construction of that theta-class region comparison
and its representative calibration from the local log-Kummer and Frobenioid
data.  The fiber-transport pointwise source now also promotes directly through
this generated-corridor boundary: its lattice-image-law quotient source supplies
the generated corridor, so the later common-kernel and target-region quotient
route no longer restates the generated-side record equality.  The theta-class
comparison itself has now been lowered to the same lattice-image-law quotient
source in the fiber-transport case: when the generated quotient is instantiated
with the fiber-transport lattice image law, the generated-corridor theta-class
image family is definitionally the concrete fiber-lattice image law.

This q-region source is now threaded into the valuation-ball localized
hull-cover boundary by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportValuationBallFactored}\\
\texttt{LocalizedHullCoverUpperRayCalibrationSource}.
\end{gathered}
\]
Thus the localized hull-cover upper-ray route can consume the packet-transport
q-region source and the valuation-ball/Haar component source together, before
projecting to the existing Remark 3.9.5 calibration.
The localized Ob3/Ob4 comparison has also been factored by
\[
\begin{gathered}
\texttt{IUTStage1Remark395LocalizedVectorBundle}\\
\texttt{ComponentTransportCalibration}.
\end{gathered}
\]
This common-component transport carries the shared tensor power, determinant
weights, \(O(-)\) log-volumes, and direct-summand log-volumes after the
determinant and local-place reindexings; Lean derives the bundle, adjusted
raw, and weighted adjusted log-volume equalities from these fields.  The
direct-summand part has now been lowered by
\[
\begin{gathered}
\texttt{IUTStage1Remark395ValuationBallLocalized}\\
\texttt{VectorBundleComponentTransportSource}.
\end{gathered}
\]
This source starts from concrete and generated valuation-ball factor-calibrated
Haar tensor-packet covers.  It identifies tensor powers, determinant weights,
structure-sheaf log-volumes, and a common normalized Haar log-volume family for
the matched valuation balls; the direct-summand equality is then derived from
the valuation-ball factor calibration rather than supplied as a bare real
equality.  The preferred boundary is now one step sharper:
\[
\begin{gathered}
\texttt{IUTStage1Remark395MatchedValuationBall}\\
\texttt{LocalizedVectorBundleComponentTransportSource}.
\end{gathered}
\]
Here the common normalized-Haar family is not supplied.  The source states
equality of each concrete normalized Haar log-volume with the generated
normalized Haar log-volume obtained by determinant and local-place reindexing;
Lean chooses the concrete value as the common value and constructs the older
valuation-ball component transport source internally.
This has been lowered again by
\[
\begin{gathered}
\texttt{IUTStage1Remark395LocalNormalizationMatched}\\
\texttt{ValuationBallLocalizedVectorBundleComponent}\\
\texttt{TransportSource}.
\end{gathered}
\]
This component source records common transported local invariants for each
matched valuation-ball factor: the finite-extension degree and the
compact-open Haar mass of the selected local ball.  Lean derives the raw
concrete/generated finite-degree and Haar-mass equalities from those common
local-normalization invariants.  Its projection is
\[
\begin{gathered}
\texttt{IUTStage1Remark395RawHaarDegreeMatched}\\
\texttt{ValuationBallLocalizedVectorBundleComponentTransportSource}.
\end{gathered}
\]
At the raw boundary the matched normalized-Haar equality is derived from equality
of the matched compact-open Haar masses and equality of the corresponding
finite-extension degrees.
This local-normalization boundary is now threaded into the packet-transport
localized hull-cover corridor by
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportLocalNormalization}\\
\texttt{MatchedValuationBallFactoredLocalized}\\
\texttt{HullCoverUpperRayCalibrationSource}.
\end{gathered}
\]
The raw Haar/degree packet boundary
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportRawHaarDegree}\\
\texttt{MatchedValuationBallFactoredLocalized}\\
\texttt{HullCoverUpperRayCalibrationSource}
\end{gathered}
\]
is now an intermediate projection from this sharper packet source.
The intermediate matched-normalized-Haar packet boundary
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportMatchedValuationBall}\\
\texttt{FactoredLocalizedHullCoverUpperRayCalibrationSource}.
\end{gathered}
\]
is in turn only a projection from the raw packet source.  The
local-normalization packet source combines the \((\Ind2)\)-backed q-region
packet transport with transported local finite-extension degree and
compact-open Haar mass data, derives the raw Haar/degree equalities and the
normalized-Haar equality internally, and then projects to the older
packet-transport valuation-ball boundary.  The
theorem
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportLocalNormalization}\\
\texttt{MatchedValuationBallFactoredLocalized}\\
\texttt{HullCoverUpperRayCalibrationSource\_}\\
\texttt{cThetaDichotomy}
\end{gathered}
\]
now runs this source directly to the existing finite-divisor \(C_\Theta\)
dichotomy while retaining an audit of the local-normalization, raw Haar
mass, finite-degree matching obligations, and the concrete
\texttt{FiberTransportQuotientComparisonAudit} inherited from the q-region
source.  Thus the sharpest packet-level \(C_\Theta\) endpoint still records
the source-level packet audit, \((\Ind_1,\Ind_2)\) quotient preservation,
the kernel-image generated possible-image law, and the local
finite-degree/Haar-mass normalization.  In particular, the lowered endpoint
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportKernelImagePullback}\\
\texttt{LocalNormalizationMatchedValuationBallFactored}\\
\texttt{LocalizedHullCoverUpperRayCalibrationSource\_}\\
\texttt{cThetaDichotomy}
\end{gathered}
\]
passes from the generated full-label kernel-image q-region source to the
local-normalization valuation-ball source before invoking the finite-divisor
\(C_\Theta\) corridor.  The q-region side has now been lowered once more by
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportGeneratedCorridor}\\
\texttt{KernelImagePullbackLocalNormalization}\\
\texttt{MatchedValuationBallFactoredLocalized}\\
\texttt{HullCoverUpperRayCalibrationSource\_}\\
\texttt{cThetaDichotomy}.
\end{gathered}
\]
This endpoint consumes the generated-corridor-backed q-region source directly,
derives the pointwise q-region route internally, and retains both the
generated-corridor audit and the target-region quotient audit at the
local-normalization valuation-ball \(C_\Theta\) boundary.  Two further lowered
endpoints now remove the generated-corridor source from the public boundary:
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{LatticeImageLawGeneratedQuotientLocalNormalization}\\
\texttt{MatchedValuationBallFactoredLocalized}\\
\texttt{HullCoverUpperRayCalibrationSource\_}\\
\texttt{cThetaDichotomy}.
\end{gathered}
\]
At this boundary Lean derives the generated-corridor q-region source from the
lattice-image-law generated quotient attached to the concrete fiber transport.
This has now been lowered further.  The current lowest packet-level
\(C_\Theta\) boundary is
\[
\begin{gathered}
\texttt{concreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FiberInd2ActionPacketTransportPointwiseGeneratedPullback}\\
\texttt{DirectLocalNormalization}\\
\texttt{ValuationBallFactoredLocalized}\\
\texttt{HullCoverUpperRayCalibrationSource\_}\\
\texttt{cThetaDichotomy}.
\end{gathered}
\]
The public q-region payload is now the pointwise Theorem~3.11 record-image
pullback to the concrete fiber-lattice theta-class image law.  The generated
target-region pullback is derived from this law using the record realization of
possible images as comparison target regions.  Lean then proves the
\((\Ind1,\Ind2)\)-quotient compatibility of the target-region family, constructs
the equality-quotient possible images, and derives the representative
target-region, common-kernel, kernel-image, generated-record, q-region, and
generated-corridor handoffs internally.  The endpoint still takes the
Remark~3.9.5 local-normalization valuation-ball/Haar hull-cover source directly.
That valuation-ball input is now audited at the same boundary by
\[
\texttt{directLocalNormalizationValuationCoverAudit}.
\]
The audit exposes the common finite-extension degrees and compact-open Haar
masses for the matched concrete/generated local factors, the derived raw
degree/Haar equalities, and the localized vector-bundle component transport
used by the upper-ray calibration.
The generated quotient evidence is now exposed at two adjacent boundaries.  At
the generated-corridor/local-normalization boundary it is recorded by
\[
\begin{gathered}
\texttt{generatedCorridorLocalNormalization}\\
\texttt{ValuationCoverQuotientHullAudit}.
\end{gathered}
\]
This uses the generated full-label quotient corridor itself, before the
finite-divisor \(C_\Theta\) handoff, to identify the selected q-region as a
selected \((\Ind1,\Ind2)\)-quotient possible image and to prove its containment
in the Remark~3.9.5 canonical hull.  At the pointwise/direct boundary the same
evidence is recovered after reconstructing the generated corridor, via
\[
\begin{gathered}
\texttt{generatedFullLabelValuationCoverQuotientHullAudit}.
\end{gathered}
\]
The direct boundary now also retains the concrete finite-label procession:
\[
\begin{gathered}
\texttt{generatedFullLabelConcreteProcession}\\
\texttt{ValuationCoverQuotientHullAudit}.
\end{gathered}
\]
For every \(F_\ell\)-label over the selected theta class, Lean proves the
generated choice has the selected Remark~3.9.5 possible region, the same hull
log-volume as the selected \(q\)-choice, and the same theta-class pullback
region.  Thus the no-omission full-label check remains visible after the
pointwise/direct local-normalization step.  At the valuation-cover level, this
audit has now been pushed through the generated-record and target-region
boundaries.  From the generated record-image pullback law, Lean reconstructs
the pointwise q-region source and the generated full-label quotient corridor;
from the target-region/common-kernel source, it derives the
\((\Ind1,\Ind2)\)-quotient family.  In both cases the source itself carries the
selected quotient/hull audit and the concrete \(F_\ell\)-procession audit.  The
quotient target-region boundary goes one step lower still: its q-side payload
is already a target-region family on the equality quotient, together with the
pullback to generated full-labels and the representative theta-class
calibration to the concrete fiber-lattice image law.  The remaining
source-facing obligation is therefore sharper: construct the target-region and
quotient target-region comparisons, together with the valuation-cover
local-normalization witnesses, from the same local log-Kummer/Frobenioid
geometry.
The older factored localized hull-cover source
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{FactoredLocalizedHullCoverUpperRayCalibrationSource}.
\end{gathered}
\]
is now an intermediate projection from the valuation-ball factored boundary
\[
\begin{gathered}
\texttt{ConcreteHodgeTheaterLogThetaGeneratedFullLabel}\\
\texttt{ValuationBallFactoredLocalizedHullCoverUpperRayCalibrationSource}.
\end{gathered}
\]
This earlier valuation-ball boundary remains an intermediate interface: it
retains the concrete/generated upper-ray objects, the theta-class q-region
calibration, the common hull system, and the hull/determinant identifications,
but obtains both localized hull-cover sources and their component transport from
matched valuation-ball Haar covers.

The practical priority order is now:
\begin{enumerate}
\item Construct the source-side witnesses for the generated-full-label to
  finite-divisor vertical-\(IQ\) handoff.  The handoff record, record-image,
  theta-class, finite-packet projection, and constructed finite-packet
  theta-class sources are now implemented.  The target-region realization is
  derived from the finite Theorem~3.11 record image, and the selected
  record-image witness is derived from an \((\Ind1,\Ind2)\)-backed fiberwise
  audited-packet representative finite theta-class image law.  The signed
  package transfer is no longer a bare equality field at the review boundary:
  it is derived from constructed Step~(xi) upper-ray q-region, q-pilot, and
  theta-hull comparisons; on the concrete/generated side, those q/theta
  comparisons have now been factored through q-region plus hull-operator
  calibration and finite adjusted determinant summand matching.  What remains
  is to construct the audited packet
  representatives, the same-theta-class
  midpoint packet, the ordered \((\Ind1)\) procession leg, the source-level
  nonarchimedean \(\mathrm{Ism}\) action leg, the raw tensor-label equations,
  the target summand-kind certificate, and the remaining q-region,
  hull-operator, and adjusted determinant-summand matching witnesses from
  paper-native finite divisors, local objects, and log-volume comparison data.
\item Construct the finite divisor-component columns--local object, prime
  multiplicities, prime degrees, and unit log-volume--and construct the
  labelled vertical object-transport records from the paper-native vertical
  log-Kummer correspondences.  The current Lean boundary constructs the
  Frobenioid degree object from these components, derives the finite degree-sum
  law definitionally, derives the labelled compatibility equality from the
  object transports, constructs the ordinary realified divisor column, then
  constructs the normalized theta and log-shell Example~3.5 copies, derives
  log-shell normalization and divisor realization, proves raw vertical
  translation, and upgrades object transport to full labelled local-object
  identity.
\item Construct the component functions below the theta-pilot representative
  section from the same log-Kummer/log-link geometry.  The current \Lean{}
  boundary builds the representative section from class-wise finite labels,
  procession states, local tensor states, and upper-semi non-volume data, then
  inserts the Frobenioid base-volume compatibility datum and derives the old
  calibration equalities, the one-sided \((\Ind3)\) base-volume inequality, the
  ordinary-copy comparison, finite local log-shell objects, base
  finite-log-volume equalities, column log-link transport family, and the
  transported \(ZMod(\ell)\), capsule, classified, and direct bridges.  The
  newest kernel separates this from the ambient choice-space assumption by
  generating the canonical theta-pilot choices themselves.  It has now been
  strengthened to generate the entire finite \(F_\ell\)-label procession over
  each theta-pilot class, with the \(Z/\ell Z\)-action closed internally,
  projected to the ambient \texttt{flProcessionTranslate}, and routed through
  Step~(xi), Remark~3.9.5, and the current global \(C_\Theta\) audit.  The
  remaining source-construction work is to derive the component functions from
  the paper-native local geometry.
\item Migrate or retire older certificate-pinned \(\IPL\) review aliases that
  are no longer preferred source surfaces.
\item Extend the recovered finite-divisor packet-local source from the
  preferred constructed-\(\IPL\) record-hull boundary to any remaining older
  vertical-\(IQ\) review aliases, and construct the deeper
  log-Kummer/Frobenioid packet calibrations of \IUT{} III, Step~(x), rather
  than accepting them as source-facing packet-boundary fields.
\item Construct the remaining Step~(xi) holomorphic-hull/determinant fields
  from Remark~3.9.5 and Step~(xi): genuine hulls, determinant lines,
  Ob5/Ob7 compatibility, and the \(\theta_{\mathrm{signed}}\) log-volume
  identification.  The preferred principal local boundary now defines the
  local log-shell as the selected compact-open factor and has a realized-exact
  boundary \(P_{\Theta,\beta}=\operatorname{real}_\beta(U_\beta)\) from which
  \Lean{} derives compact-open coordinates, image containments, realized
  valuation-ball equality, the exact \(\Xi(P_B)\) source, and the
  source-derived global \(C_\Theta\) audit.  This has now been pushed lower in
  two directions.  Valuation-ball realized exactness plus the valuation-ball
  additive Haar audit recovers the compact-open realized-exact source used by
  the preferred audit.  Equivalently, the two compact-open image containments
  construct the compact-open realized-exact source directly, recover the
  broader equality-backed log-shell source from four local
  image/valuation-ball containments, define the canonical local log-Kummer
  graph as the graph of the realization map, and now construct the map-level
  possible-region source by taking the Kummer map to be the valuation-factor
  realization and choosing its section from canonical graph left-totality.  In
  the reverse direction, that possible-region map source now constructs the
  theta-region graph source by the principal-cover equality
  \(P_{\mathrm{cover}}(\Theta)=P_\Theta\), and then reaches pointwise
  valuation-ball exactness and log-shell exactness.  The
  image containments are also derived from a cover-level exactness statement
  identifying the selected Remark~3.9.5 possible region with the realized
  compact-open local factor, and now from the lower log-shell exact source
  \(P_{\Theta,\beta}=\operatorname{real}_\beta(L_\beta)\),
  \(L_\beta=U_\beta\).  These exact equalities are themselves derived from the
  pointwise local realization source, which is now derived from compact-open
  local-chart data and from the compact-open log-Kummer graph source.  The
  theta-region-defined Step~(xi) valuation cover is now also constructed from
  the source-core Remark~3.9.5 valuation-ball/Haar cover using the
  fiber-transport-backed pointwise comparison, and from the lattice-image law
  once it is identified with the fiber-transport source, to derive the
  cover/theta-region family equality; in the fiber-derived case this
  identification is now checked definitionally.  What remains is to construct
  the fiber-transport comparison, the identification for any independently
  supplied lattice law, and the graph/local-chart laws from the paper-native
  holomorphic hull, log-Kummer, and local log-shell geometry.
\item Instantiate the valuation-ball local analytic construction from actual
  local fields, log-shell maps, compact-open Haar normalizations, and
  archimedean lattice metrics, proving the remaining Proposition~1.4
  log-shell estimates and Proposition~1.5 metric containments below those
  objects.
\item Complete the finite-extension residue/Haar layer below the current
  boundary: construct the residue field action on \(\mathcal O[K_v]\), prove
  that \(p_v\mathcal O[K_v]\) is a residue submodule, and derive the
  coset/Haar-character formula for genuine finite extensions rather than only
  for the base \(p\)-adic field and abstract finite-extension source records.
\item Derive the point-level target transport for the principal finite-divisor
  regions \(O\) and \(\lambda O\), including positive valuation-ball radius,
  coordinate-place equivalence, local scalar-image laws, direct-product
  localization covers, and the chart/direct-summand log-volume calibrations.
\item Instantiate the typed \IUT{} IV arithmetic-divisor source from actual
  number-field valuations, the different, \(q\)-parameter, and conductor
  divisors, and prove the distinguished and archimedean formula-to-gap bounds
  from the local analytic construction rather than carrying them as route
  payloads.
\item Extend the Hodge--Arakelov theta-evaluation wrapper beyond the current
  finite degree-evaluation, bad-local quotient, canonical-label, and
  canonical-one synchronization shadows toward the Gaussian/Frobenioid
  constructions of \IUT{} II and the Hodge-theater descent bridge.
\item Only then evaluate whether the Stage~1 interface has enough source
  content to bear on the Mochizuki--Scholze--Stix disagreement.
\end{enumerate}


\begingroup
\small
\begin{thebibliography}{9}
\bibitem{IUT1}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory I:
Construction of Hodge Theaters}.

\bibitem{IUT2}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory II:
Hodge-Arakelov-theoretic Evaluation}.

\bibitem{IUT3}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory III:
Canonical Splittings of the Log-theta-lattice}.

\bibitem{IUT4}
S. Mochizuki, \emph{Inter-universal Teichmuller Theory IV:
Log-volume Computations and Set-theoretic Foundations}.

\bibitem{MochizukiLean}
S. Mochizuki, \emph{On the Formalization of IUT: Preliminary Progress Report},
2026.

\bibitem{ScholzeStix}
P. Scholze and J. Stix, \emph{Why abc is still a conjecture}.
\end{thebibliography}
\endgroup

\end{document}
